### 2024-05-20 Sections/Cardano.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Following the work of \citet{Gmehling2019}, a cubic equation of state can be written a following form

	{\footnotesize
		\begin{equation}
			Z^3 + UZ^2+ SZ + T = 0
		\end{equation}
	}

	with Z as the compressibility factor. Using Cardano's formula, this type of equation can be solved analytically.

	{\footnotesize
		\begin{equation*}
			P = \cfrac{3S-U^2}{3} \qquad Q = \cfrac{2U^3}{27}-\cfrac{US}{3} + T
		\end{equation*}
	}

	the discriminant can be determined to be

	{\footnotesize
		\begin{equation}
			D = \left( \cfrac{P}{3} \right)^3 + \left( \cfrac{Q}{2} \right)^2
		\end{equation}
	}

	For $D>0$, the equation of state has one real solution:

	{\footnotesize
		\begin{equation}
			Z = \left[ \sqrt{D} - \cfrac{Q}{2} \right]^{1/3} - \cfrac{P}{ 3 \left[ \sqrt{D}-\cfrac{Q}{2} \right]^{1/3} } - \cfrac{U}{3}
		\end{equation}
	}

	For $D<0$, there are three real solutions:

	{\footnotesize
		\begin{equation*}
			\Theta = \sqrt{-\cfrac{P^3}{27}} \qquad \Phi = \arccos\left( \cfrac{-Q}{2\Theta} \right)
		\end{equation*}
	}

	they can be written as

	{\footnotesize
		\begin{align}
			Z_1 &= 2\Theta^{(1/3)} \cos \left( \cfrac{\Phi}{3} \right) - \cfrac{U}{3} \\
			Z_2 &= 2\Theta^{(1/3)} \cos \left( \cfrac{\Phi}{3} + \cfrac{2\pi}{3} \right) - \cfrac{U}{3} \\
			Z_3 &= 2\Theta^{(1/3)} \cos \left( \cfrac{\Phi}{3} + \cfrac{4\pi}{3} \right) - \cfrac{U}{3} 
		\end{align}
	}

	The largest and the smallest of the three values correspond to the vapor and to	the liquid solutions, respectively. The middle one has no physical meaning.

\end{document}

### 2024-05-20 Sections/Experiments.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Experiments}

	%In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to have knowledge of the dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}. To prepare the flowers for extraction, they were first pre-treated using a knife mill (TECNAL, model TE 340) to reduce their particle size. The Sauter equation determined the mean particle diameter and is equal to $0.3\times 10^{-3}$m. The actual density of the chamomile particles was measured through helium pycnometry at the Institute of Chemistry IQ/Unicamp's Analytical Facilities. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The total porosity of the bed, including the particles, was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$.

	%The moisture content of the flowers was then determined using an Infrared Moisture Analyser, which revealed an average moisture content of 4.83\% in the solid particles after grinding. Next, the density of the solid material was measured using a pycnometer, which can be found in Appendix \ref{CH: Solid_Density_Measurment}. Finally, the material's porosity was also calculated to be 0.5, as explained in Appendix \ref{CH: Porosity}.

	In order to solve the optimization problem presented by Equation \ref{EQ: Optimization_formulation_MLE}, it is necessary to test the process model against the experimental dataset ${\color{black}Y}(t)$, which was obtained by extracting oil from chamomile flowers. The experiments were performed by \citet{Povh2001} and \citet{Rahimi2011}. The experiments were conducted using a semi-batch extractor with a diameter of 3.96 cm and a length of 16.55 cm. Twelve experiments were performed under different operating conditions: $30-40^\circ C$, 100 - 200 bar, and 0.12 - 0.24 kg/h. The amount of solid material used for extraction was 75 grams. The bulk density of the bed was computed based on the feed's mass and the extractor's volume. The bed porosity was determined using the following calculation: $\epsilon=1-\frac{d_a}{d_r} = 1-\frac{370}{1364} = 0.73$. It is assumed that the total amount of the solute equals 3 grams, defined as the largest obtained yield after rounding up.

	%After loading the material into the extraction chamber, the extractor was pre-heated to the desired temperature. The outlet line was then closed, and the extraction chamber was filled with CO$_2$. The CO$_2$ was pumped and compressed until the desired operating pressure was reached. When the operating temperature and pressure were achieved, the outlet line was opened, allowing the solvent to flow through the system. The solvent extracted the essential oils from the solid material, and the resulting CO$_2$ and oil mixture flowed from the extractor to the separator. The separator operated at $50^\circ C$ and $50$ bar. The gaseous CO$_2$ exited from the top and was recycled to the CO$_2$ storage tank. The oil stayed at the bottom of the separator in the liquid form. The extraction time for each batch was 150 minutes, measured from the opening of the extractor outlet port. Every 5 minutes, the oil was drained from the separator, and its weight was measured. The resulting time series ${\color{black}Y}(t)$ corresponds to the output of measurement Equation \ref{Model_measurment_1} and can be used for parameter estimation.

\end{document}

### 2024-05-20 Sections/Gouverning_equation_derivation.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Gouverning equations}

	\subsubsection{Mass continuity}

	Following the work of \citet{Anderson1995}, the governing equations for compressible fluid with non-uniform cross-section can be obtained. Let's assume that any properties of the flow are uniform across any given cross-section of an extractor. The variation of the cross-section might result from the partial filling of an extractor or its irregular shape. In reality, such a flow is two-dimensional because the area changes as a function of $z$, and there is a flow-field variation in both directions. The assumption of quasi-one-dimensional flow dictates that the flow properties are a function of $z$ only. The integral form of the continuity equation is:

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \rho_f d\mathcal{V}_f + \iint_S \rho_f \textbf{V} \cdot \textbf{dS} = 0
			\label{EQ: Continuity_integral_general}
		\end{equation}
	}

	We apply this equation to the shaded control volume shown in Figure \ref{fig: control_volume}.

	\begin{figure}[h]
		\centering
		\begin{tikzpicture}
			\draw [fill=blue!20!white,opacity=0.5] (2.25,2.44) -- (2.25,0.57) -- (1.25,0.31) -- (1.25,2.69) -- cycle;%smmall triangle
			\draw[dashed,color=gray] (0,0) arc (-90:90:0.5 and 1.5);% right half of the left ellipse
			\draw[semithick] (0,0) -- (4,1);% bottom line
			\draw[semithick] (0,3) -- (4,2);% top line
			\draw[semithick] (0,0) arc (270:90:0.5 and 1.5);% left half of the left ellipse
			\draw[semithick] (4,1.5) ellipse (0.166 and 0.5);% right ellipse
			\draw (-1,1.5) node {$A_1$};
			\draw (3.3,1.5) node {$A_2$};
			\draw[|-,semithick] (0,-1.5) -- (4,-1.5);
			\draw[|->,semithick] (4,-1.5) -- (4.5,-1.5);
			\draw (0,-1) node {$z=0$};
			\draw (4,-1) node {$z=L$};
			\draw (1.75,-0.25) node{\scriptsize $ dz $}; %a number
			\draw[|<->|] (1.25,-0.5) -- (2.25,-0.5); %lenght indicator
			\draw[dashed] (1.25,-0.5) -- (1.25,0.3); %dashed line
			\draw[dashed] (2.25,-0.5) -- (2.25,0.58); %dashed line
		\end{tikzpicture}
		\caption{Control volume for deriving the partial differential equation for unsteady, quasi-one-dimensional flow}
		\label{fig: control_volume}
	\end{figure}

	 On the left side of the control volume, consistent with the quasi-one-dimensional assumptions, the density, velocity, pressure, and internal energy denoted by $\rho_f$, $v$, $P$, and $e$, respectively, are uniform over the area $A$. Similarly, on the right side of the control volume, the density, velocity, pressure, and internal energy $\rho_f+d\rho_f$, $v+dv$, $P+dP$, and $e+de$, respectively, are uniform over the area available for fluid phase $A_f+dA_f$. Applied to the control volume in Figure \ref{fig: control_volume}, the volume integral in Equation \ref{EQ: Continuity_integral_general} becomes, in the limit as $dz$ becomes very small,

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \rho_f d\mathcal{V}_f = \cfrac{\partial}{\partial t}\left( \rho_f A_f dz \right)
			\label{EQ: Cont_Simpl_Vol}
		\end{equation}
	}

	where $A~dz$ is the volume of the control volume in the limit of $dz$ becoming vanishingly small. The surface integral in Equation \ref{EQ: Continuity_integral_general} becomes

	{\footnotesize
		\begin{equation}
			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f v A_f + (\rho_f+d\rho_f)(v+dv)(A_f+dA_f)
		\end{equation}
	}

	The minus sign on the leading term on the right-hand side is due to the vectors $\textbf{V}$ and $\textbf{dS}$ pointing in opposite directions over the left of the control volume, and hence the dot product is negative. Expanding the triple product term

	{\footnotesize
		\begin{align}
			&\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = -\rho_f v A_f + \rho_f v A_f + \rho_f v dA_f + \rho_f A_f dv \nonumber \\ 
			&+ \rho_f dv dA_f + v A_f d\rho_f + v d\rho_f dA + A_f d\rho_f dv + d\rho_f dv dA_f
			\label{EQ: Triple_Prod_Cont_Surf}
		\end{align}
	}

	In the limit as $dz$ becomes very small, the terms involving products of the differential in Equation \ref{EQ: Triple_Prod_Cont_Surf}, such as $\rho_f dv dA_f,~d\rho_f dv dA_f$, go to zero much faster than those terms involving only one differential. Hence, all terms involving products of differentials can be dropped, yielding in the limit as $dz$ becomes very small

	{\footnotesize
		\begin{equation}
			\iint_S \rho_f \textbf{V} \cdot \textbf{dS} = \rho_f v dA_f + \rho_f A_f dv + v A_f d\rho_f 
			\label{EQ: Cont_Simpl_Surf}
		\end{equation}
	}

	Substituting Eqs. \ref{EQ: Cont_Simpl_Vol} and \ref{EQ: Cont_Simpl_Surf} into \ref{EQ: Continuity_integral_general}, we have

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} = 0
			\label{EQ: Conservative_continuity}
		\end{equation}
	}

	The above partial differential equation form of the continuity equation is suitable for unsteady, quasi-one-dimensional flow. The $A_f(z)$ is an arbitrary function that describes a change in the extractor's cross-section and can be defined as $A_f(z) = \textbf{A} \phi(z)$, where $\phi$ is the bed porosity and $\textbf{A}$ is the cross-section of an empty extractor.

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f \textbf{A} \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \textbf{A} \phi (z) v \right)}{\partial z} = 0
		\end{equation}
	}
	The equation can be simplified by canceling out $\textbf{A}$

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f \phi (z) v \right)}{\partial z} = 0
		\end{equation}
	}

	If so-called superficial velocity is defined as $u=\phi v$, the mass continuity becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f \phi (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f u \right)}{\partial z} = 0
			\label{EQ: Mass_Continuity}
		\end{equation}
	}

	\subsubsection{Transport of a species}

	The transport of a solute, can be described by an analogous equation to the Equation \ref{EQ: Continuity_integral_general} with additional terms on the right-hand side. The first term on the right-hand side describes diffusional movement of species and is based on the Fick's law $\left( J_{diff} = D_e^M\frac{\partial c_f}{\partial z} \right)$. The other term corresponds to the mass transfer between solid and fluid phases, which is treated as a source term.

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} c_f d\mathcal{V}_f + \iint_S c_f \textbf{V} \cdot \textbf{dS} = \iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} + \cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} c_s d\mathcal{V}_s
			\label{EQ: Integral_Mass_Species_general}
		\end{equation}
	}

	Similarly to the continuity equation, in the limit as $dz$ becomes very small

	{\footnotesize
		\begin{align}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} c_f d\mathcal{V}_f &= \cfrac{\partial}{\partial t}\left( c_f A_f dz \right) \\
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_s} c_s d\mathcal{V}_s &= \cfrac{\partial}{\partial t}\left( c_s A_s dz \right)
		\end{align}
	}

	The surface integrals in the limit of $dz$ become

	{\footnotesize
		\begin{equation}
			\iint_S c_f \textbf{V} \cdot \textbf{dS} = c_f v dA_f + c_f A_f dv + v A_f dc_f 
		\end{equation}
	}

	From the Divergence theorem in multi-variable calculus, we have

	{\footnotesize
		\begin{equation}
			\iint_S J_{diff} \cdot \textbf{n}~\textbf{dS} = \iiint_{\mathcal{V}_f} \nabla J_{diff} dv_f = \nabla \iiint_{\mathcal{V}_f} J_{diff} dv_f = \nabla \left( J_{diff} A_f dz \right)
		\end{equation}
	}

	By substituting the equations derived above into Equation \ref{EQ: Integral_Mass_Species_general} we obtain

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( c_f A_f \right)}{\partial t} + \cfrac{\partial \left( c_f A_f v \right)}{\partial z} = \cfrac{\partial \left( c_s A_s \right) }{\partial t} + \cfrac{\partial \left( J_{diff} A_f \right) }{\partial z}
		\end{equation}
	}

	By defining $A_f = A \cdot \phi$, $A_s = A \cdot \left( 1-\phi \right)$ and $u=V \cdot \phi$, and assuming that $A$ is constant, the above equation becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( c_f \phi \right)}{\partial t} + \cfrac{\partial \left( c_f u\right)}{\partial z} = \cfrac{\partial \left( c_s (1-\phi) \right) }{\partial t} + \cfrac{\partial \left( J_{diff} \phi \right) }{\partial z}
		\end{equation}
	}

	By assuming that ${\footnotesize \frac{\partial \phi}{\partial t}=0}$ and expanding $J_{diff}$, we get

	{\footnotesize
		\begin{equation}
			\cfrac{\partial c_f}{\partial t} + \cfrac{1}{\phi} \cfrac{\partial \left( c_f u\right)}{\partial z} = \cfrac{ (1-\phi)}{\phi} \cfrac{\partial c_s }{\partial t} + \cfrac{1}{\phi} \cfrac{\partial}{\partial z} \left( D_e^M \cfrac{\partial c_f}{\partial z} \right)
		\end{equation}
	}

	The equation can be further simplified if $\frac{\partial u}{\partial z} = \frac{\partial \phi}{\partial z} = D_e^M = 0$, which corresponds to the assumptions of constant velocity along the bed( which might be a case of isothermal and low-Mach number flow), constant porosity( which comes from the assumption of constant area for both solid and fluid phase) and no radial diffusion.

	{\footnotesize
		\begin{equation}
			\cfrac{\partial c_f}{\partial t} + \cfrac{u}{\phi} \cfrac{\partial c_f}{\partial z}  = \cfrac{1-\phi}{\phi} \cfrac{\partial c_s}{\partial t} 
			\label{EQ: Simplified_Species_Conservation}
		\end{equation}
	}

	The Equation \ref{EQ: Simplified_Species_Conservation} is equivalent to the equation presented by \citet{Reverchon1996}.

	\begin{comment}
	\subsubsection{Momentum conservation}

	Similarly to mass conservation, momentum conservation is derived for inviscid fluid with no body forces

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f v_z \right) d\mathcal{V}_f + \iint_S \left( \rho_f v_z \textbf{V} \right) \textbf{dS} = \iint_S \left( P dS \right)_z
			\label{EQ: Momentum_Integral_Form}
		\end{equation}
	}
	where $V_z$ is the $z$ component of the velocity.

	We the momentum conservation to the shaded control volume in Figure \ref{fig: control_volume}, the integrals on the left side are evaluated in the same manner as discussed above in the regard to the continuity equation. That is,

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \iiint_{\mathcal{V}_f} \left( \rho_f v_z \right) d \mathcal{V}_f = \cfrac{\partial}{\partial t} \left( \rho_f v A_f dz \right)
			\label{EQ: Force_Continuity_Monenmtum}
		\end{equation}equation
	}

	and

	{\footnotesize
		\begin{equation}
			\iint_S \left( \rho_f v_z \textbf{V} \right) dS = -\rho_f v^2 + \left( \rho_f + d \rho_f \right) \left( v+dv \right)^2 \left( A+dA \right)
		\end{equation}
	}

	\begin{figure}[h]
		\centering
		\includegraphics[width=\columnwidth]{Forces.pdf}
		\caption{The forces in the $z$ direction acting on the control volume}
		\label{fig: Forces_Momentum_Control_Volume}
	\end{figure}

	The evaluation of the pressure force term on the right side of Equation \ref{EQ: Momentum_Integral_Form} can be understood based on the Figure \ref{fig: Forces_Momentum_Control_Volume}. Here, the $z$ components of the vector $PdS$ are shown on all four sides of the control volume. Remember that $\textbf{dS}$ is assumed to point away from the control volume; hence  any $z$ component $\left( PdS \right)_z$ that acts toward the left (in the negative $z$ direction) is a negative quantity. Any $z$ component that acts toward the right (in the positive $z$ direction) is a positive quantity. Also note that the $z$ component of $P\textbf{dS}$ acting on the top and the bottom inclined faces of the control volume in Figure \ref{fig: Forces_Momentum_Control_Volume} can be expressed as the pressure $P$ acting on the component of the inclined is projected perpendicular to the $z$ direction, $dA_f/2$; hence, the contribution of each inclined face (top or bottom) to the pressure integral in Equation \ref{EQ: Momentum_Integral_Form} is $-P(dA_f/2)$. All together, the right-hand side of Equation \ref{EQ: Momentum_Integral_Form} is expressed as follows:

	{\footnotesize
		\begin{equation}
			\iint \left( PdS \right)_z = -PA_f + (P+dP)(A+dA_f)-2P\cfrac{dA_f}{2}
			\label{EQ: Force_Integral_Varying_Cross_Section}
		\end{equation}
	}

	Substituting Eqs. \ref{EQ: Force_Continuity_Monenmtum} to \ref{EQ: Force_Integral_Varying_Cross_Section} into Equation \ref{EQ: Momentum_Integral_Form}, we have

	{\footnotesize
		\begin{align}
			& \cfrac{\partial}{\partial t} \left( \rho_f v A_f dz \right) - \rho_f v^2 A_f + (\rho_f + d\rho_f)(v+dv)^2(A_f+dA_f)  \nonumber \\
			&= PA_f - (P+dP)(A+dA_f)+PdA_f
		\end{align}
	}

	Canceling like terms and ignoring products of differentials, the equation above becomes in the limit $dz$ becoming  very small

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \left( \rho_f v A_f dz \right) + d\left( \rho_f v^2 A_f \right) = -A dP
		\end{equation}
	}

	Dividing the above equation by $dz$ and taking the limit as $dz$ goes to zero, we obtain

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f v A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f v^2 A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
			\label{EQ: Conservative_Momentum}
		\end{equation}
	}

	The Equation \ref{EQ: Conservative_Momentum} can be expanded further by assuming that $A_f = \textbf{A}\phi$

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f v \textbf{A} \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f v^2 \textbf{A} \phi \right) }{\partial z} = - 	\textbf{A} \phi \cfrac{\partial P}{\partial t}
		\end{equation}
	}

	The equation can be further simplified by assuming that the cross-section of an extractor $\textbf{A}$ is constant and cancel out

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f v \phi \right) }{\partial t} + \cfrac{\partial \left( \rho_f v^2 \phi \right) }{\partial z} = - \phi 	\cfrac{\partial P}{\partial t}
		\end{equation}
	}

	If the superficial velocity $u=\phi V$ is introduced, then the momentum conservation becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f u \right)}{\partial z} + \cfrac{\partial \left( \rho_f u^2/\phi \right) }{\partial z} = -\phi \cfrac{\partial 	P}{\partial z}
		\end{equation}
	}

	Equation \ref{EQ: Conservative_Momentum} represents the conservative form of the momentum equation for the quasi-one-dimensional flow. The equivalent non-conservative form can be obtained by multiplying the continuity equation by $v$ and subtracting it from Equation \ref{EQ: Conservative_Momentum}

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f v A_f \right)}{\partial t} - V\cfrac{ \partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\left( \rho_f v^2 A_f 	\right)}{\partial z} - V \cfrac{\left( \rho_f v A_f \right)}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
		\end{equation}
	}

	Expanding the derivatives on the left-hand side of the above equation and canceling like terms, gives

	{\footnotesize
		\begin{equation}
			\rho_f A_f \cfrac{\partial v}{\partial t} + \rho_f A_f v \cfrac{\partial v}{\partial z} = -A_f \cfrac{\partial P}{\partial z}
		\end{equation}
	}

	Dividing the above equation by $A_f$ the non-conservative form of the momentum can be obtained

	{\footnotesize
		\begin{equation}
			\rho_f \cfrac{\partial v}{\partial t} + \rho_f v \cfrac{\partial v}{\partial z} = -\cfrac{\partial P}{\partial z}
			\label{EQ: Non-conservative_Momentum}
		\end{equation}
	}

	The Equation \ref{EQ: Non-conservative_Momentum} is stylistically the same as the general momentum conservation for one-dimensional flow with no-body forces. The momentum equation can be expressed in terms of superficial velocity $u=v\phi$.

	{\footnotesize
		\begin{equation}
			\rho_f \cfrac{\partial \left(u / \phi \right)}{\partial t} + \rho_f \cfrac{u}{\phi} \cfrac{\partial \left( u / \phi \right)}{\partial z} = - \cfrac{\partial P}{\partial z}
		\end{equation}
	}

	By expanding all the terms of the equation above, we get

	{\footnotesize
		\begin{equation}
			\cfrac{\rho_f}{\phi} \cfrac{\partial u}{\partial t} + \rho_f u \cfrac{\partial \phi^{-1}}{\partial t} + \rho_f \cfrac{u}{\phi} \cfrac{1}{\phi} \cfrac{\partial u}{\partial z} + \rho_f \cfrac{u}{\phi} u \cfrac{\partial \phi^{-1} }{\partial z} = - \cfrac{\partial P}{\partial z}
		\end{equation}
	}

	If the bed is not compressible and doesn't change its properties during the batch, then ${\footnotesize\cfrac{\partial \phi}{\partial t}=0}$

	{\footnotesize
		\begin{equation}
			\cfrac{\rho_f}{\phi} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\phi} \cfrac{\partial u}{\partial z} + u^2 \cfrac{\partial \phi^{-1}}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
		\end{equation}
	}

	If the porosity is constant along an extractor, then the momentum conservation equation becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\rho_f}{\phi} \left( \cfrac{\partial u}{\partial t} + \cfrac{u}{\phi} \cfrac{\partial u}{\partial z} \right) = -\cfrac{\partial P}{\partial z}
			\label{EQ: Non-conservative_Momentum_Const_Porosity}
		\end{equation}
	}

	The Equation \ref{EQ: Non-conservative_Momentum_Const_Porosity} represents the non-conservative form of the momentum equation for quasi-one-dimensional flow with no body forces and constant porosity.

	\subsubsection{Energy conservation}

	Let's consider the integral form of the energy equation for adiabatic flow with no body forces and no viscous effects

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial} \iiint_{\mathcal{V}_f} \rho_f \left( e_f + \cfrac{v^2}{2} \right) d\mathcal{V}_f + \iint_S \rho_f \left( e_f + \cfrac{v^2}{2} \right) \textbf{V} \cdot \textbf{dS} = - \iint_S \left( P\textbf{V} \right) \cdot \textbf{dS}
			\label{EQ: Energy_equation_integral}
		\end{equation}
	}

	Applied to the shaded control volume in Figure \ref{fig: control_volume}, and keeping in mind the pressure forces shown in Figure \ref{fig: Forces_Momentum_Control_Volume}, Equation \ref{EQ: Energy_equation_integral} becomes

	{\footnotesize
		\begin{align}
			&\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{v^2}{2} \right) A_f dz \right] - \rho_f \left( e_f + \cfrac{v^2}{2} \right) v A_f \nonumber \\
			&+ \left( \rho_f + d\rho_f \right) \left[ e_f + de_f + \cfrac{\left( v + dv \right)^2}{2} \right] \left( V+dV \right) \left( A_f+dA_f \right) \nonumber \\
			&= - \left[ -PvA_f + \left(P+dP\right) \left(v+dv\right) \left(A_f+dA_f\right) - 2\left( Pv\cfrac{dA_f}{2} \right) \right]
		\end{align}
	} %\todo[]{Check fV}

	Neglecting products of differential and canceling like terms, the above equation becomes

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{v^2}{2} \right) A_f dz \right] + d\left( \rho_f r_f A_f \right) + \cfrac{ \left( \rho_f v^3 A_f \right) }{2} = -d \left( P A_f v \right)
		\end{equation}
	}

	or

	{\footnotesize
		\begin{equation}
			\cfrac{\partial}{\partial t} \left[ \rho_f \left( e_f + \cfrac{v^2}{2} \right) A_f dz \right] + d \left[ \rho_f \left( e_f \cfrac{v^2}{2} \right) vA_f \right] = - d\left( P A_f v \right)
		\end{equation}
	}

	Taking the limit as $dz$ approaches zero, the equation above becomes the following partial differential equation

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left[ \rho_f \left( e_f + v^2 / 2 \right) A \right]}{\partial t} + \cfrac{\partial \rho_f \left( e_f + v^2 / 2 \right)vA_f}{\partial z} = -\cfrac{\partial \left( P A_f v \right)}{\partial z}
			\label{EQ: Energy_equation_conservative_total}
		\end{equation}
	}

	Equation \ref{EQ: Energy_equation_conservative_total} is the conservation form of the energy expressed in terms of the total energy $e~+~v^2/2$, appropriate for unsteady, quasi-one-dimensional flow. The energy equation can be expressed in terms of internal energy if Equation \ref{EQ: Conservative_Momentum} is multiplicated by $v$ and then subtracted from Equation \ref{EQ: Energy_equation_conservative_total}

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f v A_f \right)}{\partial z} = -P \cfrac{\partial A_f v}{\partial z}
			\label{EQ: Energy_conservative_internal}
		\end{equation}
	}

	The equation above is the conservation form of the energy equation expressed in terms of internal energy $e_f$ suitable for quasi-one-dimensional flow. The non-conservative for is then obtained by multiplying the continuity equation \ref{EQ: Conservative_continuity}, by $e_f$ and substructing it from \ref{EQ: Energy_conservative_internal}, yielding

	{\footnotesize
		\begin{equation}
			\rho_f A_f \cfrac{\partial e_f}{\partial t} + \rho_f A_f v \cfrac{\partial e_f}{\partial z} = - P \cfrac{\partial (A_f v) }{\partial z}
		\end{equation}
	}

	Expanding the right-hand side and dividing by $A_f$, the above equation becomes

	{\footnotesize
		\begin{equation}
			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f v \cfrac{\partial e_f}{\partial z} = -P \cfrac{v}{A_f} \cfrac{\partial A_f}{\partial z}
		\end{equation}
	}

	or

	{\footnotesize
		\begin{equation}
			\rho_f \cfrac{\partial e_f}{\partial t} + \rho_f v \cfrac{\partial e_f}{\partial z} = -P \cfrac{\partial v}{\partial z} - P V \cfrac{\partial (ln~A_f)}{\partial z}
			\label{EQ: Energy_equation_nonconservative}
		\end{equation}
	}

	Equation \ref{EQ: Energy_equation_nonconservative} is the non-conservative form of the energy equation expressed in terms of internal energy, appropriate to unsteady quasi-one-dimensional flow. The reason for obtaining the energy equation in the form of Equation \ref{EQ: Energy_equation_nonconservative} is that, for a calorically perfect gas, it leads directly to a form of the energy equation in terms of temperature $T$. 
%	
%	For calorically perfect gas ${\footnotesize e_f=C_vT}$
%	
%	\hrule
%	
%	{\footnotesize
%		\begin{equation}
%			\cfrac{\partial \left( \rho_f e_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f  e_f v A_f \right)}{\partial z} = -P \cfrac{\partial A_f v}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
%		\end{equation}
%	}

%	{TODO: \color{red}finish derivation of energy equation for real gas and introduce a homogenous version of the energy equation}

\end{comment}

\end{document}

### 2024-05-20 Sections/IC_BC.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{black}c_s^0}$. It is considered that the initial temperature of the extractor in every place is the same and described by ${\color{black}h^0}$.

	During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles although the operating conditions are not obtained yet. Later, the solute in the fluid phase is partially moved (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed) to the region where there is no solid phase. As a result, the distribution of solutes mass in the fluid phase is assumed to not be uniform, and described by an arbitrary function $H=H(z)$. Some conclusions can be drawn from the analysis of the initial part of each yield curve. It can be noticed that each curve at the beginning has a curvature, which is not linear. In a general sense, it can be said that a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. The graphical representation of the solute concentration in the fluid phase is shown in Figure \ref{fig: C_f_linear}.

	\begin{figure}[!h]
		\centering
		\begin{tikzpicture}[scale=2]
			\draw[->] (-2,0) -- (2,0) node[right] {z}; 
			\draw[->] (0,-1.5) -- (0,2) node[above] {$H(z)$};
%			\draw[->] (-2,1) -- (2,1);
%			\draw[->] (1,-1.5) -- (1,2);
			\draw[blue] (-1,2)  -- (2,-1);

			\node at (0,0) {\textbullet};
			\node[] at (0.2,0.1) {$z=0$};

			\node at (1,0) {\textbullet};
			\node[] at (1.2,0.1) {$z=L$};

			\node at (0,1) {\textbullet};
			%\node[] at (0.3,1) {$H=m$};

			\node[black] at (1.3,0.5) {$H(z)=-m(z-b) + a$};
		\end{tikzpicture}
	\caption{The linear distribution of the solute concentration in the fluid phase}
	\label{fig: C_f_linear}
	\end{figure}

	As presented in Figure \ref{fig: C_f_linear}, the function $H$ is defined as

	{\footnotesize
	\begin{equation}
		H(z) = -m \left( z-b \right) + a
	\end{equation}
	}

	The function $H$ can be integrated over the integral from $a$ to $b$ to describe the total amount of solute in the fluid phase ($S$) in that interval.

	{\footnotesize
		\begin{equation}
			\int_{a}^{b} H(z) dz = S 
		\end{equation}
	}

	If parameter $a$ describe the beginning of the fixed bed, then $a=0$. Similarly, $b$ can be defined as the end of the fixed bed, then $b=L$. On range from $a=0$ to $b=L$ the result of this integral is know, and it is equal to

	{\footnotesize
		\begin{equation}
			S = m_{fluid}^0 = \int_{a=0}^{b=L} -m \left(x-L\right) dz
			\label{EQ: C_f_linear_int}
		\end{equation}
	}

	where $m_{fluid}^0$ is the total mass of solute in the fluid phase and $N$ is the number of intervals between $a$ and $b$.
	The right-hand side of the above equation can be evaluated

	{\footnotesize
		\begin{align}
			\int_{a=0}^{b=L} -m \left(x-L\right) dz &= -m \left( \int_{a=0}^{b=L} z dz - \int_{a=0}^{b=L} L dz \right) \nonumber \\
													&= -m \left(\frac{z^2}{2} \biggr\rvert_0^L - Lz \biggr\rvert_0^L   \right) \nonumber \\
													&= -m \left( \frac{L^2}{2} - L^2 \right) \nonumber \\
													&=  m \frac{L^2}{2}
													\label{EQ: C_f_linear_after_int}
		\end{align}
	}

	The parameter $m$ can be obtained by equating the left-hand side of Equation \ref{EQ: C_f_linear_int} and the right-hand side of Equation \ref{EQ: C_f_linear_after_int}

	{\footnotesize
		\begin{equation}
			m_{fluid}^0 = m \frac{L^2}{2} \rightarrow m = \frac{2m_{fluid}^0}{L^2}
		\end{equation}
	}

	As can be seen from the above equation, the linearly distributed concentration of solute in the fluid phase can be fully determined if parameters $a$, $b$ and $m_{fluid}^0$ are know. $m_{fluid}^0$ can be obtained from the total mass of the solute in the system at the initial time $m_{total}^0$ and the initial mass ratio $\tau$.

	{\footnotesize
		\begin{equation*}
			\tau = \cfrac{\text{total mass of solute in the fluid phase}}{\text{total mass of solute in the system}} = \cfrac{m^0_{fluid}}{m^0_{total}}
		\end{equation*}
	}

	The initial conditions can be summarized as

	{\footnotesize
		\begin{subequations}
			\begin{align*}
				{\color{black}c_f}(t = 0, z) &= H(z)   \\
				{\color{black}c_s}(t = 0, z) &= {\color{black}c_{s0}} \\
				{\color{black}h}(t = 0, z) &= {\color{black}h_0}
			\end{align*}
	\end{subequations} }

\end{document}

### 2024-05-20 Sections/Likelihood.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Maximum likelihood estimation (MLE) is a statistical method used to estimate the parameters of a probability distribution based on observed data. The MLE works by finding the values of the parameters that maximize the likelihood function, which is the probability of observing the given data for a given set of parameter values. The MLE has desirable properties such as asymptotic efficiency and normality. Although the MLE has often been associated with the normal distribution for mathematical convenience, it can be applied to a wide range of probability distributions.

	To find the maximum likelihood estimates, we maximize the joint probability density function, or likelihood function, denoted as $p(\theta | y(t_1),y(t_2),...,y(t_n))$, where $\theta$ represents the parameters and $y(t_1),y(t_2),...,y(t_n)$ represent the observed data. The conditions at the maximum can be refined by incorporating prior information. The posterior probability density function $p(\theta|y)$ can be expressed as the ratio of two probability densities %(\ref{EQ: Probabiltiy_independet_b})
	 using the continuous variable analogue of Bayes' theorem %(details in Appendix \ref{CH: Bayes})
	 . In such a case the posteriori distribution is given by Equation \ref{EQ: Posterior_distribution}.

	{\footnotesize
		\begin{align} \label{EQ: Posterior_distribution}
			p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta, y(t_n),...,y(t_1) \right)}{p\left( y(t_n),...,y(t_1) \right)}
	\end{align} }

	The numerator of the right-hand side od Equation \ref{EQ: Posterior_distribution} becomes %using Equation \ref{EQ: Probabiltiy_dependet_a} becomes

	{\footnotesize
		\begin{equation}
			\begin{split}
				p\left( \theta,y(t_n),...,y(t_1) \right) &= p\left( y(t_n)|\theta,y(t_{n-1}),...,y(t_1) \right) \\ &\cdot p\left( \theta,y(t_{n-1}),...,y(t_1) \right)
			\end{split}
	\end{equation} }

	These operations can be continued repetitively until we get

	{\footnotesize
		\begin{equation}
			p\left( \theta, y(t_n),...,y(t_1) \right) = p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right)
	\end{equation} }

	Examination of Equation \ref{EQ: Measurment_noise} shows that $ d Y(t_i) / dt$ depends only on $t_i$, $\theta$ and $\epsilon(t_i)$ and is not conditioned by any previous measurement. Consequently, we can write

	{\footnotesize
		\begin{equation}
			p\left( y(t_i)|\theta, y(t_{i-1}),...,y(t_1) \right) = p\left( y(t_i)|\theta \right)
	\end{equation} }

	provided Equation \ref{EQ: Measurment_noise} is observed as a constraint. The desired joint conditional probability function is thus

	{\footnotesize
		\begin{equation}
			p\left( \theta| y(t_n),...,y(t_1) \right) = \cfrac{p\left( \theta \right) \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) }{p\left( y(t_n),...,y(t_1) \right)}
	\end{equation} }

	We can get rid of the evidence term $p\left( y(t_n),...,y(t_1) \right)$ because it's constant with respect to the maximization. Moreover, if we are lacking a prior distribution over the quantity we want to estimate, then $p(\theta)$ can be omitted. In such a case:

	{\footnotesize
		\begin{equation}
			p\left( \theta| y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} p\left( y(t_i)|\theta \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) 
	\end{equation} }

	The likelihood function $L\left( \theta | y \right)$ for the parameters based on several observations is the product of the individual functions if the observations are independent.

	{\footnotesize 
		\begin{multline}
			L\left( \theta|y(t_n),...,y(t_1) \right) = \prod_{i=1}^{n} L\left( \theta|y(t_i) \right) \\
			= p\left( y(t_1)| \theta \right)p\left( y(t_2)| \theta \right) ... p\left( y(t_n)| \theta \right)
	\end{multline} }

	In choosing as estimates of $\theta$ the values that maximize $L$ for the given values $\left( y(t_i) \right)$, it turns out that it is more convenient to work with the $\ln L$ than with $L$ itself:

	{\footnotesize 
		\begin{equation}
			\ln L = \ln p \left( y(t_1)| \theta \right) + \ln p\left( y(t_2)| \theta \right) + ... + \ln p \left( y(t_n)| \theta \right) = \sum_{i=1}^{n} \ln p\left( y(t_i); \theta \right)
	\end{equation} }

	By assuming that the conditional distribution of $\bar{Y}_i$, given $y_i$, is normal, then we form the likelihood function based on the probability density:

	{\footnotesize
		\begin{align} \label{EQ: MLE_Norm}
			p\left(  \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right] \nonumber \\
			L\left( \theta, \sigma | y(t_n),...,y(t_1) \right) &= \prod_{i=1}^{n} \cfrac{1}{\sqrt{2 \pi} \sigma } \exp \left[ \cfrac{1}{2  \sigma } \left( Y(t_i) - y(\theta , t_i) \right)^2 \right]
	\end{align}}
	where $\sigma$ is the variance

			%In Equation \ref{EQ: MLE_Norm} the parameters are the variables, and the values of $Y$ and $x$ are given. Then
	By taking the natural logarithm of the Equation \ref{EQ: MLE_Norm}, the final form of the objective function can be obtained:

	{\footnotesize
		\begin{equation}
			\ln L = -\cfrac{n}{2} \left( \ln \left(2 \pi \right) + \ln \sigma^2 \right)
			- \cfrac{ \sum_{i=1}^{n} \left[  Y(t_i) - y(\theta , t_i) \right]^2 }{2 \sigma^2}
			\end{equation}
	}

	\iffalse

	The parameter estimation problem can be formulated as follow:

	{\footnotesize
		\begin{equation}
			\begin{aligned} \label{EQ: Optimization_formulation_MLE}
				&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
				&\text{subject to}
				& \dot{x} = f(t,x,\theta) \\
				&& \dot{\theta} = 0 \\
				&& y = y(x) \\
				&& \theta^{lb} \leq \theta \leq \theta^{ub}
			\end{aligned}
	\end{equation} }

	where $\hat{\theta}$ is as maximum likelihood estimator, $\theta^{lb}$ define the minimal value of $\theta$ and $\theta^{ub}$ is the maximum value of $\theta$.

	Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ by equating to zero the partial derivatives of $\ln L$ with respect to each of the parameters:

	{\footnotesize
		\begin{align}\label{EQ: MLE_Basic_Solution}
			\cfrac{\partial \ln L}{\partial \theta} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | \theta \right) }{\partial \theta} = 0 
		\end{align} }

	Solution of Equations \ref{EQ: MLE_Basic_Solution} yield the desired estimates $\hat{\theta}$. For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general no closed-form solution to the maximization problem is known or available, and an maximum likelihood estimator can only be found via numerical optimization.

			It can be shown that as $n$ approaches infinity the maximum likelihood estimates have the desirable asymptotic properties:

			\begin{enumerate}[label=(\arabic*)]
				\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \mathbb{E}\{\hat{\theta}\} = \theta$ }
				\item {\footnotesize $\left[ \sqrt{n}\left( \hat{\theta} - \theta \right) \right]$ } is normally distributed
			\end{enumerate}
			and for the case of two parameters:

			\begin{enumerate}[resume,label=(\arabic*)]
				\item {\footnotesize $\lim\limits_{n \rightarrow \infty} \text{Var}\{\hat{\theta}\} = \cfrac{1}{n} \left[ \mathbb{E} \left\{ \left( \cfrac{\partial \ln p}{\partial \theta} \right)^2 \right\} \right]^{-1} \cfrac{1}{1-\rho^2_{\hat{\theta}}} $ } \label{Assumption_MLE}
			\end{enumerate}

			where $\rho^2_{\hat{\theta}}$ is the matrix of correlation coefficients.

			Maximum likelihood estimates are not necessarily unbiased. Maximum likelihood estimates, however are efficient and, hence, consistent estimates. Furthermore, where a sufficient estimate can be obtained, the maximum likelihood method will obtain it. Finally, if $\hat{\theta}$ is a maximum likelihood estimator of $\theta$, the $f\left( \hat{\theta} \right)$ is a maximum likelihood estimator of $f\left( \theta \right)$, a function of $\theta$.

			\hrule

			%Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$. Intuitively, this selects the parameter values that make the observed data most probable. The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate.

			As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate. MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data. MAP estimation can therefore be seen as a regularization of maximum likelihood estimation. The relationship between MAP and MLE can be obtained from the Bayes' rule:

			{\footnotesize
				\begin{equation} 
					\begin{split} \label{EQ: MAP_probability}
						{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
						&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
						&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
						&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
						&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
					\end{split}
			\end{equation} }

			We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$. The function to be maximized can be written as

			{\footnotesize
				\begin{equation} \label{EQ: MAP_L2}
					\begin{aligned}
						&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
						+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
						= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
						- \sum_{j=0}^{p} {\frac{\left( \theta - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
						= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
						+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \theta - \theta^0 \right)^2 \right] \\
						= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
					\end{aligned}
			\end{equation} }

			In Equation \ref{EQ: MAP_L2} some of the constants (with respect to $\theta$) were dropped and factored to simplify the expression. We can adjust the amount of regularization we want by changing $\lambda_{L2}$. Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$). If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).

			Let's assume that the prior distribution of parameter $\theta$ is given by the Laplace distribution. The likelihood function can defined as follow:

			{\footnotesize
				\begin{equation} \label{EQ: MAP_L1}
					\begin{aligned}
						&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 }{2\sigma^2}}
						+ \ln \prod_{j=0}^{p} \frac{1}{2b}e^{-\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]  \\
						= &\arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \theta, t_i \right) \right)^2}{2\sigma^2}}
						- \sum_{j=0}^{p} {\frac{ | \theta - \theta^0 | }{\sigma_\theta}} \right]\\
						= &\arg\min_{\sigma, \theta \in \Theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2
						+ \frac{\sigma^2}{\sigma_\theta} \sum_{j=0}^{p} | \theta - \theta^0 | \right] \\
						= &\arg\min_{\sigma, \theta \in \Theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \theta, t_i \right) \right)^2 + \lambda_{L1} \sum_{j=0}^{p} | \theta - \theta^0 | \right]
					\end{aligned}
			\end{equation} }

			The Laplacean prior act as $L1$-type of regularization on the optimization problem. Instead of preventing any of the coefficients from being too large (due to the squaring), $L1$ promotes sparsity. Due to the sparsity some of the parameters can be zero out, and eventually removed from the model. $L1$ is more robust to outliers than $L2$.

			If the cost function is given by Equations \ref{EQ: MAP_L2} or \ref{EQ: MAP_L1}, then the optimization problem can be formulated as follow:

			{\footnotesize
				\begin{equation}
					\begin{aligned}
						&\hat{\theta}_{MAP} &= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta) \\
						&\text{subject to}
						& \dot{x} = f(t,x,\theta) \\
						&& \dot{\theta} = 0 \\
						&& y = g(x)
					\end{aligned}
			\end{equation} }

			\hrule
			If the cost function to be maximized is given be Equation \ref{EQ: MAP_probability} and constrained by Equation \ref{EQ: Measurment_noise}, then the method of Lagrange multipliers can be used to convert a constrained problem into a form such that the derivative test of an unconstrained problem can be applied. The Lagrange function ($L^*$) can be defined as $\ln(L)$ plus the Lagrangian multipliers $\lambda(t_i)$ times the constraint function

			{\footnotesize
				\begin{equation} \label{EQ: MLE_Lagrangian}
					\begin{split}
						L^* \equiv \ln p\left( \theta \right) + \sum_{i=1}^{n} \left\{ \ln p(y(t_i)|\theta) \right. \\
						\left. + \lambda^T \cdot {\color{red} \left[ Y(t_i) - y\left( \theta,t_i \right) - \epsilon(t_i) \right] } \right\} \\ - \ln \left[ p\left( y \right) \right]
					\end{split}
			\end{equation}}

			By assumption of the relation of Equation \ref{EQ: Measurment_noise}

			{\footnotesize
				\begin{equation} \label{EQ: Noise_prob}
					p\left( y(t_i) | \theta,y_0 \right) = p\left( \epsilon(t_i) \right)
			\end{equation} }

			and specially

			{\footnotesize
				\begin{equation} \label{EQ: Noise_prob_norm}
					p\left( \epsilon(t_i) \right) = \cfrac{1}{ (2\pi)^{v/2} |\Gamma(t_i)|^{1/2} } \exp \left[ -\cfrac{1}{2}\epsilon^T(t_i) \left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \right]
			\end{equation} }
			where $|\Gamma|$ is the det$~\Gamma$, and $\Gamma$ is the covariance matrix of $\epsilon$, i.e., of the response.

			After Equation \ref{EQ: Noise_prob} is substituted into Equation \ref{EQ: MLE_Lagrangian}, and $L^*$ can be differentiated with respect to each of the estimates and $\epsilon(t_i)$. {\color{red}Based on the first order optimality conditions}, the resulting expression is equated to zero:

			{\footnotesize
				\begin{subequations} \label{EQ: MLE_Lag_diff}
					\begin{alignat}{2}
						%\cfrac{\partial L^*}{\partial y_0} &= \cfrac{\partial}{\partial y_0} \ln p(\theta,y_0) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial y_0} y(\theta ,t_i) = 0^T \\
						\cfrac{\partial L^*}{\partial \theta} &= \cfrac{\partial}{\partial \theta} \ln p(\theta) - \sum_{i=1}^{n} \lambda^T(t_i) \cfrac{\partial}{\partial \theta} y(\theta,t_i) =0 \\
						\cfrac{\partial L^*}{\partial \epsilon(t_i)} &= \cfrac{\partial}{\partial \epsilon(t_i)} \ln p(\epsilon(t_i)) - \lambda^T(t_i) = 0^T
					\end{alignat}
			\end{subequations} }

			Substitution of Equation \ref{EQ: Noise_prob_norm} into the last Equation of \ref{EQ: MLE_Lag_diff} makes it possible to solve for $\lambda(t_i)$:

			{\footnotesize
				\begin{align}
					\lambda(t_i) &= -\left( \Gamma(t_i) \right)^{-1} \epsilon(t_i) \nonumber \\
					&= -\left( \Gamma(t_i) \right)^{-1} \left[ Y(t_i) - y(\theta,t_i) \right]
			\end{align} }

			and to eliminate $\lambda(t_i)$ from the first equation of \ref{EQ: MLE_Lag_diff}.

			For convenience we shall define a new column vector $\theta^*$ in which all the elements of $\theta$ are arranged as follows:

			{\footnotesize
				\begin{equation}
					\theta^* = \begin{bmatrix}
						\theta_{1,1} & \theta_{1,2} & \cdots & \theta_{1,v} & \theta_{2,1} & \cdots & \theta_{2,v} & \cdots & \theta_{v,v}
					\end{bmatrix}^T	
			\end{equation} }

			Finally, we assume that and $\theta^*$ are distributed by a joint normal distribution and that the prior distribution are, respectively

			{\footnotesize
				\begin{subequations} \label{EQ: MLE_Priors}
					\begin{align}
						&p\left( \theta^* \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{\theta^*}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( \theta^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} \left( \theta^* - \theta^{*(0)} \right) \right] 
						%&p\left( y_0 \right) = \cfrac{1}{ (2\pi)^{v/2} |\Omega_{y_0}|^{1/2} } \exp \left[ -\cfrac{1}{2} \left( y_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} \left( y_0 - y_0^{(0)} \right) \right] 
					\end{align}
			\end{subequations} }
			where $\Omega$'s are the respective covariance matrices for $\theta^*$ and $y_0$, and the subscript $(0)$ designates the prior estimated of $\theta^*$ and $y_0$. If we assume that $\theta^*$ and $y_0$ are independent

			%{\footnotesize
				%	\begin{equation}
					%		\ln p(\theta^*,y_0) = \ln p(\theta^*) + \ln p(y_0)
					%\end{equation} }

					Introduction of the prior distributions, Equations \ref{EQ: MLE_Priors}, plus the expression for $\lambda(t_i)$ into the first two equations of \ref{EQ: MLE_Lag_diff} gives the final equations from which the estimators of $\theta^*$ and $y_0$ can be obtained:

					{\footnotesize
						\begin{subequations} 
							\begin{flalign}
								%			&-\left( \hat{y}_0 - y_0^{(0)} \right)^T \Omega_{y_0}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, \hat{y}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial y_0} y\left( \hat{\theta}, \hat{y}, t_i \right) = 0^T  &&\\
								&-\left( \hat{\theta}^* - \theta^{*(0)} \right)^T \Omega_{\theta^*}^{-1} + \sum_{i=1}^{n}\left[ Y(t_i) - y\left( \hat{\theta}, t_i \right) \right]^T \Gamma^{-1}(t_i) \cdot \cfrac{\partial}{\partial \theta^*} y\left( \hat{\theta}, t_i \right) = 0^T &&
							\end{flalign}
					\end{subequations} }
					where the overlay caret denotes estimated parameters.

					Note that under the assumption that the elements of $\Omega$ are essentially infinite (prior knowledge is diffuse), the elements of $\Omega^{-1}$ are zero, the equations for the maximum likelihood estimates coincide with those for the least squares estimates, and the same calculations for precision in the estimates apply.

					%For some models, these equations can be explicitly solved for $\hat{\theta}^*$ and $\hat{y}$ but in general no closed-form solution to the maximization problem is known or available, and an MLE can only be found via numerical optimization. Under the assumption of normality, the lack of prior knowledge about the parameters $\theta^0$ and known initial conditions $y_0$, the optimization problem is defined as follow:
					%
					%{\footnotesize
						%\begin{equation}
						%	\hat{\theta}_{MLE} = \arg \max_{\theta \in \Theta} L = \arg \max_{\theta \in \Theta} p(\theta|y)
						%\end{equation} }
						%
						%Intuitively, this selects the parameter values that make the observed data most probable. The specific value $\hat{\theta}$ that maximizes the likelihood function $L$ is called the maximum likelihood estimate. Further, if the function $\hat{\theta}:\mathbb{R}\rightarrow\Theta$ so defined is measurable, then it is called the maximum likelihood estimator.
						%
						%If the random samples $y(t_1)$, $y(t_2)$,...,$y(t_n)$ come from a normal distribution with unknown mean $\hat{\theta}$ and variance $\sigma^2$, then the joint probability function can be written as 
						%
						%{\footnotesize
							%\begin{equation}
							%	p(\theta|y(t_i)) = \cfrac{1}{\sqrt{2\pi\sigma}}\exp\left[-\cfrac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}\right]
							%\end{equation} }
							%
							%Then the likelihood function is defined as follow:
							%
							%{\footnotesize
								%\begin{equation} 
								%	L =\prod\limits_{i=1}^n p(\theta|y(t_i)) = (2\pi\sigma)^{-n/2}\exp\left[-\cfrac{1}{2\sigma}\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2\right]
								%\end{equation} }
								%
								%By taking the ln of the likelihood function, the final form of the cost function is obtained:
								%
								%{\footnotesize
									%\begin{equation} 
									%	\ln L=-\cfrac{n}{2}\ln\sigma-\cfrac{n}{2}\ln(2\pi)-\cfrac{\sum\limits_{i=1}^n \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma}
									%\end{equation} }
									%
									%\subsection{Maximum a posteriori estimation}
									%
									%As already discussed, the prior information about the estimated parameters can be incorporated in to the maximum likelihood estimator to form a maximum a posteriori probability (MAP) estimate. MAP can be used to obtain a point estimate of an unobserved quantity on the basis of empirical data. MAP estimation can therefore be seen as a regularization of maximum likelihood estimation. MLE and MAP can be connected by Bayes' rule:
									%
									%{\footnotesize
										%\begin{equation} 
										%	\begin{split}
											%		{\bf \hat{\theta}_{\text{MAP}}} &= \arg\max_{\sigma, \theta \in \Theta} p(\theta | y) \\
											%		&= \arg\max_{\sigma, \theta \in \Theta} \frac{p(y | \theta) p(\theta)}{p(y)} \\
											%		&= \arg\max_{\sigma, \theta \in \Theta} p(y | \theta) p(\theta) \\
											%		&= \arg\max_{\sigma, \theta \in \Theta} \ln(p(y | \theta) p(\theta)) \\
											%		&= \arg\max_{\sigma, \theta \in \Theta} \ln p(y | \theta) + \ln p(\theta)
											%	\end{split}
										%\end{equation} }
										%
										%Notice that we can get rid of the evidence term $P(y)$ because it's constant with respect to the maximization and also take the ln of the inner function because it's monotonically increasing.
										%
										%We assume the normal distribution of random samples, with identical variance and the prior distribution of $\theta$ given by $\mathcal{N}(\theta^0,\,\sigma_\theta^{2})$. The likelihood function to be maximized can be written as
										%
										%{\footnotesize
											%\begin{equation} \label{EQ: MAP_L2}
											%	\begin{split}
												%	&\arg\max_{\sigma, \theta \in \Theta} \left[ \ln \prod_{i=1}^{n} \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{ \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 }{2\sigma^2}}
												%	+ \ln \prod_{j=0}^{p} \frac{1}{\sigma_\theta\sqrt{2\pi}}e^{-\frac{ \left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]  \\
												%	&= \arg\max_{\sigma, \theta \in \Theta} \left[- \sum_{i=1}^{n} {\frac{\left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2}{2\sigma^2}}
												%	- \sum_{j=0}^{p} {\frac{\left( \hat{\theta} - \theta^0 \right)^2}{2\sigma_\theta^2}} \right]\\
												%	&= \arg\min_{\bf \theta} \frac{1}{2\sigma^2} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2
												%	+ \frac{\sigma^2}{\sigma_\theta^2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right] \\
												%	&= \arg\min_{\bf \theta} \left[ \sum_{i=1}^{n} \left( Y(t_i) - y\left( \hat{\theta}, t_i \right) \right)^2 + \lambda_{L2} \sum_{j=0}^{p} \left( \hat{\theta} - \theta^0 \right)^2 \right]
												%	\end{split}
											%\end{equation} }
											%
											%Notice that we dropped some of the constants (with respect to $\theta$) and factored to simplify the expression. You can see this is the same expression as Equation \ref{EQ: MAP_L2} (L2 Regularization) with $\lambda_{L2}$. We can adjust the amount of regularization we want by changing $\lambda_{L2}$. Equivalently, we can adjust how much we want to weight the priors carry on the coefficients ($\theta$). If we have a very small variance (large $\lambda_{L2}$) then the coefficients will be very close to 0; if we have a large variance (small $\lambda_{L2}$) then the coefficients will not be affected much (similar to as if we didn't have any regularization).

											\fi

										\end{document}

### 2024-05-20 Sections/Low_mach_number_expansion.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	As discussed by \citet{Lions2013}, the low Mach number equations are a subset of the fully compressible equations of motion (continuity, momentum and energy). Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible. The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \frac{|v|}{\sqrt{ \partial P / \partial \rho_f }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals. The equations are derived from the compressible equations based on the perturbation theory. The perturbation theory develops an expression for the desired solution in terms of a formal power series known as a perturbation series in some "small" parameter $\zeta$, that quantifies the deviation from the exactly solvable problem. The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution, due to the deviation from the initial problem.

	The equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case. We rescale the time variable, considering finally

	{\footnotesize
		\begin{align*}
			\rho_\zeta 	&= \rho\left( z, t/M_a \right), \quad
			v_\zeta 	= \cfrac{1}{\zeta} v\left( z, t/M_a \right) \\ 
			T_\zeta 	&= T\left( z, t/M_a \right),  \quad 
			k_\zeta 	= \zeta k(\rho_f, T) 
		\end{align*} 
	}

	The conservative non-dimensional equations of motion becomes

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_\zeta A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_\zeta A_f v_\zeta \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_\zeta A_f v_\zeta \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_\zeta v_\zeta A_f v_\zeta \right)}{\partial z} + \cfrac{A_f}{M_a^2} \cfrac{\partial P_\zeta}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_\zeta e_\zeta A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_\zeta e_\zeta v_\zeta A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_\zeta}{\partial z} \right) + P_\zeta \cfrac{\partial \left(A_f v_\zeta\right)}{\partial z} = 0
		\end{align*}
	}

	Let's define $\zeta=M_a^2$ and assume small Mach numbers, $M_a \ll 1$, then the kinetic energy, viscous work, and gravity work terms can be neglected in the energy equation since those terms are scaled by the square of the Mach number. The inverse of Mach number squared remains in the momentum equations, suggesting singular behaviour. In order to explore the singularity, the pressure, velocity and temperature are expanded as asymptotic series in terms of the parameter $\zeta$

	{\footnotesize
		\begin{align*}
			P_\zeta 	& = P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3) \\
			\rho_\zeta 	& = \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \\
			v_\zeta 	& = v_0		+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			T_\zeta 	& = T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
			e_\zeta 	& = e_0 	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \\
		\end{align*}
	}

	 By expanding performing power expansion on the continuity equation and taking the limit of $\zeta$ from the positive side we get

	 {\footnotesize
	 	\begin{align*}
	 		& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \right)}{\partial t} + \\
	 		&+ \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
	 	\end{align*}
	 }

	The continuity equation become

		 {\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_0 A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_0 A_f v_0 \right)}{\partial z} = 0
		\end{equation}
	}

	The form of the continuity equation stays the same. Considering the momentum equation, it can be seen that the inverse of Mach number squared remains which suggests singular behavior.

	{\footnotesize
		\begin{align*}
		 & \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left(  \left(  \rho_0 + \rho_1 \zeta + \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial t} + \\
		 &+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( v_0	+ v_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
		 &+ A_f \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2}	+ \cfrac{P_1 \zeta}{M_a^2}	+ \cfrac{P_2 \zeta^2}{M_a^2} + \mathcal{O}(\zeta^3) \right)
		\end{align*}
	}

	The first two terms stays the same, but the third one become different in structure. By further investigation of the pressure term in the momentum equation it can be observed

	{\footnotesize
		\begin{align*}
			& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2}	+ \cfrac{P_1 \zeta}{M_a^2}	+ \cfrac{P_2 \zeta^2}{M_a^2} + \mathcal{O}(\zeta^3) \right) = \\
			& = \lim_{\zeta \rightarrow 0_+} \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_1 \zeta^2}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_2 \zeta^2}{M_a^2} \right) \\
			& = \lim_{\zeta=M_a^2 \rightarrow 0_+} \cfrac{\partial }{\partial z} \left(  \cfrac{P_0}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_1 M_a^2}{M_a^2} \right) + \cfrac{\partial }{\partial z} \left(  \cfrac{P_2 M_a^4}{M_a^2} \right) \\
			& = \lim_{\zeta=M_a^2 \rightarrow 0_+} 0 + \cfrac{\partial P_1}{\partial z}  + 0 \\
		\end{align*}
	}

	The simplification of the $P_0$ in the momentum equation comes from the fact that $P_0$ is independent of $z$. As it was presented above, the thermodynamical pressure moves with speed of sound, and any perturbation propagates instantaneously. The term related to $P_2$ and higher order terms become zero at the limit of $M_a \rightarrow 0$. The momentum equation become

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 A_f v_0 \right) }{\partial t}	+ \cfrac{\partial \left( \rho_0 v_0 A_f v_0 \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0
		\end{equation*}
	}

	By expanding performing power expansion on the energy equation and taking the limit of $\zeta$ from the positive side we get

	{\footnotesize
		\begin{align*}
			& \lim_{\zeta \rightarrow 0_+} \cfrac{\partial \left( \left( \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right)}{\partial t} + \\
			&+ \cfrac{\partial \left(  \left(  \rho_0	+ \rho_1 \zeta	+ \mathcal{O}(\zeta^2) \right) A_f \left( v_0	+ v_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \left( e_0	+ e_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) }{\partial z} + \\
			&+ \cfrac{\partial}{\partial z} \left( k \cfrac{\partial }{\partial z} \left( T_0 	+ T_1 \zeta 	+ \mathcal{O}(\zeta^2) \right) \right) + \\
			&- \left(  P_0 	+ P_1 \zeta		+ P_2 \zeta^2 		+ \mathcal{O}(\zeta^3)  \right) \cfrac{\partial \left( A_f \left( v_0 + v_1 \zeta + \mathcal{O}(\zeta^2) \right) \right) }{\partial z} = 0
		\end{align*}
	}

	The form of the energy equation stays the same.

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left( \rho_0 e_0 A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_0 e_0 v_0 A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T_0}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v_0\right)}{\partial z} = 0
		\end{equation*}
	}

	where $e_0 = e(\rho_0, T_0)$ and $k=k(\rho_0, T_0)$.

	The expansion results in two different types of pressure and they are considered to be split into a thermodynamic component ($P_0$) and a dynamic component ($P_1$). The thermodynamic pressure is constant in space, but can change in time. The thermodynamic pressure is used in the equation of state. The dynamic pressure only arises as a gradient term in the momentum equation and acts to enforce continuity.

	The resulting unscaled low Mach number equations are:

	{\footnotesize
		\begin{align*}
			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} &+ \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} = 0 \\
			\cfrac{\partial \left( \rho_f A_f v \right) }{\partial t}	&+ \cfrac{\partial \left( \rho_f v A_f v \right)}{\partial z} + A_f \cfrac{\partial P_1}{\partial z} = 0\\
			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} &+ \cfrac{\partial \left( \rho_f e v A_f \right)}{\partial z} - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
		\end{align*}
	}

	The energy equation can be expanded through the chain rule to obtain

	{\footnotesize
		\begin{equation*}
			 \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) + e  \underbrace{ \left( \cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} \right) }_{Continutiy}  - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
		\end{equation*}
	}

	The non-conservative form of the energy equation become

	{\footnotesize
		\begin{equation*}
		\rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
		\end{equation*}
	}

	If the calorically perfect gas is assumed then $e=C_vT$, where $C_v$ is the constant specific heat. The energy equation can derived in terms of temperature $T$

	{\footnotesize
		\begin{equation*}
			\rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
		\end{equation*}
	}

	If isothermal case is assumed then, the energy equation becomes

	{\footnotesize
		\begin{equation*}
			\lim_{\Delta T \rightarrow 0_+} \rho A_f C_v \left( \cfrac{\partial T }{\partial t} + v \cfrac{\partial T}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
		\end{equation*}
	}

	which leads to

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left(A_f v\right)}{\partial z} = 0
			\label{EQ: Incompressibility_Condition_Ideal_IsoThermal}
		\end{equation}
	}

	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f v) = 0$, which known as the incompressibility condition (\citet{Lions2013}).

		A general formulation the internal energy for a real gas is:

	{\footnotesize
		\begin{equation*}
			de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{v_m}\right]dv_m
	\end{equation*} }

	where $v_m$ is the molar volume.

	The internal energy is a function of two intensive properties, in this case $T$ and $v_m=1/\rho_f$. But, in the case of an ideal gas, the equation of state is such that the second term in this equation is identically equal to zero. So the ideal gas is a special case in which the molar internal energy is a function only of temperature. For Peng-Robinson equation of state, the internal energy is defined as

	{\footnotesize
	\begin{equation*}
		e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
	\end{equation*} }

	\todo[]{Add REF}

	Assuming constant temperature and pressure along space and in time:

	{\footnotesize
		\begin{equation*}
			\lim_{\Delta T, \Delta P \rightarrow 0_+ } \rho A_f \left( \cfrac{\partial e }{\partial t} + v \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial \left(A_f v\right)}{\partial z} = 0 \rightarrow \cfrac{\partial \left(A_f v\right)}{\partial z} = 0
		\end{equation*}
	}

	It can be deduce that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure. Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.

	Assuming an arbitrary function $\hat{P}$, which describe the total pressure, the dimensional momentum equation can be written as

	{\footnotesize
		\begin{equation*}
			V \underbrace{ \left( \cfrac{\partial \left(\rho_f A_f\right)}{\partial t} + \cfrac{\left(\rho_f v A_f\right)}{\partial z} \right) }_{Continuity~equation} + \rho_f A_f \cfrac{\partial v}{\partial t} + \rho_f v A_f \cfrac{\partial v}{\partial z} = - A_f \cfrac{\partial \hat{P}}{\partial z}
		\end{equation*}
	}

	From the incompressibility conditions we can deduce that

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial \left(A_f v\right)}{\partial z} = 0 \rightarrow A_f \cfrac{\partial v}{\partial z} = - v \cfrac{\partial A_f}{\partial z}
		\end{equation*}
	}

	By combining both above equations, assuming that $\partial v / \partial t = 0$:

	{\footnotesize
		\begin{equation*}
			\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} = \cfrac{\partial \hat{P}}{\partial z} \rightarrow \int	\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int \cfrac{\partial\hat{P}}{\partial z} dz
		\end{equation*}
	}

	The l.h.s integral can be solved by assuming $\rho_f$ is constant and introducing superficial velocity $u_s=A_f v$

	{\footnotesize
		\begin{align*}
			& \int	\cfrac{\rho_f v^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int	\cfrac{\rho_f v^2}{A_f} \cfrac{A_f^2}{A_f^2} \cfrac{\partial A_f}{\partial z} dz \\
			&= \rho_f u_s^2  \int \cfrac{1}{A_f^3} \cfrac{\partial A_f}{\partial z} dz = - \cfrac{\rho_f u_s^2}{2 \Delta A_f^2} = - \cfrac{\rho_f \Delta v^2}{2} \\
			& \int \cfrac{\partial \hat{P}}{\partial z} dz = \Delta \hat{P}
		\end{align*}
	}

	The final form of the momentum equation corresponds to the Bernoulli's principle

	{\footnotesize
		\begin{equation*}
			\Delta \hat{P} = - \cfrac{\rho_f \Delta v^2}{2} \xrightarrow[]{P_0 = \text{const}} \Delta M_a^2 P_1 = - \cfrac{\rho_f \Delta v^2}{2}
		\end{equation*}
	}

	The Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-section at steady-state. Moreover, if the flow velocity is relatively low and so all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic. The effect of this is that $\partial \rho / \partial P = 0$. In other words, the small changes in pressure due to flow velocity changes do not change the density. This has a secondary effect -- the speed of sound in the fluid is $\partial P/\partial \rho = \infty$	in this instance. So there is an infinite speed of sound, which makes the equations elliptic in nature. It can be deduced that at the isothermal conditions the density in the system propagates with the same speed as pressure due to the fact that they are both connected through the equation of state.

\end{document}

### 2024-05-20 Sections/Low_mach_number_expansion_imp.tex
20.05

--- 2024-05-20 Sections/Low_mach_number_expansion.tex
@@
 	As discussed by \citet{Lions2013}, the low Mach number equations are a subset of the fully compressible equations of motion (continuity, momentum and energy).
-Such a set of equations allow for large variations in gas density but it is consider to be acoustically incompressible.
-The low Mach number equations are preferred over the full compressible equations for low speed flow problems $\left( M_a = \frac{|v|}{\sqrt{ \partial P / \partial \rho_f }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
-The equations are derived from the compressible equations based on the perturbation theory.
+Such a set of equations allow for large variations in gas density, but it is considered acoustically incompressible.
+Therefore, the low Mach number equations are preferred over the full compressible equations for low-speed flow problems $\left( M_a = \frac{|v|}{\sqrt{ \partial P / \partial \rho_f }} \ll 1 \right)$ to avoids the need to resolve fast-moving acoustic signals.
+The equations are derived from compressible equations based on the perturbation theory.
 The perturbation theory develops an expression for the desired solution in terms of a formal power series known as a perturbation series in some "small" parameter $\zeta$, that quantifies the deviation from the exactly solvable problem.
-The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution, due to the deviation from the initial problem.
+The leading term in this power series is the solution of the exactly solvable problem, while further terms describe the deviation in the solution due to the deviation from the initial problem.
 
-	The equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively the transport of mass, momentum and energy) for quasi-one-dimensional case.
+	The Equations \ref{EQ: CompressibleEuler_1} to \ref{EQ: CompressibleEuler_2} describe the fully compressible equations of motion (respectively, the transport of mass, momentum and energy) for the quasi-one-dimensional case.
 We rescale the time variable, considering finally
@@
 
-	The conservative non-dimensional equations of motion becomes
+	The conservative non-dimensional equations of motion become
 
@@
 
-	Let's define $\zeta=M_a^2$ and assume small Mach numbers, $M_a \ll 1$, then the kinetic energy, viscous work, and gravity work terms can be neglected in the energy equation since those terms are scaled by the square of the Mach number.
+	Let's define $\zeta=M_a^2$ and assume small Mach numbers, $M_a \ll 1$, then the kinetic energy, viscous work, and gravity work terms can be neglected in the energy equation since the square of the Mach number scales those terms.
 The inverse of Mach number squared remains in the momentum equations, suggesting singular behaviour.
@@
 
-	 By expanding performing power expansion on the continuity equation and taking the limit of $\zeta$ from the positive side we get
+	By expanding performing power expansion on the continuity equation and taking the limit of $\zeta$ from the positive side, we get
 
@@
 
-	The continuity equation become
+	The continuity equation becomes
 
@@
 
-	The form of the continuity equation stays the same. Considering the momentum equation, it can be seen that the inverse of Mach number squared remains which suggests singular behavior.
+	The form of the continuity equation stays the same. Considering the momentum equation, it can be seen that the inverse of Mach number squared remains, which suggests singular behaviour.
 
@@
 
-	The first two terms stays the same, but the third one become different in structure. By further investigation of the pressure term in the momentum equation it can be observed
+	The first two terms stay the same, but the third one becomes different in structure. By further investigation of the pressure term in the momentum equation, it can be observed.
 
@@
 	The simplification of the $P_0$ in the momentum equation comes from the fact that $P_0$ is independent of $z$.
-As it was presented above, the thermodynamical pressure moves with speed of sound, and any perturbation propagates instantaneously.
+As was presented above, the thermodynamical pressure moves with the speed of sound, and any perturbation propagates instantaneously.
 The term related to $P_2$ and higher order terms become zero at the limit of $M_a \rightarrow 0$.
-The momentum equation become
+The momentum equation becomes
 
@@
 
-	By expanding performing power expansion on the energy equation and taking the limit of $\zeta$ from the positive side we get
+	By expanding performing power expansion on the energy equation and taking the limit of $\zeta$ from the positive side, we get
 
@@
 
-	The non-conservative form of the energy equation become
+	The non-conservative form of the energy equation becomes
 
@@
 
-	If the calorically perfect gas is assumed then $e=C_vT$, where $C_v$ is the constant specific heat. The energy equation can derived in terms of temperature $T$
+	If the calorically perfect gas is assumed, then $e=C_vT$, where $C_v$ is the constant specific heat. The energy equation can be derived in terms of temperature $T$.
 
@@
 
-	If isothermal case is assumed then, the energy equation becomes
+	If an isothermal case is assumed, then the energy equation becomes
 
@@
 
-	In one-dimensional case, the equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f v) = 0$, which known as the incompressibility condition (\citet{Lions2013}).
+	In one-dimensional case, the Equation \ref{EQ: Incompressibility_Condition_Ideal_IsoThermal} become equivalent of $\text{div} ( A_f v) = 0$, which known as the incompressibility condition (\citet{Lions2013}).
 
-		A general formulation the internal energy for a real gas is:
+	As presented by \citet{Elliott2011}, a general formulation of the internal energy for a real gas is:
 
@@
 
-	The internal energy is a function of two intensive properties, in this case $T$ and $v_m=1/\rho_f$.
+	The internal energy is a function of two intensive properties, in this case, $T$ and $v_m=1/\rho_f$.
 But, in the case of an ideal gas, the equation of state is such that the second term in this equation is identically equal to zero.
@@
 
-	\todo[]{Add REF}
-
 	Assuming constant temperature and pressure along space and in time:
@@
 
-	It can be deduce that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure.
-Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.
+	It can be deduced that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure.
+Moreover, the incompressibility condition $div(A_fv)=0$ is obtained.
 
-	Assuming an arbitrary function $\hat{P}$, which describe the total pressure, the dimensional momentum equation can be written as
+	Assuming an arbitrary function $\hat{P}$, which describes the total pressure, the dimensional momentum equation can be written as
 
@@
 
-	From the incompressibility conditions we can deduce that
+	From the incompressibility conditions, we can deduce that
 
@@
 
-	The final form of the momentum equation corresponds to the Bernoulli's principle
+	The final form of the momentum equation corresponds to Bernoulli's principle
 
@@
 
-	The Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-section at steady-state.
-Moreover, if the flow velocity is relatively low and so all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic.
+	Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-sections at steady-state.
+Moreover, if the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic.
 The effect of this is that $\partial \rho / \partial P = 0$.
@@
 So there is an infinite speed of sound, which makes the equations elliptic in nature.
-It can be deduced that at the isothermal conditions the density in the system propagates with the same speed as pressure due to the fact that they are both connected through the equation of state.
+It can be deduced that at the isothermal conditions, the density in the system propagates with the same speed as pressure since they are both connected through the equation of state.
 

### 2024-05-20 Sections/Model.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsubsection{Continuity equation} \label{CH: Continuity}

	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating a function $A_f = A\phi$. This modification distinguishing a constant and varying terms, where the varying term accounts for the changes in the cross-sectional area available for the fluid. Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:

	{\footnotesize
		\begin{equation} \label{EQ: Continuity_differential}
			\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial z} = 0
		\end{equation}
	}
	where $A$ is the total cross-section of the extractor and $\phi$ describe porosity along the extractor.

	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial (\rho_f v A \phi )}{\partial z} dz = F \rightarrow F=\rho_f v A\phi
		\end{equation}
	}

	To simplify the system's dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.

	{\footnotesize
	\begin{equation} \label{EQ:Velocity_1}
		v = \cfrac{F}{\rho_f A\phi} 
	\end{equation}
	}

	Similarly, the superficial velocity might be introduced.

	{\footnotesize
		\begin{equation} \label{EQ:Velocity_2}
			u = v \phi = \cfrac{F}{\rho_f A }
		\end{equation}
	}

	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and thermodynamic pressure are known along $z$. The variation in fluid density may occurs due to pressure or a inlet temperature changes. In non-isothermal case, $\rho_f$ in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} is consider to be an average fluid density along the extraction column.

	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}

	Equation \ref{Model_fluid}, describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. It is also assumed that the thermodynamic pressure remains constant throughout the device. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Thus, the mass balance equation include convection, diffusion, and kinetic terms to represent the fluid phase behaviour.

	{\footnotesize
		\begin{equation}
			\label{Model_fluid}
			\frac{\partial c_f}{\partial t}
			+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z}
			= \frac{1-\phi}{\phi} r_e
			+ \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right)
		\end{equation}
	}

	$c_f$ represents the solute's concentration in the fluid phase, $r_e$ is a mass transfer kinetic term, and $D^M_e$ is the axial diffusion coefficient.

	\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}

	As given by Equation \ref{Model_solid}, the solid phase is considered to be stationary, without convection and diffusion terms in the mass balance equation. Therefore, the only significant term in this equation is the kinetic term of Equation \ref{Model_kinetic_basic}, which connects the solid and fluid phases. The extract is represented by a single pseudo-component for simplicity.

	{\footnotesize
		\begin{equation} 
			\label{Model_solid}
			%		{\scriptsize\begin{equation}
					\cfrac{\partial c_s}{\partial t} = \underbrace{ r_e }_{\text{Kinetics}}
			\end{equation} }

	\subsubsection{Kinetic term} \label{CH: Kinetic}

	%The kinetic term is based on two-film theory and follow work of \citet{Reverchon1996}. The mass transfer kinetic (Equation \ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.

	%In this study, the kinetic term is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by Equation \ref{Model_kinetic_basic}. This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.

%	As the solvent flows through the bed, the CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles through the solvent–solid matrix interactions. Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}. The mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$. At the solid-fluid interface, the equilibrium concentrations are given as ${\color{black}c_s^*}$ and ${\color{black}c_P^*}$, respectively for solid and fluid phases. The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{black}c_{P}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{Pf}}$ at the opening of the pore. The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{black}c_f}$. It can be assumed that the two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.

	As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$ and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases. The concentration of the solutes in the fluid phase in the center of the pore is denoted as $c_p$. As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the opening of the pore. Then the solute diffuses through the film around the particle and reaches bulk concentration $c_f$. The two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be determined from the relationship between the solute concentration in one phase and its equilibrium concentration.

		\begin{figure}[h!]
			\centering
			\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=0.85\columnwidth]{Figures/SFE_PFD.drawio.png}	
			\caption{The mass transfer mechanism}
			\label{fig: SFE_Mechanism}
		\end{figure}

		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, $c_f$, and in the center of the pore, $c_p^*$. The concentration $c_p^*$ is in equilibrium with $c_s$ according to an equilibrium relationship. The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$. On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$. Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}

			{\footnotesize
				\begin{equation} \label{Model_kinetic_basic}
					r_e = \cfrac{D_i}{\mu l^2 }\left(c_s - c_p^* \right)
			\end{equation} }

		where $\mu$ is sphericity, $l$ a characteristic dimension of particles and can be defined as $l = r/3$, $r$ is the mean particle radius, $\rho_s$ is the solid density, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).

		According to \citet{Bulley1984}, a linear equilibrium relationship (Equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase $c_f^*$ is based on the concentration of the solute in the solid phase $c_s$.

			{\footnotesize
				\begin{align} \label{Linear_equilibirum}
					c_f^* &= k_p c_s
			\end{align} }

			The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase. According to \citet{Spiro2007}, $k_p$ can be expressed through the mass partition coefficient $k_m$.

			{\footnotesize
				\begin{align}
					k_m = \cfrac{k_p \rho_s}{\rho_f}
			\end{align} }

			%Equation \ref{Model_kinetic_no_sat} represents of the kinetic term according to \citet{Reverchon1996}
			According to \citet{Reverchon1996}, the kinetic term becomes

			{\footnotesize
				\begin{equation}
					\label{Model_kinetic_no_sat}
					r_e = -\cfrac{D_i}{ \mu l^2 } \left(c_s - \cfrac{\rho_s c_f}{k_m \rho_f} \right)
			\end{equation} }

        \subfile{Saturation}

		\iffalse	
		\subsubsection{Heat balance} \label{CH: heat_balance}

		 {\color{black}
			The heat balance (Equation \ref{Model_heat}) consists of the convective and diffusive terms. It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases. We consider no heat loss through the wall, and there is no heat generation in the system. Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream %$T_{In}(t)$.

			We assume that at a given section, where the cross-sectional area is $A$, the flow properties are uniform across that section. Hence, although the area of an extractor changes  as a function of a distance along an extractor (e.g. if a fixed fill an extractor partially), $z$, and therefore in reality the flow field is two-dimensional (the flow varies in the two-dimensional space), we make the assumption that the flow properties vary only with $z$; this is tantamount to assuming uniform properties across any given cross section. Such flow is defined as quasi-one-dimensional flow.

		}

		\sout{The heat balance equation (equation  \ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance). Equation \ref{Model_heat} contains the convection and the diffusion terms. It is considered that there is no heat loss through the wall, and there is no heat generation in the system. The temperature of the extractor can be changed only by increasing the temperature of the inlet stream. The pseudo-homogenous phase is assumed to flow only in the axial direction. The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid $C_p$ because the solid phase is stationary. Therefore, this factor can be understood as the fraction of the fluid's total heat through convection. On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in Appendix. }

		{\color{black} The heat balance (Equation \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms. It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases. It is considered that there is no heat loss through the walls, and there is no heat generation in the system. The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{black}T_{Inlet}}(t)$.
			}

			{\footnotesize
				\begin{equation} \label{Model_heat}
					\begin{split}
						\cfrac{\partial T(t,z)}{\partial t} &= 
						\underbrace{ -\cfrac{F {\color{black}C_p}(T(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p} (T(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T(t,z)}{\partial z}  }_{\text{Convection}} + \\
						& + \underbrace{ {\color{black}D^T_e}(T(t,z),{\color{black}P}(t)) \cfrac{\partial^2 T(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
					\end{split}
			\end{equation} }

		where $ {\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial mass diffusion coefficient, ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}(T(t,z),{\color{black}P}(t),F)$ is the axial heat diffusion coefficient.

%		\todo[inline]{Draft of new heat equation starts here. TODO: \\ Check if the heat cpacity of solid phase needs to be added \\ Elaborate why pressure is know}

			The heat governing equation describe the evolution of the energy in the system and it is given by \ref{EQ: Heat_internal}. The derivation of the heat equation can be found in Appendix \ref{CH: Gouverning equations}.

			{\footnotesize
			\begin{align} \label{EQ: Heat_internal}
				&\cfrac{\partial \left( \rho_f e(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e(t,z) \right)}{\partial z} \nonumber \\
				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T(t,z)}{\partial z} \right) 
			\end{align}
			}

			The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure. The departure function is typically defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure. They are typically computed by integrating a function that depends on the equation of state and its derivatives. Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through Equation \ref{EQ: internal_energy_def}. More information on the departure functions can be found in Appendix \ref{CH:Enthalpy}.

			{\footnotesize
				\begin{equation}
					de(t,z)=C_vdT-\left[{\color{black}P}(t)-T(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial T(t,z)}\right)_{{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)
					\label{EQ: internal_energy_def}
				\end{equation} }

			where $e^{id}(t,z)$ is the internal energy of perfect gas.

			Suppose a gas is considered to be perfectly caloric ($e(t,z)={\color{black}C_v} T(t,z)$), then the energy equation can be written explicitly in the form of temperature. The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{black}C_v}$ is constant.

			For real gases, it is complicated to write the heat balance in terms of temperature, but it can be used directly in the form of internal energy, as it is given by Equation \ref{EQ: CompressibleEuler_3}. In such a case, the temperature needs to be recovered from the internal energy. A relation for the internal energy can be obtained from an equation of state. For Peng-Robinson, such a relation is given by Equation \ref{EQ: internal_energy_PR} as presented by \citet{Elliott2011}.

%			{\footnotesize
%				\begin{equation}
%					e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
%					\label{EQ: internal_energy_PR}
%				\end{equation}
%			}

			{\scriptsize
				\begin{equation}
					\begin{aligned}
					&\cfrac{e(t,z)-e^{id}(t,z)}{RT(t,z)} = \\
					& - \cfrac{{\color{black}A}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)} \right]
					\label{EQ: internal_energy_PR}
				\end{aligned}
			\end{equation}
			}

			To solve Equation \ref{EQ: internal_energy_PR}, temperature, pressure, and density values need to be known. If an equation of state is introduced, then only two out of three variables need to be obtained as the third one can be calculated; this can be represented as follow

			{\footnotesize
			\begin{equation}
				e(t,z)=e(T(t,z),{\color{black}P}(t),\rho_f)=e( T(t,z),{\color{black}P}(t), \rho_f ) 
			\end{equation}
			}

			If the value of internal energy $e(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed. A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}. Such a procedure allows to find a local temperature along spatial direction $z$ and needs to be repeated every time-step.

			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = e(t,z) + {\color{black}P}(t) / \rho_f$. By introducing the definition of enthalpy, the energy equation becomes

			{\footnotesize
				\begin{align} \label{EQ:Enthalpy_equation}
					\cfrac{\partial \left(\rho_f {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h}(t,z) A_f v \right)}{\partial z}  \nonumber \\
					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T(t,z)}{\partial z} \right)
				\end{align}
			}

			The main advantage of this formulation is the presence of term $\partial {\color{black}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable). The enthalpy is related to the pressure and temperature through the following equation:

			{\footnotesize
				\begin{equation}
					{\color{black}h}(t,z)={\color{black}h}(T(t,z),{\color{black}P}(t),\rho_f)={\color{black}h}( T(t,z),{\color{black}P}(t), \rho_f ) 
					\label{EQ:Enthalpy_root}
				\end{equation}
			}

			If the value of enthalpy is known from the time evolution and pressure can be measured, then the Equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile. For the Peng-Robinson EoS, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}. More details can be found in Appendix \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.

			{\scriptsize
				\begin{equation}
					\begin{split}
					{\color{black}h}(t,z)-{\color{black}h}(t,z)^{id}={\color{black}R}T(t,z) \left[{\color{black}T_r}({\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)-1) \right. \\
					\left. -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T(t,z)\right) } } \ln \left(\cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}\right)\right]
					\label{EQ:Enthalpy_PR}
				\end{split}
			\end{equation}				
			}

			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{black}T_{ref}}=298.15~[K]$ and ${\color{black}P_{ref}}=1.01325~[bar]$.

			As discussed by \citet{Gmehling2019}, the influence of the intermolecular forces on the enthalpy is needs to taken into account in high pressures systems. In most cases, these forces are attractive, so additional energy is necessary to move the molecules away from each other, that is, to lower the density. If this energy is not added, the substance cools down when it is expanded.

		\subsubsection{Pressure term} \label{CH: Pressure}

		The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time. As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound. Under such conditions, the term $\partial {\color{black}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system. The pressure (P) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.

		{\footnotesize
			\begin{equation}
				\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P}(t) - {\color{black}P_{in}}(t) }{\Delta t}
		\end{equation}}

		Such a simplified equation takes into account the pressure change in the energy balance, but the dynamics are simplified and do not consider the effects of pressure losses. In a real system, the dynamics of pressure change would depend on a pump used in an extraction system, as well as a back-pressure regulator used to control an outlet valve.

  		\fi

		\subsubsection{Extraction yield} \label{CH: Yield}

		The process yield is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}. The measurement equation evaluates the solute's mass at the extraction unit's outlet and sums it up. The integral form of the measurement (Equation \ref{Model_measurment_1}) can be transformed into the differential form (Equation \ref{Model_measurment_2}) and augmented with the process model.

		{\footnotesize
			\begin{align} 
				\label{Model_measurment_1}
%				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
				y &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
%				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
				\cfrac{dy}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
                \label{Model_measurment_2}
		\end{align}	}

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content $c_{s0}$. As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable. Considering that it is assumed that the $c_{f0}=0$ and that the system is isothermal. %and described by ${\color{black}h_0}$. 
		Therefore, the initial and boundary conditions are define as follow:

		\begin{comment}
		{\footnotesize
				\begin{align*}
					&{\color{black}c_f}(t = 0, z) = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} & &{\color{black}h}(t = 0, z) = {\color{black}h_0} \\
					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} & &\frac{\partial h(t,z=L)}{\partial x} = 0
				\end{align*} }
		\end{comment}

			{\footnotesize
				\begin{align*}
					&c_f(t = 0, z) = 0 && c_s(t = 0, z) = c_{s0} && {c_f}(t, z=0) = 0 \\
					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
			\end{align*} }

		\subsubsection{Discretization methods}

		The method of lines is used to transform the process model equations into a set of ODEs denoted as $G(x;\Theta)$. The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative $z$-direction. The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction. The state-space model after the discretization is denoted as $x$ and defines as follow:

		\begin{comment}
		{\footnotesize
			\begin{align*} \label{discretization}
				\dot{{\color{black}x}}(t) &= \cfrac{d x}{d t} = 
				\begin{bmatrix}
					\cfrac{d {\color{black}c_{f,1}}(t)}{d t} 	  \\
					\vdots					  \\
					\cfrac{d {\color{black}c_{f,N_z}}(t)}{d t} \\
					\\ \hline \\
					\cfrac{d {\color{black}c_{s,1}}(t)}{d t} 	  \\
					\vdots					  \\
					\cfrac{d {\color{black}c_{s,N_z}}(t)}{d t} \\
					\\ \hline \\
					\cfrac{d {\color{black}h_1}(t)}{d t} 	  \\
					\vdots 					  \\
					\cfrac{d {\color{black}h_{N_z}}(t)}{d t} \\
					\\ \hline \\
					\cfrac{d {\color{black}P}(t)}{d t} \\
					\\ \hline \\
					\cfrac{d {\color{black}y}(t)}{d t}
				\end{bmatrix}
				=
				\underbrace{\begin{bmatrix}
						{\color{black}G_1} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
						\vdots\\ 
						{\color{black}G_{N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
						\\ \hline \\ \\
						{\color{black}G_{N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
						\vdots\\
						{\color{black}G_{2N_z}} \left( {\color{black}c}(t),c_s,{\color{black}h}(t); \Theta \right)\\ 
						\\ \\ \hline \\ 
						{\color{black}G_{2N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
						\vdots\\
						{\color{black}G_{3N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\ 
						\\ \\ \hline \\
						{\color{black}G_{3N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
						\\ \\ \hline \\
						{\color{black}G_{3N_z+2}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) 
				\end{bmatrix}}_{{\color{black}G} \left( x; \Theta \right)} 
		\end{align*} }
	\end{comment}

		{\footnotesize
			\begin{align*} \label{discretization}
				\dot{x} &= \cfrac{d x}{d t} = 
				\begin{bmatrix}
					\cfrac{d c_{f,1}}{d t} 	  \\
					\vdots		\\	
					\cfrac{d c_{f,N_z}}{d t} \\
					\\ \hline  	\\
					\cfrac{d c_{s,1}}{d t} 	  \\
					\vdots		\\
					\cfrac{d c_{s,N_z}}{d t} \\
					%\\ \hline \\
					%\cfrac{d {\color{black}P}(t)}{d t} \\
					\\ \hline \\
					\cfrac{d {\color{black}y}(t)}{d t}
				\end{bmatrix}
				=
				\underbrace{\begin{bmatrix}
						G_1 \left( c_f,c_s; \Theta \right)\\ 
						\vdots\\ 
						G_{N_z} \left( c_f,c_s; \Theta \right)\\ 
						\\ \hline \\ \\
						G_{N_z+1} \left( c_f,c_s; \Theta \right)\\ 
						\vdots\\
						G_{2N_z} \left( c_f,c_s; \Theta \right)\\ 
						%\\ \\ \hline \\ 
						%{\color{black}G_{2N_z+1}} \left( c_f,c_s; \Theta \right) \\
						\\ \\ \hline \\
						G_{2N_z+2} \left( c_f,c_s; \Theta \right) 
				\end{bmatrix}}_{G \left( x; \Theta \right)} 
		\end{align*} }

		where ${\color{black}x} \in \mathbb{R}^{N_x = 2N_z+1} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.

		%As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem. The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary. That quantity is conserved and neither produced nor consumed inside the control volume. 
		For a derivative to be conservative, it must form a telescoping series. In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out. The discretization is applied to the conservative form of the model to ensure mass conservation.

		\iffalse
		\subsubsection{State-space representation} \label{CH: State_space}

		The process model can be written in a general form:

		{\footnotesize
			\begin{align}
				\begin{bmatrix}
					\cfrac{\partial c_f}{\partial t}\\
					\cfrac{\partial c_s}{\partial t}\\
					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
					\cfrac{\partial {\color{black}P}(t,z)}{\partial t} \\
					\cfrac{\partial {\color{black}y}(t)}{\partial t} 
				\end{bmatrix}
				& =
				\begin{bmatrix}
					{\color{black}\bar{\phi_1}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
					{\color{black}\bar{\phi_2}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
					{\color{black}\bar{\phi_3}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right) \\
					{\color{black}\bar{\phi_4}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
					{\color{black}\bar{\phi_5}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)
				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; \Theta \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
		\end{align} }

		where $\Theta$ is a parameter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.

		\fi

		%Function ${\color{black}\bar{\phi}}$ are transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}$.
		%The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.

		%In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c_f$ and $c_s$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$). The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor. Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$. 
		%The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$). The system is controllable by manipulating the flow rate and temperature (enthalpy) of CO$_2$ in the feed and the pressure in the extractor.

%			To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by Equation \ref{EQ:CFL}) was applied. Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
%			
%			{\footnotesize
%				\begin{equation}
%					C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1 
%					\label{EQ:CFL}
%				\end{equation}
%			}
%			
%			where u is velocity, $\Delta t$	is a time step and $\Delta x$ is the space discretization.

\end{document}

### 2024-05-20 Sections/Parameter_estimation.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Only some of the parameters in a process model can be estimated from the theoretical considerations. The goal of parameter estimation is to obtain the "best" estimate of unknown parameters $\theta$ (which is a subset of the parameter space ${\color{black}\Theta}$ containing all model's parameters) based on the continuous observations or the discrete. The unobservable error $\epsilon(t)$ is added to the deterministic model output, $y(t)$, to give the observable dependent variable $Y(t)$. For discrete observations, this can be expressed as:

	{\footnotesize
		\begin{equation*}
			Y(t_i) = y(\theta, t_i) + \epsilon(t_i)
	\end{equation*} }

	For continuous variables, the equation is:

	{\footnotesize
		\begin{equation*}
			Y(t) = y(\theta, t) + \epsilon(t)
	\end{equation*} }

	However, obtaining analytical solutions for a deterministic process model can be challenging, so experiments are often conducted where the vector of derivatives $\frac{dY(t_i)}{dt}$ is measured instead of $Y(t_i)$ itself. In such cases, it is assumed that the unobservable error is added to the deterministic derivative $\frac{dy(\theta, t_i)}{dt}$ as shown below

	{\footnotesize
		\begin{equation}  \label{EQ: Measurment_noise}
			\cfrac{d Y(t_i)}{dt} = \cfrac{dy(\theta, t_i)}{dt} + \epsilon(t_i)
	\end{equation} }

	In the case where the error in the first observation is denoted as $\epsilon_1$, the error in the second observation $\epsilon_2'$ incorporates $\epsilon_1$ as well as an independent random component, given by $\epsilon_2' = \epsilon_1 + \epsilon_2$. Similarly, the error in the third observation is $\epsilon_3' = \epsilon_1 + \epsilon_2 + \epsilon_3$, etc. \citet{Mandel1957}  made a distinction between the typically assumed independent measurement error in the dependent variable and a "cumulative" or interval error, in which each new observation encompasses the error of the previous ones. Cumulative errors arise from fluctuations in the process due to small variations in operating conditions and are not independent; only the differences in measurement from one period to the next are independent.

	Maximum likelihood estimation (MLE) is a statistical method used to estimate the parameters of a probability distribution based on observed data. The MLE works by finding the values of the parameters that maximize the likelihood function, which is the probability of observing the given data for a given set of parameter values. The MLE has desirable properties such as asymptotic efficiency and normality. Although the MLE has often been associated with the normal distribution for mathematical convenience, it can be applied to a wide range of probability distributions. The derivation of the likelihood function under the assumption of the Gaussian distribution is discussed by \citet{Himmelblau1970}. The objective function is presented by Equation \ref{EQ: Objective_function}:

	{\footnotesize
		\begin{equation} \label{EQ: Objective_function}
			\ln L = -\cfrac{n}{2}  \ln \left(2 \pi \sigma^2\right) 
			- \cfrac{ \sum_{i=1}^{n} \left[  \cfrac{d {Y}(t_i)}{dt} - \cfrac{dy(\theta, t_i)}{dt} \right]^2 }{2 \sigma^2}
		\end{equation}
	}

	The parameter estimation problem can be formulated as follow:

	{\footnotesize
		\begin{equation}
			\begin{aligned} \label{EQ: Optimization_formulation_MLE}
				&\hat{\theta}_{MLE} &= \arg \max_{\sigma, \theta \in \Theta} \ln L = \arg \max_{\sigma,\theta \in \Theta} p(\theta|y) \\
				&\text{subject to}
				& \dot{ x } = G({\color{black} x};\Theta(\theta)) \\
				&& \dot{\theta} = 0 \\
				&& y = y(t) \\
				&& \theta^{lb} \leq \theta \leq \theta^{ub}
			\end{aligned}
	\end{equation} }

	where $\hat{\theta}$ is as maximum likelihood estimator, $\theta^{lb}$ define the minimal value of $\theta$, $\theta^{ub}$ is the maximum value of $\theta$ and $\sigma$ represents the standard deviation of the residuals (errors) between the observed data points and the model outputs.

	The initial guess for each decision variable, as well as the lower and upper bounds are given in Table \ref{tab:Constraints}.

	\begin{table}[h]
		\centering
		\adjustbox{max width=\columnwidth}{%
			%\small{
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R\cdot10^{-13}$[$m^2/s$] 	& $\Upsilon$ [-] & $\sigma$		\\  \hline
				Lower bound		&0	  		& 0 	  							& 0 		  	 & 0			\\ 
				Upper bound		&$+\infty$	& $+\infty$ 						& $+\infty$		 & $+\infty$ 	\\ 
				Initial guesses	&0.1-10		& $0.1-10$ 							& 0.1-10    	 & 0.1-10		\\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

	%Based on the first order optimality condition, the $\ln L$ can be maximized with respect to the vector $\theta$ and equating to zero the partial derivatives of $\ln L$:

	%{\footnotesize
	%	\begin{align}\label{EQ: MLE_Basic_Solution}
	%		\cfrac{\partial \ln L}{\partial \theta} &= \cfrac{\partial \sum_{i=1}^{n} \ln p\left( y(t_i) | \theta \right) }{\partial \theta} = 0 
	%\end{align} }

	Solution of Equations \ref{EQ: Optimization_formulation_MLE} yield the desired estimates $\hat{\theta}$. For some models, these equations can be explicitly solved for $\hat{\theta}$ but in general, no closed-form solution to the maximization problem is known or available, and a maximum likelihood estimator can only be found via numerical optimization.

	%The decision variables are:

	%\begin{itemize}
	%	\item Partition coefficient:\qquad\quad\qquad$k_m$
	%	\item Internal diffusion coefficient: \quad$D_i^R$
	%	\item Axial diffusion coefficient: \qquad$D_e^M$
	%	\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
	%	%\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
	%\end{itemize}

	%To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced. The initial guess for each optimization, the lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.

\end{document}

### 2024-05-20 Sections/Porosity.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	To calculate the porosity of the solid particles $\phi$, we can use the following formula:

    {\footnotesize
        \begin{equation}
            \phi = \dfrac{\text{Volume with pores} - \text{Volume without pores}}{\text{Volume with pores}}
        \end{equation}
    }

    We can first calculate the volume, excluding the pore space, using the true density of the material:

    {\footnotesize
        \begin{equation}
            \text{Volume excluding pores} = \dfrac{\text{mass}}{\text{true density}} = \dfrac{1\ \text{kg}}{1256.58\ \text{kg/m}^3} 0.0007958\ \text{m}^3
        \end{equation}
    }

    We can then use the volume of the solid particles, including the pore space and the volume excluding the pore space, to calculate the porosity:

    {\footnotesize
        \begin{equation}
            \phi = \dfrac{\text{Volume with pores} - \text{Volume without pores}}{\text{Volume with pores}}   
        \end{equation}
    }

    Since 1 kg of solid particles occupies 1.6 L, which is equivalent to 0.0016 m³, we have:

    {\footnotesize
        \begin{equation}
            \phi = \dfrac{0.0016\ \text{m}^3 - 0.0007958\ \text{m}^3}{0.0016\ \text{m}^3} = 0.5026
        \end{equation}
    }

    Therefore, the porosity of the solid particles is 0.5026 or 50.26\%. This means that half of the total volume of the solid particles is made up of pore space.

\end{document}

### 2024-05-20 Sections/Qubic_EOS.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Thermodynamic_details}

	\subsubsection{Equation of state} \label{subsubsec: Equation of state}

	A cubic equation of state (EoS) serves as a mathematical model to describe the behavior of real gases and liquids through a third-degree polynomial equation that correlates the pressure, volume, and temperature of a substance. These equations constitute tools for comprehending the phase behavior, properties, and thermodynamic processes of actual substances, across various engineering and scientific applications. The cubic equation of state take into account deviations from ideal gas behavior, which are particularly important at high pressures and low temperatures, where real gases do not follow assumption of ideal gas.

	{\footnotesize
	\begin{equation}
		P = \frac{RT}{v_m-b} - \frac{\Phi}{v_m^2 - ubv_m + wb^2}
	\end{equation}
	}

	In this equation, $P$ denotes the pressure of the substance, $v_m$ represents the molar volume of the substance, $T$ stands for the absolute temperature of the substance, $u$ and $w$ are integers that vary from one equation to another, $R$ symbolizes the universal gas constant and $\omega$ denotes an acentric factor and $\Phi=a\alpha$.

	The Van der Waals constants, constitute empirical values contingent upon the particular substance being modeled. These constants factor in molecular interactions (represented by '$a$') and the finite size of gas molecules (indicated by '$b$').

	Several variations of the cubic equation of state exist, each with its own set of parameters and assumptions. Tables \ref{tab:Popular_Cubic_EoS} and \ref{tab:Popular_Cubic_EoS_alpha} show parameters for popular cubic EoS.

	\begin{table}[h!]
		\centering
		\adjustbox{width=\columnwidth}{%
			\begin{tabular}{|c| c c c c|} 
				\hline
				EoS & u & w & a & b\\
				\hline
				van der Waals  & 0 & 0 & $\frac{27}{64} \frac{R^2T_c^2}{P_c}$ & $\frac{RT_c}{8P_c}$ \\
				Redlich and Kwong & 1 & 0 & $0.42748 \frac{R^2T_c^{2.5}}{P_c}$ & $\frac{0.08664RT_c}{P_c}$ \\
				Soave & 1 & 0 & $0.42748 \frac{R^2T_c^2}{P_c}$ & $\frac{0.08664RT_c}{P_c}$ \\
				Peng and Robinson \cite{Peng1976} & 2 & -1 & $0.45724 \frac{R^2T_c^2}{P_c}$ & $\frac{0.07780T_c}{P_c}$\\
				\hline
		\end{tabular} }
		\caption{Parameters for Popular Cubic EoS}
		\label{tab:Popular_Cubic_EoS}
	\end{table}

	\begin{table}[h!]
		\centering
		\adjustbox{width=\columnwidth}{%
			\begin{tabular}{|c| c c|} 
				\hline
				EoS & $\alpha$ & f($\omega$)\\
				\hline
				van der Waals  & - & - \\
				Redlich and Kwong & $\frac{1}{\sqrt{T_r}}$ & - \\
				Soave & $\left[ 1 + f(\omega) \left( 1-\sqrt{T_r} \right) \right]^2$ & 0.48+1.574$\omega$-0.176$\omega^2$\\
				Peng and Robinson (\cite{Peng1976}) & $\left[ 1 + f(\omega) \left( 1-\sqrt{T_r} \right) \right]^2$ & 0.37464+1.54226$\omega$-0.26992$\omega^2$ \\
				\hline
		\end{tabular} }
		\caption{Parameters for Popular Cubic EoS}
		\label{tab:Popular_Cubic_EoS_alpha}
	\end{table}

	The general cubic equation of state can be represented as a polynomial, as indicated in Equation \ref{EQ:Compressibility_Polynomial}. In a one-phase region, the fluid is characterized by a single real root, corresponding to the gas, liquid, or supercritical phase. In the two-phase region, a gas-liquid mixture exists, and two roots are identified. The larger root corresponds to the gas phase, while the smaller root pertains to the liquid phase.

	{\footnotesize
		\begin{equation}
			\label{EQ:Compressibility_Polynomial}
			Z^3 - (1+B-uB)Z^2+(A+wB^2-uB-uB^2)Z - AB - wB^2 - wB^3 = 0
	\end{equation} }

	where $A=\frac{\Phi P}{R^2T^2}$ and $B=\frac{bP}{RT}$.

	If the Peng-Robinson equation of state (\citet{Peng1976}) is used, the polynomial equation becomes

	{\footnotesize
	\begin{equation}
		\label{EQ:Peng_Robinson_Polynomial}
		Z^3 - (1-B)Z^2+(A-2B-3B^2)Z -(AB-B^2-B^3) = 0
	\end{equation} }

	For an ideal gas, the compressibility factor is defined as $Z = 1$, but the deviation of Z needs to be consider for real-life cases. The value of $Z$ typically increases with pressure and decreases with temperature. At elevated pressures, molecules collide more frequently, allowing repulsive forces between molecules to influence the molar volume of the real gas ($v_m$) to surpass that of the corresponding ideal gas $\left( \left(v_m\right)_{ideal~gas} = \frac{RT}{P} \right)$, resulting in $Z$ exceeding one. At lower pressures, molecules move freely, with attractive forces predominating, leading to $Z < 1$.

	Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ at given temperature and pressure. Alternatively, the closed form solution can by obtained by Cardano formula ( Appendix \ref{CH: Cardano}).

	\subsubsection{Density of the fluid phase} \label{subsubsec: Fluid density}

	The density of the fluid can be calculated from the real gas equation $\rho = \frac{P}{RTZ} \frac{1}{m_{CO2}}$. The temperature can be obtain from the time evolution of governing equations, the pressure is consider to be constant along the system to be a know.

	\begin{comment}
	\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
	%	\noindent\textbf{Heat capacity of the fluid phase} \\

	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state,  under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}:

	{\footnotesize
	\begin{align}
		C_v &= C_v^{id} + C_v^R \\
		C_p &= C_p^{id} + C_p^R
	\end{align}}

	The ideal-gas contribution is found using heat-capacity data applicable to gases at very low pressures, which are available in many thermodynamics textbooks in the polynomial form, such as $C_p^{id}(T) = A + BT + CT^2 + DT^3$.

	where the coefficients of the expansion are ${\color{black}C_{P0}} = 22.26$, ${\color{black}C_{P1}} = 5.981 \times 10^{-2}$, ${\color{black}C_{P2}} = -3.501 \times 10^{-5}$, and ${\color{black}C_{P3}} = 7.469 \times 10^{-9}$, as given by \citet{Kyle1999}.

	The residual component of the specific heat can obtained from general relation between $C_v$ and $C_p$ as given by \citet{Poling2001}.

	{\footnotesize
	\begin{equation} \label{EQ:CP_residual}
		C_p^R = C_v^R + T\left(\frac{\partial P}{\partial T}\right)_{v_m} \left(\frac{\partial v_m}{\partial T}\right)_P - R
	\end{equation}}

	The effects of pressure and temperature for liquids are not great, but both $C_p$ and $C_v$ diverge at the critical point of a pure fluid. In the neighborhood of the critical, $\left(\frac{\partial P}{\partial v_m}\right)_T$ approaches zero, so $C_p$ increases much faster than $C_v$. At both high and low densities, the differences are small, but for $T_r$ near unity, they increase rapidly as the critical density is approached. At fixed density in this region, $C_p$ actually decreases as T increases.

	The term $\left(\frac{\partial P}{\partial T}\right)_{v_m}$ can be obtain by direct differentiation of P-R EoS

	{\footnotesize
	\begin{equation}
		\left(\frac{\partial P}{\partial T}\right)_{v_m} = \frac{R}{v_m - b} - \frac{\frac{d \Phi}{dT}}{\left[v_m(v_m+b)+b(v_m-b)\right]^2}
	\end{equation}}

	where $\left(\frac{\partial \Phi}{\partial T}\right)_{v_m} = \frac{-f(\omega)a}{\sqrt{TT_c}(1 + f(\omega)( 1 - \sqrt{T/T_c}))}$

	The term $\left(\frac{\partial v_m}{\partial T}\right)_P = \frac{R}{P} \left(T \left(\frac{\partial Z}{\partial T}\right)_P + Z \right)$

	The term $\left(\frac{\partial Z}{\partial T}\right)_P$ can be defined as below

	{\footnotesize
	\begin{equation}
		\left(\frac{\partial Z}{\partial T}\right)_P = \frac{ \left(\frac{\partial A}{\partial T}\right)_P (B-Z) + \left( \frac{\partial B}{\partial T} \right)_P \left( 6BZ+2Z-3B^2-2B+A-Z^2 \right)}{3Z^2 + 2(B-1)Z + (A-2B-3B^2)}
	\end{equation}}

	{\footnotesize
	\begin{align}
		\left(\frac{\partial A}{\partial T}\right)_P &= (P/(RT)^2)(\frac{d \Phi}{dT} - 2a/T) \\
		\left(\frac{\partial B}{\partial T}\right)_P &= -bP/(RT^2)
	\end{align}}

	The first component of Equation \ref{EQ:CP_residual} from definition of $C_v = \left(\frac{\partial U^R}{\partial T}\right)_{v_m}$, where $U^R$ represents internal energy. In case of Pen-Robinson $U^R$ equals to

	{\footnotesize
	\begin{equation}
		U^R = \frac{T \frac{d^2 \Phi}{dT^2}}{b \sqrt{8}} \ln \left( \frac{Z+B\left(1+\sqrt{2}\right)}{Z+B\left(1-\sqrt{2}\right)} \right)
	\end{equation}}

	As given by \citet{Pratt2001}, for Peng-Robinson EoS the term $\frac{d^2 \Phi}{dT^2}$ is defined as follow

	{\footnotesize
	\begin{equation}
		\frac{d^2\Phi}{dT^2} = \frac{af(\omega)\sqrt{\frac{T_c}{T}} \left( 1+ f\left(\omega\right) \right)}{2TT_c}
	\end{equation} }

	\subsubsection{Departure functions for enthalpy calculations} \label{CH:Enthalpy}

	In thermodynamics, a departure function is a concept used to calculate the difference between a real fluid's thermodynamic properties (enthalpy, entropy, or internal energy) and those of an ideal gas, given a specific temperature and pressure. These functions are used to calculate extensive properties, which are properties computed as a difference between two states.

	To evaluate the enthalpy change between two points, $h(V_1,T_1)$ and $h(V_2,T_2)$, the enthalpy departure function between the initial volume $V_1$ and infinite volume at temperature $T_1$ is calculated. Then it is added to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, and finally subtract the departure function value between the final volume $V_2$ and infinite volume.

	Departure functions are computed by integrating a function that depends on an equation of state and its derivative. The general form of the enthalpy equation is given by:

	{\footnotesize
		\begin{equation}
			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left(T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right){\frac{dv_m}{v_m}} + 1-Z
		\end{equation}
	}

	Here, $h^{id}$ represents the enthalpy of an ideal gas, $h$ is the enthalpy of a real fluid, $R$ is the universal gas constant, $T$ is temperature, $v_m$ is the molar volume, and $Z$ is the compressibility factor.

	The integral in the equation is evaluated over the range of molar volumes from $v_m$ to infinity. The integral includes a term that depends on the derivative of the compressibility factor with respect to temperature, evaluated at the molar volume $v_m$. Finally, the term $1-Z$ is added to account for the deviation of the fluid's properties from an ideal state.

	The Peng–Robinson EoS relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $v_m$. From the state properties ($P$, $v_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:

	{\footnotesize
		\begin{equation}
			h-h^{\mathrm {id} }=RT_c\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
		\end{equation}
	}

	\end{comment}

\end{document}

### 2024-05-20 Sections/Results.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	 %and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.

	 The parameter estimation problem was solved by fitting the process model to the dataset given in the Figure \ref{fig: estimation_results}. Each time-series was fitted to the model separately. The blue dots indicate the data point obtained as a measurement from the laboratory experiments. The black curve represents the yield curve obtained from the initial guess of the parameters. The red curve correspond to yield curve obtained as a solution of the optimization problem. Every sub-figure is made of two figure of which one represent the cumulative yield, and the second one shows the derivative of the cumulative yield. As explained in Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
	 The parameters obtained from solving the optimization problem can be found in Table \ref{tab: Estimation_results}.

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
			\csvautobooktabular[separator=comma, table head = \toprule & $40~^\circ C$ & $50~^\circ C$ & $40~^\circ C$ & $50~^\circ C$ \\ & $200~bar$ & $200~bar$ & $300~bar$ & $300~bar$ \\\midrule]{Figures/Results_estimation/estimation.csv} }
		\caption{Parameter estimation results}
		\label{tab: Estimation_results}
	\end{table}

	As shown in the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors ${\color{black}k_m}$ at relatively high levels. Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of the concentration gradient

	{\footnotesize
	\begin{equation*}
		\begin{split}
			&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right)  = \\
			&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{\infty{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}  {\color{black}c_f}(t,z) \right) = \left({\color{black}{\color{black} c_s} }(t,z) - 0 \right)
		\end{split}
	\end{equation*} }

	Values of the reference internal diffusion coefficients are distinguished for each experiment. The order of magnitude of ${\color{black}D_i^R}$ obtained from the optimization is similar to values found by other researchers. \citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported ${\color{black}D_i^R} \approx 6\cdot 10^{-13}[m^2/s]$. Figure \ref{fig: results_DI} represent the ${\color{black}D_i^R}$ as the function of density. As the reference internal diffusion coefficient describes the diffusion inside of a particle, it is independent of external factors such as a fluid velocity around that particle. The reference internal diffusion depends only on local conditions given by temperature and pressure, which defines the physical properties of a stagnant fluid inside of pores of a particle—considering that the reference internal diffusion can be represented as a function of the density of the fluid, which is uniquely defined at a given temperature and pressure in the one-phase region. The linear trend in Figure \ref{fig: results_DI} suggests that ${\color{black}D_i^R}$ increases with fluid density.

	Similarly to the internal diffusion coefficient, the obtained values of ${\color{black}\Upsilon}$ depends only on temperature and pressure, or by uniquely defined physical properties such as density. Figure \ref{fig: results_upsilon} shows that of ${\color{black}\Upsilon}$ grows with density. This can be explained if the solubility increases as the density grows. \citet{Shojaie2010}, showed that the solubility of carvone (one of the main components of caraway oil) rises together with pressure increase and decreases when temperature increases.

	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{black}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions. The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and steeper curvature of ${\color{black}D_i}$ function.

		\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 10.5cm 14.0cm 10.0cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{Dependency of ${\color{black}D_i}$}
			\label{fig: results_DI}
		\end{subfigure}
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 3.0cm 7.9cm 17.7cm 7.7cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{Dependency of ${\color{black}\Upsilon}$}
			\label{fig: results_upsilon}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\columnwidth}
			\includegraphics[trim = 1.0cm 0cm 2.0cm 0cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
			\caption{Dependency of ${\color{black}D^R_i}$}
			\label{fig:Di_upsilon_res}
		\end{subfigure}
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 18.0cm 14.0cm 2.5cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{Dependency of ${\color{black}D^M_e}$}
			\label{fig: results_De}
		\end{subfigure}
		\caption{Results of parameter estimation}
		\label{fig: estimation_results_DI_GAMMA}
	\end{figure}

	The axial diffusion coefficient obtained from the optimizer is relatively high compared to the internal diffusion coefficients. The values of ${\color{black}D_e^M}$ have a similar order of magnitude as reported in the literature (\citet{ReisVasco2000}).
	The axial diffusion can be further analyzed by defining the Peclet number $\left( {\color{black}Pe} = \frac{v d_p}{D_e^M} \right)$ and the Reynolds number $\left( {\color{black}Re} = \frac{v d_p}{\mu} \right)$, where ${\color{black}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity.
	The obtained Pecelt numbers are ${\color{black}Pe} \gg 1$, which suggests that mass diffusion is negligible and advection dominates mass transport. The experiment was performed in the laminar region and narrow Reynolds number range. Moreover, the volumetric flow-rate was kept constant during all experiments, so the changes in the Reynolds number are related to changes of $CO_2$ properties at different operating conditions. As the result, the Figure \ref{fig: results_De} shows a simplified relationship of axial diffusion as a function of density only. The plot show a decrease of the axial diffusion coefficient as the density increase. That behaviour can be explained by higher resistance of the mass transfer caused by denser fluids.

	%\citet{Chung1968} presented an idea for a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers. By modifying the idea of \citet{Chung1968}, a direct relation between the diffusion coefficient and the Reynolds number is used in the work as shown in Figure \ref{fig: results_De}. The obtained values of the mass diffusion coefficient increase almost linearly with the increment of the Reynolds number, which is in agreement with the observation that the advection dominates the diffusion.

	As the total amount of oil present in the system is unknown, and as such, it has been obtained from the optimizer. Given the dataset and the process model, the optimizer found that the best fit is obtained if the total mass of the oil reaches a lower bound equal to 80 g. The lower bound was estimated by rounding up the biggest value of the collected cumulative amount of the extraction product. As the same raw material was used in all experiments, the same initial amount of solute was assumed for all the cases.

	The initial state estimation resulted in values of $\tau$ in the range from 0.69 to 0.76. In the equipment used in this experiment, around 25\%-30\% of the solute was extracted to the fluid phase during the preparation period.

	The noise present in each dataset is quantified by the parameter $\sigma^2$. It can be observed dataset obtained at $40~^\circ C$ / 200 bar and $30~^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$. The slightly better results were obtained for the experiment at $50~^\circ C$ / 300 bar when $\sigma^2\approx0.05$. The noisiest dataset corresponds to $50~^\circ C$ / 200 bar when $\sigma^2\approx0.12$. All values of $\sigma^2$ are relatively low, suggesting the mathematical model can mimic the physical system.

	%The results obtained from the parameter estimation are used to develop a generalized process model. The model generalization is performed by introducing correlations which link the estimated parameters and the operating conditions. Since the experiments were performed under varying temperature and pressure, the influence of these variables is taken into account. To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure. Since the optimizer found that ${\color{black}k_m}$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.

%	\begin{figure}[!h]
%		\centering
%		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
%		\caption{Second-order polynomial regression of fitted parameters (${\color{black}D_i^R}$ and ${\color{black}D_e^M}$) as a function of fluid density $\rho_f$}
%		\label{fig:Regression_2}
%	\end{figure}

\end{document}

### 2024-05-20 Sections/Results_Chamomile.tex
20.05

\documentclass[../Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	To solve the parameter estimation problem, the single shooting method was used to transform the boundary-value problem into the initial value problem and to formulate the non-linear programming problem. This non-linear optimisation task was tackled using the CasADi framework (\citet{Andersson2018}). Each time series was fitted separately to the model with the linear extraction kinetics (Equation \ref{Model_kinetic_no_sat}). The parameter estimation problem was solved multiple times with varying parameter initial values to identify the global minimum. In the case of linear, two parameters remain to be determined: the partition coefficient $k_m$ and the internal diffusion coefficient $D_i$. \citet{Rahimi2011} analysed the same dataset and reported Peclet numbers between 290 and 400. Large Peclet number suggests that the advection term dominates the mass transfer, and the axial diffusion is negligible, which is one of the modelling assumptions.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_Space_Linear_Dataset_1.png}
			\caption{The linear kinetic model \\ ~}
			\label{fig: Fit_1_linear}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Parameter_space_Di_Gamma_dataset_1_org.png}
			\caption{The modified model}
			\label{fig: Fit_1_Di_Gamma}
		\end{subfigure}
		\caption{Parameter space for experiment 1}
		%\label{fig: Fit_Di_Gamma}
	\end{figure}

	Figure \ref{fig: Fit_1_linear} shows the parameter space and corresponding values of the cost function for experiment 1 ($40^\circ C$, 100 bar and 6.67$\cdot 10^{-5}$ kg/s). A black-coloured section, in the shape of a vertical stripe at $D_i \approx 0.2$, indicates the minimum values of the cost function $-\ln(L)$. In the direction of $k_m$, the cost function is almost flat, which suggests that any value of $k_m$ above 0.1 fits the data equally well. If $k_m$ can be an arbitrary point, then it can grow to infinity, which suggests that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of $k_m$:

	{\footnotesize
		\begin{equation*}
			\begin{split}
				&\lim_{k_m \rightarrow \infty} \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{{\color{black}\rho_s}}{{\color{black}k_m}(T(t,z)){\color{black}\rho}(T(t,z),{\color{black}P}(t))}  c_f \right)  = \\
				&= \left({\color{black}{\color{black} c_s} }(t,z)  - \cfrac{\rho_s}{\infty \cdot \rho(T(t,z),P(t))}  {c_f}(t,z) \right) = \left(c_s(t,z) - 0 \right)
			\end{split}
	\end{equation*} }

	In the scenario previously discussed, the fitting outcomes were not deemed satisfactory. Building upon the concepts underlying the Broken-and-Intact and Shrinking Core models (detailed in Chapter \ref{CH: Gamma_Function}), the $\gamma$-function is introduced to capture the decreasing extraction kinetics. The correction factor is combined with the simplified linear model, resulting in a two-parameter model ($D_i^R$ and $\Upsilon$) as given by Equation \ref{Model_kinetic}. Figure \ref{fig: Fit_1_Di_Gamma} shows the parameter space and the corresponding cost function values.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4_1.png}
			\caption{Parameter estimation results at $6.67\cdot 10^{-5}$ kg/s and temperature of 40 $^\circ C$}
			\label{fig: Fit_1_4_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8_1.png}
			\caption{Parameter estimation results at $6.67\cdot 10^{-5}$ kg/s and temperature of 30 $^\circ C$}
			\label{fig: Fit_5_8_Di_Gamma}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12_1.png}
			\caption{Results of parameter estimation for experiments at $3.33\cdot 10^{-5}$ kg/s}
			\label{fig: Fit_9_12_Di_Gamma}
		\end{subfigure}
		\caption{Parameter estimation results obtained from the modified model}
		\label{fig: Fit_Di_Gamma}
	\end{figure}

	The parameter space for the modified model exhibits a distinct minimum value corresponding to the solution of the parameter estimation problem for experiment 1. The red circle highlights the minimum value of the cost function found by the optimizer. The remaining experiments are fitted to the modified extraction model, and results, presented in Figure \ref{fig: Fit_Di_Gamma}, show good agreement with experimental data.

	The parameter estimation results are combined to analyse the relationship between the obtained parameters and the operating conditions. Unlike traditional methods that employ a combination of Reynolds, Schmidt, and Sherwood numbers to find correlation, the approach in this study leverages the fixed-bed Reynolds number $\left(Re = \frac{2r \cdot \rho_f \cdot u}{\mu}\right)$ as the sole independent variable. Using the Reynolds number has the advantage of considering the influence of all the control variables (temperature, pressure and flow rate), which means it can be uniquely defined by selecting operating conditions.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Di_Re_1.png}
			\caption{Linear regression $D_i^R = f(Re)$}
			\label{fig: Correlations_Di_Re}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Correlation_Gamma_Re_1.png}
			\caption{Linear regression $\Upsilon = f(Re)$}
			\label{fig: Correlations_Gamma_Re}
		\end{subfigure}
		\caption{Linear correlations between parameters}
		%\label{fig: Correlations_surface}
	\end{figure}

	In Figures \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re}, two distinct data clusters emerge, each corresponding to a different mass flow rate. Despite the linear trends observed in both sets of correlations, the correlations for $D_i^R$ exhibit a decline with increasing $Re$, whereas those for $\Upsilon$ show an upward trend with $Re$. The decrease in $D_i^R$ across each data line can be attributed to higher fluid density and increased mass transfer resistance.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Di_Re_F_1.png}
			\caption{Multiple linear regression $D_i^R = f(Re, F)$}
			\label{fig: Correlations_Di_Re_F}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Gamma_Re_F_1.png}
			\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
			\label{fig: Correlations_Gamma_Re_F}
		\end{subfigure}
		\caption{Empirical correlations between parameters}
		%\label{fig: Correlations_surface}
	\end{figure}

	A more general relationship can be obtained by applying multiple linear regression instead of linear regression. The data clusters in Figure \ref{fig: Correlations_Di_Re} and \ref{fig: Correlations_Gamma_Re} are close to parallel, suggesting that a plane would combine all the data points. The Reynolds number and mass flow rate act as independent variables for $D_i^R$ and $\Upsilon$ as presented in Figures \ref{fig: Correlations_Di_Re_F} and \ref{fig: Correlations_Gamma_Re_F}. The presented correlations are valid in the whole range of investigated operating conditions. The correlations are later tested against the original dataset to show that the correlations can reproduce the results with satisfactory accuracy. Figure \ref{fig: Fit_Di_Gamma_correlation} shows the results of the simulations with incorporated correlations. A good agreement between simulation results and the dataset can be observed. If Figures \ref{fig: Fit_Di_Gamma} and \ref{fig: Fit_Di_Gamma_correlation} are compared, a decrease in the accuracy of simulations can be observed. Such behaviour is expected due to the bias-variance trade-off, which describes the relationship between a model's complexity and the accuracy of its predictions.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_1_4_correlation_1.png}
			\caption{Simulation results obtained at $6.67\cdot 10^{-5}$ kg/s and temperature of 40 $^\circ C$}
			\label{fig: Fit_1_4_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_5_8_correlation_1.png}
			\caption{Simulation results obtained at $6.67\cdot 10^{-5}$ kg/s and temperature of 30 $^\circ C$}
			\label{fig: Fit_5_8_Di_Gamma_correlation}
		\end{subfigure}
		\hfill
		\begin{subfigure}{0.9\columnwidth}
			\centering
			\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip, width=\columnwidth]{/Results_estimation/Fit_Di_Gamma_9_12_correlation_1.png}
			\caption{Simulation results obtained at $3.33 \cdot 10^{-5}$ kg/s}
			\label{fig: Fit_9_12_Di_Gamma_correlation}
		\end{subfigure}
		\caption{Simulation results from the modified model and correlations}
		\label{fig: Fit_Di_Gamma_correlation}
	\end{figure}

	The parameter estimation results are compared against those presented by \citet{Povh2001}, who applied the Sovova model to the same dataset. It is important to note that \citet{Povh2001} use as the initial solute mass ratio a value of 10\% above the total amount of extract for every experiment, while in this work, the initial conditions are the same for all the experiments. In contrast to this work, \citet{Povh2001} did not utilise numerical solvers but used a mix of analytical methodologies and trial-and-error procedures. \citet{Povh2001} remarked that 'the direct fitting of experimental data to Sovova's model produced parameters that could not be accepted after a careful physical interpretation of the system'. The parameters identified in this study have a physical interpretation and are within the expected range.

	\citet{Rahimi2011} analysed the same dataset using the desorption–dissolution–diffusion model. To decrease the number of unknown parameters, \citet{Rahimi2011} applied a set of empirical correlations. The remaining parameters were determined using a genetic algorithm to solve the parameter estimation problem for each experiment individually. Results obtained by \citet{Rahimi2011} show that the desorption–dissolution–diffusion model fails to reproduce the yield data. The main difference between the model employed by \citet{Rahimi2011} and the one in this study is the $\gamma$-function. The $\gamma$-function increases the model's flexibility by adjusting $D_i$ and allows it to obtain a better fit.

	\citet{Povh2001} and \citet{Rahimi2011} delivered a set of independent parameters for every experiment. This work combines the parameters obtained from each experiment to get a single correlation valid for the whole range of investigated operating conditions.

\end{document}

### 2024-05-20 Sections/Saturation.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsubsection{Uneven solute's distribution in the solid phase} \label{CH: Gamma_Function}

	Following the idea of the Broken-and-Intact Cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is consider to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}.

	{\footnotesize
		\begin{equation}
			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right) \label{EQ: C_sat_function}
		\end{equation} }

	where the ${\color{black}\Upsilon}$ describe the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term

	{\footnotesize
		\begin{equation}
			\label{Model_kinetic}
				r_e = -\cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
		\end{equation} }

	The $\gamma$-function limits the solute's availability in the solid phase. Similarly to the BIC model, the solute is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact. The diffusion of the solute from a particle's core takes more time than the diffusion of the solute close to the outer surface. The same idea can be represented by the decaying internal diffusion coefficient, where the decreasing term is a function of the solute concentration in the solid.

	Alternatively, the decay function $\gamma$ can be consider with respect to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius change as the amount of solute in the solid phase decrease. As the particle size decreases due to dissolution, the diffusion path increases, which makes the diffusion slower and reduces the value of a diffusion coefficient. This analogy can be applied to the Equation \ref{EQ: C_sat_function} to justify the application of varying diffusion coefficient.

\end{document}

### 2024-05-20 Sections/Thermo_imp.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	A supercritical fluid (SCF) is a substance at a temperature and pressure above its critical point, where there are no distinct liquid and gas phases but below the pressure required to compress it into a solid. SCFs can move through porous solids like gases, which is faster than liquid transport through such materials. SCFs have a higher ability to dissolve materials like liquids or solids compared to gases. Near the critical point, small changes in pressure or temperature result in significant changes in density, allowing many properties of an SCF to be fine-tuned. By changing the pressure and temperature, the properties of carbon dioxide can be tuned to be more liquid-like or gas-like.

	Fluid properties can be divided into two kinds: equilibrium properties and transport properties. The equation of state can be used accurately to predict the equilibrium properties, such as fluid density, enthalpy, vapour pressure, fugacity and fugacity coefficient, vapour-liquid equilibrium, and all kinds of excess properties.

	Supercritical $CO_2$'s thermodynamic properties, such as density or specific heat capacity, vary significantly with slight changes in temperature and pressure due to real gas effects. The Peng-Robinson equation of state (P-R EOS) is used to calculate the thermodynamic properties by accounting for these real gas effects are presented in Appendix \ref{subsubsec: Equation of state}. The P-R EOS belongs to a specific class of thermodynamic models for modelling the pressure of a solvent as a function of temperature and density and which can be rewritten as a cubic function of the molar volume.

	To determine the thermodynamic properties of a real gas, it is necessary to evaluate the departure function of the chosen equation of state for that property. As explained by \citet{Elliott2011}, the departure function describe the difference between the actual value of a thermodynamic property of a real gas and its value if the gas were ideal under the same temperature and pressure conditions. The ideal gas serves as a reference state to which the properties of real gases are compared. The departure function measures the extent to which a real gas deviates from ideal gas behaviour. The departure functions allow for the accurate calculation of thermodynamic properties for real gases. %(10.1007/s10494-017-9872-4)

	The properties of $CO_2$ are presented as a function of operating conditions (temperature and pressure) in Figure \ref{fig: SFE_Properties}. At standard atmospheric pressure and temperature, $CO_2$  behaves as an ideal gas, and its compressibility factor equals unity. However, at high pressures and/or low temperatures, intermolecular forces between gas molecules become more significant, causing them to deviate from ideal behaviour. As a result, the compressibility factor can be greater than or less than unity, depending on the magnitude of these forces. As presented in Figure \ref{fig: SFE_Properties_Compressibility}, the compressibility factor obtained from the Peng-Robinson equation of state varies strongly depending on the operating conditions.

	The real gas effects are also visible on the density plot presented in Figure \ref{fig: SFE_Properties_Density}. The density calculations are based on the compressibility factor, and its value depends on the operating conditions. The fluid properties near the critical point are unique and combine gas-like and liquid-like properties. The details of calculations are explained in Appendix \ref{subsubsec: Fluid density}.

	Figure \ref{fig: SFE_Properties_CP} show the behaviour of the heat capacity of a supercritical fluid at constant pressure ($C_p$). The details of the calculations can be found in Appendix \ref{subsubsec: Fluid heat capacity}. Contrary to the density, which varies monotonically, the specific heat shows very high levels in a narrow region. In the subcritical region, the phase transition is associated with an effective spike in the heat capacity (i.e., the latent heat). Approaching the critical point, the latent heat falls to zero, which is accompanied by a gradual rise in heat capacity in the pure phases near phase transition. At the critical point, the latent heat is zero, but the heat capacity shows a diverging singularity. Beyond the critical point, there is no divergence, but rather a peak in the heat capacity; the highest point of this peak identifies the Widom line (as discussed by \citet{Simeoni2010} and \citet{Banuti2019}).

	Figure \ref{fig: SFE_Properties_h} represent how the specific enthalpy change with the operating conditions. The details of calculations are discussed in Appendix \ref{CH:Enthalpy}.

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{Compressibility factor}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{Density}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{Specific heat}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
			\caption{Enthalpy}
			\label{fig: SFE_Properties_h}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/MU.pdf}
			\caption{Viscosity}
			\label{fig: SFE_Properties_Viscosity}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/KT.pdf}	
			\caption{Thermal conductivity}
			\label{fig: SFE_Properties_Thermal}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state and correlations}
		\label{fig: SFE_Properties}
	\end{figure*}

	%Transport properties such as viscosity and conductivity play a crucial role in engineering design for production, fluid transportation, and processing. However, as highlighted by \citet{Sheng1989}, developing a satisfactory theory for transport properties of real dense gases and liquids is a challenging task. This is due to the inherent difficulties involved in accurate measurements and the complexity involved in theoretical treatments.

	%To address this issue, the correlations of transport coefficients are either empirical or based on some theoretical foundation. Chapman-Enskog's theory (presented in \citet{Chapman1991}) for transport properties of dense gases based on the distribution function is a popular theoretical approach. However, the Chapman-Enskog theory was developed for rigid spherical molecules and modifications are required to apply it to real gases. Many correlations have been proposed following the Chapman-Enskog theory in the form of reduced density and reduced temperature, such as those developed by \citet{Fenghour1998}, and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST). The correlation of \citet{Laesecke2017} is presented in Figure \ref{fig: SFE_Properties_Viscosity}.

	%NIST has developed a viscosity formulation consisting of four contributions: (i) for the limit of zero density, (ii) for the initial density dependence, (iii) for the residual viscosity, and (iv) for the singularity of the viscosity at the critical point. The NIST correlation covers temperatures from 100 to 2000 K for gaseous $CO_2$, and from 220 to 700 K with pressures along the melting line up to 8000 MPa for compressed and supercritical liquid states. These correlations and theories are essential in predicting transport properties for real gases and liquids and can assist in engineering design and analysis.

	Transport properties, including viscosity and thermal conductivity, are fundamental to the engineering design process for production, fluid transport, and processing operations. However, as \citet{Sheng1989} notes, formulating a comprehensive theory for the transport properties of real dense gases and liquids remains a formidable challenge. This difficulty stems from the obstacles in making precise measurements and the complexities of theoretical analysis.

	To tackle these challenges, the correlations used to estimate transport coefficients are typically empirical or rooted in theoretical principles. A well-regarded theoretical framework is the Chapman-Enskog theory, as discussed in \citet{Chapman1991}, which addresses the transport properties of dense gases using the distribution function. Originally designed for rigid spherical molecules, the Chapman-Enskog theory requires adaptations to be applicable to real gases. Following this theoretical approach, numerous correlations have been proposed, such as those by \citet{Fenghour1998}, and \citet{Laesecke2017} from the National Institute of Standards and Technology (NIST), which utilize reduced density and temperature. The viscosity correlation from \citet{Laesecke2017} is detailed in Figure \ref{fig: SFE_Properties_Viscosity}.

	NIST has formulated a viscosity model that comprises four distinct components: (i) the zero-density limit, (ii) the initial density dependence, (iii) the residual viscosity, and (iv) the critical point viscosity singularity. This NIST viscosity correlation spans temperatures from 100 to 2000 K for gaseous $CO_2$, and from 220 to 700 K under pressures up to 8000 MPa along the melting line for both compressed and supercritical liquid states. Such correlations and theoretical models are invaluable for accurately predicting the transport properties of real gases and liquids, thereby facilitating engineering design and analytical processes.

%	Similarly, several correlations for thermal conductivity of $CO_2$ were compared in Figure \ref{fig: SFE_Properties_Thermal}. The presented figures show regions around the critical point where the singularity is present. Similarities between specific heat and thermal conductivity can be observed. The NIST correlation (\citet{Huber2016}) captures the singular behaviour of thermal conductivity around the critical point. The correlations are applicable for the temperature range from the triple point to 1100 $K$ and pressures up to 200 $MPa$.

	Similarly, NIST has formulated a correlation that characterizes the thermal diffusivity behavior of carbon dioxide ($CO_2$). The study by \citet{Huber2016} highlights the unique behavior of thermal conductivity in the vicinity of the critical point. This correlation is valid for temperatures spanning from the triple point to 1100 K and for pressures reaching up to 200 MPa. Figure \ref{fig: SFE_Properties_Thermal} illustrates the variation in thermal conductivity of carbon dioxide under different operating conditions, demonstrating how it adapts to changes in temperature and pressure.

\end{document}

### 2024-05-20 Sections/introduction_imp.tex
20.05

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process. Chamomile is a medicinal herb widely cultivated in southern and eastern Europe—such as Germany, Hungary, France, and Russia. It can be found outside of Europe in Brazil as discussed by \citet{Singh2011}. This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets. Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy. Chamomile's aqueous extract is widely used to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}. \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg. The highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine. In comparison, chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.

	Evaluating the economic viability of the process is essential when choosing the suitable technology for essential oil extraction. Traditional methods, such as distillation and organic solvent extraction, are commonly employed but come with drawbacks. Distillation, for example, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds. This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction. Supercritical carbon dioxide is appealing due to its distinctive properties: it is inflammable, non-toxic, and non-corrosive. Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.

	The literature offers various mathematical models to describe the extraction of valuable compounds from biomass. Selecting a process model is case-to-case dependent and requires analysing each model's specific assumptions about mass transfer and thermodynamic equilibrium.

	The model proposed by \citet{Reverchon1993} is called the hot ball model, as it is based on an analogy to heat transfer and describes an extraction process from solid particles. This model assumes that particles contain low quantities of solute and that solubility is not a limiting factor.

	The Broken-and-Intact Cell model, proposed by \citet{Sovova1994}, assumes that external surfaces of particles are mechanically disrupted, allowing the solvent's access to the solute in broken cells. In contrast, the solute in intact cells remains less accessible due to higher mass transfer resistance.

	\citet{Reverchon1996} formulated a fluid-solid extraction model where the solute is treated as a single component, governed by internal mass transfer resistance and omitting the effects of external mass transfer, axial dispersion, and variations in fluid density and flow rate throughout the bed.

	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process. This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel. The process involves supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract. Parameters such as the pressure ($P$), feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored. Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.

	\begin{figure}[h!]
		\centering
		\includegraphics[width=\columnwidth]{Figures/PFD.drawio.pdf}
		\caption{Process flow diagram}
		\label{fig: SFE_drawing}
	\end{figure}

	This study focuses on finding a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$. The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions. The maximum likelihood estimation is employed to solve the parameter estimation problem. Later, the correlations between parameters and operating conditions are proposed.

\end{document}

### 2024-05-20 Short_no_axDiff_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
20.05

% ---------------------------------------------------------------
% Preamble
% ---------------------------------------------------------------
%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
\documentclass[a4paper,fleqn]{cas-dc}
%\documentclass[a4paper]{cas-dc}
%\documentclass[a4paper]{cas-sc}
% ---------------------------------------------------------------
% Make margins bigger to fit annotations. Use 1, 2 and 3. TO be removed later
%\paperwidth=\dimexpr \paperwidth + 6cm\relax
%\oddsidemargin=\dimexpr\oddsidemargin + 3cm\relax
%\evensidemargin=\dimexpr\evensidemargin + 3cm\relax
%\marginparwidth=\dimexpr \marginparwidth + 3cm\relax
% -------------------------------------------------------------------- 
% Packages
% --------------------------------------------------------------------
% Figure packages
\usepackage{graphicx}
\usepackage{float}
\restylefloat{table}
\usepackage{adjustbox}
% Text, input, formatting, and language-related packages
\usepackage[T1]{fontenc}
\usepackage{subcaption}

\usepackage{csvsimple}

% TODO package
\usepackage[bordercolor=gray!20,backgroundcolor=blue!10,linecolor=black,textsize=footnotesize,textwidth=1in]{todonotes}
\setlength{\marginparwidth}{1in}
% \usepackage[utf8]{inputenc}
% \usepackage[nomath]{lmodern}

% Margin and formatting specifications
%\usepackage[authoryear]{natbib}
\usepackage[sort]{natbib}
\setcitestyle{square,numbers}

 %\bibliographystyle{cas-model2-names}

\usepackage{setspace}
\usepackage{subfiles} % Best loaded last in the preamble

% \usepackage[authoryear,longnamesfirst]{natbib}

% Math packages
\usepackage{amsmath, amsthm, amssymb, amsfonts, bm, nccmath, mathdots, mathtools, bigints, ulem}

\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{shapes.geometric,angles,quotes,calc}

\usepackage{placeins}

\usepackage[final]{pdfpages}

\usepackage{numprint}

% --------------------------------------------------------------------
% Packages Configurations
\usepackage{enumitem}
% --------------------------------------------------------------------
% (General) General configurations and fixes
\AtBeginDocument{\setlength{\FullWidth}{\textwidth}}	% Solves els-cas caption positioning issue
\setlength{\parindent}{20pt}
%\doublespacing
% --------------------------------------------------------------------
% Other Definitions
% --------------------------------------------------------------------
\graphicspath{{Figures/}}
% --------------------------------------------------------------------
% Environments
% --------------------------------------------------------------------
% ...

% --------------------------------------------------------------------
% Commands
% --------------------------------------------------------------------

% ==============================================================
% ========================== DOCUMENT ==========================
% ==============================================================
\begin{document} 
%  --------------------------------------------------------------------

% ===================================================
% METADATA
% ===================================================
\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation}                      
\shorttitle{Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation}

\shortauthors{OS, PO}

\author[1]{Oliwer Sliczniuk}[orcid=0000-0003-2593-5956]
\ead{oliwer.sliczniuk@aalto.fi}
\cormark[1]
\credit{a}

\author[1]{Pekka Oinas}[orcid=0000-0002-0183-5558]
\credit{b}

\address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
%\address[2]{2}

\cortext[cor1]{Corresponding author}

% ===================================================
% ABSTRACT
% ===================================================
\begin{abstract}
This study investigates the supercritical extraction process of essential oil from chamomile flowers. Essential oils of chamomile are used extensively for medicinal purposes. Many different chamomile products have been developed, the most popular of which is herbal tea. In this study, a mathematical model describing the governing mass transfer phenomena in solid-fluid environment at supercritical conditions using carbon dioxide is formulated. The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions. The flow of carbon dioxide is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor. The physical properties of the solvent are estimated based on the Peng-Robinson equation of state. Model parameters, including the partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors. A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.

%A distributed-parameter model describes the fluid-solid extraction process.

\end{abstract}

\begin{keywords}
Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
\end{keywords}

% ===================================================
% TITLE
% ===================================================
\maketitle

% ===================================================
% Section: Introduction
% ===================================================\section{Introduction}

\section{Introduction}
\subfile{Sections/introduction_imp}

\section{Materials and methods} \label{CH: Materials and methods}

%\subsection{Supercritical fluids} \label{CH: Thermodynamic}
%\subfile{Sections/Thermo_imp}

\subsection{Governing equations} \label{CH:Governing_equations_chapter}
	Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived. Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any given cross-section. This simplification is typically applied in situations where the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor. According to this assumption, velocity and other flow properties change solely in the flow direction.

	As discussed by \citet{Anderson2023}, all flows are compressible but some of them can be treated as incompressible when the Mach number is smaller than 0.3. This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The restraint allows for the removal of acoustic waves, and allows for large perturbations in density and/or temperature. In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.

	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.

{\footnotesize
	\begin{align}
		\label{EQ: CompressibleEuler_1}
		\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)   
		\label{EQ: CompressibleEuler_3}
	\end{align}  
}

where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.

\begin{comment}
Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed. The analysis follows the work of \citet{Schreier1982}.

\begin{figure}[!h]
	\centering
	\resizebox{0.95\columnwidth}{!}{%
		\begin{tikzpicture}[]
			\draw (0,2) -- (9,2);	% Top line
			\draw (0,0) -- (9,0); 	% Bottom line
			\draw (4.5,0) -- (4.5,2); 	% Bottom line
			\node at (4,1.5) {$\rho_f$};
			\node at (5.5,1.5) {$\rho_f+\delta\rho_f$};
			\node at (4,1.0) {$P$};
			\node at (5.5,1.0) {$P+\delta P$};
			\node at (4,0.5) {$T$};
			\node at (5.5,0.5) {$T+\delta T$};
			\node at (1,1.0) {$v \rightarrow$};
			\node at (8,1.0) {$v + \delta v \rightarrow$};
	\end{tikzpicture} }
	\caption{Small discontinuity in one-dimensional flow}
	\label{fig: Discontinuity_slow_flow}
\end{figure}

The discontinuity is presumed to be at rest relative, and the balance equations become

{\footnotesize
	\begin{align*}
		&\rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
		&\delta P = \delta v \delta \rho_f
	\end{align*}
}

These relations are equally valid if both regions are separated by a region of finite width rather than a discontinuity.

{\footnotesize
	\begin{equation*}
		\lim_{\rho_f v \rightarrow 0} \rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 / \delta \rho_f \rightarrow \cfrac{d v}{d \rho_f} = - \cfrac{v}{\rho_f}
	\end{equation*}
}

By combining the momentum equation with the above equation, we get

{\footnotesize
	\begin{equation} \label{EQ: Pressure_Velocity}
		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
	\end{equation}
}

Suppose the flow is presumed to be isentropic, $dP/d\rho_f = c^2$, so $v^2=c^2$, where $c$ is the speed of sound. This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow. If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial \rho_f / \partial P \approx 0$. The small changes in pressure due to flow velocity changes do not change the density.

The low Mach number condition leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow. The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature. The assumption is that the flow remains within a Mach number limit (usually less than 0.3) for any solution using such a constraint to be valid. In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.

\end{comment}

\subsection{Extraction model} \label{CH: Extraction_model}
\subfile{Sections/Model}

\subsection{Parameter estimation} \label{CH: Parameter_estimation}
\subfile{Sections/Parameter_estimation}

\subsection{Experimental work}
\subfile{Sections/Experiments}

\section{Results}
\subfile{Sections/Results_Chamomile}

\section{Conclusions} \label{CH: Conclusion}

The article presents a comprehensive study on supercritical fluid extraction of essential oil from chamomile flowers, focusing on developing and applying a distributed-parameter model to describe the fluid-solid extraction process. By employing the concept of quasi-one-dimensional flow, the study simplifies the spatial dimensions of the extraction process, ensuring uniform flow across any cross-section while allowing for variations in the area available for the fluid phase. The physical properties of the solvent are estimated using the Peng-Robinson equation of state.

The model calibration is based on the laboratory experiments data conducted by \citet{Povh2001} under various conditions. The model parameters, such as partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data. The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the partition factor, had a low impact on the model's output. The identification of low-impact parameters leads to model reduction. This work introduced a set of correlations to find a general relationship between parameters and the operating conditions. The obtained correlations were incorporated into the process model and tested against the dataset. The process model is capable of reproducing the dataset with satisfactory accuracy.

The presented model can be further used with the presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes, such as yield maximisation, local sensitivity analysis, techno-economic analysis, or optimal experiments design.

% ===================================================
% Bibliography
% ===================================================
%% Loading bibliography style file
%\clearpage
\newpage
%\bibliographystyle{model1-num-names}
\bibliographystyle{unsrtnat}
\bibliography{mybibfile}

\clearpage \appendix \label{appendix}
\section{Appendix}

%\subsection{Governing equations}
%\subfile{Sections/Gouverning_equation_derivation}

\subsection{Thermodynamic}
\subfile{Sections/Qubic_EOS} \label{CH: EOS}

\subsection{Cardano's Formula} \label{CH: Cardano}
\subfile{Sections/Cardano}

%\subsection{Initial and boundary conditions} \label{CH: IC_BC}
%\subfile{Sections/IC_BC}

%\subsection{Maximum likelihood} \label{CH: ML}
%\subfile{Sections/Likelihood}

%\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}

%Figure \ref{fig:density_cal} shows results of density measurement performed with pycnometer.

%\begin{figure}[!h]
%	\centering 
%	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
%	\caption{The result of solid density measurement}
%	\label{fig:density_cal}
%\end{figure}

%{\footnotesize
%	\begin{equation*}
%		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
%	\end{equation*}
%}

%\subsection{Porosity calculations} \label{CH: Porosity}
%\subfile{Sections/Porosity}

\end{document}

### 2024-05-20 Article_Sensitivity_Analsysis_short-Chamomile.tex
20.05

--- 2024-05-20 Short_no_axDiff_Supercritical_fluid_extraction_of_essential_oil_from_chamomile.tex
@@
 % Figure packages
-\usepackage{graphicx}
-\usepackage{float}
-\restylefloat{table}
+\usepackage{graphicx,float}
 \usepackage{adjustbox}
@@
 
-\usepackage{numprint}
-
 % --------------------------------------------------------------------
@@
 % ===================================================
-\title[mode=title]{Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation}                      
-\shorttitle{Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation}
+\title[mode=title]{Sensitivity Analysis}                      
+\shorttitle{Sensitivity Analysis}
 
@@
 
+%\author[1]{Francesco Corona}[orcid=0000-0002-3615-1359]
+%\credit{c}
+
 \address[1]{Aalto University, School of Chemical Engineering, Espoo, 02150, Finland}
@@
 \begin{abstract}
-This study investigates the supercritical extraction process of essential oil from chamomile flowers.
-Essential oils of chamomile are used extensively for medicinal purposes.
-Many different chamomile products have been developed, the most popular of which is herbal tea.
-In this study, a mathematical model describing the governing mass transfer phenomena in solid-fluid environment at supercritical conditions using carbon dioxide is formulated.
+This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers.
+The distributed-parameter model describes the fluid-solid extraction process.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
-The flow of carbon dioxide is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-The physical properties of the solvent are estimated based on the Peng-Robinson equation of state.
-Model parameters, including the partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data assuming normally distributed errors.
+The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
 A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-
-%A distributed-parameter model describes the fluid-solid extraction process.
+Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model.
+The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.
 
@@
 \begin{keywords}
-Supercritical extraction \sep Parameter estimation \sep Mathematical modelling
+Supercritical extraction \sep Sensitivity analysis \sep Mathematical modelling
 \end{keywords}
@@
 \section{Introduction}
+
 \subfile{Sections/introduction_imp}
 
-\section{Materials and methods} \label{CH: Materials and methods}
+\subfile{Sections/Literature_Review}
 
-%\subsection{Supercritical fluids} \label{CH: Thermodynamic}
-%\subfile{Sections/Thermo_imp}
-
-\subsection{Governing equations} \label{CH:Governing_equations_chapter}
-	Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived.
-Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any given cross-section.
-This simplification is typically applied in situations where the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor.
-According to this assumption, velocity and other flow properties change solely in the flow direction.
-
-	As discussed by \citet{Anderson2023}, all flows are compressible but some of them can be treated as incompressible when the Mach number is smaller than 0.3.
-This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
-The restraint allows for the removal of acoustic waves, and allows for large perturbations in density and/or temperature.
-In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
-
-	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
-
-{\footnotesize
-	\begin{align}
-		\label{EQ: CompressibleEuler_1}
-		\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
-		\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
-		\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
-		\label{EQ: CompressibleEuler_3}
-	\end{align}  
-}
-
-where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
-
-\begin{comment}
-Based on governing equations, the small discontinuity (defined as $\delta$) in flow properties, shown in Figure \ref{fig: Discontinuity_slow_flow}, can be analysed.
-The analysis follows the work of \citet{Schreier1982}.
-
-\begin{figure}[!h]
-	\centering
-	\resizebox{0.95\columnwidth}{!}{%
-		\begin{tikzpicture}[]
-			\draw (0,2) -- (9,2);	% Top line
-			\draw (0,0) -- (9,0); 	% Bottom line
-			\draw (4.5,0) -- (4.5,2); 	% Bottom line
-			\node at (4,1.5) {$\rho_f$};
-			\node at (5.5,1.5) {$\rho_f+\delta\rho_f$};
-			\node at (4,1.0) {$P$};
-			\node at (5.5,1.0) {$P+\delta P$};
-			\node at (4,0.5) {$T$};
-			\node at (5.5,0.5) {$T+\delta T$};
-			\node at (1,1.0) {$v \rightarrow$};
-			\node at (8,1.0) {$v + \delta v \rightarrow$};
-	\end{tikzpicture} }
-	\caption{Small discontinuity in one-dimensional flow}
-	\label{fig: Discontinuity_slow_flow}
-\end{figure}
-
-The discontinuity is presumed to be at rest relative, and the balance equations become
-
-{\footnotesize
-	\begin{align*}
-		&\rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 \\
-		&\delta P = \delta v \delta \rho_f
-	\end{align*}
-}
-
-These relations are equally valid if both regions are separated by a region of finite width rather than a discontinuity.
-
-{\footnotesize
-	\begin{equation*}
-		\lim_{\rho_f v \rightarrow 0} \rho_f \delta v + v \delta \rho_f + \delta \rho_f \delta v = 0 / \delta \rho_f \rightarrow \cfrac{d v}{d \rho_f} = - \cfrac{v}{\rho_f}
-	\end{equation*}
-}
-
-By combining the momentum equation with the above equation, we get
-
-{\footnotesize
-	\begin{equation} \label{EQ: Pressure_Velocity}
-		\cfrac{d v}{d \rho_f} = - \cfrac{d v}{dP} \cfrac{d P}{d \rho_f} = -\cfrac{1}{\rho v} \cfrac{dP}{d\rho_f} = -\cfrac{v}{\rho_f}
-	\end{equation}
-}
-
-Suppose the flow is presumed to be isentropic, $dP/d\rho_f = c^2$, so $v^2=c^2$, where $c$ is the speed of sound.
-This can be interpreted as a small pressure wave propagating with the speed of sound relative to the flow.
-If the flow velocity is relatively low, all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic, which leads to $\partial \rho_f / \partial P \approx 0$.
-The small changes in pressure due to flow velocity changes do not change the density.
-
-The low Mach number condition leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
-The restraint allows for the removal of acoustic waves, but also allows for large perturbations in density and/or temperature.
-The assumption is that the flow remains within a Mach number limit (usually less than 0.3) for any solution using such a constraint to be valid.
-In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
-
-\end{comment}
-
-\subsection{Extraction model} \label{CH: Extraction_model}
 \subfile{Sections/Model}
 
-\subsection{Parameter estimation} \label{CH: Parameter_estimation}
-\subfile{Sections/Parameter_estimation}
-
-\subsection{Experimental work}
-\subfile{Sections/Experiments}
+\subsection{Sensitivity Analysis} \label{CH: Sensitivity_Analysis}
+\subfile{Sections/Sensitivity_Analysis}
 
 \section{Results}
-\subfile{Sections/Results_Chamomile}
+\subfile{Sections/Results_Sensitivity}
 
@@
 
-The article presents a comprehensive study on supercritical fluid extraction of essential oil from chamomile flowers, focusing on developing and applying a distributed-parameter model to describe the fluid-solid extraction process.
-By employing the concept of quasi-one-dimensional flow, the study simplifies the spatial dimensions of the extraction process, ensuring uniform flow across any cross-section while allowing for variations in the area available for the fluid phase.
-The physical properties of the solvent are estimated using the Peng-Robinson equation of state.
+Sensitivity analysis is a tool to understand the parametric dependence on the dynamic behaviour of the analysed system.
+The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
+The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
+The sensitivity equations can be obtained in various ways, but the automatic differentiation technique was implemented to obtain the sensitivity equations in this work.
+Local sensitivity analysis can bring valuable information about process modelling, design of experiments or model reduction by identifying which parameters are influential and how these influence changes in time.
 
-The model calibration is based on the laboratory experiments data conducted by \citet{Povh2001} under various conditions.
-The model parameters, such as partition factor, internal diffusion coefficient, and decaying factor, were determined through maximum likelihood estimation based on experimental data.
-The parameter space exploration revealed that while some parameters could be determined with a high degree of confidence, others, like the partition factor, had a low impact on the model's output.
-The identification of low-impact parameters leads to model reduction.
-This work introduced a set of correlations to find a general relationship between parameters and the operating conditions.
-The obtained correlations were incorporated into the process model and tested against the dataset.
-The process model is capable of reproducing the dataset with satisfactory accuracy.
+This study used sensitivity analysis to evaluate the influence of pressure increase on the state-space, which consisted of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
+At given operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the step change of pressure enhance the mass transfer, which leads to faster loss of solute from solid particles and consequently to negative sensitivities.
+An analogous response is visible in the fluid phase, where the concentration of solute increases and is visible as positive sensitivities.
+As more solute is transported to the fluid phase, the extraction yield is improved and characterised by positive sensitivities.
 
-The presented model can be further used with the presented correlations to introduce an extraction model with dynamically changing operating conditions for multiple purposes, such as yield maximisation, local sensitivity analysis, techno-economic analysis, or optimal experiments design.
+This information can be utilised to identify which control variables influence the extraction yield the most.
+The controls with high sensitivities to the extraction can be used to investigate optimal operating conditions from an economic point of view.
 
@@
 %\clearpage
-\newpage
 %\bibliographystyle{model1-num-names}
@@
 
-%\subsection{Governing equations}
-%\subfile{Sections/Gouverning_equation_derivation}
-
-\subsection{Thermodynamic}
+%\subsection{Thermodynamic}
 \subfile{Sections/Qubic_EOS} \label{CH: EOS}
@@
 
-%\subsection{Initial and boundary conditions} \label{CH: IC_BC}
-%\subfile{Sections/IC_BC}
-
-%\subsection{Maximum likelihood} \label{CH: ML}
-%\subfile{Sections/Likelihood}
-
-%\subsection{Solid density measurement} \label{CH: Solid_Density_Measurment}
-
-%Figure \ref{fig:density_cal} shows results of density measurement performed with pycnometer.
-
-%\begin{figure}[!h]
-%	\centering 
-%	\includegraphics[trim=2cm 6cm 4cm 0cm, clip,width=\columnwidth]{Sections/ultraReportT5.pdf}
-%	\caption{The result of solid density measurement}
-%	\label{fig:density_cal}
-%\end{figure}
-
-%{\footnotesize
-%	\begin{equation*}
-%		\rho_s^{ave} = \frac{1.2585+1.2582+1.2561+1.2546+1.2555}{5} = 1.25658 [g/cc]
-%	\end{equation*}
-%}
-
-%\subsection{Porosity calculations} \label{CH: Porosity}
-%\subfile{Sections/Porosity}
-
 \end{document}

### 2024-05-20 Sections/Literature_Review.tex
20.05

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	This study aims to analyze the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}. The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature. The relation between input and output is obtained by applying a sensitivity analysis. Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output. The aim is to understand and to allocate the source of uncertainty in the output to the corresponding inputs or parameters. There are many sensitivity analysis methods, which include but are not limited to those listed below:

	\begin{itemize}
		\item One-at-a-time method
		\item Derivative-based local methods
		\item Variance-based methods
	\end{itemize}

	Different supercritical extraction models were analyzed using sensitivity analysis. \citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed. This allows to evaluate the effect of the uncertainties on model predictions. The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are significant for the extraction process. The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.

	\citet{Santos2000}, in their work, considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent. The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.

	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables. Their findings show that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.

	\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils and applied a sensitivity analysis. They found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process. The sensitivity calculations were performed by varying the parameters and analysing the model response.

\end{document}

### 2024-05-20 Sections/Model.tex
20.05

@@
 
+	\section{Materials and methods} \label{CH: Materials and methods}
+
+	\subsection{Governing equations} \label{CH:Governing_equations_chapter}
+	Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived.
+Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any cross-section.
+This simplification is typically applied when the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor.
+According to this assumption, velocity and other flow properties change solely in the flow direction.
+
+	As discussed by \citet{Anderson2023}, all flows are compressible, but some of them can be treated as incompressible when the Mach number is smaller than 0.3.
+This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
+The assumption allows for removing acoustic waves and large perturbations in density and/or temperature.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
+
+	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
+
+	{\footnotesize
+		\begin{align}
+			\label{EQ: CompressibleEuler_1}
+			\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0 \\
+			\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2} \\
+			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+			\label{EQ: CompressibleEuler_3}
+		\end{align}  
+	}
+
+	where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+
+	\subsection{Extraction model} \label{CH: Extraction_model}
 	\subsubsection{Continuity equation} \label{CH: Continuity}
@@
 	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating a function $A_f = A\phi$.
-This modification distinguishing a constant and varying terms, where the varying term accounts for the changes in the cross-sectional area available for the fluid.
+This modification distinguishes constant and varying terms, where the varying term accounts for the changes in the cross-sectional area available for the fluid.
 Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:
@@
 	}
-	where $A$ is the total cross-section of the extractor and $\phi$ describe porosity along the extractor.
+	where $A$ is the total cross-section of the extractor and $\phi$ describes porosity along the extractor.
 
@@
 	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and thermodynamic pressure are known along $z$.
-The variation in fluid density may occurs due to pressure or a inlet temperature changes.
-In non-isothermal case, $\rho_f$ in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} is consider to be an average fluid density along the extraction column.
+The fluid density variation may occur due to pressure or inlet temperature changes.
+In the non-isothermal case, $\rho_f$ in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} is considered an average fluid density along the extraction column.
 
@@
 
-	Equation \ref{Model_fluid}, describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption.
+	Equation \ref{Model_fluid} describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption.
 Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
 It is also assumed that the thermodynamic pressure remains constant throughout the device.
-The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction.
-Thus, the mass balance equation include convection, diffusion, and kinetic terms to represent the fluid phase behaviour.
+The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall.
+This leads to a uniform velocity profile across any cross-section perpendicular to the axial direction.
+Thus, the mass balance equation includes convection, diffusion, and kinetic terms representing the fluid phase behaviour.
 
@@
 
-	As given by Equation \ref{Model_solid}, the solid phase is considered to be stationary, without convection and diffusion terms in the mass balance equation.
+	As given by Equation \ref{Model_solid}, the solid phase is considered stationary, without convection and diffusion terms in the mass balance equation.
 Therefore, the only significant term in this equation is the kinetic term of Equation \ref{Model_kinetic_basic}, which connects the solid and fluid phases.
-The extract is represented by a single pseudo-component for simplicity.
+For simplicity, the extract is represented by a single pseudo-component.
 
@@
 
-	%The kinetic term is based on two-film theory and follow work of \citet{Reverchon1996}.
-The mass transfer kinetic (Equation \ref{Model_kinetic_basic}) consists of the overall diffusion coefficient and the concentration gradient, which acts as a driving force for the process.
-
-	%In this study, the kinetic term is based on the two-film theory proposed by \citet{Reverchon1996}, and the mass transfer kinetic is given by Equation \ref{Model_kinetic_basic}.
-This equation takes into account the overall diffusion coefficient and the concentration gradient, which acts as the driving force for the process.
-
-%	As the solvent flows through the bed, the CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles through the solvent–solid matrix interactions.
-Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected.
-The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}.
-The mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$.
-At the solid-fluid interface, the equilibrium concentrations are given as ${\color{black}c_s^*}$ and ${\color{black}c_P^*}$, respectively for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{black}c_{P}}$.
-As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{Pf}}$ at the opening of the pore.
-The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{black}c_f}$.
-It can be assumed that the two-film theory describes the solid-fluid interface inside the pore.
-The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.
-
 			As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions.
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$ and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases.
-The concentration of the solutes in the fluid phase in the center of the pore is denoted as $c_p$.
-As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the opening of the pore.
-Then the solute diffuses through the film around the particle and reaches bulk concentration $c_f$.
+Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$, and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases.
+The concentration of the solutes in the fluid phase in the centre of the pore is denoted as $c_p$.
+As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the pore's opening.
+Then, the solute diffuses through the film around the particle and reaches bulk concentration $c_f$.
 The two-film theory describes the solid-fluid interface inside the pore.
@@
 
-		\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, $c_f$, and in the center of the pore, $c_p^*$.
+			\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, $c_f$, and in the centre of the pore, $c_p^*$.
 The concentration $c_p^*$ is in equilibrium with $c_s$ according to an equilibrium relationship.
@@
 
-		According to \citet{Bulley1984}, a linear equilibrium relationship (Equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase $c_f^*$ is based on the concentration of the solute in the solid phase $c_s$.
+			According to \citet{Bulley1984}, a linear equilibrium relationship (Equation \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase $c_f^*$ based on the concentration of the solute in the solid phase $c_s$.
 
@@
 
-			%Equation \ref{Model_kinetic_no_sat} represents of the kinetic term according to \citet{Reverchon1996}
 			According to \citet{Reverchon1996}, the kinetic term becomes
@@
 
-		\iffalse	
-		\subsubsection{Heat balance} \label{CH: heat_balance}
-
-		 {\color{black}
-			The heat balance (Equation \ref{Model_heat}) consists of the convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-We consider no heat loss through the wall, and there is no heat generation in the system.
-Therefore, the temperature of the extractor can be changed only by manipulating the temperature of the inlet stream %$T_{In}(t)$.
-
-			We assume that at a given section, where the cross-sectional area is $A$, the flow properties are uniform across that section.
-Hence, although the area of an extractor changes  as a function of a distance along an extractor (e.g.
-if a fixed fill an extractor partially), $z$, and therefore in reality the flow field is two-dimensional (the flow varies in the two-dimensional space), we make the assumption that the flow properties vary only with $z$; this is tantamount to assuming uniform properties across any given cross section.
-Such flow is defined as quasi-one-dimensional flow.
-
-		}
-
-		\sout{The heat balance equation (equation  \ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance).
-Equation \ref{Model_heat} contains the convection and the diffusion terms.
-It is considered that there is no heat loss through the wall, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by increasing the temperature of the inlet stream.
-The pseudo-homogenous phase is assumed to flow only in the axial direction.
-The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid $C_p$ because the solid phase is stationary.
-Therefore, this factor can be understood as the fraction of the fluid's total heat through convection.
-On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in Appendix.
-}
-
-		{\color{black} The heat balance (Equation \ref{Model_heat}), is based on \citet{Srinivasan2012}, and consists of convective and diffusive terms.
-It follows the assumption of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases.
-It is considered that there is no heat loss through the walls, and there is no heat generation in the system.
-The temperature of the extractor can be changed only by manipulating the temperature of the inlet stream ${\color{black}T_{Inlet}}(t)$.
-			}
-
-			{\footnotesize
-				\begin{equation} \label{Model_heat}
-					\begin{split}
-						\cfrac{\partial T(t,z)}{\partial t} &= 
-						\underbrace{ -\cfrac{F {\color{black}C_p}(T(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p} (T(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T(t,z)}{\partial z}  }_{\text{Convection}} + \\
-						& + \underbrace{ {\color{black}D^T_e}(T(t,z),{\color{black}P}(t)) \cfrac{\partial^2 T(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
-					\end{split}
-			\end{equation} }
-
-		where $ {\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial mass diffusion coefficient, ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}(T(t,z),{\color{black}P}(t),F)$ is the axial heat diffusion coefficient.
-
-%		\todo[inline]{Draft of new heat equation starts here. TODO: \\ Check if the heat cpacity of solid phase needs to be added \\ Elaborate why pressure is know}
-
-			The heat governing equation describe the evolution of the energy in the system and it is given by \ref{EQ: Heat_internal}.
-The derivation of the heat equation can be found in Appendix \ref{CH: Gouverning equations}.
-
-			{\footnotesize
-			\begin{align} \label{EQ: Heat_internal}
-				&\cfrac{\partial \left( \rho_f e(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e(t,z) \right)}{\partial z} \nonumber \\
-				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( \cfrac{\partial T(t,z)}{\partial z} \right) 
-			\end{align}
-			}
-
-			The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
-The departure function is typically defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
-They are typically computed by integrating a function that depends on the equation of state and its derivatives.
-Following \citet{Elliott2011} or \citet{Gmehling2019}, a real gas internal energy definition can be obtained from the departure functions, defined through Equation \ref{EQ: internal_energy_def}.
-More information on the departure functions can be found in Appendix \ref{CH:Enthalpy}.
-
-			{\footnotesize
-				\begin{equation}
-					de(t,z)=C_vdT-\left[{\color{black}P}(t)-T(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial T(t,z)}\right)_{{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)
-					\label{EQ: internal_energy_def}
-				\end{equation} }
-
-			where $e^{id}(t,z)$ is the internal energy of perfect gas.
-
-			Suppose a gas is considered to be perfectly caloric ($e(t,z)={\color{black}C_v} T(t,z)$), then the energy equation can be written explicitly in the form of temperature.
-The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{black}C_v}$ is constant.
-
-			For real gases, it is complicated to write the heat balance in terms of temperature, but it can be used directly in the form of internal energy, as it is given by Equation \ref{EQ: CompressibleEuler_3}.
-In such a case, the temperature needs to be recovered from the internal energy.
-A relation for the internal energy can be obtained from an equation of state.
-For Peng-Robinson, such a relation is given by Equation \ref{EQ: internal_energy_PR} as presented by \citet{Elliott2011}.
-
-%			{\footnotesize
-%				\begin{equation}
-%					e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
-%					\label{EQ: internal_energy_PR}
-%				\end{equation}
-%			}
-
-			{\scriptsize
-				\begin{equation}
-					\begin{aligned}
-					&\cfrac{e(t,z)-e^{id}(t,z)}{RT(t,z)} = \\
-					& - \cfrac{{\color{black}A}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)} \right]
-					\label{EQ: internal_energy_PR}
-				\end{aligned}
-			\end{equation}
-			}
-
-			To solve Equation \ref{EQ: internal_energy_PR}, temperature, pressure, and density values need to be known.
-If an equation of state is introduced, then only two out of three variables need to be obtained as the third one can be calculated; this can be represented as follow
-
-			{\footnotesize
-			\begin{equation}
-				e(t,z)=e(T(t,z),{\color{black}P}(t),\rho_f)=e( T(t,z),{\color{black}P}(t), \rho_f ) 
-			\end{equation}
-			}
-
-			If the value of internal energy $e(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed.
-A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}.
-Such a procedure allows to find a local temperature along spatial direction $z$ and needs to be repeated every time-step.
-
-			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = e(t,z) + {\color{black}P}(t) / \rho_f$.
-By introducing the definition of enthalpy, the energy equation becomes
-
-			{\footnotesize
-				\begin{align} \label{EQ:Enthalpy_equation}
-					\cfrac{\partial \left(\rho_f {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h}(t,z) A_f v \right)}{\partial z}  \nonumber \\
-					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T(t,z)}{\partial z} \right)
-				\end{align}
-			}
-
-			The main advantage of this formulation is the presence of term $\partial {\color{black}P}(t) / \partial t $, which allows it to directly affect the system through the change of thermodynamic pressure (which is a control variable).
-The enthalpy is related to the pressure and temperature through the following equation:
-
-			{\footnotesize
-				\begin{equation}
-					{\color{black}h}(t,z)={\color{black}h}(T(t,z),{\color{black}P}(t),\rho_f)={\color{black}h}( T(t,z),{\color{black}P}(t), \rho_f ) 
-					\label{EQ:Enthalpy_root}
-				\end{equation}
-			}
-
-			If the value of enthalpy is known from the time evolution and pressure can be measured, then the Equation \ref{EQ:Enthalpy_root} can be solved for the temperature to recover the temperature profile.
-For the Peng-Robinson EoS, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}.
-More details can be found in Appendix \ref{CH:Enthalpy} or given by \citet{Gmehling2019}.
-
-			{\scriptsize
-				\begin{equation}
-					\begin{split}
-					{\color{black}h}(t,z)-{\color{black}h}(t,z)^{id}={\color{black}R}T(t,z) \left[{\color{black}T_r}({\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)-1) \right. \\
-					\left.
--2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T(t,z)\right) } } \ln \left(\cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}\right)\right]
-					\label{EQ:Enthalpy_PR}
-				\end{split}
-			\end{equation}				
-			}
-
-			The Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which in this case is assumed to be ${\color{black}T_{ref}}=298.15~[K]$ and ${\color{black}P_{ref}}=1.01325~[bar]$.
-
-			As discussed by \citet{Gmehling2019}, the influence of the intermolecular forces on the enthalpy is needs to taken into account in high pressures systems.
-In most cases, these forces are attractive, so additional energy is necessary to move the molecules away from each other, that is, to lower the density.
-If this energy is not added, the substance cools down when it is expanded.
-
 			\subsubsection{Pressure term} \label{CH: Pressure}
@@
 As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial {\color{black}P}/\partial t$ can be approximated by an ordinary differential equation, which describes the instantaneous change of pressure in the system.
-The pressure (P) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by an difference equation, which describes the change of pressure in the whole system.
+The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
 
@@
 				\begin{equation}
-				\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P}(t) - {\color{black}P_{in}}(t) }{\Delta t}
+					\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P_{in}}(t) - {\color{black}P}(t) }{\Delta t}
 			\end{equation}}
@@
 
-  		\fi
+			\subsubsection{Heat balance} \label{CH: heat_balance}
+
+			The heat balance equation describe the evolution of the internal energy in the system and it is given by Equation \ref{EQ:Enthalpy_equation}
+
+			{\footnotesize
+				\begin{equation} \label{EQ:Enthalpy_equation}
+					\cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f {\color{black}h} A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+				\end{equation}
+			}
+
+			The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure (which is a control variable).
+%The enthalpy is related to the pressure and temperature through the following equation:
+
+			If the value of enthalpy $h$ is known from the time evolution of the energy equation, and pressure $P$ is known from measurement, then the temperature $T$ can be reconstructed based on the departure function.
+The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+The departure function is defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
+They are computed by integrating a function that depends on the equation of state and its derivatives.
+As presented by \citet{Gmehling2019}, for the Peng-Robinson equation of state, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}.
+
+			{\scriptsize
+				\begin{equation}
+					{\color{black}h}-{\color{black}h}^{id}={\color{black}R}T \left[{\color{black}T_r}({\color{black}Z}-1) -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T\right) } } \ln \left(\cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}}\right)\right]
+					\label{EQ:Enthalpy_PR}
+				\end{equation}				
+			}
+
+			Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which is assumed to be $T_{ref}=298.15$[K] and $P_{ref}=1.01325$[bar].
+
+			A root-finder can be used to find a value of temperature, which minimizes the difference between the value of enthalpy coming from the heat balance and the departure functions.
+The root fining procedure to repeated at every time step to find a local temperature along spatial direction $z$.
+
+			{\footnotesize
+				\begin{equation}
+					\underbrace{h\left(t,x\right)}_{\text{Heat balance}}=\underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}}
+					\label{EQ:Enthalpy_root}
+				\end{equation}
+			}
 
@@
 					\label{Model_measurment_1}
-%				y(t) \left[ kg \right] &= \int_{t_0}^{t_f} Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right] dt \left[ s \right] \\
 					y &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
-%				\cfrac{dy}{dt} \left[ \cfrac{kg}{s} \right] &= Q(t,z) \left[ \cfrac{m^3}{s} \right] c_f(t,z) \biggr\rvert_{z=L} \left[ \cfrac{kg}{m^3} \right]  \\
 					\cfrac{dy}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
@@
 			\subsubsection{Initial and boundary conditions} 
-		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content $c_{s0}$.
-As the residence time is much shorter than the sampling time, the initial state estimate for the concentration of the solute in the fluid phase would be not reliable.
-Considering that it is assumed that the $c_{f0}=0$ and that the system is isothermal.
-%and described by ${\color{black}h_0}$.
-		Therefore, the initial and boundary conditions are define as follow:
-
-		\begin{comment}
-		{\footnotesize
-				\begin{align*}
-					&{\color{black}c_f}(t = 0, z) = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} & &{\color{black}h}(t = 0, z) = {\color{black}h_0} \\
-					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 & {\color{black}c_s}(t = 0, z) = {\color{black}c_{s0}} & &\frac{\partial h(t,z=L)}{\partial x} = 0
-				\end{align*} }
-		\end{comment}
+			It is assumed that the solvent is free of solute at the beginning of the process $c_{f0}=0$, that all the solid particles have the same initial solute content $c_{s0}$, and that the system is isothermal.
+The fluid at the inlet is also considered not to contain any solute.
+As the residence time is much shorter than the sampling time, the initial state estimate for the solute concentration in the fluid phase would be unreliable.
+The initial and boundary conditions are defined as follows:
 
@@
 				\begin{align*}
-					&c_f(t = 0, z) = 0 && c_s(t = 0, z) = c_{s0} && {c_f}(t, z=0) = 0 \\
-					&\frac{\partial c_f(t,z=L)}{\partial x} = 0 && c_s(t, z=\{0,L\}) = 0 && y(0) = 0
+					&c_f(t = 0, z) = 0  && c_s(t = 0, z) = c_{s0} && h(t = 0, z) = h_0 \\
+					&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}(t)  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
+					&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0 \quad P(0) = P_0 \\
 			\end{align*} }
@@
 
-		\begin{comment}
 				{\footnotesize
@@
 				\end{align*} }
-	\end{comment}
+			where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
 
-		{\footnotesize
-			\begin{align*} \label{discretization}
-				\dot{x} &= \cfrac{d x}{d t} = 
-				\begin{bmatrix}
-					\cfrac{d c_{f,1}}{d t} 	  \\
-					\vdots		\\	
-					\cfrac{d c_{f,N_z}}{d t} \\
-					\\ \hline  	\\
-					\cfrac{d c_{s,1}}{d t} 	  \\
-					\vdots		\\
-					\cfrac{d c_{s,N_z}}{d t} \\
-					%\\ \hline \\
-					%\cfrac{d {\color{black}P}(t)}{d t} \\
-					\\ \hline \\
-					\cfrac{d {\color{black}y}(t)}{d t}
-				\end{bmatrix}
-				=
-				\underbrace{\begin{bmatrix}
-						G_1 \left( c_f,c_s; \Theta \right)\\ 
-						\vdots\\ 
-						G_{N_z} \left( c_f,c_s; \Theta \right)\\ 
-						\\ \hline \\ \\
-						G_{N_z+1} \left( c_f,c_s; \Theta \right)\\ 
-						\vdots\\
-						G_{2N_z} \left( c_f,c_s; \Theta \right)\\ 
-						%\\ \\ \hline \\ 
-						%{\color{black}G_{2N_z+1}} \left( c_f,c_s; \Theta \right) \\
-						\\ \\ \hline \\
-						G_{2N_z+2} \left( c_f,c_s; \Theta \right) 
-				\end{bmatrix}}_{G \left( x; \Theta \right)} 
-		\end{align*} }
-
-		where ${\color{black}x} \in \mathbb{R}^{N_x = 2N_z+1} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters, $N_{u}$ is the number of control variables.
-
-		%As presented in Appendix \ref{CH: Gouverning equations}, all the governing can be written in the integral form using the Divergence Theorem.
-The integral equation states that the change rate of the integral of any quantity over an arbitrary control volume is given by the flux through the boundary of the control volume, with being the outer surface normal through the boundary.
-That quantity is conserved and neither produced nor consumed inside the control volume.
 			For a derivative to be conservative, it must form a telescoping series.
@@
 
-		\iffalse
-		\subsubsection{State-space representation} \label{CH: State_space}
-
-		The process model can be written in a general form:
-
-		{\footnotesize
-			\begin{align}
-				\begin{bmatrix}
-					\cfrac{\partial c_f}{\partial t}\\
-					\cfrac{\partial c_s}{\partial t}\\
-					\cfrac{\partial {\color{black}h}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{black}P}(t,z)}{\partial t} \\
-					\cfrac{\partial {\color{black}y}(t)}{\partial t} 
-				\end{bmatrix}
-				& =
-				\begin{bmatrix}
-					{\color{black}\bar{\phi_1}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
-					{\color{black}\bar{\phi_2}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
-					{\color{black}\bar{\phi_3}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right) \\
-					{\color{black}\bar{\phi_4}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)\\
-					{\color{black}\bar{\phi_5}} \left( c_f,c_s,{\color{black}h}(t,z); \Theta \right)
-				\end{bmatrix} = {\color{black}\bar{\phi}} \left( t,z; \Theta \right) = \cfrac{\partial {\color{black}\chi}(t,z)}{\partial t}
-		\end{align} }
-
-		where $\Theta$ is a parameter space, ${\color{black}\bar{\phi}}$ is a set of functions that correspond to state equations of the model, and ${\color{black}\chi}$ is the state-space model.
-
-		\fi
-
-		%Function ${\color{black}\bar{\phi}}$ are transformed to a corresponding set of $N_z$ discretized equations denoted as ${\color{black}G}$.
-		%The state-space model ${\color{black}\chi}(t,z)$ after the discretization is represented by $\dot{{\color{black}x}}(t)$.
-
-		%In a state-space sense, the state variables of the system are the local concentrations of solute in the fluid and solid phases ($c_f$ and $c_s$, respectively), and the local enthalpy of the pseudo-homogeneous phase (${\color{black}h}(t,z)$).
-The controllable input variables are the mass flow rate and temperature of the solvent in the feed and the pressure in the extractor.
-Additionally, the pressure change is augmented with the state-space and denoted as ${\color{black}P}(t)$.
-		%The system state-space is extended by assuming that extraction yield can be modelled as a function of a known initial mass of solute in the solid phase, and it can be measured after the separator (${\color{black}Y}(t)$).
-The system is controllable by manipulating the flow rate and temperature (enthalpy) of CO$_2$ in the feed and the pressure in the extractor.
-
-%			To ensure the stability of the convergence while solving the partial differential equations, the Courant–Friedrichs–Lewy condition (given by Equation \ref{EQ:CFL}) was applied.
-Based on the discretization step and the velocity, the Courant–Friedrichs–Lewy condition can be used to find.
-%			
-%			{\footnotesize
-%				\begin{equation}
-%					C = \cfrac{u\Delta t}{\Delta x} \leq C_{max} = 1 
-%					\label{EQ:CFL}
-%				\end{equation}
-%			}
-%			
-%			where u is velocity, $\Delta t$	is a time step and $\Delta x$ is the space discretization.
-
 		\end{document}

### 2024-05-20 Sections/Qubic_EOS.tex
20.05

@@
 
-	\subsubsection{Equation of state} \label{subsubsec: Equation of state}
+	\subsection{Equation of state} \label{subsubsec: Equation of state}
 
-	A cubic equation of state (EoS) serves as a mathematical model to describe the behavior of real gases and liquids through a third-degree polynomial equation that correlates the pressure, volume, and temperature of a substance.
-These equations constitute tools for comprehending the phase behavior, properties, and thermodynamic processes of actual substances, across various engineering and scientific applications.
-The cubic equation of state take into account deviations from ideal gas behavior, which are particularly important at high pressures and low temperatures, where real gases do not follow assumption of ideal gas.
+	A cubic equation of state (EoS) serves as a mathematical model to describe the behaviour of real gases and liquids through a third-degree polynomial equation that correlates a substance's pressure, volume, and temperature.
+These equations constitute tools for comprehending real substances' phase behaviour, properties, and thermodynamic processes across various engineering and scientific applications.
+The cubic equation of state takes into account deviations from ideal gas behaviour, which are particularly important at high pressures and low temperatures, where real gases do not follow the assumption of an ideal gas.
 
@@
 
-	The Van der Waals constants, constitute empirical values contingent upon the particular substance being modeled.
+	The Van der Waals constants constitute empirical values contingent upon the particular substance being modelled.
 These constants factor in molecular interactions (represented by '$a$') and the finite size of gas molecules (indicated by '$b$').
@@
 	The general cubic equation of state can be represented as a polynomial, as indicated in Equation \ref{EQ:Compressibility_Polynomial}.
-In a one-phase region, the fluid is characterized by a single real root, corresponding to the gas, liquid, or supercritical phase.
+In a one-phase region, the fluid is characterized by a single real root corresponding to the gas, liquid, or supercritical phase.
 In the two-phase region, a gas-liquid mixture exists, and two roots are identified.
@@
 
-	For an ideal gas, the compressibility factor is defined as $Z = 1$, but the deviation of Z needs to be consider for real-life cases.
+	For an ideal gas, the compressibility factor is defined as $Z = 1$, but the deviation of Z needs to be considered for real-life cases.
 The value of $Z$ typically increases with pressure and decreases with temperature.
@@
 
-	Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility ${\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)$ at given temperature and pressure.
-Alternatively, the closed form solution can by obtained by Cardano formula ( Appendix \ref{CH: Cardano}).
+	Numerical methods such as Newton-Raphson can be used to solve the polynomial equation to obtain the compressibility $Z\left(T(t,z), P(t)\right)$ at a given temperature and pressure.
+Alternatively, the closed-form solution can be obtained by the Cardano formula ( Appendix \ref{CH: Cardano}).
 
@@
 
-	\begin{comment}
-	\subsubsection{Heat capacity of the fluid phase} \label{subsubsec: Fluid heat capacity}
-	%	\noindent\textbf{Heat capacity of the fluid phase} \\
-
-	The specific heat $C_p^{\text{F}}$ can be calculated from the equation of state,  under the assumption that the fluid phase consists of pure carbon dioxide and that the specific heat of real fluids can be calculated from an ideal contribution plus a residual term \citet{Pratt2001}:
-
-	{\footnotesize
-	\begin{align}
-		C_v &= C_v^{id} + C_v^R \\
-		C_p &= C_p^{id} + C_p^R
-	\end{align}}
-
-	The ideal-gas contribution is found using heat-capacity data applicable to gases at very low pressures, which are available in many thermodynamics textbooks in the polynomial form, such as $C_p^{id}(T) = A + BT + CT^2 + DT^3$.
-
-	where the coefficients of the expansion are ${\color{black}C_{P0}} = 22.26$, ${\color{black}C_{P1}} = 5.981 \times 10^{-2}$, ${\color{black}C_{P2}} = -3.501 \times 10^{-5}$, and ${\color{black}C_{P3}} = 7.469 \times 10^{-9}$, as given by \citet{Kyle1999}.
-
-	The residual component of the specific heat can obtained from general relation between $C_v$ and $C_p$ as given by \citet{Poling2001}.
-
-	{\footnotesize
-	\begin{equation} \label{EQ:CP_residual}
-		C_p^R = C_v^R + T\left(\frac{\partial P}{\partial T}\right)_{v_m} \left(\frac{\partial v_m}{\partial T}\right)_P - R
-	\end{equation}}
-
-	The effects of pressure and temperature for liquids are not great, but both $C_p$ and $C_v$ diverge at the critical point of a pure fluid.
-In the neighborhood of the critical, $\left(\frac{\partial P}{\partial v_m}\right)_T$ approaches zero, so $C_p$ increases much faster than $C_v$.
-At both high and low densities, the differences are small, but for $T_r$ near unity, they increase rapidly as the critical density is approached.
-At fixed density in this region, $C_p$ actually decreases as T increases.
-
-	The term $\left(\frac{\partial P}{\partial T}\right)_{v_m}$ can be obtain by direct differentiation of P-R EoS
-
-	{\footnotesize
-	\begin{equation}
-		\left(\frac{\partial P}{\partial T}\right)_{v_m} = \frac{R}{v_m - b} - \frac{\frac{d \Phi}{dT}}{\left[v_m(v_m+b)+b(v_m-b)\right]^2}
-	\end{equation}}
-
-	where $\left(\frac{\partial \Phi}{\partial T}\right)_{v_m} = \frac{-f(\omega)a}{\sqrt{TT_c}(1 + f(\omega)( 1 - \sqrt{T/T_c}))}$
-
-	The term $\left(\frac{\partial v_m}{\partial T}\right)_P = \frac{R}{P} \left(T \left(\frac{\partial Z}{\partial T}\right)_P + Z \right)$
-
-	The term $\left(\frac{\partial Z}{\partial T}\right)_P$ can be defined as below
-
-	{\footnotesize
-	\begin{equation}
-		\left(\frac{\partial Z}{\partial T}\right)_P = \frac{ \left(\frac{\partial A}{\partial T}\right)_P (B-Z) + \left( \frac{\partial B}{\partial T} \right)_P \left( 6BZ+2Z-3B^2-2B+A-Z^2 \right)}{3Z^2 + 2(B-1)Z + (A-2B-3B^2)}
-	\end{equation}}
-
-	{\footnotesize
-	\begin{align}
-		\left(\frac{\partial A}{\partial T}\right)_P &= (P/(RT)^2)(\frac{d \Phi}{dT} - 2a/T) \\
-		\left(\frac{\partial B}{\partial T}\right)_P &= -bP/(RT^2)
-	\end{align}}
-
-	The first component of Equation \ref{EQ:CP_residual} from definition of $C_v = \left(\frac{\partial U^R}{\partial T}\right)_{v_m}$, where $U^R$ represents internal energy.
-In case of Pen-Robinson $U^R$ equals to
-
-	{\footnotesize
-	\begin{equation}
-		U^R = \frac{T \frac{d^2 \Phi}{dT^2}}{b \sqrt{8}} \ln \left( \frac{Z+B\left(1+\sqrt{2}\right)}{Z+B\left(1-\sqrt{2}\right)} \right)
-	\end{equation}}
-
-	As given by \citet{Pratt2001}, for Peng-Robinson EoS the term $\frac{d^2 \Phi}{dT^2}$ is defined as follow
-
-	{\footnotesize
-	\begin{equation}
-		\frac{d^2\Phi}{dT^2} = \frac{af(\omega)\sqrt{\frac{T_c}{T}} \left( 1+ f\left(\omega\right) \right)}{2TT_c}
-	\end{equation} }
-
-	\subsubsection{Departure functions for enthalpy calculations} \label{CH:Enthalpy}
-
-	In thermodynamics, a departure function is a concept used to calculate the difference between a real fluid's thermodynamic properties (enthalpy, entropy, or internal energy) and those of an ideal gas, given a specific temperature and pressure.
-These functions are used to calculate extensive properties, which are properties computed as a difference between two states.
-
-	To evaluate the enthalpy change between two points, $h(V_1,T_1)$ and $h(V_2,T_2)$, the enthalpy departure function between the initial volume $V_1$ and infinite volume at temperature $T_1$ is calculated.
-Then it is added to that the ideal gas enthalpy change due to the temperature change from $T_1$ to $T_2$, and finally subtract the departure function value between the final volume $V_2$ and infinite volume.
-
-	Departure functions are computed by integrating a function that depends on an equation of state and its derivative. The general form of the enthalpy equation is given by:
-
-	{\footnotesize
-		\begin{equation}
-			\frac{h^{id}-h}{RT} =\int_{v_m}^{\infty }\left(T\left({\frac{\partial Z}{\partial T}}\right)_{v_m}\right){\frac{dv_m}{v_m}} + 1-Z
-		\end{equation}
-	}
-
-	Here, $h^{id}$ represents the enthalpy of an ideal gas, $h$ is the enthalpy of a real fluid, $R$ is the universal gas constant, $T$ is temperature, $v_m$ is the molar volume, and $Z$ is the compressibility factor.
-
-	The integral in the equation is evaluated over the range of molar volumes from $v_m$ to infinity.
-The integral includes a term that depends on the derivative of the compressibility factor with respect to temperature, evaluated at the molar volume $v_m$.
-Finally, the term $1-Z$ is added to account for the deviation of the fluid's properties from an ideal state.
-
-	The Peng–Robinson EoS relates the three interdependent state properties pressure $P$, temperature $T$, and molar volume $v_m$.
-From the state properties ($P$, $v_m$, $T$), one may compute the departure function for enthalpy per mole (denoted $h$) as presented by \citet{Gmehling2019} or \citet{Elliott2011}:
-
-	{\footnotesize
-		\begin{equation}
-			h-h^{\mathrm {id} }=RT_c\left[T_{r}(Z-1)-2.078(1+\kappa ){\sqrt {\alpha }}\ln \left({\frac {Z+2.414B}{Z-0.414B}}\right)\right]
-		\end{equation}
-	}
-
-	\end{comment}
-
 \end{document}

### 2024-05-20 Sections/Results_Sensitivity.tex
20.05

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\label{CH: Results}

	This work investigates the influence of pressure change on the state space and the extraction yield. The process model and parameters have been discussed in {\color{red}article 1}. The process model was calibrated on the set of experiments obtained at different operating conditions, $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s. The sensitivity analysis has been performed assuming that the system operates at $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.

	%\subfile{Sensitivity_Flow_Rate}

    \subfile{Sensitivity_Pressure}

    %\texttt{}\subfile{Sensitivity_Inlet_Temperature}

\end{document}

### 2024-05-20 Sections/Sensitivity_Analysis.tex
20.05

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	Local derivative-based methods involve taking the partial derivative of the output with respect to an input parameter. This set of derivatives, known as sensitivity equations, is solved simultaneously with the process model. The sensitivity analysis aims to investigate how responsive the solution is for the perturbation of the parameter ${p}$. As discussed by \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system. A sensitivity analysis can be used to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction. Finally, from a control engineering point of view, the sensitivity analysis allows sorting the control variables with respect to the level of effort required to change the model's output.

	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) are developed by taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of the parameter space $\theta$.

	{\footnotesize
		\begin{align}
			%		\label{SA_def}
			{Z}({x}(t);{p}) &= \cfrac{d {x}(t)}{d {p}}
	\end{align} }

	The new system of equations can be obtained by taking derivatives of $Z$ with respect to time $t$ and applying the chain rule.

	{\footnotesize
		\begin{equation} \label{SA_dt} 
			{\dot{Z}}({x}(t);{p})  = \cfrac{d {Z}(x(t);{p})}{d t} = \cfrac{d}{d t} \left( \cfrac{d {x}(t)}{d {p}} \right) = \cfrac{d }{d {p}} \left( \cfrac{d {x}(t)}{d t} \right) = \cfrac{d {G}({x}(t);{p})}{d {p}} 
	\end{equation} }

	The sensitivity equation can be obtained by applying the definition of the total derivative to the Equation \ref{SA_dt}.

	{\footnotesize
		\begin{align}		
			\label{SA_eq_full}\cfrac{d {G}({x}(t);{p})}{d {p}} &=  \underbrace{ \cfrac{\partial {G}({x}(t);{p})}{\partial {x}(t)} }_{{J_x}({x}(t);{p})} \underbrace{\cfrac{\partial {x}(t)}{\partial {p}} }_{{S}({x}(t);{p})} + \underbrace{ \cfrac{\partial {G}({x}(t);{p})}{\partial {p}} }_{{J_p}({x}(t);{p})}
	\end{align} }

	The sensitivity Equation \ref{SA_eq_full} is solved simultaneously with the original system and is made of three terms: jacobian ${J_x}({x}(t);{p})$, sensitivity matrix ${S}({x}(t);{p})$ and jacobian ${J_p}({x}(t);{p})$. The jacobian ${J_x}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${G}_{n_x}({x}(t);{p})$ with respect to the state variable $x_{n_p}$.

	{\footnotesize
		\begin{align}
			\begingroup % keep the change local
			\setlength\arraycolsep{2pt}
			{J_x}({x}(t);{p})=\begin{pmatrix}
				\cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
				\cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
				\vdots & \vdots & \ddots & \vdots\\ 
				\cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
			\end{pmatrix}
			\endgroup
	\end{align} }

	The sensitivity matrix ${S}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${S}(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.

	{\footnotesize
		\begin{equation}
			\begin{split}
				{S}({x}(t);{p}) & = 
				%				\begingroup % keep the change local
				%				\setlength\arraycolsep{2pt}
				%				\begin{pmatrix}
					%					{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
					%					{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
					%					\vdots & \vdots & \ddots & \vdots\\
					%					{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
					%				\end{pmatrix}
				%				\endgroup
				%				=\\
				%				&=
				\begingroup % keep the change local
				\setlength\arraycolsep{2pt}
				\begin{pmatrix}
					\cfrac{\partial {x_{1}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{1}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{1}}(t)}{\partial {p_{N_p}}}\\
					\cfrac{\partial {x_{2}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{2}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{2}}(t)}{\partial {p_{N_p}}}\\
					\vdots					 	    & \vdots 					   	  & \ddots & \vdots\\
					\cfrac{\partial {x_{N_x}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{N_x}}(t)}{d {p_{2}}}     & \cdots & \cfrac{\partial {x_{N_x}}(t)}{d {p_{N_p}}}
				\end{pmatrix} 
				\endgroup
			\end{split}
	\end{equation} }

	The jacobian ${J_p}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.

	{\footnotesize
		\begin{align}
			{J_p}({x}(t);{p}) & =
			\begingroup % keep the change local
			\setlength\arraycolsep{2pt}
			\begin{pmatrix}
				\cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{N_p}}}\\
				\cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{N_p}}}\\
				\vdots & \vdots & \ddots & \vdots\\
				\cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{N_p}}}
			\end{pmatrix}
			\endgroup
	\end{align}}

	The combined system containing the original set of equations ${G}({x}(t);{p})$ and sensitivity equations can be formulated as ${\textbf{G}}\left({x}(t);{p}\right)$. The size of ${\textbf{G}}\left({x}(t);{p}\right)$ is equal to $N_s = N_x(N_p + 1)$.

	{\footnotesize
		\begin{align}
			{\textbf{G}}\left({x}(t);{p}\right) = 
			\begin{bmatrix}
				{G}({x}(t);{p})\\
				{J_x}({x}(t);{p}){S}({x}(t);{p}) + {J_p}({x}(t);{p})
			\end{bmatrix}
	\end{align} }

	The initial conditions are described as

	{\footnotesize
		\begin{align}
			{\textbf{G}}\left({x}(t_0);{p}\right)  = 
			\begin{bmatrix} {x}(t_0),						& 
				\cfrac{ \text{d}{x}(t_0) }{ d{p_1} },		& 
				\cdots,					 					&
				\cfrac{ d{x}(t_0) }{ d{p_{N_p}} } 
			\end{bmatrix}^T
	\end{align} }

	The sensitivity analysis of the output function can be performed with respect to parameters ${p}$. The output function ${g}({x}(t))$ returns ${y}(t)$. By taking a total derivative of ${y}(t)$ with respect to ${p}$, the new sensitivity equation can be found.

	{\footnotesize
		\begin{align}
			\cfrac{d {y}(t)}{d{p}} = \cfrac{d {g}({x}(t))}{d{p}} = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)} \cfrac{\partial {x}(t)}{\partial {p}} + \cfrac{\partial {g}({x}(t))}{\partial {p}}
	\end{align} }

%	The ${g}({x}(t))$ itself is independent of the parameters, but it dependents on ${x}(t)$, which is the function of ${p}$. In such a case the sensitivity equation for the output becomes
%	
%	{\footnotesize
%		\begin{equation} \label{EQ:Output_sens_full}
%			\cfrac{d {g}({x}(t))}{d {p}} = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)} \cfrac{\partial {x}(t)}{\partial {p}} + 0 = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)}  {S}({x}(t);{p}) = 
%		\end{equation} 
%		
%		\begin{equation} 
%			= \begingroup % keep the change local
%			\setlength\arraycolsep{2pt}
%			\begin{pmatrix}
%				\cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{N_x}}}\\
%				\cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{N_x}}}\\
%				\vdots & \vdots & \ddots & \vdots\\
%				\cfrac{\partial {g_{N_g}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{N_g}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{N_g}}({}(t))}{\partial {x_{N_x}}}
%			\end{pmatrix}
%			\begin{pmatrix}
%				{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
%				{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
%				\vdots & \vdots & \ddots & \vdots\\
%				{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
%			\end{pmatrix}
%			\endgroup
%	\end{equation} }

%	Keeping in mind that the output function returns only one value, the sensitivity equation of the output (\ref{EQ:Output_sens_full}) becomes:
%	
%	{\footnotesize
%		\begin{equation} \label{EQ:Output_sens_short}
%			\begin{split}
%				& \left( \cfrac{d {y}({x}(t))}{d {p_{1}}}, \cfrac{d {y}({x}(t))}{d {p_{2}}}, \cdots, \cfrac{d {y}({x}(t))}{d {p_{N_p}}} \right)  = \\
%				& =  \left( \cfrac{\partial {g}({x}(t))}{\partial {x_{1}}}, \cfrac{\partial {g}({x}(t))}{\partial {x_{2}}}, \cdots, \cfrac{\partial {g}({x}(t))}{\partial {x_{N_x}}} \right)
%				\begingroup % keep the change local
%				\setlength\arraycolsep{2pt}
%				\begin{pmatrix}
%					{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
%					{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
%					\vdots & \vdots & \ddots & \vdots\\
%					{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
%				\end{pmatrix} \endgroup
%			\end{split}
%	\end{equation} }

\end{document}

### 2024-05-20 Sections/Sensitivity_Flow_Rate.tex
20.05

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsection{Flow rate}

	The increase in the mass-flow rate affects the system simultaneously along the spatial direction by increasing the velocity but without affecting the thermodynamic state of the fluid. As a result, Figure \ref{fig:Sensitivty_F_P} indicates that the system's pressure remains unaffected by changes in the flow rate.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_F.png}
		\caption{The effect of $F$ change on $P$}
		\label{fig:Sensitivty_F_P}
	\end{figure}

	It is important to note that $h$ represents enthalpy but not total enthalpy, thus excluding kinetic energy. As a consequence of the modelling assumptions, changes in $h$ and $\rho$ occur in response to changes in pressure or temperature, which explains no deviation of $h \times \rho$ in Figure \ref{fig:Sensitivty_F_H}.

	%When utilizing Dirichlet boundary conditions, it's crucial to be aware of potential numerical artefacts from the differing methods used to compute them. The system's enthalpy is determined through the time evolution of governing equations, while the inlet's enthalpy depends on the inlet temperature and pressure, which are the controls. A minor numerical mismatch between these values may manifest as an enthalpy difference propagating along the spatial domain. To ensure consistency between the fluid at the inlet and inside the computational domain, this analysis employs Neumann boundary conditions.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_F.png}
		\caption{The effect of $F$ change on $h \times \rho$}
		\label{fig:Sensitivty_F_H}
	\end{figure}

	Figure \ref{fig:Sensitivty_F_CS} visualizes how the solute concentration in the solid phase is affected by the mass flow change. It is postulated that with an increase in the mass flow rate, the concentration gradient becomes larger leading to an accelerated decrease of the solute from solid particles and it is characterized by negative sensitivity values. Gradually, the sensitivities decrease until they reach minimum values and the effect of mass flow rate on extraction is most significant.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_F.png}
		\caption{The effect of $F$ change on $C_s$}
		\label{fig:Sensitivty_F_CS}
	\end{figure}

	As the extraction progresses, the sensitivity values become less negative, moving towards zero. This gradual change corresponds to the decreasing concentration of the solute in the solid phase, which results in a diminishing concentration gradient and, consequently, a reduction in the rate of extraction. The sensitivity approaching zero suggests that the driving force for mass transfer is decreasing as the solute is being depleted. The asymptotic behaviour can be interpreted as a point where the remaining solute concentration in the solid phase is minimal and becomes less dependent on the mass flow rate. At this stage, other factors, such as internal diffusion within the solid matrix or equilibrium limitations, may limit the extraction rate.

	%The asymptotic approach to zero sensitivity indicates a physical plateau in the extraction process, where further increases in mass flow rate no longer enhance the extraction efficiency. In practical terms, this asymptotic behavior signifies the approach towards an extraction endpoint where the remaining solute concentration in the solid phase is minimal and becomes less dependent on the mass flow rate. At this stage, other factors, such as diffusion within the solid matrix or equilibrium limitations, may limit the extraction rate.

	%In the most extreme cases, depicted by the uniform regions in the plot, the solute has been effectively exhausted, and the remaining traces in the solid phase are no longer influenced by changes in the mass flow rate. This stage represents the final equilibrium, where the concentration gradient effectively drops to zero, rendering the mass flow rate inconsequential for the extraction of the remaining solute. At this juncture, the system has reached its thermodynamic limit, and the efficiency of extraction cannot be enhanced by merely increasing the flow rate. This underscores the importance of optimizing the mass flow rate at the beginning and throughout the extraction process to ensure efficient solute recovery before reaching this terminal stage.

	%Figure \ref{fig:Sensitivty_F_CS} shows how the flow rate affects the solute concentration in the solid phase. At the beginning of the extraction process, the flow rate has a low impact on the extraction process due to the dominance of the concentration gradient in the kinetic regime. The corresponding sensitivities are close to zero. As time progresses, the increment in the mass flow rate has a greater influence on the extraction kinetics, causing the sensitivities to decrease towards their minimum values. Negative sensitivities indicate a faster extraction rate.

	The Figure \ref{fig:Sensitivty_F_CF} depicts the sensitivity of the solute concentration in the fluid phase to the flow rate within a supercritical fluid extraction system. In the initial phase of the extraction, the sensitivities near the inlet are negligible, as characterized by values close to zero. This indicates a minimal initial response to changes in the flow rate, which could be due to the presence of an high concentration gradient, allowing the fluid phase to rapidly reach solute regardless of the flow rate.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_F.png}
		\caption{The effect of $F$ change on $C_f$}
		\label{fig:Sensitivty_F_CF}
	\end{figure}

	As the extraction progresses, positive sensitivities emerge along the length of the extractor and form the concentration front that moves in the flow direction. This front represents the increased movement of the solute with the fluid phase as the flow rate increases, suggesting an enhanced mass transfer due to the elevated velocity of the supercritical fluid. Following the positive front, there is an emergence of a front characterized by negative sensitivities. This trend illustrates a diminishing solute concentration in the fluid phase, and it reflects a point in the extraction where the solute availability in the solid phase becomes a limiting factor; the depletion of solute reduces the concentration gradient, thereby decelerating the extraction rate. \todo{here}

	Toward the end of the extraction process, the sensitivities are shown to increase from their negative values towards zero. This asymptotic approach suggests that the system is reaching a kinetic regime where further increases in the flow rate have a low impact on the solute concentration in the fluid phase. This behavior reflects a physical limit where the remaining solute in the solid phase is insufficient to sustain a high concentration in the fluid phase, regardless of the flow rate. It indicates a terminal phase of the extraction process where the available solute has been largely exhausted, and the system response to changes in flow rate is inherently constrained by the depletion of extractable material.

	%Figure \ref{fig:Sensitivty_F_CF} shows how the concentration of solute in the fluid phase responds to an increase in the flow rate. Initially, sensitivities are close to zero, indicating a minimal system response. The growth in flow rate affects $C_f(z,t)$ indirectly by increasing the velocity and consequently elevating the concentration gradient. As a result, positive sensitivities emerge within the system, forming a front that progresses in the direction of flow. The positive front indicates that the larger amount of solute moves faster across the system. When the amount of the solute in the solid phase becomes a limiting factor, then the concentration gradient diminishes and slows down the extraction kinetics. The corresponding sensitivities form a front composed of negative sensitivities propagating through the extractor. The negative front indicates that the solute concentration in the fluid phase becomes lower than before the flow rate increment. Eventually, the negative sensitivities start to increase and asymptotically approach zero.

	The Figure \ref{fig:Sensitivty_F_y} depicts the sensitivity of the extraction yield to variations in mass flow rate  as a function of time. The curve’s initial rise to a peak followed by a decline conveys the dynamic relationship between the mass flow rate and the extraction yield within the supercritical extraction process.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_F.png}
		\caption{The effect of $F$ change on $y(t)$}
		\label{fig:Sensitivty_F_y}
	\end{figure}

	In the early phase, the sensitivity is minimal, denoting that adjustments to the mass flow rate have a negligible influence on the yield. This can be attributed to the initial phase of the extraction, where the mass transport mechanisms are mainly controlled by a high concentration gradient.

	As the process evolves, the curve's ascent to its apex signifies a period during which the extraction yield becomes increasingly sensitive to the mass flow rate. This is likely due to the mass flow rate enhancing the convective transport of solute, maximizing the extraction efficiency. At this stage, the solute transfer from the solid to the fluid phase is most responsive to changes in flow rate.

	However, the curve’s descent past the peak suggests a diminishing return on sensitivity with further increases in mass flow rate. The decrease indicates a transitional phase where the extraction process likely encounters diffusion limitations or a depletion of readily extractable solute. The concentration gradient, which drives the mass transfer, may be reduced due to the depletion of solute in the solid phase, or the system may be experiencing diffusive resistances that limit the rate at which solute can be delivered to the fluid phase.

	The asymptotic approach to zero sensitivity towards the end of the curve reflects a regime where the yield is no longer significantly influenced by the mass flow rate. At this juncture, the extraction process has likely exhausted the available solute, and any further increase in mass flow rate does not result in a proportional increase in yield. The extraction system has reached a point of saturation or equilibrium where the mass transfer is limited by factors other than flow rate, such as the intrinsic properties of the solute or the matrix, indicating that the system has achieved as much extraction as is practically feasible under the given conditions.

	The curve captures the non-linear and transient nature of the extraction yield's response to the mass flow rate, underscoring the importance of optimizing flow rates over the duration of the extraction to maximize yield. It also highlights the multifaceted dependencies and constraints inherent in supercritical fluid extraction processes, such as mass transfer rates, solute availability, and diffusion limitations.

	%In Figure \ref{fig:Sensitivty_F_y}, the curve's shape reveals the time-dependent sensitivity of extraction yield to mass flow rate variations. The curve peaks and then falls, indicating a transient behavior in extraction efficiency. Initially, there's a negligible response, suggesting that changes in mass flow rate have little to no immediate impact on yield. As time progresses, however, yield becomes increasingly sensitive to the flow rate, reaching a peak sensitivity. Beyond this peak, the sensitivity decreases, which might reflect a saturation point in the extraction process where further increases in mass flow rate do not translate to increased yield, possibly due to limitations in solute diffusion rates from the solid matrix and decreasing concentration gradient. Eventually, $dy/dF$ asymptotically approaches zero. This happens because the amount of solute in the fluid phase becomes a limiting factor, and the process is in the diffusion regime.

\end{document}

### 2024-05-20 Sections/Sensitivity_Inlet_Temperature.tex
20.05

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsection{Inlet temperature}

	The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through it.

	Figure \ref{fig:Sensitivty_P_T} presents the sensitivity of the system's pressure response to changes in the inlet temperature over time during a supercritical fluid extraction process. The flat curve, hovering at zero, indicates a system where the pressure does not exhibit any response to changes in the inlet temperature throughout the entire operation period. In other words, the extraction system maintains a constant pressure regardless of any fluctuations in the temperature of the fluid entering the system. The invariance in pressure displayed in the Figure \ref{fig:Sensitivty_P_T} corroborates the model assumptions discussed in the Chapter X, where the pressure is assumed to be a control variable.

	%The Figure \ref{fig:Sensitivty_P_T} shows the system pressure response. A flat curve indicates an invariant behavior of pressure in response to inlet temperature changes throughout the time. The pressure in the modelled system is controlled and maintained independently of the inlet temperature variations as a results of the assumptions as explained in the Chapter X.

	%The sensitivity analysis of the inlet temperature differs from the two cases presented earlier because the perturbation does not affect the entire system instantaneously; instead, it propagates through the system. As the fluid with the modified temperature flows along the system, it gradually modifies the mass transfer parameters. One important assumption is that the inlet temperature change does not affect the pressure, which explains a horizontal line in Figure \ref{fig:Sensitivty_P_T}.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $P$ in the system}
		\label{fig:Sensitivty_P_T}
	\end{figure}

	Figure \ref{fig:Sensitivty_T_H} displays the sensitivity of the fluid enthalpy density to changes in the inlet temperature across the extraction bed over time. Given that the Dirichlet boundary conditions are applied to the system, any alteration in inlet temperature will have an immediate and localized effect on the enthalpy density at the entrance of the extraction column on the fluids enthalpy. This alteration results in a heat front propagation from the inlet to the outlet of the extractor as presented on the Figure \ref{fig:Sensitivty_T_H}. As time progresses, the impact of the inlet temperature on enthalpy diminish and the sensitivities converging towards zero. This convergence suggests that the system is reaching a new thermal equilibrium. The uniformity of the enthalpy at later times implies that the initial temperature perturbations have equilibrated throughout the bed, and the system has adapted to the new inlet temperature condition.

	%The inlet enthalpy is characterized by the Dirichlet boundary condition. The boundary value of $(h\times \rho)$ is calculated based on two controls which can be manipulated: inlet temperature and given pressure. Any deviation in $T_{in}$ affects $(h\times \rho)$ at the inlet, propagating according to the governing equations.
	%Figure \ref{fig:Sensitivty_T_H} showcases the sensitivity of the fluid enthalpy to the inlet temperature over both time and the length of the extraction bed. The fluid entering the extraction bed will have its enthalpy directly influenced by the boundary conditions. The heat front propagation from the inlet of the extractor to its outlet. As the fluid progresses through the bed, the enthalpy change affects the whole system gradually. Over time, the system's approach to a new thermal steady state and the sensitivities becomes zero.

	%The heat front propagation is presented in Figure \ref{fig:Sensitivty_T_H}. The initial system had constant temperature along the whole spatial domain.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $(h \times \rho)$ in the system}
		\label{fig:Sensitivty_T_H}
	\end{figure}

	Figure \ref{fig:Sensitivty_T_CS} shows the temporal and spatial sensitivity of the solute concentration in the solid phase to changes in the inlet temperature during a supercritical fluid extraction process. The positive sensitivities observed suggest that the solute concentration in the solid phase increases with rising inlet temperature. This initial increase could be attributed to a reduction in solute solubility in the supercritical fluid at higher temperatures or a slowdown in mass transfer kinetics. As presented in {\color{red}article 1}, a rise in temperature at constant pressure would increase solute diffusivity $D_i^R$ in supercritical fluids; however, the increase in concentration in the solid phase indicates other dominating factors, such as changes in solubility described by the solubility parameter ($\Upsilon$), which might decrease, thereby reducing the extraction rate.

	As the extraction progresses, the sensitivities flatten out and then decrease. Towards the end of the extraction period, the sensitivities approach a positive constant, implying that the effect of inlet temperature on the concentration of the solute in the solid phase becomes negligible. This behaviour can be explained if it assumed that the extraction kinetic slowed because at the high temperature, which leads to higher concentration gradient in the later part of the process. The reduced availability of extractable solute in the later part of the process corresponds to the diminishing of the sensitivity.

	%Figure \ref{fig:Sensitivty_T_CS} shows the curve depicts an initial increase (the positive sign of the sensitivities) in the solute concentration in the solid phase as a function of time, which later asymptotically approaches a stable value before decreasing again towards the end of the period. Although $D_i^R$ decreases with the fluid's density, the $\Upsilon$ increases, which explains the system responses. This suggests that an increase in temperature slows the mass transfer of solutes from the solid phase to the supercritical fluid; hence, the solute concentration in the solid phase increases. Over time, this effect stabilizes, which could indicate the exhaustion of easily extractable solutes.

	%Figure \ref{fig:Sensitivty_T_CS} illustrates how the change in inlet temperature affects the concentration of solute in the solid phase. As presented in {\color{red}article 1}, the value of $D_i^R$ decreases as density decreases. Therefore, it is expected to observe positive sensitivities in Figure \ref{fig:Sensitivty_T_CS}, indicating a slower extraction rate. Initially, the sensitivities are zero along the fixed bed because the heat front requires time to reach the fixed bed. Since this propagation is not instantaneous, a non-uniform distribution of sensitivities along the fixed bed becomes evident. All the sensitivities gradually increase until they reach their maximum. When the concentration gradient becomes the limiting factor, the sensitivities decrease.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $C_s$ in the system}
		\label{fig:Sensitivty_T_CS}
	\end{figure}

	The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature. In the initial phase of the process, indicated by the area where sensitivities are at or near zero, there is a lack of response, likely reflecting an idle period or delay as the system adjusts to the new inlet temperature. This could represent the time needed for the thermal front to propagate through the system and influence the solubility and mass transfer rates of the solutes. As the warmer fluid begins to interact with the solid phase, the negative sensitivities are observed. These negative values imply a decrease in solute concentration within the fluid phase, which might be attributed to a reduced diffusion coefficient ($D_i^R$) due to increased fluid viscosity at higher temperatures, or possibly due to a change in the solubility ($\Upsilon$) of the solute with temperature. If the solubility decreases with temperature for the given solute, an increase in temperature could indeed result in a lower solute concentration in the fluid phase. Later the sensitivities starts to increase due higher concentration gradient if compared to before the temperature change. Towards the end of the time period, the figure shows the sensitivities stabilizing at a constant value. Eventually, the system response stabilize around a constant value when the extraction kinetics become a limiting factor.

	%The Figure \ref{fig:Sensitivty_T_CF} represents the sensitivity of the concentration of solutes in the fluid phase over a period of 600 minutes as a result of changes in the inlet temperature. Initially, all the sensitivities remain at zero due to the idle period. As the fluid with elevated temperature flows through the fixed bed, the internal mass transfer slows down (the $D_i^R$ is proportional to density as presented in {\color{red}article 1}), resulting in negative sensitivities. The negative sensitivities can be explained by considering that the heat front slowed mass transfer, causing more solute to remain in the solid phase. After reaching their minima, the sensitivities increase and reach positive values. Later the sensitivities starts to increase due higher concentration gradient if compared to before the temperature change. Eventually, the system response stabilize around a constant value when the extraction kinetics become a limiting factor.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $C_f$ in the system}
		\label{fig:Sensitivty_T_CF}
	\end{figure}

	Figure \ref{fig:Sensitivty_T_y} shows the time-dependent response of the extraction yield's sensitivity to changes in the inlet temperature. Initially, there is no change in yield as the heat front needs to propagate the along the system. That delayed response, cause the yield sensitivity to stay flat at the beginning of the extraction.

	As the system starts responding, a small increase in sensitivity can be observed, which indicates a transient enhancement in yield. This is due to the velocity of the fluid, which is inversely proportional to density. The sensitivity peak comes from the fact that the fluid moves faster across the system, while the mass transfer kinetic is mainly driven by high concentration gradient.

	Subsequently, the sensitivity curve descends into negative territory, suggesting that the increased inlet temperature eventually reduces the extraction efficiency. As explained above, due to complex relation between temperature and various mass transfer parameters, including the solubility of different compounds and the diffusivity within the supercritical fluid, the temperature increase might have a negatively affected on the extraction efficiency. The minimum point reached by the sensitivity curve implies a period where the yield is affected the most by the temperature increase.

	Afterward, the curve's gradual ascent towards zero reflects a stabilizing effect. The curve eventually flattens out, maintaining a slightly negative sensitivity, suggesting that while the system has reached a new quasi-steady state. The overall yield remains slightly compromised compared to the baseline. At this point, the extraction process is limited by availability of the solute in the solid particles.	This extended simulation offers a comprehensive view of how inlet temperature variations can impact the extraction yield over time.

	%Figure \ref{fig:Sensitivty_T_y} depicts how an increase in inlet temperature alters the extraction yield. Initially, the sensitivity curve remains flat due to the idle time. The first observed response of the system is a small increment of the $dy/dT_{in}$ caused by an increment of the velocity( which is inversely proportional to the fluid density). After the small positive peak, the sensitivity curve begins to decrease. The negative value of the sensitivity indicates a lower process efficiency. Over time, the sensitivity reaches its minimum and then increases due to a higher concentration gradient than in the case without the disturbance. Eventually, the $dy/dT_{in}$ curve flattens around a negative value. The flattening of the yield curve suggests that the mass transfer parameters limit the extraction rate, and the residual solute in the solid phase becomes difficult to obtain. The simulation time was extended to show how the sensitivity plot flattened.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_T_{in}.png}
		\caption{The effect of $T_{in}$ change on $y(t)$ in the system}
		\label{fig:Sensitivty_T_y}
	\end{figure}

\end{document}

### 2024-05-20 Sections/Sensitivity_Pressure.tex
20.05

\documentclass[../Article_Sensitivity_Analsysis.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\subsection{Pressure}

	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow. If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic. The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system. A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the device. A step-function shown on Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/P_P.png}
		\caption{The effect of $P$ change on $P$ in the system}
		\label{fig:Sensitivty_P_P}
	\end{figure}

	\todo{caption and label}

	The model is build such that the pressure change first affects the energy balance through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}. In the following time step, the energy balance response becomes noticeable, as does the change in the physical properties of the solvent. The uniform response across the entire extraction column length and time, represented by the homogeneously dark red colour, indicates that the entire system experiences an immediate and uniform change in enthalpy density in response to pressure changes.

	The pressure change affects the fluid's temperature inside the computational domain, but boundary values are subject to constraints specified at the extremes of that domain. Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which can lead to a thermal gradient propagating along the system. In contrast, Neumann boundary conditions would dictate the heat flux at the boundaries. In this work, the Neumann boundary conditions equal to zero have been applied, which leads to a uniform response and ensures that the temperatures at the inlet, the outlet, and the middle of the extractor are the same.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/H_P.png}
		\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
		\label{fig:Sensitivty_P_H}
	\end{figure}

	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase with respect to pressure change along a fixed bed in a supercritical fluid extraction process. As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that with higher fluid density, the velocity decreases. This leads to an extended residence time, ergo, a longer interaction between the solute and the solvent. Initially, the extraction process is in the kinetically-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility. As discussed in ({\color{red}article 1}), the system is considered to be far from saturation, which can explain the low system response at the beginning of the process. The system response becomes more evident when the concentration gradient diminishes, and the extraction moves from the kinetic-controlled to the diffusion-controlled regime. The negative sign can be interpreted as a faster loss of a solute from the solid phase, which corresponds to enhanced mass transfer. Over time, the amount of solute becomes a limiting factor, and the pressure change has a lower effect on the system, increasing the negative sensitivities. Eventually, sensitivities approach zero asymptotically. The solute concentration in the solid phase has been reduced, and further changes in pressure have a low influence on the state space.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CS_P.png}
		\caption{The effect of $P$ change on $C_s$}
		\label{fig:Sensitivty_P_CS}
	\end{figure}

	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase with respect to the pressure change. As analysed above, an increase in pressure enhances the mass transfer, resulting in the concentration front moving through the system. The system response is initially low, reflecting the idle period discussed above. Later, the sensitivities start to increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase. When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, sensitivities decline asymptotic towards zero, and the impact of the pressure change gradually decreases. As the fluid phase is mobile, the advection affects the sensitivities, which causes the sensitivities to move along the system analogously to the solute in the fluid phase.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CF_P.png}
		\caption{The effect of $P$ change on $C_f$}
		\label{fig:Sensitivty_P_CF}
	\end{figure}

	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to the pressure change. Initially, the sensitivity curve stays almost flat, suggesting a latency in the system's response to pressure changes. Due to the decreased velocity of the fluid, the solute reaches the extractor's outlet later, which causes minor negative sensitivities to appear. The process continues, and the sensitivity curve increases rapidly when the solute reaches the extractor's outlet. The positive yield sensitivity indicates an improvement in the process efficiency, which is directly related to enhanced mass transfer. The peak in $\frac{dy}{dP}$ reflects when the deviation from the original system is the largest. Beyond the peak, the sensitivity declines and converges towards zero. The concentration gradient becomes a limiting factor, and the enhanced mass transfer no longer plays a dominant role compared to the original system.

	\begin{figure}[h!]
		\centering
		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/Y_P.png}
		\caption{The effect of $P$ change on $y(t)$}
		\label{fig:Sensitivty_P_y}
	\end{figure}

\end{document}

### 2024-05-20 Sections/introduction_imp.tex
20.05

@@
 	Evaluating the economic viability of the process is essential when choosing the suitable technology for essential oil extraction.
-Traditional methods, such as distillation and organic solvent extraction, are commonly employed but come with drawbacks.
+Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
 Distillation, for example, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
@@
 
-	This study focuses on finding a process model for the extraction of natural substances from solid materials using supercritical fluids, with a particular emphasis on supercritical CO$_2$.
-The approach involves estimating the solvent properties through thermodynamic relationships and determining the extraction kinetic parameters via a series of experiments conducted under a variety of conditions.
-The maximum likelihood estimation is employed to solve the parameter estimation problem.
-Later, the correlations between parameters and operating conditions are proposed.
-
 \end{document}

### 2024-05-20 Sections/Cardano.tex
Updates from Overleaf

@@
 
-	Following the work of \citet{Gmehling2019}, a cubic equation of state can be written a following form
+	Following the work of \citet{Gmehling2019}, a cubic equation of state can be written in the following form
 
@@
 
-	with Z as the compressibility factor. Using Cardano's formula, this type of equation can be solved analytically.
+	where Z is the compressibility factor. Cubic equations can be solved analytically using Cardano's formula.
 
@@
 
-	the discriminant can be determined to be
+	The discriminant can be determined to be
 
@@
 
-	they can be written as
+	They can be written as
 
@@
 
-	The largest and the smallest of the three values correspond to the vapor and to	the liquid solutions, respectively. The middle one has no physical meaning.
+	The largest and smallest are the vapour and liquid phases, respectively. The middle one has no physical interpretation.
 

### 2024-05-20 Sections/Literature_Review.tex
Updates from Overleaf

@@
 
-	This study aims to analyze the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
+	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
 The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature.
@@
 Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output.
-The aim is to understand and to allocate the source of uncertainty in the output to the corresponding inputs or parameters.
+The aim is to understand and allocate the source of uncertainty in the output to the corresponding inputs or parameters.
 There are many sensitivity analysis methods, which include but are not limited to those listed below:
@@
 
-	Different supercritical extraction models were analyzed using sensitivity analysis.
+	Different supercritical extraction models were analysed using sensitivity analysis.
 \citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed.

### 2024-05-20 Sections/Model.tex
Updates from Overleaf

@@
 
-	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and thermodynamic pressure are known along $z$.
+	The fluid density $\rho_f$ can be obtained from an equation of state ({\color{red}article 1}) if temperature and thermodynamic pressure are known along $z$.
 The fluid density variation may occur due to pressure or inlet temperature changes.

### 2024-05-20 Sections/Saturation.tex
20.05
Updates from Overleaf

@@
 
-	Following the idea of the Broken-and-Intact Cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is consider to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}.
+	Following the idea of the Broken-and-Intact Cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}.
 
@@
 
-	Alternatively, the decay function $\gamma$ can be consider with respect to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius change as the amount of solute in the solid phase decrease.
+	Alternatively, the decay function $\gamma$ can be interpreted by referring to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius changes as the amount of solute in the solid phase decreases.
 As the particle size decreases due to dissolution, the diffusion path increases, which makes the diffusion slower and reduces the value of a diffusion coefficient.

### 2024-05-20 Sections/Sensitivity_Analysis.tex
Updates from Overleaf

@@
 
-	Local derivative-based methods involve taking the partial derivative of the output with respect to an input parameter.
-This set of derivatives, known as sensitivity equations, is solved simultaneously with the process model.
-The sensitivity analysis aims to investigate how responsive the solution is for the perturbation of the parameter ${p}$.
+	Local derivative-based methods involve taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of the parameter space $\theta$.
+This set of derivatives, known as sensitivity equations, is integrated simultaneously with the process model.
+The sensitivity analysis investigates how responsive the solution is for the perturbation of the parameter $p$.
 As discussed by \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
@@
 
-	As presented in the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) are developed by taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of the parameter space $\theta$.
+	Following the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) can be defined as follow:
 
@@
 		\begin{align}
-			%		\label{SA_def}
-			{Z}({x}(t);{p}) &= \cfrac{d {x}(t)}{d {p}}
+			\label{SA_def}
+			{Z}(x(t);p) &= \cfrac{dx(t)}{dp}
 	\end{align} }
@@
 		\begin{equation} \label{SA_dt} 
-			{\dot{Z}}({x}(t);{p})  = \cfrac{d {Z}(x(t);{p})}{d t} = \cfrac{d}{d t} \left( \cfrac{d {x}(t)}{d {p}} \right) = \cfrac{d }{d {p}} \left( \cfrac{d {x}(t)}{d t} \right) = \cfrac{d {G}({x}(t);{p})}{d {p}}
+			{\dot{Z}}(x(t);p)  = \cfrac{dZ(x(t);p)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx(t)}{dp} \right) = \cfrac{d }{dp} \left( \cfrac{dx(t)}{d t} \right) = \cfrac{d {G}(x(t);p)}{dp} 
 	\end{equation} }
@@
 	{\footnotesize
-		\begin{align}		
-			\label{SA_eq_full}\cfrac{d {G}({x}(t);{p})}{d {p}} &=  \underbrace{ \cfrac{\partial {G}({x}(t);{p})}{\partial {x}(t)} }_{{J_x}({x}(t);{p})} \underbrace{\cfrac{\partial {x}(t)}{\partial {p}} }_{{S}({x}(t);{p})} + \underbrace{ \cfrac{\partial {G}({x}(t);{p})}{\partial {p}} }_{{J_p}({x}(t);{p})}
-	\end{align} }
+		\begin{equation} \label{SA_eq_full}
+			\cfrac{dG(x(t);p)}{dp} = \underbrace{ \cfrac{\partial {G}(x(t);p)}{\partial x(t)} }_{{J_x}(x(t);p)} \underbrace{\cfrac{\partial x(t)}{\partial p} }_{S(x(t);p)} + \underbrace{ \cfrac{\partial {G}(x(t);p)}{\partial p} }_{{J_p}(x(t);p)}
+	  \end{equation} }
 
-	The sensitivity Equation \ref{SA_eq_full} is solved simultaneously with the original system and is made of three terms: jacobian ${J_x}({x}(t);{p})$, sensitivity matrix ${S}({x}(t);{p})$ and jacobian ${J_p}({x}(t);{p})$.
-The jacobian ${J_x}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${G}_{n_x}({x}(t);{p})$ with respect to the state variable $x_{n_p}$.
+	The sensitivity Equation \ref{SA_eq_full} is solved simultaneously with the original system and is made of three terms: Jacobian ${J_x}(x(t);p)$, sensitivity matrix $S(x(t);p)$ and Jacobian ${J_p}(x(t);p)$.
+The Jacobian ${J_x}(x(t);p)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${G}_{n_x}(x(t);p)$ with respect to the state variable $x_{n_p}$.
 
@@
 			\setlength\arraycolsep{2pt}
-			{J_x}({x}(t);{p})=\begin{pmatrix}
-				\cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
-				\cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
+			{J_x}(x(t);p)=\begin{pmatrix}
+				\cfrac{\partial {G_{1}}(x(t);p)}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {x_{N_x}}(t)}\\
+				\cfrac{\partial {G_{2}}(x(t);p)}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {x_{N_x}}(t)}\\
 				\vdots & \vdots & \ddots & \vdots\\ 
-				\cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {x_{N_x}}(t)}\\
+				\cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {x_{N_x}}(t)}\\
 			\end{pmatrix}
@@
 
-	The sensitivity matrix ${S}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${S}(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
+	The sensitivity matrix $S(x(t);p)$ represents the matrix of equations of size $N_x \times N_p$, where each subequation $S(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
 
@@
 			\begin{split}
-				{S}({x}(t);{p}) & = 
-				%				\begingroup % keep the change local
-				%				\setlength\arraycolsep{2pt}
-				%				\begin{pmatrix}
-					%					{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
-					%					{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
-					%					\vdots & \vdots & \ddots & \vdots\\
-					%					{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
-					%				\end{pmatrix}
-				%				\endgroup
-				%				=\\
-				%				&=
+				S(x(t);p) & = 
 				\begingroup % keep the change local
@@
 
-	The jacobian ${J_p}({x}(t);{p})$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
+	The Jacobian ${J_p}(x(t);p)$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
 
@@
 		\begin{align}
-			{J_p}({x}(t);{p}) & =
+			{J_p}(x(t);p) & =
 			\begingroup % keep the change local
@@
 			\begin{pmatrix}
-				\cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{1}}({x}(t);{p})}{\partial {p_{N_p}}}\\
-				\cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{2}}({x}(t);{p})}{\partial {p_{N_p}}}\\
+				\cfrac{\partial {G_{1}}(x(t);p)}{\partial {p_{1}}} & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {p_{N_p}}}\\
+				\cfrac{\partial {G_{2}}(x(t);p)}{\partial {p_{1}}} & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {p_{N_p}}}\\
 				\vdots & \vdots & \ddots & \vdots\\
-				\cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{1}}} & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}({x}(t);{p})}{\partial {p_{N_p}}}
+				\cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {p_{1}}} & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {p_{N_p}}}
 			\end{pmatrix}
@@
 
-	The combined system containing the original set of equations ${G}({x}(t);{p})$ and sensitivity equations can be formulated as ${\textbf{G}}\left({x}(t);{p}\right)$.
-The size of ${\textbf{G}}\left({x}(t);{p}\right)$ is equal to $N_s = N_x(N_p + 1)$.
+	The combined system containing the original set of equations ${G}(x(t);p)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x(t);p\right)$.
+The size of ${\textbf{G}}\left(x(t);p\right)$ is equal to $N_s = N_x(N_p + 1)$.
 
@@
 		\begin{align}
-			{\textbf{G}}\left({x}(t);{p}\right) = 
+			{\textbf{G}}\left(x(t);p\right) = 
 			\begin{bmatrix}
-				{G}({x}(t);{p})\\
-				{J_x}({x}(t);{p}){S}({x}(t);{p}) + {J_p}({x}(t);{p})
+				{G}(x(t);p)\\
+				{J_x}(x(t);p)S(x(t);p) + {J_p}(x(t);p)
 			\end{bmatrix}
@@
 		\begin{align}
-			{\textbf{G}}\left({x}(t_0);{p}\right)  = 
-			\begin{bmatrix} {x}(t_0),						& 
-				\cfrac{ \text{d}{x}(t_0) }{ d{p_1} },		& 
+			{\textbf{G}}\left(x(t_0);p\right)  = 
+			\begin{bmatrix}x(t_0),						& 
+				\cfrac{ \text{d}x(t_0) }{ d{p_1} },		& 
 				\cdots,					 				&
-				\cfrac{ d{x}(t_0) }{ d{p_{N_p}} } 
+				\cfrac{ dx(t_0) }{ d{p_{N_p}} } 
 			\end{bmatrix}^T
@@
 
-	The sensitivity analysis of the output function can be performed with respect to parameters ${p}$.
-The output function ${g}({x}(t))$ returns ${y}(t)$.
-By taking a total derivative of ${y}(t)$ with respect to ${p}$, the new sensitivity equation can be found.
+	The sensitivity analysis of the output function can be performed with respect to parameters $p$.
+The output function $g(x(t))$ returns ${y}(t)$.
+By taking a total derivative of ${y}(t)$ with respect to $p$, the new sensitivity equation can be found.
 
 	{\footnotesize
-		\begin{align}
-			\cfrac{d {y}(t)}{d{p}} = \cfrac{d {g}({x}(t))}{d{p}} = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)} \cfrac{\partial {x}(t)}{\partial {p}} + \cfrac{\partial {g}({x}(t))}{\partial {p}}
-	\end{align} }
-
-%	The ${g}({x}(t))$ itself is independent of the parameters, but it dependents on ${x}(t)$, which is the function of ${p}$. In such a case the sensitivity equation for the output becomes
-%	
-%	{\footnotesize
-%		\begin{equation} \label{EQ:Output_sens_full}
-%			\cfrac{d {g}({x}(t))}{d {p}} = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)} \cfrac{\partial {x}(t)}{\partial {p}} + 0 = \cfrac{\partial {g}({x}(t))}{\partial {x}(t)}  {S}({x}(t);{p}) = 
-%		\end{equation} 
-%		
-%		\begin{equation} 
-%			= \begingroup % keep the change local
-%			\setlength\arraycolsep{2pt}
-%			\begin{pmatrix}
-%				\cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{1}}({x}(t))}{\partial {x_{N_x}}}\\
-%				\cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{2}}({x}(t))}{\partial {x_{N_x}}}\\
-%				\vdots & \vdots & \ddots & \vdots\\
-%				\cfrac{\partial {g_{N_g}}({x}(t))}{\partial {x_{1}}} & \cfrac{\partial {g_{N_g}}({x}(t))}{\partial {x_{2}}} & \cdots & \cfrac{\partial {g_{N_g}}({}(t))}{\partial {x_{N_x}}}
-%			\end{pmatrix}
-%			\begin{pmatrix}
-%				{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
-%				{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
-%				\vdots & \vdots & \ddots & \vdots\\
-%				{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
-%			\end{pmatrix}
-%			\endgroup
-%	\end{equation} }
-
-%	Keeping in mind that the output function returns only one value, the sensitivity equation of the output (\ref{EQ:Output_sens_full}) becomes:
-%	
-%	{\footnotesize
-%		\begin{equation} \label{EQ:Output_sens_short}
-%			\begin{split}
-%				& \left( \cfrac{d {y}({x}(t))}{d {p_{1}}}, \cfrac{d {y}({x}(t))}{d {p_{2}}}, \cdots, \cfrac{d {y}({x}(t))}{d {p_{N_p}}} \right)  = \\
-%				& =  \left( \cfrac{\partial {g}({x}(t))}{\partial {x_{1}}}, \cfrac{\partial {g}({x}(t))}{\partial {x_{2}}}, \cdots, \cfrac{\partial {g}({x}(t))}{\partial {x_{N_x}}} \right)
-%				\begingroup % keep the change local
-%				\setlength\arraycolsep{2pt}
-%				\begin{pmatrix}
-%					{s_{({1,1})}} & {s_{({1,2})}} & \cdots & {s_{({1,N_p})}}\\
-%					{s_{({2,1})}} & {s_{({2,2})}} & \cdots & {s_{({2,N_p})}}\\
-%					\vdots & \vdots & \ddots & \vdots\\
-%					{s_{({N_x,1})}} & {s_{({N_x,2})}} & \cdots & {s_{({N_x,N_p})}}\\
-%				\end{pmatrix} \endgroup
-%			\end{split}
-%	\end{equation} }
+		\begin{equation}
+			\cfrac{d {y}(t)}{dp} = \cfrac{d g(x(t))}{dp} = \cfrac{\partial g(x(t))}{\partial x(t)} \cfrac{\partial x(t)}{\partial p} + \cfrac{\partial g(x(t))}{\partial p}
+	   \end{equation} }
 

### 2024-05-20 Sections/Sensitivity_Pressure.tex
Updates from Overleaf

@@
 A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the device.
-A step-function shown on Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change.
+A step-function shown in Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change.
 
@@
 
-	The model is build such that the pressure change first affects the energy balance through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
+	The model is built such that the pressure change first affects the energy balance through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
 In the following time step, the energy balance response becomes noticeable, as does the change in the physical properties of the solvent.
-The uniform response across the entire extraction column length and time, represented by the homogeneously dark red colour, indicates that the entire system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
+The uniform response across the entire extraction column length and time, represented by the homogeneously dark red colour, indicates that the whole system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
 
@@
 The system response becomes more evident when the concentration gradient diminishes, and the extraction moves from the kinetic-controlled to the diffusion-controlled regime.
-The negative sign can be interpreted as a faster loss of a solute from the solid phase, which corresponds to enhanced mass transfer.
+The negative sign can be interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
 Over time, the amount of solute becomes a limiting factor, and the pressure change has a lower effect on the system, increasing the negative sensitivities.
@@
 	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase with respect to the pressure change.
-As analysed above, an increase in pressure enhances the mass transfer, resulting in the concentration front moving through the system.
+As analysed above, increased pressure enhances the mass transfer, moving the concentration front through the system.
 The system response is initially low, reflecting the idle period discussed above.
-Later, the sensitivities start to increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase.
+Later, the sensitivities increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase.
 When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, sensitivities decline asymptotic towards zero, and the impact of the pressure change gradually decreases.
@@
 The process continues, and the sensitivity curve increases rapidly when the solute reaches the extractor's outlet.
-The positive yield sensitivity indicates an improvement in the process efficiency, which is directly related to enhanced mass transfer.
+The positive yield sensitivity indicates improved process efficiency, which is directly related to enhanced mass transfer.
 The peak in $\frac{dy}{dP}$ reflects when the deviation from the original system is the largest.

### 2024-05-22 Article_Sensitivity_Analsysis_short-Chamomile.tex
Updates from Overleaf

@@
 \begin{abstract}
-This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers.
-The distributed-parameter model describes the fluid-solid extraction process.
-The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
-The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model.
-The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.
+The article presents a comprehensive study on the supercritical fluid extraction of essential oil from chamomile flowers, focusing on model dynamics and applying a distributed-parameter model to describe the fluid-solid extraction process.
+By employing the concept of quasi-one-dimensional flow, the study simplifies the spatial dimensions of the extraction process, ensuring uniform flow across any cross-section while allowing for variations in the area available for the fluid phase.
+The physical properties of the solvent are estimated using the Peng-Robinson equation of state.
+The model was validated under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The model dynamic is investigated by analysing how sensitive the model output is to model parameters.
+In this work, the local sensitivity analysis is introduced and used to examine the influence of infinitely small changes in the pressure on the state space and the extraction yield.
 
@@
 
-\clearpage \appendix \label{appendix}
-\section{Appendix}
-
-%\subsection{Thermodynamic}
-\subfile{Sections/Qubic_EOS} \label{CH: EOS}
-
-\subsection{Cardano's Formula} \label{CH: Cardano}
-\subfile{Sections/Cardano}
+%\clearpage \appendix \label{appendix}
+%\section{Appendix} 
+%\subfile{Sections/Qubic_EOS} \label{CH: EOS}
+%\subsection{Cardano's Formula} \label{CH: Cardano}
+%\subfile{Sections/Cardano}
 

### 2024-05-22 Sections/Literature_Review.tex
Updates from Overleaf

@@
 
-	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
-The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature.
+	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction model described in {\color{red}article 1}.
 The relation between input and output is obtained by applying a sensitivity analysis.
@@
 This allows to evaluate the effect of the uncertainties on model predictions.
-The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are significant for the extraction process.
-The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
+The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are the most influential factors in the extraction process.
+The effect of changing operating conditions was also investigated, underlining how solvent flow rate and seed milling affect extraction.
 
-	\citet{Santos2000}, in their work, considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent.
-The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.
+	In the work of \citet{Santos2000}, a diffusive model for the semi-continuous, isothermal, and isobaric extraction process is analysed by a parametric sensitivity analysis using a factorial design in two levels.
+The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of nominal values of velocity, particle diameter, and initial concentration in the solid and liquid phases.
+The authors concluded that it is necessary to determine the optimum particle diameter and manipulate the solvent superficial velocity to control the process.
 
-	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables.
-Their findings show that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
+	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis and employed two distinct strategies to conduct their analysis: the first strategy involved applying an equal fluctuation to all technical and economic parameters, while the second strategy utilised real ranges for fluctuating these parameters.
+The authors found that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
+Moreover, in this study tried to determine rhe upper and lower bounds for technical and economic factors, utilizing pertinent literature data.
 
-	\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils and applied a sensitivity analysis.
-They found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process.
+	\citet{Poletto1996} provided a general dimensionless model for the supercritical vegetable and essential oils extraction process and applied a sensitivity analysis.
+They found that a dimensionless partition coefficient and a dimensionless characteristic time are the most influential parameters of the extraction process.
 The sensitivity calculations were performed by varying the parameters and analysing the model response.

### 2024-05-22 Sections/Model.tex
Updates from Overleaf

@@
 
-			\subsubsection{Pressure term} \label{CH: Pressure}
-
-			The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time.
-As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial P/\partial t$ can be approximated by an difference equation, which describes the change of pressure in the whole system.
-The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
-
-			{\footnotesize
-				\begin{equation}
-					\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P_{in}}(t) - {\color{black}P}(t) }{\Delta t}
-			\end{equation}}
-
-			Such a simplified equation takes into account the pressure change in the energy balance, but the dynamics are simplified and do not consider the effects of pressure losses.
-In a real system, the dynamics of pressure change would depend on a pump used in an extraction system, as well as a back-pressure regulator used to control an outlet valve.
-
 			\subsubsection{Heat balance} \label{CH: heat_balance}
@@
 				\begin{equation}
-					\underbrace{h\left(t,x\right)}_{\text{Heat balance}}=\underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}}
+					\min_T \left( \underbrace{h\left(t,x\right)}_{\text{Heat balance}} - \underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}} \right)^2
 					\label{EQ:Enthalpy_root}
@@
 			}
+
+            \subsubsection{Pressure term} \label{CH: Pressure}
+
+			The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time.
+As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, which describes the pressure change in the whole system.
+The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
+
+			{\footnotesize
+				\begin{equation}
+					\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P_{in}}(t) - {\color{black}P}(t) }{\Delta t}
+			\end{equation}}
+
+			Such a simplified equation allows for instantaneous pressure change in the system but does not consider a gradual pressure build-up and the effects of pressure losses.
+In a real system, the dynamics of pressure change would depend on a pump used in an extraction system and a back-pressure regulator used to control an outlet valve.
 

### 2024-05-23 Sections/Sensitivity_Pressure.tex
Updates from Overleaf

@@
 
-	\subsection{Pressure}
+    %\subsection{Pressure}
 
@@
 A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the device.
-A step-function shown in Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change.
+A step-function shown in Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change in the extractor.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/P_P.png}
-		\caption{The effect of $P$ change on $P$ in the system}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/P_P_1.png}
+		\caption{The effect of $P_{in}$ change on $P$ in the system}
 		\label{fig:Sensitivty_P_P}
@@
 
-	\todo{caption and label}
-
-	The model is built such that the pressure change first affects the energy balance through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
-In the following time step, the energy balance response becomes noticeable, as does the change in the physical properties of the solvent.
-The uniform response across the entire extraction column length and time, represented by the homogeneously dark red colour, indicates that the whole system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
+	The model is built such that the pressure change first affects $\frac{dP}{dt}$, and in the next time step, the energy balance through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
+The energy balance response becomes noticeable, as well as the change in the physical properties of the solvent.
+The uniform response across the entire extraction column length, represented by the homogeneously dark red colour, indicates that the whole system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
 
@@
 In contrast, Neumann boundary conditions would dictate the heat flux at the boundaries.
-In this work, the Neumann boundary conditions equal to zero have been applied, which leads to a uniform response and ensures that the temperatures at the inlet, the outlet, and the middle of the extractor are the same.
+In this work, the Neumann boundary conditions equal to zero were applied to ensure that the temperatures at the inlet, the outlet, and the middle of the extractor are the same all the time.
 
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/H_P.png}
-		\caption{The effect of $P$ change on $(h \times \rho)$ in the system}
+		\caption{The effect of $P_{in}$ change on $(h \times \rho)$ in the system}
 		\label{fig:Sensitivty_P_H}
@@
 	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase with respect to pressure change along a fixed bed in a supercritical fluid extraction process.
-As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that with higher fluid density, the velocity decreases.
+As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that the pressure increase decreases the velocity.
 This leads to an extended residence time, ergo, a longer interaction between the solute and the solvent.
@@
 As discussed in ({\color{red}article 1}), the system is considered to be far from saturation, which can explain the low system response at the beginning of the process.
-The system response becomes more evident when the concentration gradient diminishes, and the extraction moves from the kinetic-controlled to the diffusion-controlled regime.
+The system response becomes more evident when the concentration gradient starts diminishing, and the extraction switches from the kinetic-controlled to the diffusion-controlled regime.
 The negative sign can be interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
 Over time, the amount of solute becomes a limiting factor, and the pressure change has a lower effect on the system, increasing the negative sensitivities.
-Eventually, sensitivities approach zero asymptotically.
-The solute concentration in the solid phase has been reduced, and further changes in pressure have a low influence on the state space.
+Sensitivities approach zero asymptotically when the solid bed is exhausted of the solute.
 
-	\begin{figure}[h!]
+	\begin{figure}[!ht]
 		\centering
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CS_P.png}
-		\caption{The effect of $P$ change on $C_s$}
+		\caption{The effect of $P_{in}$ change on $C_s$}
 		\label{fig:Sensitivty_P_CS}
@@
 
-	Figure \ref{fig:Sensitivty_P_CF} shows the sensitivity of the solute concentration in the fluid phase with respect to the pressure change.
-As analysed above, increased pressure enhances the mass transfer, moving the concentration front through the system.
-The system response is initially low, reflecting the idle period discussed above.
+	Figure \ref{fig:Sensitivty_P_CF} shows how sensitive is the solute concentration in the fluid phase to the pressure change.
+Although the pressure increase enhances the mass transfer, the system response is initially low, which reflects the idle period discussed above.
 Later, the sensitivities increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase.
 When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, sensitivities decline asymptotic towards zero, and the impact of the pressure change gradually decreases.
-As the fluid phase is mobile, the advection affects the sensitivities, which causes the sensitivities to move along the system analogously to the solute in the fluid phase.
+As the fluid phase is mobile, the advection causes the sensitivities to move along the system analogously to the solute in the fluid phase.
 
-	\begin{figure}[h!]
+	\begin{figure}[!ht]
 		\centering
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CF_P.png}
-		\caption{The effect of $P$ change on $C_f$}
+		\caption{The effect of $P_{in}$ change on $C_f$}
 		\label{fig:Sensitivty_P_CF}
@@
 
-	\begin{figure}[h!]
+	\begin{figure}[!ht]
 		\centering
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/Y_P.png}
-		\caption{The effect of $P$ change on $y(t)$}
+		\caption{The effect of $P_{in}$ change on $y(t)$}
 		\label{fig:Sensitivty_P_y}

### 2024-05-24 Sections/Model.tex

@@
 			\subsubsection{Initial and boundary conditions} 
-			It is assumed that the solvent is free of solute at the beginning of the process $c_{f0}=0$, that all the solid particles have the same initial solute content $c_{s0}$, and that the system is isothermal.
-The fluid at the inlet is also considered not to contain any solute.
-As the residence time is much shorter than the sampling time, the initial state estimate for the solute concentration in the fluid phase would be unreliable.
+			It is assumed that the solvent is free of solute at the beginning of the process $c_{f0}=0$, that all the solid particles have the same initial solute content $c_{s0}$, and that the system is isothermal, hence the initial state is $h_0$.
+The fluid at the inlet is considered not to contain any solute.
 The initial and boundary conditions are defined as follows:
@@
 					\begin{align*} \label{discretization}
-						\dot{{\color{black}x}}(t) &= \cfrac{d x}{d t} = 
+						\dot{x}(t) &= \cfrac{d x}{d t} = 
 						\begin{bmatrix}
-							\cfrac{d {\color{black}c_{f,1}}(t)}{d t} 	  \\
+							\cfrac{d c_{f,1}(t)}{d t} 	  \\
 							\vdots					  \\
-							\cfrac{d {\color{black}c_{f,N_z}}(t)}{d t} \\
+							\cfrac{d c_{f,N_z}(t)}{d t} \\
 							\\ \hline \\
-							\cfrac{d {\color{black}c_{s,1}}(t)}{d t} 	  \\
+							\cfrac{d c_{s,1}(t)}{d t} 	  \\
 							\vdots					  \\
-							\cfrac{d {\color{black}c_{s,N_z}}(t)}{d t} \\
+							\cfrac{d c_{s,N_z}(t)}{d t} \\
 							\\ \hline \\
-							\cfrac{d {\color{black}h_1}(t)}{d t} 	  \\
+							\cfrac{d h_1(t)}{d t} 	  \\
 							\vdots 					  \\
-							\cfrac{d {\color{black}h_{N_z}}(t)}{d t} \\
+							\cfrac{d h_{N_z}(t)}{d t} \\
 							\\ \hline \\
-							\cfrac{d {\color{black}P}(t)}{d t} \\
+							\cfrac{d P(t)}{d t} \\
 							\\ \hline \\
-							\cfrac{d {\color{black}y}(t)}{d t}
+							\cfrac{d y(t)}{d t}
 						\end{bmatrix}
@@
 						\underbrace{\begin{bmatrix}
-								{\color{black}G_1} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
+								G_1 \left( c_f,c_s,h; \Theta \right)\\ 
 								\vdots\\ 
-								{\color{black}G_{N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
+								G_{N_z} \left( c_f,c_s,h; \Theta \right)\\ 
 								\\ \hline \\ \\
-								{\color{black}G_{N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right)\\ 
+								G_{N_z+1} \left( c_f,c_s,h; \Theta \right)\\ 
 								\vdots\\
-								{\color{black}G_{2N_z}} \left( {\color{black}c}(t),c_s,{\color{black}h}(t); \Theta \right)\\ 
+								G_{2N_z} \left( c_f,c_s,h; \Theta \right)\\ 
 								\\ \\ \hline \\ 
-								{\color{black}G_{2N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
+								G_{2N_z+1} \left( c_f,c_s,h; \Theta \right) \\
 								\vdots\\
-								{\color{black}G_{3N_z}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\ 
+								G_{3N_z} \left( c_f,c_s,h; \Theta \right) \\ 
 								\\ \\ \hline \\
-								{\color{black}G_{3N_z+1}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) \\
+								G_{3N_z+1} \left( c_f,c_s,h; \Theta \right) \\
 								\\ \\ \hline \\
-								{\color{black}G_{3N_z+2}} \left( c_f,c_s,{\color{black}h}(t); \Theta \right) 
-						\end{bmatrix}}_{{\color{black}G} \left( x; \Theta \right)} 
+								G_{3N_z+2} \left( c_f,c_s,h; \Theta \right) 
+						\end{bmatrix}}_{G \left( x; \Theta \right)} 
 				\end{align*} }

### 2024-05-24 Sections/Sensitivity_Analysis.tex
Updates from Overleaf

@@
 	Local derivative-based methods involve taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of the parameter space $\theta$.
-This set of derivatives, known as sensitivity equations, is integrated simultaneously with the process model.
-The sensitivity analysis investigates how responsive the solution is for the perturbation of the parameter $p$.
+The set of derivatives, known as sensitivity equations, is integrated simultaneously with the process model.
+The sensitivity analysis shows how responsive the solution is for changes in the parameter $p$.
 As discussed by \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
@@
 	{\footnotesize
-		\begin{align}
+		\begin{equation}
 			\label{SA_def}
-			{Z}(x(t);p) &= \cfrac{dx(t)}{dp}
-	\end{align} }
+			Z(x(t);p) = \cfrac{dx(t)}{dp}
+	   \end{equation} }
 
@@
 
-	The sensitivity equation can be obtained by applying the definition of the total derivative to the Equation \ref{SA_dt}.
+	The sensitivity equation can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}.
 
@@
 
-	The sensitivity Equation \ref{SA_eq_full} is solved simultaneously with the original system and is made of three terms: Jacobian ${J_x}(x(t);p)$, sensitivity matrix $S(x(t);p)$ and Jacobian ${J_p}(x(t);p)$.
-The Jacobian ${J_x}(x(t);p)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of process model equations ${G}_{n_x}(x(t);p)$ with respect to the state variable $x_{n_p}$.
+	Equation \ref{SA_eq_full} is solved simultaneously with the process model and consists of three terms: Jacobian ${J_x}(x(t);p)$, sensitivity matrix $S(x(t);p)$ and Jacobian ${J_p}(x(t);p)$.
+The Jacobian ${J_x}(x(t);p)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of ${G}_{n_x}(x(t);p)$ with respect to the state variable $x_{n_p}$.
 
@@
 	The sensitivity matrix $S(x(t);p)$ represents the matrix of equations of size $N_x \times N_p$, where each subequation $S(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
+Matrix ${J_x}(x(t);p)$ and $S(x(t);p)$ describe indirect influence of $p_{n_p}$ on the model output.
 
@@
 	The Jacobian ${J_p}(x(t);p)$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
+${J_p}(n_x,n_p)$ can be defines direct effect of $p_{n_p}$ on the model output.
 
@@
 		\begin{align}
-			{\textbf{G}}\left(x(t_0);p\right)  = 
-			\begin{bmatrix}x(t_0),						& 
+			{\textbf{G}}\left(x(t_0);p\right)  &= 
+			\begin{bmatrix}
+                x(t_0),						               &
 				\cfrac{ \text{d}x(t_0) }{ d{p_1} },		   &
@@
 				\cfrac{ dx(t_0) }{ d{p_{N_p}} }            
-			\end{bmatrix}^T
+			\end{bmatrix}^\top = \\ &=
+            \begin{bmatrix} 
+                \quad x_0,	                               &
+				\quad ~0,		                           &
+			    \quad \cdots,			                   &
+				\quad 0 \quad~~
+			\end{bmatrix}^\top
 	\end{align} }

### 2024-05-24 Article_Sensitivity_Analsysis_short-Chamomile.tex
Updates from Overleaf

@@
 The model dynamic is investigated by analysing how sensitive the model output is to model parameters.
-In this work, the local sensitivity analysis is introduced and used to examine the influence of infinitely small changes in the pressure on the state space and the extraction yield.
+In this work, the local sensitivity analysis is introduced and used to examine the influence of infinitely small changes in the pressure on the model's state space and the extraction yield.
 
@@
 % Section: Introduction
-% ===================================================\section{Introduction}
+% ===================================================
 
@@
 
+% ===================================================
+% Section: Main
+% ===================================================
+
 \subfile{Sections/Model}
@@
 \subfile{Sections/Sensitivity_Analysis}
+
+% ===================================================
+% Section: Summary
+% ===================================================
 
@@
 
-Sensitivity analysis is a tool to understand the parametric dependence on the dynamic behaviour of the analysed system.
+Sensitivity analysis is a tool to understand how parameters affect a model's output.
+In the case of dynamical systems, local sensitivity analysis provides a time series describing how that dependency evolves.
 The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
 The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
-The sensitivity equations can be obtained in various ways, but the automatic differentiation technique was implemented to obtain the sensitivity equations in this work.
-Local sensitivity analysis can bring valuable information about process modelling, design of experiments or model reduction by identifying which parameters are influential and how these influence changes in time.
-
-This study used sensitivity analysis to evaluate the influence of pressure increase on the state-space, which consisted of the concentration of the solute in solid and liquid phases, the fluid's enthalpy density, system pressure, and extraction yield.
-At given operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the step change of pressure enhance the mass transfer, which leads to faster loss of solute from solid particles and consequently to negative sensitivities.
+The sensitivity equations can be obtained in various ways.
+This work implemented the automatic differentiation technique to get the sensitivity equations, which evaluate the effect of pressure increase on the supercritical extraction model.
+At given operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the step change of pressure enhance the mass transfer, which leads to faster loss of solute from solid particles and consequently to negative sensitivities in the solid phase.
 An analogous response is visible in the fluid phase, where the concentration of solute increases and is visible as positive sensitivities.
 As more solute is transported to the fluid phase, the extraction yield is improved and characterised by positive sensitivities.
-
-This information can be utilised to identify which control variables influence the extraction yield the most.
-The controls with high sensitivities to the extraction can be used to investigate optimal operating conditions from an economic point of view.
+Local sensitivity analysis can provide valuable information about process modelling, experiment design, or model reduction by identifying which parameters are influential and how these influence changes over time.
 

### 2024-05-24 Sections/Sensitivity_Pressure.tex
Updates from Overleaf

@@
 The negative sign can be interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
-Over time, the amount of solute becomes a limiting factor, and the pressure change has a lower effect on the system, increasing the negative sensitivities.
-Sensitivities approach zero asymptotically when the solid bed is exhausted of the solute.
+Over time, the amount of solute becomes a limiting factor, and the pressure change has a lower effect on the system.
+Eventually, the sensitivities approach zero asymptotically when the solute is exhausted from the solid bed.
 
@@
 Later, the sensitivities increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase.
-When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, sensitivities decline asymptotic towards zero, and the impact of the pressure change gradually decreases.
-As the fluid phase is mobile, the advection causes the sensitivities to move along the system analogously to the solute in the fluid phase.
+When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, sensitivities decline asymptotic towards zero, and the impact of the pressure change decreases.
+The advection causes the sensitivities to move along the system analogously to the solute in the fluid phase.
 
@@
 The positive yield sensitivity indicates improved process efficiency, which is directly related to enhanced mass transfer.
-The peak in $\frac{dy}{dP}$ reflects when the deviation from the original system is the largest.
+The peak in $\frac{dy}{dP_{in}}$ reflects when the deviation from the original system is the largest.
 Beyond the peak, the sensitivity declines and converges towards zero.

### 2024-05-24 Sections/Sensitivity_Pressure.tex
Updates from Overleaf

@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/H_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/H_P_1.png}
 		\caption{The effect of $P_{in}$ change on $(h \times \rho)$ in the system}
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CS_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CS_P_1.png}
 		\caption{The effect of $P_{in}$ change on $C_s$}
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CF_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CF_P_1.png}
 		\caption{The effect of $P_{in}$ change on $C_f$}
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/Y_P.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/Y_P_1.png}
 		\caption{The effect of $P_{in}$ change on $y(t)$}

### 2024-05-28 Sections/Model.tex
28.05

@@
 	\subsection{Governing equations} \label{CH:Governing_equations_chapter}
-	Following the work of \citet{Anderson1995}, the governing equations for quasi-one-dimensional were derived.
-Quasi-one-dimensional flow refers to a fluid flow scenario assuming that flow properties are uniformly distributed across any cross-section.
-This simplification is typically applied when the flow channel's cross-sectional area changes, such as through irregular shapes or partial fillings of an extractor.
+	Following the work of \citet{Anderson1995}, the governing equations for a quasi-one-dimensional flow were derived.
+A quasi-one-dimensional flow refers to a fluid flow scenario assuming that the flow properties are uniformly distributed across any cross-section.
+This simplification is typically applied when the flow channel's cross-sectional area changes, such as through irregular shapes or partial filling of an extractor.
 According to this assumption, velocity and other flow properties change solely in the flow direction.
@@
 
-	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}.
+	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}:
 
@@
 
-	where $\rho_f$ is the density of the fluid, $A_f$ is the function which describe change of the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spacial direction.
+	where $\rho_f$ is the density of the fluid, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spatial direction.
 
@@
 
-	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating a function $A_f = A\phi$.
-This modification distinguishes constant and varying terms, where the varying term accounts for the changes in the cross-sectional area available for the fluid.
+	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating the function $A_f = A\phi$.
+This modification distinguishes constant and varying terms, where the varying term accounts for changes in the cross-sectional area available for the fluid.
 Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:
@@
 
-	To simplify the system's dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.
+	To simplify the system dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$ and $\rho_f$:
 
@@
 
-	Similarly, the superficial velocity might be introduced.
+	Similarly, superficial velocity may be introduced:
 
@@
 
-	The fluid density $\rho_f$ can be obtained from an equation of state ({\color{red}article 1}) if temperature and thermodynamic pressure are known along $z$.
-The fluid density variation may occur due to pressure or inlet temperature changes.
-In the non-isothermal case, $\rho_f$ in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} is considered an average fluid density along the extraction column.
+	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{subsubsec: Equation of state}) if the temperature and thermodynamic pressure are known along $z$.
+Variation in fluid density may occur due to pressure or inlet temperature changes.
+In a non-isothermal case, in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2} $\rho_f$ is considered the average fluid density along the extraction column.
 
@@
 	Equation \ref{Model_fluid} describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption.
-Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself.
+Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to those of the solvent itself.
 It is also assumed that the thermodynamic pressure remains constant throughout the device.
@@
 This leads to a uniform velocity profile across any cross-section perpendicular to the axial direction.
-Thus, the mass balance equation includes convection, diffusion, and kinetic terms representing the fluid phase behaviour.
+Thus, the mass balance equation includes convection, diffusion and kinetic terms representing the fluid phase behaviour:
 
@@
 
-	$c_f$ represents the solute's concentration in the fluid phase, $r_e$ is a mass transfer kinetic term, and $D^M_e$ is the axial diffusion coefficient.
+	where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the axial diffusion coefficient.
 
@@
 Therefore, the only significant term in this equation is the kinetic term of Equation \ref{Model_kinetic_basic}, which connects the solid and fluid phases.
-For simplicity, the extract is represented by a single pseudo-component.
+For simplicity, the extract is represented by a single pseudo-component:
 
@@
 			As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions.
-The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk.
-Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$, and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$, respectively, for solid and fluid phases.
+The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore and the film into the bulk.
+Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as $c_s$, and the equilibrium concentrations at the solid-fluid interface are denoted as $c_s^*$ and $c_p^*$ for the solid and fluid phases, respectively.
 The concentration of the solutes in the fluid phase in the centre of the pore is denoted as $c_p$.
-As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the pore's opening.
+As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the pore opening.
 Then, the solute diffuses through the film around the particle and reaches bulk concentration $c_f$.
@@
 				\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=0.85\columnwidth]{Figures/SFE_PFD.drawio.png}	
-				\caption{The mass transfer mechanism}
+				\caption{Mass transfer mechanism.}
 				\label{fig: SFE_Mechanism}
@@
 
-			\citet{Bulley1984} suggests a process where the driving force for extraction is given by the difference between the concentration of the solute in bulk, $c_f$, and in the centre of the pore, $c_p^*$.
-The concentration $c_p^*$ is in equilibrium with $c_s$ according to an equilibrium relationship.
+			\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between the concentration of the solute in the bulk, $c_f$, and in the centre of the pore, $c_p^*$.
+The concentration $c_p^*$ is in equilibrium with $c_s$ according to the equilibrium relationship.
 The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$.
-On the other hand, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
-Concentration $c_p^*$ is determined by an equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}
+In contrast, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
+Concentration $c_p^*$ is determined by the equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}:
 
@@
 
-			where $\mu$ is sphericity, $l$ a characteristic dimension of particles and can be defined as $l = r/3$, $r$ is the mean particle radius, $\rho_s$ is the solid density, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
+			where $\mu$ is sphericity, $l$ a characteristic dimension of particles that can be defined as $l = r/3$, $r$ is the mean particle radius, $\rho_s$ is the solid density, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is the concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).
 
-			According to \citet{Bulley1984}, a linear equilibrium relationship (Equation \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase $c_f^*$ based on the concentration of the solute in the solid phase $c_s$.
+			According to \citet{Bulley1984}, a linear equilibrium relationship (Equation \ref{Linear_equilibirum}) can be used to find the equilibrium concentration of the solute in the fluid phase $c_f^*$ based on the concentration of the solute in the solid phase $c_s$:
 
@@
 			The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-According to \citet{Spiro2007}, $k_p$ can be expressed through the mass partition coefficient $k_m$.
+According to \citet{Spiro2007}, $k_p$ can be expressed through the mass partition coefficient $k_m$:
 
@@
 			The process yield is calculated according to Equation \ref{Model_measurment_1} as presented by \citet{Sovova1994a}.
-The measurement equation evaluates the solute's mass at the extraction unit's outlet and sums it up.
+The measurement equation evaluates the solute's mass at the extraction unit outlet and sums it up.
 The integral form of the measurement (Equation \ref{Model_measurment_1}) can be transformed into the differential form (Equation \ref{Model_measurment_2}) and augmented with the process model.
@@
 			The method of lines is used to transform the process model equations into a set of ODEs denoted as $G(x;\Theta)$.
-The backward finite difference is used to approximate the first-order derivative, while the central difference scheme is used to approximate the second-order derivative $z$-direction.
-The length of the fixed bed is divided into $N_z$ equally distributed points in $z$-direction.
-The state-space model after the discretization is denoted as $x$ and defines as follow:
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme approximates the second-order derivative $z$ direction.
+The length of the fixed bed is divided into $N_z$, i.e.
+equally distributed points in the $z$ direction.
+The state-space model after discretization is denoted as $x$ and defined as follows:
 
@@
 			For a derivative to be conservative, it must form a telescoping series.
-In other words, after the addition of all terms coming from the discretization over a grid, only the boundary terms should remain, and the artificial interior points should cancel out.
-The discretization is applied to the conservative form of the model to ensure mass conservation.
+In other words, only the boundary terms should remain after adding all terms coming from the discretization over a grid, and the artificial interior points should be cancelled out.
+Discretization is applied to the conservative form of the model to ensure mass conservation.
 

### 2024-05-28 Sections/Saturation.tex
28.05

@@
 
-	Following the idea of the Broken-and-Intact Cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}.
+	Following the idea of the Broken-and-Intact Cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}:
 
@@
 
-	where the ${\color{black}\Upsilon}$ describe the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term
+	where  ${\color{black}\Upsilon}$ describes the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term:
 
@@
 
-	The $\gamma$-function limits the solute's availability in the solid phase.
-Similarly to the BIC model, the solute is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact.
+	The $\gamma$ function limits the solute's availability in the solid phase.
+Similarly to the BIC model, the solute is assumed to be contained in the cells, some of which are open because the cell walls were broken by grinding, with the rest remaining intact.
 The diffusion of the solute from a particle's core takes more time than the diffusion of the solute close to the outer surface.
@@
 	Alternatively, the decay function $\gamma$ can be interpreted by referring to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius changes as the amount of solute in the solid phase decreases.
-As the particle size decreases due to dissolution, the diffusion path increases, which makes the diffusion slower and reduces the value of a diffusion coefficient.
-This analogy can be applied to the Equation \ref{EQ: C_sat_function} to justify the application of varying diffusion coefficient.
+As the particle size decreases due to dissolution, the diffusion path increases, which makes the diffusion slower and reduces the value of the diffusion coefficient.
+This analogy can be applied to Equation \ref{EQ: C_sat_function} to justify the application of a varying diffusion coefficient.
 

### 2024-05-31 Sections/Results_Sensitivity.tex
31.05

@@
 
-	This work investigates the influence of pressure change on the state space and the extraction yield.
+	%This work investigates the influence of pressure change on the state space and the extraction yield.
 The process model and parameters have been discussed in {\color{red}article 1}.
 The process model was calibrated on the set of experiments obtained at different operating conditions, $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-The sensitivity analysis has been performed assuming that the system operates at $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+The sensitivity analysis has been performed assuming that the system operates in the middle of validate range, hence at $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+
+	This study examines the impact of pressure change on the state space and extraction yield.
+The process model and parameters are described in {\color{red}article 1}.
+Calibration of the process model was based on experiments performed under varying operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow between $3.33-6.67 \cdot 10^{-5}$ kg/s.
+A sensitivity analysis was conducted, assuming the system operates at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
 

### 2024-05-31 Sections/Sensitivity_Pressure.tex
31.05

@@
 If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
-The Low Mach-number assumption leads to instant propagation of the thermodynamic pressure throughout the system.
+The Low Mach number assumption leads to instant propagation of the thermodynamic pressure throughout the system.
 A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the device.
@@
 
-	The model is built such that the pressure change first affects $\frac{dP}{dt}$, and in the next time step, the energy balance through $\frac{\partial (P(t) A_f)}{\partial t}$, leading to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
-The energy balance response becomes noticeable, as well as the change in the physical properties of the solvent.
+	The model is built such that the pressure change first affects $\frac{dP}{dt}$, then in next time step, the energy balance is influenced through $\frac{\partial (P A_f)}{\partial t}$.
+This leads to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
 The uniform response across the entire extraction column length, represented by the homogeneously dark red colour, indicates that the whole system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
@@
 In contrast, Neumann boundary conditions would dictate the heat flux at the boundaries.
-In this work, the Neumann boundary conditions equal to zero were applied to ensure that the temperatures at the inlet, the outlet, and the middle of the extractor are the same all the time.
+In this work, the Neumann boundary conditions equal to zero were applied to ensure that the temperatures at the inlet, the outlet, and the middle of the extractor depends only on the pressure change.
 
@@
 	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase with respect to pressure change along a fixed bed in a supercritical fluid extraction process.
-As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that the pressure increase decreases the velocity.
-This leads to an extended residence time, ergo, a longer interaction between the solute and the solvent.
-Initially, the extraction process is in the kinetically-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility.
+As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that the pressure reduces the fluid's velocity.
+As a result, the residence time was extended, causing longer interaction between the solute and the solvent.
+Initially, the extraction process is in the kinetic-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility.
 As discussed in ({\color{red}article 1}), the system is considered to be far from saturation, which can explain the low system response at the beginning of the process.
@@
 The negative sign can be interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
-Over time, the amount of solute becomes a limiting factor, and the pressure change has a lower effect on the system.
+Over time, the amount of solute becomes a limiting factor, and the pressure change effect on the system is reduced.
 Eventually, the sensitivities approach zero asymptotically when the solute is exhausted from the solid bed.
@@
 	Figure \ref{fig:Sensitivty_P_CF} shows how sensitive is the solute concentration in the fluid phase to the pressure change.
-Although the pressure increase enhances the mass transfer, the system response is initially low, which reflects the idle period discussed above.
+Compare to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of the fluid phase sensitivities can be observed.
+The sensitivities moves along the system analogously to the solute in the fluid phase due to the advection.	Although the pressure increase enhances the mass transfer, the system response is initially low, which reflects the idle period discussed above.
 Later, the sensitivities increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase.
-When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, sensitivities decline asymptotic towards zero, and the impact of the pressure change decreases.
-The advection causes the sensitivities to move along the system analogously to the solute in the fluid phase.
+When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down and sensitivities decline asymptotic towards zero.
 

### 2024-06-07 Article_Sensitivity_Analsysis_short-Chamomile.tex
07.06

@@
 \begin{abstract}
-The article presents a comprehensive study on the supercritical fluid extraction of essential oil from chamomile flowers, focusing on model dynamics and applying a distributed-parameter model to describe the fluid-solid extraction process.
-By employing the concept of quasi-one-dimensional flow, the study simplifies the spatial dimensions of the extraction process, ensuring uniform flow across any cross-section while allowing for variations in the area available for the fluid phase.
-The physical properties of the solvent are estimated using the Peng-Robinson equation of state.
-The model was validated under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-The model dynamic is investigated by analysing how sensitive the model output is to model parameters.
-In this work, the local sensitivity analysis is introduced and used to examine the influence of infinitely small changes in the pressure on the model's state space and the extraction yield.
+This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers.
+The distributed-parameter model describes the fluid-solid extraction process.
+The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
+The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
+A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model.
+The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.
 
@@
 
-\subsection{Sensitivity Analysis} \label{CH: Sensitivity_Analysis}
+\subsection{Local sensitivity analysis} \label{CH: Sensitivity_Analysis}
 \subfile{Sections/Sensitivity_Analysis}
@@
 The sensitivity equations can be obtained in various ways.
-This work implemented the automatic differentiation technique to get the sensitivity equations, which evaluate the effect of pressure increase on the supercritical extraction model.
+This work implemented the automatic differentiation technique to derive the sensitivity equations.
+The effect of pressure increase on the outcome of the supercritical extraction model is analysed in this work.
 At given operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the step change of pressure enhance the mass transfer, which leads to faster loss of solute from solid particles and consequently to negative sensitivities in the solid phase.
-An analogous response is visible in the fluid phase, where the concentration of solute increases and is visible as positive sensitivities.
-As more solute is transported to the fluid phase, the extraction yield is improved and characterised by positive sensitivities.
+Analogously, the sensitivities in the fluid phase are characterized by positive deviations, which indicates that more solute is transported to the fluid phase.
+As a result, the extraction yield is improved and characterised by positive sensitivities as well.
 Local sensitivity analysis can provide valuable information about process modelling, experiment design, or model reduction by identifying which parameters are influential and how these influence changes over time.

### 2024-06-07 Sections/Literature_Review.tex
07.06

--- 2024-05-20 Sections/Literature_Review.tex
@@
 
-	\citet{Santos2000}, in their work, considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent.
-The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.
+	\citet{Santos2000}, in their work, considered the model of \citet{Sovova1994} for the semi-continuous isothermal and isobaric extraction processes using carbon dioxide as a solvent.
+The parametric sensitivity analysis using a factorial design in two levels was carried out.
+The model parameters were disturbed by 10\%, and their main effects were analysed so that it is possible to propose strategies for high-performance operation.
+The authors performed the sensitivity analysis with respect to the superficial velocity, particle diameter, initial concentration of solute in the solid phase and the concentration of solute in the fluid phase at the inlet to the extractor.
 
-	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables.
+	\citet{Hatami2024} performed a one-factor-at-a-time sensitivity analysis to	assess the response of net present value concerning variations in both technical and economic variables.
+The analysis is divided into two parts.
+In the first part, the sensitivity analysis is carried out for a SFE plant with a constant	extractor volume of 300 L.
+Here, the focus is on examining how net present value is influenced by changes in individual technical and economic parameters while keeping the extractor volume fixed.
+In the second part, the investigation revolves around the effects of altering the extractor volume (between 1 to 600 L) on the overall profitability of the project.
 Their findings show that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
@@
 	\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils and applied a sensitivity analysis.
-They found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process.
 The sensitivity calculations were performed by varying the parameters and analysing the model response.
+The authors found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process.
 

### 2024-06-07 Sections/Model.tex
07.06

@@
 
-	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{subsubsec: Equation of state}) if the temperature and thermodynamic pressure are known along $z$.
+	The fluid density $\rho_f$ can be obtained from the Peng-Robinson equation of state if the temperature and thermodynamic pressure are known along $z$.
 Variation in fluid density may occur due to pressure or inlet temperature changes.
@@
 
-			The heat balance equation describe the evolution of the internal energy in the system and it is given by Equation \ref{EQ:Enthalpy_equation}
+			The heat balance equation describe the evolution of the enthalpy in the system and it is given by Equation \ref{EQ:Enthalpy_equation}
 
@@
 
-			The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure (which is a control variable).
-%The enthalpy is related to the pressure and temperature through the following equation:
+			The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure.
 
@@
 They are computed by integrating a function that depends on the equation of state and its derivatives.
-As presented by \citet{Gmehling2019}, for the Peng-Robinson equation of state, the enthalpy can be defined by Equation \ref{EQ:Enthalpy_PR}.
+As presented by \citet{Gmehling2019}, for the Peng-Robinson equation of state, the enthalpy departure function is defined by Equation \ref{EQ:Enthalpy_PR}.
 
@@
 
-			The pressure term in the energy equation, given by Equation \ref{EQ:Enthalpy_equation}, describes the change of the thermodynamic pressure with respect to time.
 			As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
 Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, which describes the pressure change in the whole system.
-The pressure ($P$) in the system is considered a state variable, while the pressure in the new time-step ($P_{in}$) is considered a control variable.
+The pressure $P$ in the system is considered a state variable, while the pressure in the new time-step $P_{in}$ is considered a control variable.
 
@@
 				\begin{equation}
-					\frac{\partial {\color{black}P}(t)}{\partial t} \approx \frac{{\color{black}P_{in}}(t) - {\color{black}P}(t) }{\Delta t}
+					\frac{\partial {\color{black}P}}{\partial t} \approx \frac{{\color{black}P_{in}} - {\color{black}P} }{\Delta t}
 			\end{equation}}
@@
 			Such a simplified equation allows for instantaneous pressure change in the system but does not consider a gradual pressure build-up and the effects of pressure losses.
-In a real system, the dynamics of pressure change would depend on a pump used in an extraction system and a back-pressure regulator used to control an outlet valve.
+In a real system, the dynamics of pressure change would depend on a pump and a back-pressure regulator.
 
@@
 					&c_f(t = 0, z) = 0  && c_s(t = 0, z) = c_{s0} && h(t = 0, z) = h_0 \\
-					&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}(t)  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
+					&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
 					&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0 \quad P(0) = P_0 \\
@@
 					\begin{align*} \label{discretization}
-						\dot{x}(t) &= \cfrac{d x}{d t} = 
+						\dot{x} &= \cfrac{d x}{d t} = 
 						\begin{bmatrix}
-							\cfrac{d c_{f,1}(t)}{d t} 	  \\
+							\cfrac{d c_{f,1}}{d t} 	  \\
 							\vdots					  \\
-							\cfrac{d c_{f,N_z}(t)}{d t} \\
+							\cfrac{d c_{f,N_z}}{d t} \\
 							\\ \hline \\
-							\cfrac{d c_{s,1}(t)}{d t} 	  \\
+							\cfrac{d c_{s,1}}{d t} 	  \\
 							\vdots					  \\
-							\cfrac{d c_{s,N_z}(t)}{d t} \\
+							\cfrac{d c_{s,N_z}}{d t} \\
 							\\ \hline \\
-							\cfrac{d h_1(t)}{d t} 	  \\
+							\cfrac{d h_1}{d t} 	  \\
 							\vdots 					  \\
-							\cfrac{d h_{N_z}(t)}{d t} \\
+							\cfrac{d h_{N_z}}{d t} \\
 							\\ \hline \\
-							\cfrac{d P(t)}{d t} \\
+							\cfrac{d P}{d t} \\
 							\\ \hline \\
-							\cfrac{d y(t)}{d t}
+							\cfrac{d y}{d t}
 						\end{bmatrix}

### 2024-06-07 Sections/Results_Sensitivity.tex
07.06

@@
 The process model and parameters are described in {\color{red}article 1}.
-Calibration of the process model was based on experiments performed under varying operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow between $3.33-6.67 \cdot 10^{-5}$ kg/s.
-A sensitivity analysis was conducted, assuming the system operates at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+Calibration of the process model is based on experiments performed under varying operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow between $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The local sensitivity analysis was conducted, assuming the system operates at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
 

### 2024-06-07 Sections/Sensitivity_Analysis.tex
28.05
07.06

@@
 
-	Local derivative-based methods involve taking the total derivative of the state vector $x$ with respect to parameters $p$, where $p$ is a subset of the parameter space $\theta$.
+	Local derivative-based methods involve taking the total derivative of the state vector $x$ with respect to the parameter space $\Theta$.
 The set of derivatives, known as sensitivity equations, is integrated simultaneously with the process model.
-The sensitivity analysis shows how responsive the solution is for changes in the parameter $p$.
+The sensitivity analysis shows how responsive the solution is for changes in the parameter $\Theta$.
 As discussed by \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
@@
 			\label{SA_def}
-			Z(x(t);p) = \cfrac{dx(t)}{dp}
+			Z(x;\Theta) = \cfrac{dx}{d\Theta}
 	   \end{equation} }
@@
 		\begin{equation} \label{SA_dt} 
-			{\dot{Z}}(x(t);p)  = \cfrac{dZ(x(t);p)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx(t)}{dp} \right) = \cfrac{d }{dp} \left( \cfrac{dx(t)}{d t} \right) = \cfrac{d {G}(x(t);p)}{dp} 
+			{\dot{Z}}(x;\Theta)  = \cfrac{dZ(x;\Theta)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx}{d\Theta} \right) = \cfrac{d }{d\Theta} \left( \cfrac{dx}{d t} \right) = \cfrac{d {G}(x;\Theta)}{d\Theta} 
 	\end{equation} }
 
-	The sensitivity equation can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}.
+	The sensitivity Equation \ref{SA_eq_full} can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}.
 
@@
 		\begin{equation} \label{SA_eq_full}
-			\cfrac{dG(x(t);p)}{dp} = \underbrace{ \cfrac{\partial {G}(x(t);p)}{\partial x(t)} }_{{J_x}(x(t);p)} \underbrace{\cfrac{\partial x(t)}{\partial p} }_{S(x(t);p)} + \underbrace{ \cfrac{\partial {G}(x(t);p)}{\partial p} }_{{J_p}(x(t);p)}
+			\cfrac{dG(x;\Theta)}{d\Theta} = \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial x} }_{{J_x}(x;\Theta)} \underbrace{\cfrac{\partial x}{\partial \Theta} }_{S(x;\Theta)} + \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial \Theta} }_{{J_\Theta}(x;\Theta)}
 	  \end{equation} }
 
-	Equation \ref{SA_eq_full} is solved simultaneously with the process model and consists of three terms: Jacobian ${J_x}(x(t);p)$, sensitivity matrix $S(x(t);p)$ and Jacobian ${J_p}(x(t);p)$.
-The Jacobian ${J_x}(x(t);p)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of ${G}_{n_x}(x(t);p)$ with respect to the state variable $x_{n_p}$.
+	The Jacobian ${J_x}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of ${G}_{n_x}(x;\Theta)$ with respect to the state variable $x_{n_\Theta}$.
 
@@
 			\setlength\arraycolsep{2pt}
-			{J_x}(x(t);p)=\begin{pmatrix}
-				\cfrac{\partial {G_{1}}(x(t);p)}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {x_{N_x}}(t)}\\
-				\cfrac{\partial {G_{2}}(x(t);p)}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {x_{N_x}}(t)}\\
+			{J_x}(x;\Theta)=\begin{pmatrix}
+				\cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{1}}} & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{2}}} & \cdots & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{N_x}}}\\
+				\cfrac{\partial {G_{2}}(x;\Theta)}{\partial {x_{1}}} & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {x_{2}}} & \cdots & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {x_{N_x}}}\\
 				\vdots & \vdots & \ddots & \vdots\\ 
-				\cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {x_{1}}(t)} & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {x_{2}}(t)} & \cdots & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {x_{N_x}}(t)}\\
+				\cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {x_{1}}} & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {x_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {x_{N_x}}}\\
 			\end{pmatrix}
@@
 
-	The sensitivity matrix $S(x(t);p)$ represents the matrix of equations of size $N_x \times N_p$, where each subequation $S(n_x,n_p)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $p_{n_p}$.
-Matrix ${J_x}(x(t);p)$ and $S(x(t);p)$ describe indirect influence of $p_{n_p}$ on the model output.
+	The sensitivity matrix $S(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each subequation $S(n_x,n_\Theta)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
+Matrix ${J_x}(x;\Theta)$ and $S(x;\Theta)$ describe indirect influence of $\Theta_{n_\Theta}$ on the model output.
 
@@
 			\begin{split}
-				S(x(t);p) & = 
+				S(x;\Theta) & = 
 				\begingroup % keep the change local
@@
 				\begin{pmatrix}
-					\cfrac{\partial {x_{1}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{1}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{1}}(t)}{\partial {p_{N_p}}}\\
-					\cfrac{\partial {x_{2}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{2}}(t)}{d {p_{2}}}     & \cdots & \cfrac{d {x_{2}}(t)}{\partial {p_{N_p}}}\\
+					\cfrac{\partial {x_{1}}}{\partial {\Theta_{1}}} 	& \cfrac{\partial {x_{1}}}{d {\Theta_{2}}}     & \cdots & \cfrac{d {x_{1}}}{\partial {\Theta_{N_\Theta}}}\\
+					\cfrac{\partial {x_{2}}}{\partial {\Theta_{1}}} 	& \cfrac{\partial {x_{2}}}{d {\Theta_{2}}}     & \cdots & \cfrac{d {x_{2}}}{\partial {\Theta_{N_\Theta}}}\\
 					\vdots					 	    & \vdots 					   	  & \ddots & \vdots\\
-					\cfrac{\partial {x_{N_x}}(t)}{\partial {p_{1}}} 	& \cfrac{\partial {x_{N_x}}(t)}{d {p_{2}}}     & \cdots & \cfrac{\partial {x_{N_x}}(t)}{d {p_{N_p}}}
+					\cfrac{\partial {x_{N_x}}}{\partial {\Theta_{1}}} 	& \cfrac{\partial {x_{N_x}}}{d {\Theta_{2}}}     & \cdots & \cfrac{\partial {x_{N_x}}}{d {\Theta_{N_\Theta}}}
 				\end{pmatrix} 
@@
 
-	The Jacobian ${J_p}(x(t);p)$ represents the matrix of equations of size $N_x \times N_p$, where each subequation ${J_p}(n_x,n_p)$ is the partial derivative of the process model equation $F_{n_x}$ with respect to the parameter $p_{n_p}$.
-${J_p}(n_x,n_p)$ can be defines direct effect of $p_{n_p}$ on the model output.
+	The Jacobian ${J_\Theta}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each subequation ${J_\Theta}(n_x,n_\Theta)$ is the partial derivative of the process model equation $G_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
+${J_\Theta}(n_x,n_\Theta)$ defines direct effect of $\Theta_{n_\Theta}$ on the model output.
 
@@
 		\begin{align}
-			{J_p}(x(t);p) & =
+			{J_\Theta}(x;\Theta) & =
 			\begingroup % keep the change local
@@
 			\begin{pmatrix}
-				\cfrac{\partial {G_{1}}(x(t);p)}{\partial {p_{1}}} & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{1}}(x(t);p)}{\partial {p_{N_p}}}\\
-				\cfrac{\partial {G_{2}}(x(t);p)}{\partial {p_{1}}} & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{2}}(x(t);p)}{\partial {p_{N_p}}}\\
+				\cfrac{\partial {G_{1}}(x;\Theta)}{\partial {\Theta_{1}}} & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {\Theta_{2}}} & \cdots & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {\Theta_{N_\Theta}}}\\
+				\cfrac{\partial {G_{2}}(x;\Theta)}{\partial {\Theta_{1}}} & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {\Theta_{2}}} & \cdots & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {\Theta_{N_\Theta}}}\\
 				\vdots & \vdots & \ddots & \vdots\\
-				\cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {p_{1}}} & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {p_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}(x(t);p)}{\partial {p_{N_p}}}
+				\cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {\Theta_{1}}} & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {\Theta_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {\Theta_{N_\Theta}}}
 			\end{pmatrix}
@@
 
-	The combined system containing the original set of equations ${G}(x(t);p)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x(t);p\right)$.
-The size of ${\textbf{G}}\left(x(t);p\right)$ is equal to $N_s = N_x(N_p + 1)$.
+	The combined system containing the original set of equations ${G}(x;\Theta)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x;\Theta\right)$.
+The size of ${\textbf{G}}\left(x;\Theta\right)$ is equal to $N_s = N_x(N_\Theta + 1)$.
 
@@
 		\begin{align}
-			{\textbf{G}}\left(x(t);p\right) = 
+			{\textbf{G}}\left(x;\Theta\right) = 
 			\begin{bmatrix}
-				{G}(x(t);p)\\
-				{J_x}(x(t);p)S(x(t);p) + {J_p}(x(t);p)
+				{G}(x;\Theta)\\
+				{J_x}(x;\Theta)S(x;\Theta) + {J_\Theta}(x;\Theta)
 			\end{bmatrix}
@@
 		\begin{align}
-			{\textbf{G}}\left(x(t_0);p\right)  &= 
+			{\textbf{G}}\left(x(t_0);\Theta\right)  &= 
 			\begin{bmatrix}
                 x(t_0),						               &
-				\cfrac{ \text{d}x(t_0) }{ d{p_1} },		   &
+				\cfrac{ \text{d}x(t_0) }{ d{\Theta_1} },		   &
 				\cdots,					 				   &
-				\cfrac{ dx(t_0) }{ d{p_{N_p}} }            
+				\cfrac{ dx(t_0) }{ d{\Theta_{N_\Theta}} }            
 			\end{bmatrix}^\top = \\ &=
@@
 
-	The sensitivity analysis of the output function can be performed with respect to parameters $p$.
-The output function $g(x(t))$ returns ${y}(t)$.
-By taking a total derivative of ${y}(t)$ with respect to $p$, the new sensitivity equation can be found.
+	The sensitivity analysis of the output function can be performed with respect to parameters $\Theta$.
+The output function $g(x)$ returns ${y}$.
+By taking a total derivative of ${y}$ with respect to $\Theta$, the new sensitivity equation can be found.
 
@@
 		\begin{equation}
-			\cfrac{d {y}(t)}{dp} = \cfrac{d g(x(t))}{dp} = \cfrac{\partial g(x(t))}{\partial x(t)} \cfrac{\partial x(t)}{\partial p} + \cfrac{\partial g(x(t))}{\partial p}
+			\cfrac{d {y}}{d\Theta} = \cfrac{d g(x)}{d\Theta} = \cfrac{\partial g(x)}{\partial x} \cfrac{\partial x}{\partial \Theta} + \cfrac{\partial g(x)}{\partial \Theta}
 	   \end{equation} }

### 2024-06-07 Sections/Sensitivity_Pressure.tex
07.06

@@
 
+	A step-function shown in Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change in the extractor.
 As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow.
 If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
-The Low Mach number assumption leads to instant propagation of the thermodynamic pressure throughout the system.
-A single pressure value can be considered for the entire system, as all changes occur simultaneously throughout the device.
-A step-function shown in Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change in the extractor.
+The Low Mach number assumption leads to instant propagation of the thermodynamic pressure throughout the system and allows for considering a single pressure value for the entire system.
+The model is built such that the pressure change first affects $\frac{dP}{dt}$; then in the next time step, the energy balance is influenced through $\frac{\partial (P A_f)}{\partial t}$.
+Analogously, the pressure change affects the enthalpy balance by introducing a step-change along the entire system as presented in Figure \ref{fig:Sensitivty_P_H}.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/P_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P_1.png}
 		\caption{The effect of $P_{in}$ change on $P$ in the system}
@@
 
-	The model is built such that the pressure change first affects $\frac{dP}{dt}$, then in next time step, the energy balance is influenced through $\frac{\partial (P A_f)}{\partial t}$.
-This leads to the step change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
-The uniform response across the entire extraction column length, represented by the homogeneously dark red colour, indicates that the whole system experiences an immediate and uniform change in enthalpy density in response to pressure changes.
-
 	The pressure change affects the fluid's temperature inside the computational domain, but boundary values are subject to constraints specified at the extremes of that domain.
-Applying the Dirichlet boundary conditions assumes a fixed temperature value at the inlet, which can lead to a thermal gradient propagating along the system.
+Applying the Dirichlet boundary conditions imposes a fixed temperature value at the inlet, which leads to a thermal gradient propagating along the system.
 In contrast, Neumann boundary conditions would dictate the heat flux at the boundaries.
-In this work, the Neumann boundary conditions equal to zero were applied to ensure that the temperatures at the inlet, the outlet, and the middle of the extractor depends only on the pressure change.
+In this work, the Neumann boundary conditions equal to zero were applied to ensure that the temperatures at the inlet, the outlet, and the middle of the extractor vary, respectively, to the pressure change.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/H_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P_1.png}
 		\caption{The effect of $P_{in}$ change on $(h \times \rho)$ in the system}
@@
 
-	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase with respect to pressure change along a fixed bed in a supercritical fluid extraction process.
+	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase in response to pressure change.
 As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that the pressure reduces the fluid's velocity.
-As a result, the residence time was extended, causing longer interaction between the solute and the solvent.
+As a result, the residence time is extended, causing longer interaction between the solute and solvent.
 Initially, the extraction process is in the kinetic-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility.
 As discussed in ({\color{red}article 1}), the system is considered to be far from saturation, which can explain the low system response at the beginning of the process.
+\citet{Fiori_2007} in their work also observed low sensitivity at the beginning of extraction.
 The system response becomes more evident when the concentration gradient starts diminishing, and the extraction switches from the kinetic-controlled to the diffusion-controlled regime.
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CS_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P_1.png}
 		\caption{The effect of $P_{in}$ change on $C_s$}
@@
 	Figure \ref{fig:Sensitivty_P_CF} shows how sensitive is the solute concentration in the fluid phase to the pressure change.
-Compare to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of the fluid phase sensitivities can be observed.
-The sensitivities moves along the system analogously to the solute in the fluid phase due to the advection.	Although the pressure increase enhances the mass transfer, the system response is initially low, which reflects the idle period discussed above.
-Later, the sensitivities increase due to faster solute loss from the solid phase, which indicates that more solute is transported to the fluid phase.
-When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down and sensitivities decline asymptotic towards zero.
+Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of the fluid phase sensitivities can be observed.
+Due to the advection, the sensitivities move along the system analogously to the solute in the fluid phase.	Although the pressure increase enhances the mass transfer, the system response is initially low, which reflects the idle period discussed above.
+Later, the sensitivities increase due to faster solute loss from the solid phase.
+The positive sensitivities indicate that more solute is transported to the fluid phase.
+When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, and sensitivities decline asymptotically towards zero.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/CF_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P_1.png}
 		\caption{The effect of $P_{in}$ change on $C_f$}
@@
 The peak in $\frac{dy}{dP_{in}}$ reflects when the deviation from the original system is the largest.
-Beyond the peak, the sensitivity declines and converges towards zero.
+Eventually, the sensitivity declines and converges towards zero.
 The concentration gradient becomes a limiting factor, and the enhanced mass transfer no longer plays a dominant role compared to the original system.
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=0.9\columnwidth]{/Results_sensitivity/Y_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P_1.png}
 		\caption{The effect of $P_{in}$ change on $y(t)$}

### 2024-06-10 Article_Sensitivity_Analsysis_short-Chamomile.tex
10.06

@@
 \begin{abstract}
-This study aimed to investigate the supercritical extraction process of caraway oil from chamomile flowers.
-The distributed-parameter model describes the fluid-solid extraction process.
+This study aims to investigate the extraction process of caraway oil from chamomile flowers.
+A mathematical model is used to describe the governing mass transfer phenomena in a solid-fluid environment under supercritical conditions using carbon dioxide as a solvent.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
@@
 A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-Sensitivity analyses play a crucial role in assessing the robustness of the findings or conclusions based on mathematical model.
-The local sensitivity analysis investigates the influence of infinitely small changes in the inlet temperature, pressure, and flow rate on the extraction yield.
+Different sensitivity analysis methods can be applied to assess the robustness of the model parameters and its influence on the process model.
+The local sensitivity analysis investigates the influence of infinitely small changes in the model parameters and the controls on model output.
+In particular,  this work focuses on analysing the step change of pressure on the extraction yield and the model state space.
 

### 2024-06-10 Sections/Literature_Review.tex
10.06

--- 2024-05-20 Sections/Literature_Review.tex
@@
 
-	This study aims to analyse the influence of changes in operating conditions on the supercritical extraction process described in {\color{red}article 1}.
-The emphasis is put on the effect of the mass flow rate, pressure, and the inlet temperature.
-The relation between input and output is obtained by applying a sensitivity analysis.
-Sensitivity analysis examines the impact of varying inputs or model parameters on the system's output.
-The aim is to understand and allocate the source of uncertainty in the output to the corresponding inputs or parameters.
+	This study aims to analyse the influence of changes in operating conditions on the process model described in {\color{red}article 1}.
+The relation between input and output is obtained by applying a sensitivity analysis, which examines the impact of model parameters or controls on the model output.
+The result of sensitivity analysis can be used to allocate the source of uncertainty in the system, perform the model reduction or search for errors in the model (by identifying unexpected relationships between inputs and outputs).
 There are many sensitivity analysis methods, which include but are not limited to those listed below:
@@
 
-	Different supercritical extraction models were analysed using sensitivity analysis.
+	In the literature, many different supercritical extraction models were analysed using different sensitivity analysis techniques.
 \citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed.
-This allows to evaluate the effect of the uncertainties on model predictions.
-The sensitivity analysis revealed that the particle diameter and the internal mass transfer coefficient are significant for the extraction process.
-The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
+Their sensitivity analysis revealed that changes in particle diameter and the internal mass transfer coefficient have the strongest influence on extraction in the second phase of the process (diffusion-control regime).% The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
 
-	\citet{Santos2000}, in their work, considered a model of supercritical extraction process for semi-continuous isothermal and isobaric extraction process using carbon dioxide as a solvent.
-The parametric sensitivity analysis was carried out by applying disturbances of 10\% in the values of the normal operation conditions.
+	\citet{Santos2000}, in their work, considered the model of \citet{Sovova1994} for the semi-continuous isothermal and isobaric extraction processes using carbon dioxide as a solvent.
+The parametric sensitivity analysis was carried out using a factorial design in two levels.
+The model parameters were disturbed by 10\%, and their main effects were analysed and strategies for high-performance operation are proposed.
+The authors performed the sensitivity analysis with respect to the superficial velocity, particle diameter, initial concentration of solute in the solid phase and the concentration of solute in the fluid phase at the inlet to the extractor.
 
-	\citet{Hatami2024} used a one-factor-at-a-time sensitivity analysis to assess the response of NPV concerning variations in both technical and economic variables.
-Their findings show that the most influential factors on NPV include the price of the extract, the interest rate, the dynamic time of SFE, and the project lifetime.
+	\citet{Hatami2024} performed the one-factor-at-a-time sensitivity analysis to assess the response of net present value concerning variations in both technical and economic variables.
+Their study is divided into two parts.
+In the first part, the sensitivity analysis is carried out for an extraction plant with a constant extractor volume of 300 L.
+The focus is on examining how net present value is influenced by changes in individual technical and economic parameters while keeping the extractor volume fixed.
+In the second part, the investigation revolves around the effects of altering the extractor volume (from 1 to 600 L) on the project's overall profitability.
+Their findings show that the most influential factors on net present value include the price of the extract, the interest rate, the dynamic time, and the project lifetime.
 
-	\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils and applied a sensitivity analysis.
-They found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process.
+	%\citet{Poletto1996} provided a general dimensionless model for the supercritical extraction process of vegetable and essential oils.
 The sensitivity calculations were performed by varying the parameters and analysing the model response.
+The authors found that a dimensionless partition coefficient and a dimensionless characteristic time appeared as the most important parameters of the extraction process.
 

### 2024-06-10 Sections/Model.tex
10.06

@@
 The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, and internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
-The departure function is defined as the difference between the value of a thermodynamic property for a real fluid and the corresponding value for an ideal gas at the same temperature and pressure.
-They are computed by integrating a function that depends on the equation of state and its derivatives.
 As presented by \citet{Gmehling2019}, for the Peng-Robinson equation of state, the enthalpy departure function is defined by Equation \ref{EQ:Enthalpy_PR}.
@@
 
-			Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which is assumed to be $T_{ref}=298.15$[K] and $P_{ref}=1.01325$[bar].
+			Equation \ref{EQ:Enthalpy_PR} requires an reference sate, which is assumed to be $T_{ref}=298.15$ K and $P_{ref}=1.01325$ bar.
 
 			A root-finder can be used to find a value of temperature, which minimizes the difference between the value of enthalpy coming from the heat balance and the departure functions.
-The root fining procedure to repeated at every time step to find a local temperature along spatial direction $z$.
+The root fining procedure to repeated at every time step to find a temperature profile along spatial direction $z$.
 

### 2024-06-10 Sections/Results_Sensitivity.tex
10.06

@@
 The process model and parameters are described in {\color{red}article 1}.
-Calibration of the process model is based on experiments performed under varying operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow between $3.33-6.67 \cdot 10^{-5}$ kg/s.
+Calibration of the process model is based on experiments performed under multiple  operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
 The local sensitivity analysis was conducted, assuming the system operates at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.

### 2024-06-10 Sections/Sensitivity_Analysis.tex
10.06

@@
 	The sensitivity matrix $S(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each subequation $S(n_x,n_\Theta)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
-Matrix ${J_x}(x;\Theta)$ and $S(x;\Theta)$ describe indirect influence of $\Theta_{n_\Theta}$ on the model output.
+Matrix ${J_x}(x;\Theta)$ and $S(x;\Theta)$ describe indirect influence of $\Theta_{n_\Theta}$ on the state space.
 
@@
 	The Jacobian ${J_\Theta}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each subequation ${J_\Theta}(n_x,n_\Theta)$ is the partial derivative of the process model equation $G_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
-${J_\Theta}(n_x,n_\Theta)$ defines direct effect of $\Theta_{n_\Theta}$ on the model output.
+${J_\Theta}(n_x,n_\Theta)$ defines direct effect of $\Theta_{n_\Theta}$ on the state space.
 
@@
 
-	The combined system containing the original set of equations ${G}(x;\Theta)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x;\Theta\right)$.
+	The augmented system containing the original set of equations ${G}(x;\Theta)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x;\Theta\right)$.
 The size of ${\textbf{G}}\left(x;\Theta\right)$ is equal to $N_s = N_x(N_\Theta + 1)$.

### 2024-06-10 Article_Sensitivity_Analsysis_short-Chamomile.tex
10.06

@@
 \begin{abstract}
-This study aims to investigate the extraction process of caraway oil from chamomile flowers.
-A mathematical model is used to describe the governing mass transfer phenomena in a solid-fluid environment under supercritical conditions using carbon dioxide as a solvent.
+This study investigates the process of caraway oil extraction from chamomile flowers.
+A parameter-distributed model consisting of a set of partial differential equations is used to describe the governing mass transfer phenomena in a solid-fluid environment under supercritical conditions using carbon dioxide as a solvent.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
@@
 A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-Different sensitivity analysis methods can be applied to assess the robustness of the model parameters and its influence on the process model.
+Different sensitivity analysis methods can be applied to assess the robustness of the model parameters and their influence on the process model.
 The local sensitivity analysis investigates the influence of infinitely small changes in the model parameters and the controls on model output.
-In particular,  this work focuses on analysing the step change of pressure on the extraction yield and the model state space.
+This work focuses on analysing the effect of pressure on the model state space and the extraction yield.
 
@@
 
-Sensitivity analysis is a tool to understand how parameters affect a model's output.
+Sensitivity analysis is a tool to understand how model parameters affect its output.
+The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
+The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
+This work implemented the automatic differentiation to derive the sensitivity equations.
 In the case of dynamical systems, local sensitivity analysis provides a time series describing how that dependency evolves.
-The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
-The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions unless the discussed system is a linear model.
-The sensitivity equations can be obtained in various ways.
-This work implemented the automatic differentiation technique to derive the sensitivity equations.
-The effect of pressure increase on the outcome of the supercritical extraction model is analysed in this work.
-At given operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the step change of pressure enhance the mass transfer, which leads to faster loss of solute from solid particles and consequently to negative sensitivities in the solid phase.
-Analogously, the sensitivities in the fluid phase are characterized by positive deviations, which indicates that more solute is transported to the fluid phase.
-As a result, the extraction yield is improved and characterised by positive sensitivities as well.
-Local sensitivity analysis can provide valuable information about process modelling, experiment design, or model reduction by identifying which parameters are influential and how these influence changes over time.
+
+The local sensitivity analysis can be performed with respect to any model parameter, but this work focuses on the effect of pressure increase.
+At selected operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster loss of solute from particles and consequently to negative sensitivities in the solid phase.
+Analogously, the sensitivities in the fluid phase are characterised by positive deviations, which indicates that more solute is transported to the fluid phase.
+As a result, the extraction yield is improved and characterised by positive sensitivities.
+Local sensitivity analysis can provide valuable information by identifying which parameters are influential and how these influence changes over time.
+The sensitivity analysis results can be utilised for process modelling, experiment design, or model reduction.
 

### 2024-06-10 Sections/Results_Sensitivity.tex
10.06

--- 2024-05-31 Sections/Results_Sensitivity.tex
@@
 
-	This study examines the impact of pressure change on the state space and extraction yield.
-The process model and parameters are described in {\color{red}article 1}.
-Calibration of the process model was based on experiments performed under varying operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow between $3.33-6.67 \cdot 10^{-5}$ kg/s.
-A sensitivity analysis was conducted, assuming the system operates at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+	This study examines the impact of pressure change on the state space and extraction yield through the local sensitivity analysis.
+The details of the process model and parameters are delivered in {\color{red}article 1}.
+The process model was validated under the following range of operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The system is assumed to operate at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
 

### 2024-06-10 Sections/Sensitivity_Analysis.tex
10.06

@@
 
-	Following the work of \citet{Maly1996}, the sensitivity analysis equations(${\dot{Z}}$) can be defined as follow:
+	Following the work of \citet{Maly1996}, the sensitivity equations (${\dot{S}}$) can be defined as follow:
 
@@
 			\label{SA_def}
-			Z(x;\Theta) = \cfrac{dx}{d\Theta}
+			S(x;\Theta) = \cfrac{dx}{d\Theta}
 	   \end{equation} }
 
-	The new system of equations can be obtained by taking derivatives of $Z$ with respect to time $t$ and applying the chain rule.
+	The new system of equations can be obtained by taking derivatives of $S$ with respect to time $t$ and applying the chain rule.
 
@@
 		\begin{equation} \label{SA_dt} 
-			{\dot{Z}}(x;\Theta)  = \cfrac{dZ(x;\Theta)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx}{d\Theta} \right) = \cfrac{d }{d\Theta} \left( \cfrac{dx}{d t} \right) = \cfrac{d {G}(x;\Theta)}{d\Theta} 
+			{\dot{S}}(x;\Theta)  = \cfrac{dS(x;\Theta)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx}{d\Theta} \right) = \cfrac{d }{d\Theta} \left( \cfrac{dx}{d t} \right) = \cfrac{d {G}(x;\Theta)}{d\Theta} 
 	\end{equation} }
@@
 		\begin{equation} \label{SA_eq_full}
-			\cfrac{dG(x;\Theta)}{d\Theta} = \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial x} }_{{J_x}(x;\Theta)} \underbrace{\cfrac{\partial x}{\partial \Theta} }_{S(x;\Theta)} + \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial \Theta} }_{{J_\Theta}(x;\Theta)}
+			\cfrac{d G(x;\Theta)}{d \Theta} = \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial x} }_{{J_x}(x;\Theta)} \underbrace{\cfrac{\partial x}{\partial \Theta} }_{S(x;\Theta)} + \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial \Theta} }_{{J_\Theta}(x;\Theta)}
 	  \end{equation} }

### 2024-06-10 Sections/Sensitivity_Pressure.tex
10.06

@@
 The Low Mach number assumption leads to instant propagation of the thermodynamic pressure throughout the system and allows for considering a single pressure value for the entire system.
-The model is built such that the pressure change first affects $\frac{dP}{dt}$; then in the next time step, the energy balance is influenced through $\frac{\partial (P A_f)}{\partial t}$.
-Analogously, the pressure change affects the enthalpy balance by introducing a step-change along the entire system as presented in Figure \ref{fig:Sensitivty_P_H}.
+Analogously to Figure \ref{fig:Sensitivty_P_P}, the pressure change affects the enthalpy balance by introducing a step-change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
 
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P_1.png}
-		\caption{The effect of $P_{in}$ change on $P$ in the system}
+		\caption{The effect of $P_{in}$ change on $P$}
 		\label{fig:Sensitivty_P_P}
@@
 Applying the Dirichlet boundary conditions imposes a fixed temperature value at the inlet, which leads to a thermal gradient propagating along the system.
-In contrast, Neumann boundary conditions would dictate the heat flux at the boundaries.
-In this work, the Neumann boundary conditions equal to zero were applied to ensure that the temperatures at the inlet, the outlet, and the middle of the extractor vary, respectively, to the pressure change.
+In contrast, Neumann boundary conditions dictate the heat flux at the boundaries.
+In this work, Neumann boundary conditions of zero were used to ensure that the temperatures at the inlet, outlet, and inside the extractor would vary uniformly and according to the pressure change.
 
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P_1.png}
-		\caption{The effect of $P_{in}$ change on $(h \times \rho)$ in the system}
+		\caption{The effect of $P_{in}$ change on $(h \times \rho)$}
 		\label{fig:Sensitivty_P_H}
@@
 Initially, the extraction process is in the kinetic-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility.
-As discussed in ({\color{red}article 1}), the system is considered to be far from saturation, which can explain the low system response at the beginning of the process.
-\citet{Fiori_2007} in their work also observed low sensitivity at the beginning of extraction.
-The system response becomes more evident when the concentration gradient starts diminishing, and the extraction switches from the kinetic-controlled to the diffusion-controlled regime.
+As discussed in {\color{red}article 1}, the system is considered to be far from saturation, which explains the low system response at the beginning of the process.
+\citet{Fiori_2007} also observed low sensitivity at the beginning of extraction.
+The system response becomes evident when the concentration gradient diminishes, and the extraction switches from the kinetic-controlled to the diffusion-controlled regime.
 The negative sign can be interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
 Over time, the amount of solute becomes a limiting factor, and the pressure change effect on the system is reduced.
-Eventually, the sensitivities approach zero asymptotically when the solute is exhausted from the solid bed.
+Eventually, the sensitivities approach zero asymptotically when the solute is washed out from the solid bed.
 
@@
 Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of the fluid phase sensitivities can be observed.
-Due to the advection, the sensitivities move along the system analogously to the solute in the fluid phase.	Although the pressure increase enhances the mass transfer, the system response is initially low, which reflects the idle period discussed above.
+Due to the advection, the sensitivities move along the system analogously to the solute in the fluid phase.
+Although the pressure increase improves the mass transfer, the system response is initially low, which reflects the idle period discussed above.
 Later, the sensitivities increase due to faster solute loss from the solid phase.
-The positive sensitivities indicate that more solute is transported to the fluid phase.
+The positive sensitivities indicate that more solute is transported from the particles to the fluid.
 When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, and sensitivities decline asymptotically towards zero.
@@
 	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to the pressure change.
-Initially, the sensitivity curve stays almost flat, suggesting a latency in the system's response to pressure changes.
+Initially, the sensitivity curve stays almost flat, suggesting a latency in the system's response.
 Due to the decreased velocity of the fluid, the solute reaches the extractor's outlet later, which causes minor negative sensitivities to appear.
-The process continues, and the sensitivity curve increases rapidly when the solute reaches the extractor's outlet.
+When the solute reaches exits the extractor, the sensitivity curve increases rapidly.
 The positive yield sensitivity indicates improved process efficiency, which is directly related to enhanced mass transfer.

### 2024-06-11 Sections/Sensitivity_Pressure.tex
11.06

@@
 The Low Mach number assumption leads to instant propagation of the thermodynamic pressure throughout the system and allows for considering a single pressure value for the entire system.
-Analogously to Figure \ref{fig:Sensitivty_P_P}, the pressure change affects the enthalpy balance by introducing a step-change along the whole system as presented in Figure \ref{fig:Sensitivty_P_H}.
+Analogously to Figure \ref{fig:Sensitivty_P_P}, a step-change can be observed in the energy balance presented in Figure \ref{fig:Sensitivty_P_H}.
 
@@
 As discussed in {\color{red}article 1}, the system is considered to be far from saturation, which explains the low system response at the beginning of the process.
-\citet{Fiori_2007} also observed low sensitivity at the beginning of extraction.
+In the sensitivity analysis of \citet{Fiori_2007}, the low initial system response was also observed.
 The system response becomes evident when the concentration gradient diminishes, and the extraction switches from the kinetic-controlled to the diffusion-controlled regime.
-The negative sign can be interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
+The negative sign is interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
 Over time, the amount of solute becomes a limiting factor, and the pressure change effect on the system is reduced.
@@
 The positive sensitivities indicate that more solute is transported from the particles to the fluid.
-When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, and sensitivities decline asymptotically towards zero.
+When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, and sensitivities decline to negative values and eventually goes asymptotically towards zero.
 

### 2024-07-01 Sections/Sensitivity_Pressure.tex
01.07

@@
 
-	A step-function shown in Figure \ref{fig:Sensitivty_P_P} illustrates the pressure change in the extractor.
 	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow.
@@
 The Low Mach number assumption leads to instant propagation of the thermodynamic pressure throughout the system and allows for considering a single pressure value for the entire system.
-Analogously to Figure \ref{fig:Sensitivty_P_P}, a step-change can be observed in the energy balance presented in Figure \ref{fig:Sensitivty_P_H}.
+The local sensitivity analysis results can be interpreted as a system response to the step-change (deviation) of the pressure.
 
+	\begin{comment}
 	\begin{figure}[h!]
@@
 	\end{figure}
+	\end{comment}
 
+	In response to the pressure change, the energy equation experiences a deviation in the whole spatial domain simultaneously.
 The pressure change affects the fluid's temperature inside the computational domain, but boundary values are subject to constraints specified at the extremes of that domain.
@@
 
+	\begin{comment}
 	\begin{figure}[h!]
@@
 	\end{figure}
+	\end{comment}
 
@@
 
-	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to the pressure change.
-Initially, the sensitivity curve stays almost flat, suggesting a latency in the system's response.
+	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to the pressure changes.
+The effect of pressure change on the yield is expanded and consider for multiple values of pressure.
+Initially, all the sensitivity curve stay almost flat, suggesting a latency in the system's response.
 Due to the decreased velocity of the fluid, the solute reaches the extractor's outlet later, which causes minor negative sensitivities to appear.
-When the solute reaches exits the extractor, the sensitivity curve increases rapidly.
-The positive yield sensitivity indicates improved process efficiency, which is directly related to enhanced mass transfer.
+When the solute reaches exits the extractor, the sensitivity curves increase rapidly.
+The positive yield sensitivities indicate improved process efficiency, which is directly related to enhanced mass transfer.
 The peak in $\frac{dy}{dP_{in}}$ reflects when the deviation from the original system is the largest.
-Eventually, the sensitivity declines and converges towards zero.
+Eventually, the sensitivities decline and converge towards zero.
 The concentration gradient becomes a limiting factor, and the enhanced mass transfer no longer plays a dominant role compared to the original system.
+It can be observed that the yield is more sensitivity at low pressure.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple.png}
 		\caption{The effect of $P_{in}$ change on $y(t)$}

### 2024-07-06 Article_Sensitivity_Analsysis-Chamomile.tex
11.06
06.07

--- 2024-06-10 Article_Sensitivity_Analsysis_short-Chamomile.tex
@@
 \begin{abstract}
-This study investigates the process of caraway oil extraction from chamomile flowers.
-A parameter-distributed model consisting of a set of partial differential equations is used to describe the governing mass transfer phenomena in a solid-fluid environment under supercritical conditions using carbon dioxide as a solvent.
+This study investigates the process of chamomile oil extraction from chamomile flowers.
+A parameter-distributed model, consisting of a set of partial differential equations, is used to describe the governing mass transfer phenomena between solid and fluid phases under supercritical conditions using carbon dioxide as the solvent.
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
 The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-The physical properties of the solvent are estimated from the Peng-Robinson equation of state.
-A set of laboratory experiments was performed under multiple constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The physical properties of the solvent are estimated using the Peng-Robinson equation of state.
+Laboratory experiments were conducted under various, but constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
 Different sensitivity analysis methods can be applied to assess the robustness of the model parameters and their influence on the process model.
-The local sensitivity analysis investigates the influence of infinitely small changes in the model parameters and the controls on model output.
-This work focuses on analysing the effect of pressure on the model state space and the extraction yield.
+Local sensitivity analysis investigates the impact of infinitesimally small changes in model parameters and controls on model output.
+This study focuses on analysing the effect of pressure on the model state space and extraction yield.
 
@@
 
-Sensitivity analysis is a tool to understand how model parameters affect its output.
+Sensitivity analysis is a tool used to understand how model parameters affect its output.
 The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
+This work implemented the automatic differentiation to derive the sensitivity equations.
 The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
-This work implemented the automatic differentiation to derive the sensitivity equations.
 In the case of dynamical systems, local sensitivity analysis provides a time series describing how that dependency evolves.
@@
 As a result, the extraction yield is improved and characterised by positive sensitivities.
+As the results of the local sensitivity analysis depends on the operating point, the analysis was repeated at different nominal pressures.
+It can be observed that system responses at low-pressures are stronger than at high-pressures.
+This behaviour can be explained by more rapid changes of the solvent properties close to the critical point and lower process efficiency at low-pressure.
+
 Local sensitivity analysis can provide valuable information by identifying which parameters are influential and how these influence changes over time.
-The sensitivity analysis results can be utilised for process modelling, experiment design, or model reduction.
+Sensitivity analysis can highlight discrepancies between model predictions and actual experimental results.
+Identifying unexpected relationships or non-linearities can prompt further investigation and refinement of the process model.
+Sensitivity analysis can inform the design of future experiments by indicating which parameters should be varied and monitored.
 

### 2024-07-06 Sections/Literature_Review.tex
06.07

@@
 
-	This study aims to analyse the influence of changes in operating conditions on the process model described in {\color{red}article 1}.
-The relation between input and output is obtained by applying a sensitivity analysis, which examines the impact of model parameters or controls on the model output.
-The result of sensitivity analysis can be used to allocate the source of uncertainty in the system, perform the model reduction or search for errors in the model (by identifying unexpected relationships between inputs and outputs).
-There are many sensitivity analysis methods, which include but are not limited to those listed below:
+	This study aims to analyze the influence of changes in operating conditions on the process model described in {\color{red}article 1}.
+Sensitivity analysis is applied to examine the impact of model parameters or controls on the model output.
+The results of sensitivity analysis can be used to identify sources of uncertainty, simplify the model, or detect errors by revealing unexpected relationships between inputs and outputs.
+Various sensitivity analysis methods are available, including:
 
@@
 
-	In the literature, many different supercritical extraction models were analysed using different sensitivity analysis techniques.
-\citet{Fiori_2007}, performed the sensitivity calculations by varying the parameters within their confidence interval and observing how the model results changed.
-Their sensitivity analysis revealed that changes in particle diameter and the internal mass transfer coefficient have the strongest influence on extraction in the second phase of the process (diffusion-control regime).% The effect of changing some operative conditions was also investigated, underlining how the solvent flow rate and the seed milling affect the extraction process.
+	Different supercritical extraction models have been analyzed using various sensitivity analysis techniques in the literature.
+For instance, \citet{Fiori_2007} performed sensitivity calculations by varying parameters within their confidence intervals and observing the changes in model results.
+Their analysis revealed that particle diameter and internal mass transfer coefficient significantly influence extraction during the diffusion-control regime.
 
-	\citet{Santos2000}, in their work, considered the model of \citet{Sovova1994} for the semi-continuous isothermal and isobaric extraction processes using carbon dioxide as a solvent.
-The parametric sensitivity analysis was carried out using a factorial design in two levels.
-The model parameters were disturbed by 10\%, and their main effects were analysed and strategies for high-performance operation are proposed.
-The authors performed the sensitivity analysis with respect to the superficial velocity, particle diameter, initial concentration of solute in the solid phase and the concentration of solute in the fluid phase at the inlet to the extractor.
+	\citet{Santos2000} considered the model of \citet{Sovova1994} for semi-continuous isothermal and isobaric extraction processes using carbon dioxide as a solvent.
+They conducted a parametric sensitivity analysis using a two-level factorial design, disturbing model parameters by 10\% and analyzing their main effects.
+They proposed strategies for high-performance operation based on sensitivities related to superficial velocity, particle diameter, initial solute concentration in the solid phase, and solute concentration in the fluid phase at the extractor inlet.
 
-	\citet{Hatami2024} performed the one-factor-at-a-time sensitivity analysis to assess the response of net present value concerning variations in both technical and economic variables.
-Their study is divided into two parts.
-In the first part, the sensitivity analysis is carried out for an extraction plant with a constant extractor volume of 300 L.
-The focus is on examining how net present value is influenced by changes in individual technical and economic parameters while keeping the extractor volume fixed.
-In the second part, the investigation revolves around the effects of altering the extractor volume (from 1 to 600 L) on the project's overall profitability.
-Their findings show that the most influential factors on net present value include the price of the extract, the interest rate, the dynamic time, and the project lifetime.
+	\citet{Hatami2024} performed a one-factor-at-a-time sensitivity analysis to assess the response of net present value to variations in technical and economic variables.
+Their study consists of two parts.
+The first part examines how net present value is influenced by changes in individual technical and economic parameters, keeping the extractor volume constant at 300 L.
+The second part investigates the effects of varying the extractor volume (from 1 to 600 L) on the project's overall profitability.
+Their findings indicate that the most influential factors on net present value include the price of the extract, interest rate, dynamic time, and project lifetime.
 

### 2024-07-06 Sections/Results_Sensitivity.tex
06.07

@@
 
-	%This work investigates the influence of pressure change on the state space and the extraction yield.
-The process model and parameters have been discussed in {\color{red}article 1}.
-The process model was calibrated on the set of experiments obtained at different operating conditions, $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-The sensitivity analysis has been performed assuming that the system operates in the middle of validate range, hence at $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
-
-	This study examines the impact of pressure change on the state space and extraction yield through the local sensitivity analysis.
 	The details of the process model and parameters are delivered in {\color{red}article 1}.
 The process model was validated under the following range of operating conditions: temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
-The system is assumed to operate at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+The sensitivity analysis is performed at the midpoint of the validated range: $35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+This study examines the impact of pressure change on the state space and extraction yield through the local sensitivity analysis.
+The local sensitivity analysis results can be interpreted as the system's response to an infinitesimal deviation in pressure.
 

### 2024-07-06 Sections/Sensitivity_Analysis.tex
11.06
06.07

@@
 As discussed by \citet{Dickinson1976}, the sensitivity analysis can be used to determine the influence of the uncertainty on the solution of the original system.
-A sensitivity analysis can be used to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction.
+Another application of sensitivity analysis is to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction.
 Finally, from a control engineering point of view, the sensitivity analysis allows sorting the control variables with respect to the level of effort required to change the model's output.
 
-	Following the work of \citet{Maly1996}, the sensitivity equations (${\dot{S}}$) can be defined as follow:
+	Following the work of \citet{Maly1996}, the sensitivity equations can be defined as follow:
 
@@
 
-	The new system of equations can be obtained by taking derivatives of $S$ with respect to time $t$ and applying the chain rule.
+	The new system of equations can be obtained by taking the total derivative of $S$ with respect to time $t$.
 
@@
 		\begin{equation} \label{SA_dt} 
-			{\dot{S}}(x;\Theta)  = \cfrac{dS(x;\Theta)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx}{d\Theta} \right) = \cfrac{d }{d\Theta} \left( \cfrac{dx}{d t} \right) = \cfrac{d {G}(x;\Theta)}{d\Theta} 
+			{\dot{S}}(x;\Theta)  = \cfrac{dS(x;\Theta)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx}{d\Theta} \right) = \cfrac{d }{d\Theta} \left( \cfrac{dx}{d t} \right) = \cfrac{d G(x;\Theta)}{d\Theta} 
 	\end{equation} }
@@
 		\begin{equation} \label{SA_eq_full}
-			\cfrac{d G(x;\Theta)}{d \Theta} = \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial x} }_{{J_x}(x;\Theta)} \underbrace{\cfrac{\partial x}{\partial \Theta} }_{S(x;\Theta)} + \underbrace{ \cfrac{\partial {G}(x;\Theta)}{\partial \Theta} }_{{J_\Theta}(x;\Theta)}
+			\cfrac{d G(x;\Theta)}{d \Theta} = \underbrace{ \cfrac{\partial G(x;\Theta)}{\partial x} }_{{\bar{J}_x}(x;\Theta)} \underbrace{\cfrac{\partial x}{\partial \Theta} }_{\bar{S}(x;\Theta)} + \underbrace{ \cfrac{\partial G(x;\Theta)}{\partial \Theta} }_{{\bar{J}_\Theta}(x;\Theta)}
 	  \end{equation} }
 
-	The Jacobian ${J_x}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${J_x}(n_x,n_x)$ is the derivative of ${G}_{n_x}(x;\Theta)$ with respect to the state variable $x_{n_\Theta}$.
+	The Jacobian ${\bar{J}_x}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${\bar{J}_x}(n_x,n_x)$ is the derivative of $G_{n_x}(x;\Theta)$ with respect to the state variable $x_{n_\Theta}$.
 
@@
 			\setlength\arraycolsep{2pt}
-			{J_x}(x;\Theta)=\begin{pmatrix}
+			{\bar{J}_x}(x;\Theta)=\begin{pmatrix}
 				\cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{1}}} & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{2}}} & \cdots & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{N_x}}}\\
@@
 
-	The sensitivity matrix $S(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each subequation $S(n_x,n_\Theta)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
-Matrix ${J_x}(x;\Theta)$ and $S(x;\Theta)$ describe indirect influence of $\Theta_{n_\Theta}$ on the state space.
+	The sensitivity matrix $\bar{S}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each entry $\bar{S}(n_x,n_\Theta)$ is the derivative of the state variable $x_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
+Matrix ${\bar{J}_x}(x;\Theta)$ and $\bar{S}(x;\Theta)$ describe indirect influence of $\Theta_{n_\Theta}$ on the state space.
 
@@
 			\begin{split}
-				S(x;\Theta) & = 
+				\bar{S}(x;\Theta) & = 
 				\begingroup % keep the change local
@@
 
-	The Jacobian ${J_\Theta}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each subequation ${J_\Theta}(n_x,n_\Theta)$ is the partial derivative of the process model equation $G_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
-${J_\Theta}(n_x,n_\Theta)$ defines direct effect of $\Theta_{n_\Theta}$ on the state space.
+	The Jacobian ${\bar{J}_\Theta}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each subequation ${\bar{J}_\Theta}(n_x,n_\Theta)$ is the partial derivative of the process model equation $G_{n_x}$ with respect to the parameter $\Theta_{n_\Theta}$.
+${\bar{J}_\Theta}(n_x,n_\Theta)$ defines direct effect of $\Theta_{n_\Theta}$ on the state space.
 
@@
 		\begin{align}
-			{J_\Theta}(x;\Theta) & =
+			{\bar{J}_\Theta}(x;\Theta) & =
 			\begingroup % keep the change local
@@
 
-	The augmented system containing the original set of equations ${G}(x;\Theta)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x;\Theta\right)$.
+	The augmented system containing the original set of equations $G(x;\Theta)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x;\Theta\right)$.
 The size of ${\textbf{G}}\left(x;\Theta\right)$ is equal to $N_s = N_x(N_\Theta + 1)$.
@@
 			\begin{bmatrix}
-				{G}(x;\Theta)\\
-				{J_x}(x;\Theta)S(x;\Theta) + {J_\Theta}(x;\Theta)
+				G(x;\Theta)\\
+				{\bar{J}_x}(x;\Theta)\bar{S}(x;\Theta) + {\bar{J}_\Theta}(x;\Theta)
 			\end{bmatrix}

### 2024-07-06 Sections/Sensitivity_Pressure.tex
06.07

@@
 	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow.
-If the flow velocity is relatively low, all pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
-The Low Mach number assumption leads to instant propagation of the thermodynamic pressure throughout the system and allows for considering a single pressure value for the entire system.
-The local sensitivity analysis results can be interpreted as a system response to the step-change (deviation) of the pressure.
+When the flow velocity is relatively low, pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
+The Low Mach number assumption allows for the instant propagation of thermodynamic pressure throughout the system, enabling a single pressure value to be considered for the entire system.
+In response to a pressure change, the energy equation experiences a simultaneous deviation across the entire spatial domain.
+This pressure change impacts the fluid's temperature within the computational domain, while boundary values are constrained by conditions specified at the domain's extremes.
+Dirichlet boundary conditions impose a fixed temperature value at the inlet, creating a thermal gradient that propagates through the system.
+Conversely, Neumann boundary conditions specify the heat flux at the boundaries.
+In this study, zero Neumann boundary conditions were applied to ensure that the temperatures at the inlet, outlet, and within the extractor vary uniformly in response to the pressure change.
 
-	\begin{comment}
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/P_P_1.png}
-		\caption{The effect of $P_{in}$ change on $P$}
-		\label{fig:Sensitivty_P_P}
-	\end{figure}
-	\end{comment}
-
-	In response to the pressure change, the energy equation experiences a deviation in the whole spatial domain simultaneously.
-The pressure change affects the fluid's temperature inside the computational domain, but boundary values are subject to constraints specified at the extremes of that domain.
-Applying the Dirichlet boundary conditions imposes a fixed temperature value at the inlet, which leads to a thermal gradient propagating along the system.
-In contrast, Neumann boundary conditions dictate the heat flux at the boundaries.
-In this work, Neumann boundary conditions of zero were used to ensure that the temperatures at the inlet, outlet, and inside the extractor would vary uniformly and according to the pressure change.
-
-	\begin{comment}
-	\begin{figure}[h!]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/H_P_1.png}
-		\caption{The effect of $P_{in}$ change on $(h \times \rho)$}
-		\label{fig:Sensitivty_P_H}
-	\end{figure}
-	\end{comment}
-
-	Figure \ref{fig:Sensitivty_P_CS} shows the sensitivity of the solute concentration in the solid phase in response to pressure change.
-As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, which suggests that the pressure reduces the fluid's velocity.
-As a result, the residence time is extended, causing longer interaction between the solute and solvent.
-Initially, the extraction process is in the kinetic-controlled regime, where the concentration gradient is high, and the limiting factor is the solute solubility.
-As discussed in {\color{red}article 1}, the system is considered to be far from saturation, which explains the low system response at the beginning of the process.
-In the sensitivity analysis of \citet{Fiori_2007}, the low initial system response was also observed.
-The system response becomes evident when the concentration gradient diminishes, and the extraction switches from the kinetic-controlled to the diffusion-controlled regime.
-The negative sign is interpreted as a faster solute loss from the solid phase, which corresponds to enhanced mass transfer.
-Over time, the amount of solute becomes a limiting factor, and the pressure change effect on the system is reduced.
-Eventually, the sensitivities approach zero asymptotically when the solute is washed out from the solid bed.
+	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of solute concentration in the solid phase to pressure changes.
+As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, indicating that increased pressure reduces the fluid's velocity.
+This results in an extended residence time, allowing for longer interaction between the solute and solvent.	Initially, the extraction process operates in the kinetic-controlled regime, where the concentration gradient is high, and solute solubility is the limiting factor.
+As noted in [article 1], the system is considered far from saturation, which explains the low initial system response.
+This low initial response was also observed in the sensitivity analysis by \citet{Fiori_2007}.
+The system's response becomes more pronounced as the concentration gradient decreases and the extraction shifts from the kinetic-controlled to the diffusion-controlled regime.
+The negative sensitivity indicates a faster solute loss from the solid phase, corresponding to enhanced mass transfer.
+Over time, as the amount of solute decreases, it becomes a limiting factor, reducing the effect of pressure changes on the system.
+Eventually, the sensitivities approach zero asymptotically as the solute is washed out from the bed.
 
@@
 
-	Figure \ref{fig:Sensitivty_P_CF} shows how sensitive is the solute concentration in the fluid phase to the pressure change.
-Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of the fluid phase sensitivities can be observed.
-Due to the advection, the sensitivities move along the system analogously to the solute in the fluid phase.
-Although the pressure increase improves the mass transfer, the system response is initially low, which reflects the idle period discussed above.
-Later, the sensitivities increase due to faster solute loss from the solid phase.
-The positive sensitivities indicate that more solute is transported from the particles to the fluid.
-When the amount of solute in the solid phase becomes a limiting factor, the extraction rate slows down, and sensitivities decline to negative values and eventually goes asymptotically towards zero.
+	Figure \ref{fig:Sensitivty_P_CF} illustrates the sensitivity of solute concentration in the fluid phase to pressure changes.
+Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of fluid phase sensitivities is more apparent.
+Due to advection, the sensitivities move through the system similarly to the solute in the fluid phase.	Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period.
+As the process continues, the sensitivities increase, indicating faster solute loss from the solid phase.
+The positive sensitivities show that more solute is being transported from the solid particles to the fluid.
+When the solute in the solid phase becomes a limiting factor, the extraction rate slows, and sensitivities decline to negative values, eventually approaching zero asymptotically.
 
@@
 
-	Figure \ref{fig:Sensitivty_P_y} illustrates how sensitive the extraction yield is to the pressure changes.
-The effect of pressure change on the yield is expanded and consider for multiple values of pressure.
-Initially, all the sensitivity curve stay almost flat, suggesting a latency in the system's response.
-Due to the decreased velocity of the fluid, the solute reaches the extractor's outlet later, which causes minor negative sensitivities to appear.
-When the solute reaches exits the extractor, the sensitivity curves increase rapidly.
-The positive yield sensitivities indicate improved process efficiency, which is directly related to enhanced mass transfer.
-The peak in $\frac{dy}{dP_{in}}$ reflects when the deviation from the original system is the largest.
-Eventually, the sensitivities decline and converge towards zero.
-The concentration gradient becomes a limiting factor, and the enhanced mass transfer no longer plays a dominant role compared to the original system.
-It can be observed that the yield is more sensitivity at low pressure.
+	Figure \ref{fig:Sensitivty_P_y} show how sensitive the extraction yield is to pressure changes over an extended period for various pressure values.
+Initially, all sensitivity curves remain nearly flat, indicating a delayed response in the system.
+Due to the reduced fluid velocity, the solute reaches the extractor's outlet later, causing minor negative sensitivities to appear.
+Once the solute exits the extractor, the sensitivity curves rise rapidly.
+Positive yield sensitivities indicate improved process efficiency and enhanced mass transfer.
+The peak in $\frac{dy}{dP_{in}}$ represents the point of greatest deviation from the original system.
+Eventually, the sensitivities decline and converge towards zero as the concentration gradient becomes a limiting factor, reducing the impact of enhanced mass transfer.
+
+	As presented in Figure \ref{fig:Sensitivty_P_y}, higher sensitivities are observed for the low-pressure system.
+At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction as shown by data given in {\color{red}article 1}.
+Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield.
+Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity.
+These changes can strongly affect the solute's solubility and the mass transfer rates, resulting in higher sensitivity at lower pressures where the system operates closer to the critical point.
 

### 2024-07-09 SFE_Sensitivity_Analysis_Chamomile/main_Sensitivity_Analysis_Chamomile.m
09.07

@@ -1,0 +1,275 @@
+startup;
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
+
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+import casadi.*
+%%
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('wpd_datasets.xlsx');
+which_dataset           = 4;
+
+SAMPLE                  = LabResults(21:34,1);
+data_org                = LabResults(21:34,which_dataset+1)';
+
+%% Load paramters
+m_total                 = 3.0;
+
+% Bed geometry
+before                  = 0.04;                                             % Precentage of length before which is empty
+bed                     = 0.92;                                             % Percentage of length occupied by fixed bed
+
+% Set time of the simulation
+PreparationTime         = 0;
+ExtractionTime          = 15000;
+timeStep                = 1;                                                % Minutes
+
+simulationTime          = PreparationTime + ExtractionTime;
+
+timeStep_in_sec         = timeStep * 60;                                    % Seconds
+Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+Time                    = [0 Time_in_sec/60];                               % Minutes
+
+N_Time                  = length(Time_in_sec);
+
+%% Specify parameters to estimate
+nstages                 = Parameters{1};
+
+nstagesbefore           = 1:floor(before*nstages);
+nstagesbed              = nstagesbefore(end)+1 : nstagesbefore(end) + floor(bed*nstages);
+nstagesafter            = nstagesbed(end)+1:nstages;
+
+bed_mask                = nan(nstages,1);
+bed_mask(nstagesbefore) = 0;
+bed_mask(nstagesbed)    = 1;
+bed_mask(nstagesafter)  = 0;
+
+%% Number of variables
+Nx                      = 3 * nstages+2;                                    % 3*Nstages(C_f, C_s, H) + P(t) + yield
+Nu                      = 3 + numel( Parameters );                          % T_in, P, F + numel(Parameters)
+
[…]

### 2024-07-09 SFE_Sensitivity_Analysis_Chamomile/modelSFE.m

@@ -1,0 +1,139 @@
+function xdot = modelSFE(x, p, mask, dt)
+    % (t, x, u, parameters)
+    % Model with (F)luid, (S)olid, (T)emperature
+    % Di is a function of temperature (T), the function works with numbers,
+    % vectors of numbers and vectors of symbolic variables
+    % Rho (Peng-Robinson) are constant numbers
+
+    %% Load Paramters
+    T_u           =     p{1};
+    P_u           =     p{2};
+    F_u           =     p{3};
+
+    parameters    =     p(4:end);
+
+    %nstages       =     parameters{1};
+    C0solid       =     parameters{2};     % Extractor initial concentration of extract
+    r             =     parameters{3};     % Extractor radius (m)
+    epsi          =     parameters{4};     % Void bed fraction
+    dp            =     parameters{5};     % Diameter of the particle (m)
+    L             =     parameters{6};     % Length of the extractor (m)
+    rho_s         =     parameters{7};     %
+    mi            =     parameters{9};
+
+    km            =     parameters{8} ;
+    %Di            =     parameters{44}* 1e-13;      
+    %Dx            =     parameters{45}* 1e-12;      
+    Dx            =     1e-15;      
+    %gamma         =     parameters{46};
+
+    nstages_index =     numel(mask);
+    
+    %% Properties of the bed
+    A             =     pi*r^2 ;       % Cross-section of the extractor (m^2)
+    rp            =     dp / 2;
+    lp2           =     (rp / 3)^2;
+
+    %% States
+    FLUID         =     x(0*nstages_index+1:1*nstages_index);
+    SOLID         =     x(1*nstages_index+1:2*nstages_index);
+    ENTHALPY_RHO  =     x(2*nstages_index+1:3*nstages_index);
+    PRESSURE      =     x(3*nstages_index+1);
+
+    TEMP          =     Reconstruct_T_from_enthalpy(ENTHALPY_RHO, PRESSURE, parameters);
+      
+    %Properties of the fluid in the extractor
+    Z             =     Compressibility(TEMP, PRESSURE,    parameters);
+
+    RHO           =     rhoPB_Comp(     TEMP, PRESSURE, Z, parameters);   
+    MU            =     Viscosity(TEMP,RHO);
+
+    VELOCITY      =     Velocity(F_u, mean([RHO(2:9:end)]), parameters);
+
+    RE            =     dp .* RHO .* VELOCITY ./ MU;
+    
[…]

### 2024-09-18 Article_Sensitivity_Analsysis-Chamomile.tex
18.09

@@
 \usepackage{subcaption}
+
+\usepackage{nomencl}
+\makenomenclature
+
+\usepackage{etoolbox}
+\renewcommand\nomgroup[1]{%
+	\item[\bfseries
+	\ifstrequal{#1}{A}{Latin symbols}{%
+		\ifstrequal{#1}{B}{Greek symbols}{%
+			\ifstrequal{#1}{C}{Abberivations}{
+	}}}%
+	]}
 
@@
 The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
-In the case of dynamical systems, local sensitivity analysis provides a time series describing how that dependency evolves.
+In the case of dynamical systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies in time with respect to small perturbations in parameters.
 
 The local sensitivity analysis can be performed with respect to any model parameter, but this work focuses on the effect of pressure increase.
-At selected operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster loss of solute from particles and consequently to negative sensitivities in the solid phase.
+At selected operating conditions ($35^\circ C$ and $5\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster loss of solute from particles and consequently to negative sensitivities in the solid phase.
 Analogously, the sensitivities in the fluid phase are characterised by positive deviations, which indicates that more solute is transported to the fluid phase.
@@
 It can be observed that system responses at low-pressures are stronger than at high-pressures.
-This behaviour can be explained by more rapid changes of the solvent properties close to the critical point and lower process efficiency at low-pressure.
+This behaviour can be explained by rapid changes of the solvent properties close to the critical point.
 
-Local sensitivity analysis can provide valuable information by identifying which parameters are influential and how these influence changes over time.
-Sensitivity analysis can highlight discrepancies between model predictions and actual experimental results.
-Identifying unexpected relationships or non-linearities can prompt further investigation and refinement of the process model.
-Sensitivity analysis can inform the design of future experiments by indicating which parameters should be varied and monitored.
+Local sensitivity analysis results provide valuable information by identifying which parameters are influential and how these influence changes over time.
+One application of the sensitivity analysis is to spot discrepancies between model predictions and actual experimental results.
+Identifying unexpected system responses prompts further investigation and refinement of the process model.
+Sensitivity analysis results can be used to design future experiments by indicating which parameters should be varied and monitored.
+Moreover, the parameters which are characterized by low sensitivity can be subject of model reduction.
 
@@
 %\clearpage
+\newpage
 %\bibliographystyle{model1-num-names}
@@
 
+\newpage
+
+\nomenclature[A]{\(P\)}{Pressure}
+\nomenclature[A]{\(T\)}{Temperature}
+\nomenclature[A]{\(T^{in}\)}{Inlet temperature}
+\nomenclature[A]{\(T^{out}\)}{Outlet temperature}
+\nomenclature[A]{\(F\)}{Mass flow rate}
+\nomenclature[A]{\(u\)}{Superfical velocity}
+\nomenclature[A]{\(v\)}{Linear velocity}
+\nomenclature[A]{\(z\)}{Spatial direction}
+\nomenclature[A]{\(e\)}{Internal energy}
+\nomenclature[A]{\(h\)}{Enthalpy}
+\nomenclature[A]{\(t\)}{Time}
+\nomenclature[A]{\(t_f\)}{Total extraction time}
+\nomenclature[A]{\(t_0\)}{Inital extraction time}
+\nomenclature[A]{\(A\)}{Total cross section of the bed}
+\nomenclature[A]{\(A_f\)}{Cross section of the bed accupied by the fluid}
+\nomenclature[A]{\(c_f\)}{Concentration of solute in fluid phase}
+\nomenclature[A]{\(c_{f0}\)}{Inital concentration of solute in fluid phase}
+\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface}
+\nomenclature[A]{\(c_s\)}{Concentration of solute in solid phase}
+\nomenclature[A]{\(c_{s0}\)}{Inital concentration of solute in solid phase}
+\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface}
+\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore}
+\nomenclature[A]{\(c_{pf}\)}{Concentration of solute in the pore opening}
+\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficeint}
+\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term}
+\nomenclature[A]{\(L\)}{Length of fixed bed}
+\nomenclature[A]{\(S\)}{Sensitivity equations}
+\nomenclature[A]{\(\textbf{G}\)}{Augumented system}
+\nomenclature[A]{\(\dot{S}\)}{Time derivative of sensitivity equations}
+\nomenclature[A]{\(\bar{S}\)}{Sensitivity matrix}
+\nomenclature[A]{\(\bar{J}_x\)}{Jacobian matrix with respect to the state space}
+\nomenclature[A]{\(\bar{J}_\Theta\)}{Jacobian matrix with respect to the paramters}
+%\nomenclature[A]{\(\mathcal{L}\)}{Log-likelihood function}
+\nomenclature[A]{\(l\)}{Characterisitic diemsinon of particles}
+\nomenclature[A]{\(D_i\)}{Interanl diffusion coefficient}
+\nomenclature[A]{\(D_i^R\)}{Reference value of interanl diffusion coefficient}
+\nomenclature[A]{\(r\)}{Particle radius}
+\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient}
+\nomenclature[A]{\(k_m\)}{Mass partition coefficient}
+\nomenclature[A]{\(y\)}{Extraction yield}
+\nomenclature[A]{\(Y\)}{Yield measurment}
+\nomenclature[A]{\(x\)}{State vector}
+\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
+\nomenclature[A]{\(p\)}{Probaility disribution model}
+\nomenclature[A]{\(R_e\)}{Reynolds number}
+
+\nomenclature[B]{\(\rho_f\)}{Fluid density}
+\nomenclature[B]{\(\Phi\)}{Bed porosity}
+\nomenclature[B]{\(\rho_s\)}{Bulk density of solid}
+\nomenclature[B]{\(\mu\)}{Sphericity coefficient}
+\nomenclature[B]{\(\gamma\)}{Decaying function}
+\nomenclature[B]{\(\Upsilon\)}{Decay coefficient}
+\nomenclature[B]{\(\Theta\)}{Paramter space}
+\nomenclature[B]{\(\theta\)}{vector of unknown parameters}
+\nomenclature[B]{\(\epsilon\)}{Unobervable error}
+\nomenclature[B]{\(\sigma\)}{Standard deviation}
+
+\nomenclature[C]{BIC}{Broke-and-Intact Cell model}
+%\nomenclature[C]{MLE}{Maximum Likelihood Estimation}
+\nomenclature[C]{SFE}{Supercritical Fluid Extraction}
+\nomenclature[C]{HBD}{Hot Ball Diffusion}
+\nomenclature[C]{SC}{Shrinking Core}
+
+\printnomenclature
+
 \end{document}

### 2024-09-18 Sections/Sensitivity_Pressure.tex
18.09

@@
 Dirichlet boundary conditions impose a fixed temperature value at the inlet, creating a thermal gradient that propagates through the system.
-Conversely, Neumann boundary conditions specify the heat flux at the boundaries.
+On the other hand, Neumann boundary conditions specify the heat flux at the boundaries.
 In this study, zero Neumann boundary conditions were applied to ensure that the temperatures at the inlet, outlet, and within the extractor vary uniformly in response to the pressure change.
@@
 Due to the reduced fluid velocity, the solute reaches the extractor's outlet later, causing minor negative sensitivities to appear.
-Once the solute exits the extractor, the sensitivity curves rise rapidly.
+Once the solute exits the extractor, the sensitivity curves rise.
 Positive yield sensitivities indicate improved process efficiency and enhanced mass transfer.
@@
 Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield.
-Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity.
-These changes can strongly affect the solute's solubility and the mass transfer rates, resulting in higher sensitivity at lower pressures where the system operates closer to the critical point.
+Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity and consequently to higher sensitivity of the system state-space.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple.png}
+		\includegraphics[trim = 0.1cm 0.0cm 1.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple.png}
 		\caption{The effect of $P_{in}$ change on $y(t)$}

### 2024-09-18 Sections/introduction_imp.tex
Updates from Overleaf
18.09

@@
 
+	Supercritical CO$_2$ is defined as carbon dioxide that is pressurized and heated above its critical point (31.1 $^\circ C$, 74 bar).
+Depending on the operating conditions, the fluid properties such as viscosity and density can vary, which leads to multiple industrial applications of CO$_2$.
+
+	The supercritical carbon dioxide is commonly used for impregnation as described by \citet{Weidner2018}, \citet{Machado2022} or \citet{Fathi2022}.
+Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
+The main advantage of using supercritical CO$_2$ is that after depressurization, it desorbs from the surface and evaporates, leaving a solvent-free product.
+On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.
+
+	Another application of supercritical CO$_2$ is nanoparticles formation as investigated by \citet{Padrela2018}, \citet{Franco2021}, \citet{SaadatiArdestani2020} or \citet{Sodeifian2022}.
+Supercritical carbon-dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating operating conditions.
+Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nanosized particles or crystals, such as reduced use of toxic solvents.
+Moreover, the CO$_2$ is completely removed from the final product by simple depressurization.
+
+	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993} or \citet{Sovova1994}.
+Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
+Distillation, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
+This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction.
+Supercritical CO$_2$ is appealing due to its distinctive properties: it is inflammable, non-toxic and non-corrosive.
+Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
+
 	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process.
-Chamomile is a medicinal herb widely cultivated in southern and eastern Europe—such as Germany, Hungary, France, and Russia.
-It can be found outside of Europe in Brazil as discussed by \citet{Singh2011}.
+Chamomile is a medicinal herb widely cultivated in southern and eastern Europe — in countries such as Germany, Hungary, France and Russia.
+It can be found outside Europe, for instance in Brazil as discussed by \citet{Singh2011}.
 This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets.
 Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy.
-Chamomile's aqueous extract is widely used to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia, and other sleep-related conditions, according to \citet{Srivastava2009}.
+Extracts of chamomile are widely used to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia and other sleep-related conditions, according to \citet{Srivastava2009}.
 \citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg.
@@
 
-	Evaluating the economic viability of the process is essential when choosing the suitable technology for essential oil extraction.
-Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
-Distillation, for example, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
-This limitation has led to the increased popularity of alternative techniques like supercritical fluid extraction.
-Supercritical carbon dioxide is appealing due to its distinctive properties: it is inflammable, non-toxic, and non-corrosive.
-Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
+	The literature offers various mathematical models to describe the extraction of valuable compounds from biomass.
+Selecting a process model is case-to-case dependent and requires analysis of each model's specific assumptions about mass transfer and thermodynamic equilibrium.
 
-	The literature offers various mathematical models to describe the extraction of valuable compounds from biomass.
-Selecting a process model is case-to-case dependent and requires analysing each model's specific assumptions about mass transfer and thermodynamic equilibrium.
+	\citet{Goto1996} presented the Shrinking Core (SC) model, which describes a process of irreversible desorption that is followed by diffusion through the pores of a porous solid.
+When the mass transfer rate of the solute in the non-extracted inner region is significantly slower than in the outer region, where most of the solute has already been extracted, or when the solute concentration exceeds its solubility in the solvent, a distinct boundary may form between the inner and outer regions.
+As extraction progresses, the core of the inner region shrinks.
+The model envisions supercritical CO$_2$ extraction as a sharp, inward-moving front, with a completely non-extracted core ahead of the front and a fully extracted shell behind it.
 
-	The model proposed by \citet{Reverchon1993} is called the hot ball model, as it is based on an analogy to heat transfer and describes an extraction process from solid particles.
-This model assumes that particles contain low quantities of solute and that solubility is not a limiting factor.
+	\citet{Sovova1994} proposed The Broken-and-Intact Cell (BIC) model, which assumes that a portion of the solute, initially stored within plant structures and protected by cell walls, is released during the mechanical breakdown of the material.
+The solute located in the region of broken cells near the particle surface is directly exposed to the solvent, while the core of the particle contains intact cells with undamaged walls.
+This model describes three extraction phases: a fast extraction phase for accessible oil, a transient phase, and a slow phase controlled by diffusion.
+The model has been successfully applied to the extraction of grape oil (\citet{Sovova1994b}) and caraway oil (\citet{Sovova1994a}).
 
-	The Broken-and-Intact Cell model, proposed by \citet{Sovova1994}, assumes that external surfaces of particles are mechanically disrupted, allowing the solvent's access to the solute in broken cells.
-In contrast, the solute in intact cells remains less accessible due to higher mass transfer resistance.
+	The Supercritical Fluid Extraction (SFE) process can be be treated similarly to heat transfer, considering solid particles like hot balls cooling down in a uniform environment.
+\citet{Bartle1990} introduced the hot ball diffusion (HBD) model, where spherical particles with uniformly distributed solute diffuse similarly to heat diffusion.
+Unlike the BIC model, where solute is readily available on the particle surface, the HBD model is suited for systems with small quantities of extractable materials and is not limited by solubility.
+The model is particularly relevant when internal diffusion controls mass transfer, allowing results from single particles to be extended to the entire bed under uniform conditions.
+\citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes for natural materials.
 
-	\citet{Reverchon1996} formulated a fluid-solid extraction model where the solute is treated as a single component, governed by internal mass transfer resistance and omitting the effects of external mass transfer, axial dispersion, and variations in fluid density and flow rate throughout the bed.
+	\citet{Reverchon1996} proposed a model for extraction of essential oils, which are mainly located inside the vegetable cells in organules called vacuoles.
+Only a small fraction of essential oil might be near the particle surface due to the breaking up of cells during grinding or in epidermal hairs located on the leaf surface.
+The fraction of oil freely available on the particle surface should not be significant in the case of SFE from leaves.
+Consequently, SFE of essential oil from leaves should be mainly controlled by the internal mass-transfer resistance.
+Therefore, the external mass-transfer coefficient was neglected in the development of the model of \citet{Reverchon1996}.
+The mass balances were developed in the additional hypotheses that the axial dispersion can be neglected and that the solvent density and flow rate are constant along the bed.
 
@@
 This model aims for control-oriented simplicity, assuming a semi-continuous operation within a cylindrical vessel.
-The process involves supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
-Parameters such as the pressure ($P$), feed flow rate ($F_{in}$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
+The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
+Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T^{in}$) are adjustable and measurable, while the outlet temperature ($T^{out}$) and the amount of product at the outlet can only be monitored.
 Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.
@@
 		\includegraphics[width=\columnwidth]{Figures/PFD.drawio.pdf}
-		\caption{Process flow diagram}
+		\caption{Process flow diagram.}
 		\label{fig: SFE_drawing}

### 2024-09-18 SFE_Sensitivity_Analysis_Chamomile/main_Chamomile_Error.m

@@ -9,23 +9,19 @@ import casadi.*
 Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
 Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
 
-LabResults              = xlsread('wpd_datasets.xlsx');
-which_dataset           = 4;
-
-SAMPLE                  = LabResults(21:34,1);
-data_org                = LabResults(21:34,which_dataset+1)';
+LabResults              = xlsread('dataset_2.xlsx');
 
 %% Load paramters
 m_total                 = 3.0;
 
 % Bed geometry
 before                  = 0.04;                                             % Precentage of length before which is empty
-bed                     = 0.92;                                              % Percentage of length occupied by fixed bed
+bed                     = 0.92;                                             % Percentage of length occupied by fixed bed
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 100;
-timeStep                = 1;                                                % Minutes
+ExtractionTime          = 600;
+timeStep                = 0.5;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
 
@@ -89,7 +85,7 @@ x                       = MX.sym('x', Nx);
 u                       = MX.sym('u', Nu);
 
 %% Set Integrator
-f                       = @(x, u) modelSFE(x, u, bed_mask, timeStep_in_sec);
+f                       = @(x, u) modelSFE_2(x, u, bed_mask, timeStep_in_sec);
 xdot                    = modelSFE(x, u, bed_mask, timeStep_in_sec);
 
 % Integrator
@@ -111,13 +107,24 @@ m_fluid                 = G(L_bed_after_nstages)*( L_bed_after_nstages(2) ); % L
 m_fluid                 = [zeros(1,numel(nstagesbefore)) m_fluid];
 C0fluid                 = m_fluid * 1e-3 ./ V_fluid';
 
-RES                     = [];
+MSE = [];
+STD = [];
 
-for PP = [100,150,200]
-    %% Set operating conditions
-    T0homog                 = 35+273;                    % K
[…]

### 2024-09-18 SFE_Sensitivity_Analysis_Chamomile/main_Sensitivity_Analysis_Chamomile.m

@@ -24,8 +24,8 @@ bed                     = 0.92;                                             % Pe
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 15000;
-timeStep                = 1;                                                % Minutes
+ExtractionTime          = 60000;
+timeStep                = 10;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
 
@@ -199,8 +199,8 @@ for PP = [100,125,150,175,200]
                 set(gca,'FontSize',My_Font)
                 %xscale log
                 
-                %exportgraphics(figure(1),[name_p{ind+1},'_',name_v{ii},'.png'], "Resolution",300);
-                %close all;
+                exportgraphics(figure(1),[name_p{ind+1},'_',name_v{ii},'.png'], "Resolution",300);
+                close all;
             end
     
             %% Sensitivities plot - P and y
@@ -214,18 +214,19 @@ for PP = [100,125,150,175,200]
                 hold off
                 set(gca,'FontSize',My_Font)
                 
-                %exportgraphics(figure(1),[name_p{ind+1},'_',name_v{ii},'.png'], "Resolution",300);
-                %close all;
+                exportgraphics(figure(1),[name_p{ind+1},'_',name_v{ii},'.png'], "Resolution",300);
+                close all;
                 indx = indx + 1;
             end     
             %}   
     end
 end
 %%
+%{
 plot(Time, RES','LineWidth',2)
 legend('100 bar', '125 bar', '150 bar', '175 bar', '200 bar', 'Location','best')
 legend box off
-xlabel('Time [min]'); 
+xlabel('Time min'); 
 ylabel(['$\frac{d ',name_s{5},'}{d',name_v{2},'}$'])
 set(gca,'FontSize',My_Font)
 %exportgraphics(figure(1),['Yield_multiple.png'], "Resolution",300);

### 2024-09-18 SFE_Sensitivity_Analysis_Chamomile/modelSFE_2.m

@@ -48,9 +48,9 @@ function xdot = modelSFE(x, p, mask, dt)
     RHO           =     rhoPB_Comp(     TEMP, PRESSURE, Z, parameters);   
     MU            =     Viscosity(TEMP,RHO);
 
-    VELOCITY      =     Velocity(F_u, mean([RHO(2:9:end)]), parameters);
+    VELOCITY      =     Velocity(F_u, mean([RHO(2:25:end)]), parameters);
 
-    RE            =     dp .* RHO .* VELOCITY ./ MU .* 1.3;
+    RE            =     dp .* RHO .* VELOCITY ./ MU .* 1.3 ;
     
     %% Thermal Properties
     CP            =     SpecificHeatComp(TEMP, PRESSURE, Z, RHO,                 parameters);            % [kJ/kg/K]
@@ -73,23 +73,20 @@ function xdot = modelSFE(x, p, mask, dt)
     Cf_B          =     FLUID(nstages_index);
                                                                                             % If the sensitivity of P and F is consider, then set the input T as equal to the T inside of the extractor
                                                                                             % to avoid different small mismatch of T between the inlet and inside of the extractor
-    %T_0           =     T_u;
-    T_0           = if_else( km==2 , TEMP(1) , T_u );
+    T_0           =      T_u;
     
     T_B           =     TEMP(nstages_index);
 
-    Z_0           =     Compressibility(T_0, PRESSURE,      parameters);
+    Z_0           =     Compressibility(T_0, PRESSURE,     parameters);
     
-    rho_0         =     rhoPB_Comp(     T_0, PRESSURE, Z_0, parameters);
+    rho_0         =     rhoPB_Comp(     T_0, P_u, Z_0, parameters);
     
-    u_0           =     VELOCITY;
+    u_0           =      VELOCITY(1);
     
     H_0           =     SpecificEnthalpy(T_0, PRESSURE, Z_0, rho_0, parameters );   
 
-    %enthalpy_rho_0 =   ENTHALPY_RHO(1);                                                      % If the sensitivity of F is consider, then set the input h*rho as equal to the h*rho inside of the extractor
+    enthalpy_rho_0 = rho_0 .* H_0 ;                                                         % If the sensitivity of F is consider, then set the input h*rho as equal to the h*rho inside of the extractor
[…]

### 2024-10-10 Sections/Saturation.tex
10.10

@@
 
+	\subsubsection{Empirical correlations}
+
+	The empirical correlations for $D_i$ and $\Upsilon$ were derived by {\color{red}article 1} and validated for temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
+Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables.
+The region marked with the white dashed line represents the confidence region, where the model has been tested.
+Both correlations should be equal of greater than zero, to avoid unphysical behaviour such as the reverse mass transfer.
+The multiple linear regression functions are combined with the rectifier function to ensure the non-negativity.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Di.png}
+		\caption{Multiple linear regression $D_i^R = f(Re, F)$}
+		\label{fig:Correlation_Di}
+	\end{figure}
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Gamma.png}
+		\caption{Multiple linear regression $\Upsilon = f(Re, F)$}
+		\label{fig:Correlation_Gamma}
+	\end{figure}
+
 \end{document}

### 2024-10-10 SFE_Sensitivity_Analysis_Chamomile/Diffusion.m

@@ -5,5 +5,5 @@ function D = Diffusion(Re, F, parameters)
     c = parameters{46};
 
     D =  a -  b * Re + c  * F * 10^5;
-    
+    D = max(D,0) ;
 end

### 2024-10-10 SFE_Sensitivity_Analysis_Chamomile/main_Chamomile_Error.m

@@ -86,7 +86,7 @@ u                       = MX.sym('u', Nu);
 
 %% Set Integrator
 f                       = @(x, u) modelSFE_2(x, u, bed_mask, timeStep_in_sec);
-xdot                    = modelSFE(x, u, bed_mask, timeStep_in_sec);
+xdot                    = modelSFE_2(x, u, bed_mask, timeStep_in_sec);
 
 % Integrator
 F                       = buildIntegrator(f, [Nx,Nu] , timeStep_in_sec);
@@ -110,7 +110,7 @@ C0fluid                 = m_fluid * 1e-3 ./ V_fluid';
 MSE = [];
 STD = [];
 
-for jj=1:12%N_trial
+for jj=5:8%N_trial
 
     which_dataset           = jj;
     data_org                = LabResults(6:19,which_dataset+1)';
@@ -157,7 +157,7 @@ for jj=1:12%N_trial
 
     MSE = [MSE, mse(data_org, xx_0(end,N_Sample))];
     STD = [STD, std(data_org - xx_0(end,N_Sample))];
-    %hold on; plot(Time,xx_0(end,:), 'LineWidth',2); plot(SAMPLE, data_org,'ko', 'LineWidth',2, 'HandleVisibility','off' ); hold off
+    hold on; plot(Time,xx_0(end,:), 'LineWidth',2); plot(SAMPLE, data_org,'ko', 'LineWidth',2, 'HandleVisibility','off' ); hold off
     %subplot(2,1,2)
     %hold on; plot(SAMPLE(2:end),diff(xx_0(end,N_Sample))); plot(SAMPLE(2:end), data_diff,'o'); hold off
     %xlabel('t [min]')

### 2024-10-11 Article_Sensitivity_Analsysis-Chamomile.tex
11.10

--- 2024-07-06 Article_Sensitivity_Analsysis-Chamomile.tex
@@
 % Packages
+\usepackage[switch]{lineno}
+\linenumbers
+
 % --------------------------------------------------------------------
@@
 \usepackage{subcaption}
+
+\usepackage{nomencl}
+\makenomenclature
+
+\usepackage{etoolbox}
+\renewcommand\nomgroup[1]{%
+	\item[\bfseries
+	\ifstrequal{#1}{A}{}{%
+		\ifstrequal{#1}{B}{Greek symbols}{%
+			\ifstrequal{#1}{C}{Abberivations}{
+	}}}%
+	]}
+\newcommand{\nomunit}[1]{%
+	\renewcommand{\nomentryend}{\hspace*{\fill}#1}}
 
@@
 The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
-The flow is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+The {\color{blue}flow of carbon dioxide} is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
 The physical properties of the solvent are estimated using the Peng-Robinson equation of state.
-Laboratory experiments were conducted under various, but constant operating conditions: $30 - 40^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-Different sensitivity analysis methods can be applied to assess the robustness of the model parameters and their influence on the process model.
-Local sensitivity analysis investigates the impact of infinitesimally small changes in model parameters and controls on model output.
+Laboratory experiments were conducted under various, but constant operating conditions.
+$30 - 40~^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+{\color{blue}The local sensitivity analysis method was applied to evaluate the model parameters' robustness by investigating the impact of infinitesimally small changes in model parameters and controls on model outputs}.
 This study focuses on analysing the effect of pressure on the model state space and extraction yield.
@@
 The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
-In the case of dynamical systems, local sensitivity analysis provides a time series describing how that dependency evolves.
+In the case of dynamic systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies in time with respect to small perturbations in parameters.
 
-The local sensitivity analysis can be performed with respect to any model parameter, but this work focuses on the effect of pressure increase.
-At selected operating conditions ($35^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster loss of solute from particles and consequently to negative sensitivities in the solid phase.
+%The local sensitivity analysis can be performed with respect to any model parameter, but this work focuses on the effect of pressure increase.
+At selected operating conditions( $35^\circ C$ and $5\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster mass transfer from particles and consequently to negative sensitivities in the solid phase.
 Analogously, the sensitivities in the fluid phase are characterised by positive deviations, which indicates that more solute is transported to the fluid phase.
@@
 It can be observed that system responses at low-pressures are stronger than at high-pressures.
-This behaviour can be explained by more rapid changes of the solvent properties close to the critical point and lower process efficiency at low-pressure.
+This behaviour can be explained by rapid changes of the solvent properties close to the critical point.
 
-Local sensitivity analysis can provide valuable information by identifying which parameters are influential and how these influence changes over time.
-Sensitivity analysis can highlight discrepancies between model predictions and actual experimental results.
-Identifying unexpected relationships or non-linearities can prompt further investigation and refinement of the process model.
-Sensitivity analysis can inform the design of future experiments by indicating which parameters should be varied and monitored.
+{\color{blue}Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of increasing pressure.
+Under the selected operating conditions ($35~^\circ C$ and $5 \times 10^{-5}$ kg/s), it was observed for all the cases that the pressure increment enhances mass transfer, leading to a more faster mass transfer of solute from the particles.
+Consequently, the negative sensitivities can be observed in the diagram for the solid phase.
+The corresponding response in the fluid phase is characterized by positive-valued sensitivities, indicating that more amount of solute is transported into the fluid phase.
+As a result, the extraction yield is improved and characterized by positive sensitivities.
+Given that the results of the local sensitivity analysis depend on the operating point, the analysis was repeated at different pressures.
+It was observed that the system responses at low pressures are stronger than those at higher pressures.
+This behaviour can be explained by the rapid changes in solvent properties occurring near the critical point of CO$_2$}.
+
+Local sensitivity analysis results provide valuable information by identifying which parameters are influential and how these influence changes over time.
+One application of the sensitivity analysis is to spot discrepancies between model predictions and actual experimental results.
+Identifying unexpected system responses prompts further investigation and refinement of the process model.
+Sensitivity analysis results can be used to design future experiments by indicating which parameters should be varied and monitored.
+Moreover, the parameters which are characterized by low sensitivity can be subject of model reduction.
+
+\section*{Acknowledgement} 
+This work was supported by NovelBaltic, CEForestry (IBC), BIO4P (BF)
 
@@
 
+\newpage
+
+\nomenclature[A]{\(P\)}{Pressure \nomunit{bar}}
+\nomenclature[A]{\(T\)}{Temperature \nomunit{K}}
+\nomenclature[A]{\(T_{in}\)}{Inlet temperature \nomunit{K}}
+\nomenclature[A]{\(T_{out}\)}{Outlet temperature \nomunit{K}}
+\nomenclature[A]{\(F\)}{Mass flow rate \nomunit{kg/s}}
+\nomenclature[A]{\(u\)}{Superficial velocity \nomunit{m/s}}
+\nomenclature[A]{\(v\)}{Linear velocity \nomunit{m/s}}
+\nomenclature[A]{\(z\)}{Spatial direction \nomunit{m}}
+\nomenclature[A]{\(e\)}{Internal energy \nomunit{J/kg}}
+\nomenclature[A]{\(h\)}{Enthalpy \nomunit{J}}
+\nomenclature[A]{\(t\)}{Time \nomunit{s}}
+\nomenclature[A]{\(t_f\)}{Total extraction time \nomunit{s}}
+\nomenclature[A]{\(t_0\)}{Initial extraction time \nomunit{s}}
+\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{m$^2$}}
+\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{m$^2$}}
+\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg$^3$}}
+\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/m$^3$}}
+\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{m$^2$/s}}
+\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/m$^3$/s}}
+\nomenclature[A]{\(L\)}{Length of the fixed bed \nomunit{m}}
+\nomenclature[A]{\(S\)}{Sensitivity equations}
+\nomenclature[A]{\(\textbf{G}\)}{Augmented system}
+\nomenclature[A]{\(\dot{S}\)}{Time derivative of the sensitivity equations}
+\nomenclature[A]{\(\bar{S}\)}{Sensitivity matrix}
+\nomenclature[A]{\(\bar{J}_x\)}{Jacobian matrix with respect to the state variables}
+\nomenclature[A]{\(\bar{J}_\Theta\)}{Jacobian matrix with respect to the parameters}
+%\nomenclature[A]{\(\mathcal{L}\)}{Log-likelihood function}
+\nomenclature[A]{\(l\)}{Characteristic dimension of particles \nomunit{m}}
+\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{m$^2$/s}}
+\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{m$^2$/s}}
+\nomenclature[A]{\(r\)}{Particle radius \nomunit{m}}
+\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient \nomunit{-}}
+\nomenclature[A]{\(k_m\)}{Mass partition coefficient \nomunit{-}}
+\nomenclature[A]{\(y\)}{Extraction yield \nomunit{g}}
+\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
+\nomenclature[A]{\(x\)}{State vector}
+\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
+\nomenclature[A]{\(p\)}{Probability distribution model \nomunit{-}}
+\nomenclature[A]{\(R_e\)}{Reynolds number \nomunit{-}}
+
+\nomenclature[B]{\(\rho_f\)}{Fluid density \nomunit{kg/m$^3$}}
+\nomenclature[B]{\(\Phi\)}{Bed porosity \nomunit{-}}
+\nomenclature[B]{\(\rho_s\)}{Bulk density of the solid \nomunit{kg/m$^3$}}
+\nomenclature[B]{\(\mu\)}{Sphericity coefficient \nomunit{-}}
+\nomenclature[B]{\(\gamma\)}{Decay function \nomunit{-}}
+\nomenclature[B]{\(\Upsilon\)}{Decay coefficient \nomunit{-}}
+\nomenclature[B]{\(\Theta\)}{Parameter space}
+\nomenclature[B]{\(\theta\)}{Vector of unknown parameters}
+\nomenclature[B]{\(\epsilon\)}{Unobservable error \nomunit{g}}
+\nomenclature[B]{\(\sigma\)}{Standard deviation \nomunit{g}}
+
+\nomenclature[C]{BIC}{Broke-and-Intact Cell model}
+%\nomenclature[C]{MLE}{Maximum Likelihood Estimation}
+\nomenclature[C]{SFE}{Supercritical Fluid Extraction}
+\nomenclature[C]{HBD}{Hot Ball Diffusion}
+\nomenclature[C]{SC}{Shrinking Core}
+
+\printnomenclature
+
 \end{document}

### 2024-10-11 Sections/Literature_Review.tex
11.10

@@
 
-	This study aims to analyze the influence of changes in operating conditions on the process model described in {\color{red}article 1}.
+	This study aims to analyze the influence of changes in operating conditions on the process model described by \citet{Sliczniuk2024}.
 Sensitivity analysis is applied to examine the impact of model parameters or controls on the model output.
@@
 The second part investigates the effects of varying the extractor volume (from 1 to 600 L) on the project's overall profitability.
-Their findings indicate that the most influential factors on net present value include the price of the extract, interest rate, dynamic time, and project lifetime.
+{\color{blue}The authors found that the raw material price, discount rate and residence time had the biggest impact on NPV}.
+	%Their findings indicate that the most influential factors on net present value include the price of the extract, interest rate, dynamic time, and project lifetime.
 

### 2024-10-11 Sections/Model.tex
11.10

@@
 
-	As discussed by \citet{Anderson2023}, all flows are compressible, but some of them can be treated as incompressible when the Mach number is smaller than 0.3.
+	As discussed by \citet{Anderson2023}, all flows are compressible, but some of them can be treated as {\color{blue}incompressible since the velocities are low}.
 This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
 The assumption allows for removing acoustic waves and large perturbations in density and/or temperature.
-In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant along the $z-$ direction.
 
@@
 
-			The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure.
+			%The main advantage of this formulation is the presence of term $\partial P / \partial t $, which directly affects the system through the change of thermodynamic pressure.
 
@@
 			}
+
+			where $\alpha$ is defined as $\left( 1+\kappa \left( 1 - \sqrt{T_r} \right) \right)^2$, $T_r$ is the reduced temperature, $P_r$ is the reduced pressure, $Z$ is the compressibility factor, $\kappa$ is a quadratic function of the acentric factor and $B$ is calculated as $0.07780\frac{P_r}{T_r}$.
 
@@
 
-			As explained in Chapters \ref{CH:Governing_equations_chapter}, at Low-Mach number conditions, the thermodynamic pressure is nearly constant in space due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, which describes the pressure change in the whole system.
+			As explained in Chapters \ref{CH:Governing_equations_chapter}, {\color{blue}this low velocity region, pressure is}, nearly constant due to the small pressure wave propagation that occurs at the speed of sound.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, {\color{blue}describing} the pressure change in the whole system.
 The pressure $P$ in the system is considered a state variable, while the pressure in the new time-step $P_{in}$ is considered a control variable.

### 2024-10-11 Sections/Saturation.tex
11.10

@@
 
-	The empirical correlations for $D_i$ and $\Upsilon$ were derived by {\color{red}article 1} and validated for temperatures between $30 - 40^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
+	The empirical correlations for $D_i$ and $\Upsilon$ were derived by \citet{Sliczniuk2024} and validated for temperatures between $30 - 40~^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
 Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables.

### 2024-10-11 Sections/Sensitivity_Pressure.tex
11.10

@@
 When the flow velocity is relatively low, pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
-The Low Mach number assumption allows for the instant propagation of thermodynamic pressure throughout the system, enabling a single pressure value to be considered for the entire system.
+{\color{blue}Low velocity results in the instant propagation} of thermodynamic pressure throughout the system, enabling a single pressure value to be considered for the entire system.
 In response to a pressure change, the energy equation experiences a simultaneous deviation across the entire spatial domain.
-This pressure change impacts the fluid's temperature within the computational domain, while boundary values are constrained by conditions specified at the domain's extremes.
+This pressure change impacts the fluid temperature within the computational domain, while boundary values are constrained by conditions specified at the domain's extremes.
 Dirichlet boundary conditions impose a fixed temperature value at the inlet, creating a thermal gradient that propagates through the system.
@@
 	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of solute concentration in the solid phase to pressure changes.
-As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, indicating that increased pressure reduces the fluid's velocity.
+As discussed in Chapter \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, indicating that increased pressure reduces the fluid velocity.
 This results in an extended residence time, allowing for longer interaction between the solute and solvent.	Initially, the extraction process operates in the kinetic-controlled regime, where the concentration gradient is high, and solute solubility is the limiting factor.
-As noted in [article 1], the system is considered far from saturation, which explains the low initial system response.
+As noted by \citet{Sliczniuk2024}, the system is considered far from saturation, which explains the low initial system response.
 This low initial response was also observed in the sensitivity analysis by \citet{Fiori_2007}.
 The system's response becomes more pronounced as the concentration gradient decreases and the extraction shifts from the kinetic-controlled to the diffusion-controlled regime.
-The negative sensitivity indicates a faster solute loss from the solid phase, corresponding to enhanced mass transfer.
+{\color{blue}In Figure \ref{fig:Sensitivty_P_CS}, all $\frac{dc_s}{dP}$ values are negative, which indicates a faster mass transfer} from the solid phase, corresponding to enhanced mass transfer.
 Over time, as the amount of solute decreases, it becomes a limiting factor, reducing the effect of pressure changes on the system.
@@
 Due to advection, the sensitivities move through the system similarly to the solute in the fluid phase.	Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period.
-As the process continues, the sensitivities increase, indicating faster solute loss from the solid phase.
-The positive sensitivities show that more solute is being transported from the solid particles to the fluid.
-When the solute in the solid phase becomes a limiting factor, the extraction rate slows, and sensitivities decline to negative values, eventually approaching zero asymptotically.
+As the process continues, the sensitivities increase, indicating faster mass transfer from the solid phase.
+The corresponding improvement in the mass transfer from the solid particles to the fluid is represented by the positive values in Figure \ref{fig:Sensitivty_P_CF}.
+When the solute in the solid phase becomes a limiting factor, the extraction rate slows, and sensitivities eventually approaching zero asymptotically.
 
@@
 	As presented in Figure \ref{fig:Sensitivty_P_y}, higher sensitivities are observed for the low-pressure system.
-At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction as shown by data given in {\color{red}article 1}.
+At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction as shown by data given by \citet{Sliczniuk2024}.
 Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield.

### 2024-10-11 Sections/introduction_imp.tex
11.10

@@
 The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
-Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T^{in}$) are adjustable and measurable, while the outlet temperature ($T^{out}$) and the amount of product at the outlet can only be monitored.
+Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
 Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.

### 2024-10-30 Article_Sensitivity_Analsysis-Chamomile.tex
30.10

@@
 % ===================================================
-\title[mode=title]{Sensitivity Analysis}                      
+\title[mode=title]{Local sensitivity analysis of a supercritical extraction model}                      
 \shorttitle{Sensitivity Analysis}
@@
 
-\section{Results}
 \subfile{Sections/Results_Sensitivity}
@@
 
-{\color{blue}Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of increasing pressure.
-Under the selected operating conditions ($35~^\circ C$ and $5 \times 10^{-5}$ kg/s), it was observed for all the cases that the pressure increment enhances mass transfer, leading to a more faster mass transfer of solute from the particles.
+{\color{blue}Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of pressure.
+Under the selected operating conditions, it was observed for all the cases that the pressure increment enhances mass transfer, leading to a faster mass transfer of solute from the particles.
 Consequently, the negative sensitivities can be observed in the diagram for the solid phase.
@@
 Sensitivity analysis results can be used to design future experiments by indicating which parameters should be varied and monitored.
-Moreover, the parameters which are characterized by low sensitivity can be subject of model reduction.
+Moreover, the parameters which are characterized by low sensitivity can be subject of model refinement.
 
 \section*{Acknowledgement} 
-This work was supported by NovelBaltic, CEForestry (IBC), BIO4P (BF)
+This work was supported by: NovelBaltic, CEForestry (IBC), BIO4P (BF)
 
@@
 %\clearpage
-\newpage
+%\newpage
 %\bibliographystyle{model1-num-names}
@@
 \nomenclature[A]{\(y\)}{Extraction yield \nomunit{g}}
-\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
+%\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
 \nomenclature[A]{\(x\)}{State vector}

### 2024-10-30 Sections/Model.tex
30.10

@@
 
-			As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions.
+			{\color{blue}As the solvent flows through the fixed bed, CO$_2$ molecules diffuse into the pores, adsorb on the inner surface and form a film due to solvent-solid matrix interactions}.
 The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore and the film into the bulk.
@@
 The concentration of the solutes in the fluid phase in the centre of the pore is denoted as $c_p$.
-As the solute diffuses through the pore, its concentration changes and reaches $c_{pf}$ at the pore opening.
+As the solute diffuses through the pore, its concentration changes, reaching $c_{pf}$ at the opening.
 Then, the solute diffuses through the film around the particle and reaches bulk concentration $c_f$.
@@
 In contrast, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
-Concentration $c_p^*$ is determined by the equilibrium relationship with $c_f$ and the extraction rate given by Equation \ref{Model_kinetic_basic}:
+As given by Equation \ref{Model_kinetic_basic}, the concentration $c_p^*$ is determined by the equilibrium relationship with $c_f$:
 
@@
 			The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-According to \citet{Spiro2007}, $k_p$ can be expressed through the mass partition coefficient $k_m$:
+\citet{Spiro2007} proposed to define the mass partition coefficient $k_m$ as
 

### 2024-10-30 Sections/Saturation.tex
30.10

@@
 
-	Alternatively, the decay function $\gamma$ can be interpreted by referring to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius changes as the amount of solute in the solid phase decreases.
+	%Alternatively, the decay function $\gamma$ can be interpreted by referring to the Shrinking Core model presented by \citet{Goto1996}, where the particle radius changes as the amount of solute in the solid phase decreases.
 As the particle size decreases due to dissolution, the diffusion path increases, which makes the diffusion slower and reduces the value of the diffusion coefficient.
 This analogy can be applied to Equation \ref{EQ: C_sat_function} to justify the application of a varying diffusion coefficient.
+
+	{\color{blue}An alternative interpretation of the decay function $\gamma$ involves considering the porous structure of the solid particles, where the pores are initially saturated with the solute.
+During extraction, the solute within these pores gradually dissolves into the surrounding fluid.
+Initially, the solute molecules near the pore openings dissolve and diffuse rapidly due to the short diffusion paths.
+As the extraction progresses, the dissolution front moves deeper into the pore structure, and solute from the inner regions of the pores begins to dissolve.
+The diffusion of solute molecules from the interior of the pores to the external fluid becomes progressively slower because the effective diffusion path length increases.
+This lengthening of the diffusion path enhances the mass transfer resistance, reducing the overall diffusion rate.
+
+	In an extreme case, this model could be compared with the Shrinking Core Model presented by \citet{Goto1996}, where the particle radius decreases as the solute content in the solid phase diminishes.
+In the SC model, the reduction in particle size leads to significant changes in both the diffusion path length and the surface area available for mass transfer.
+The diminishing particle size increases the diffusion path within the remaining solid core and decreases the external surface area, both of which contribute to a slower extraction rate.
+By comparing this to the varying diffusion coefficient in our model, some conceptual similarities can be noticed}.
 

### 2024-10-30 Sections/Sensitivity_Analysis.tex
18.09
30.10

@@
 
-	The augmented system containing the original set of equations $G(x;\Theta)$ and sensitivity equations can be formulated as ${\textbf{G}}\left(x;\Theta\right)$.
+	The augmented system containing the original set of equations $G(x;\Theta)$ and sensitivity equations is called ${\textbf{G}}\left(x;\Theta\right)$.
 The size of ${\textbf{G}}\left(x;\Theta\right)$ is equal to $N_s = N_x(N_\Theta + 1)$.
@@
 				\quad 0 \quad~~
-			\end{bmatrix}^\top
+			\end{bmatrix}^\top \nonumber
 	\end{align} }
-
-	The sensitivity analysis of the output function can be performed with respect to parameters $\Theta$.
-The output function $g(x)$ returns ${y}$.
-By taking a total derivative of ${y}$ with respect to $\Theta$, the new sensitivity equation can be found.
-
-	{\footnotesize
-		\begin{equation}
-			\cfrac{d {y}}{d\Theta} = \cfrac{d g(x)}{d\Theta} = \cfrac{\partial g(x)}{\partial x} \cfrac{\partial x}{\partial \Theta} + \cfrac{\partial g(x)}{\partial \Theta}
-	   \end{equation} }
-
 \end{document}

### 2024-10-30 Sections/Sensitivity_Pressure.tex
30.10

@@
 
-	As discussed in Chapter \ref{CH:Governing_equations_chapter}, a small pressure wave propagates at the speed of sound relative to the flow.
-When the flow velocity is relatively low, pressure changes are hydrodynamic (resulting from velocity motion) rather than thermodynamic.
-{\color{blue}Low velocity results in the instant propagation} of thermodynamic pressure throughout the system, enabling a single pressure value to be considered for the entire system.
+	{\color{blue} As discussed in Chapter \ref{CH:Governing_equations_chapter}, at the low velocity, the fluid can be treated as incompressible, which results in the instant propagation} of pressure throughout the system, enabling a single pressure value to be considered for the entire system.
 In response to a pressure change, the energy equation experiences a simultaneous deviation across the entire spatial domain.
@@
 Dirichlet boundary conditions impose a fixed temperature value at the inlet, creating a thermal gradient that propagates through the system.
-On the other hand, Neumann boundary conditions specify the heat flux at the boundaries.
-In this study, zero Neumann boundary conditions were applied to ensure that the temperatures at the inlet, outlet, and within the extractor vary uniformly in response to the pressure change.
+Alternatively, the Neumann boundary conditions specify a heat flux at the extremes.
+The zero Neumann boundary conditions are applied to ensure an uniform response of temperatures at the inlet, outlet, and within the extractor to the pressure change.
 
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
 		\caption{The effect of $P_{in}$ change on $C_s$}
@@
 Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of fluid phase sensitivities is more apparent.
-Due to advection, the sensitivities move through the system similarly to the solute in the fluid phase.	Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period.
+{\color{blue}Due to advection, the sensitivities related to the fluid phase moves across the system in the direction of flow}.
+Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period.
 As the process continues, the sensitivities increase, indicating faster mass transfer from the solid phase.
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P_1.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
 		\caption{The effect of $P_{in}$ change on $C_f$}

### 2024-10-30 Sections/introduction_imp.tex
30.10

@@
 
-	The supercritical carbon dioxide is commonly used for impregnation as described by \citet{Weidner2018}, \citet{Machado2022} or \citet{Fathi2022}.
+	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993} or \citet{Sovova1994}.
+Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
+Distillation, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
+This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction.
+Supercritical CO$_2$ is appealing due to its distinctive properties: it is inflammable, non-toxic and non-corrosive.
+Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
+
+	{\color{blue}The applications of supercritical carbon dioxide are not limited only to an extraction process but can also be used for impregnation as described by \citet{Weidner2018}, \citet{Machado2022} or \citet{Fathi2022}}.
 Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
@@
 Moreover, the CO$_2$ is completely removed from the final product by simple depressurization.
-
-	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993} or \citet{Sovova1994}.
-Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
-Distillation, involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
-This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction.
-Supercritical CO$_2$ is appealing due to its distinctive properties: it is inflammable, non-toxic and non-corrosive.
-Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
 

### 2024-10-30 SFE_Sensitivity_Analysis_Chamomile/main_Sensitivity_Analysis_Chamomile.m

@@ -24,8 +24,8 @@ bed                     = 0.92;                                             % Pe
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 60000;
-timeStep                = 10;                                                % Minutes
+ExtractionTime          = 600;
+timeStep                = 1;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
 
@@ -113,7 +113,7 @@ C0fluid                 = m_fluid * 1e-3 ./ V_fluid';
 
 RES                     = [];
 
-for PP = [100,125,150,175,200]
+for PP = 150
     %% Set operating conditions
     T0homog                 = 35+273;                    % K
     feedPress               = PP;                        % bar
@@ -155,7 +155,7 @@ for PP = [100,125,150,175,200]
     
     %% Set sensitivity analysis
     
-    name_v = {'T_{in}', 'P_{in}', 'F'                                   };
+    name_v = {'T_{in}', 'P'     , 'F'                                   };
     name_s = {'c_f'   , 'c_s'   , '(h\times\rho)' , 'P_{t-1}'     , 'y' };
     name_p = {'CF'    , 'CS'    , 'H'             , 'P_{in}'      , 'Y' };
     
@@ -179,11 +179,11 @@ for PP = [100,125,150,175,200]
             RES = [RES; Res(end,:)];
     
             %% Sensitivities plot 
-            %{
-            for ind=0:2
+            %{\
+            for ind=0%0:2
                 figure()
                 %subplot(2,1,1)
-                imagesc(Time, L_nstages, Res(ind*nstages+1:(ind+1)*nstages,:)); cb = colorbar; colormap turbo;
+                imagesc(Time, L_nstages, Res(ind*nstages+1:(ind+1)*nstages,:) ); cb = colorbar; colormap turbo;
                 %subplot(2,1,2)
                 %contourf(Time, L_nstages, flip(Res(ind*nstages+1:(ind+1)*nstages,:)),'EdgeColor','none','Levels',200); cb = colorbar; colormap turbo;
     
@@ -194,8 +194,11 @@ for PP = [100,125,150,175,200]
                 hold off
     
                 title(cb, ['$\frac{d',name_s{ind+1},'}{d',name_v{ii},'}$'], 'Interpreter', 'latex'); cb.TickLabelInterpreter = 'latex'; 
+                set(cb,'TickLabelInterpreter','latex'); cb.Ruler.Exponent = -3;
[…]

### 2025-01-11 Article_Sensitivity_Analsysis-Chamomile.tex
11.01

@@
 	% ===================================================
-\title[mode=title]{Local sensitivity analysis of a supercritical extraction model}                      
+	\title[mode=title]{Local Sensitivity Analysis of a Supercritical Extraction Model}                      
 	\shorttitle{Sensitivity Analysis}
@@
 		This study investigates the process of chamomile oil extraction from chamomile flowers.
-A parameter-distributed model, consisting of a set of partial differential equations, is used to describe the governing mass transfer phenomena between solid and fluid phases under supercritical conditions using carbon dioxide as the solvent.
-The concept of quasi-one-dimensional flow is applied to reduce the number of spatial dimensions.
-The {\color{blue}flow of carbon dioxide} is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
-The physical properties of the solvent are estimated using the Peng-Robinson equation of state.
-Laboratory experiments were conducted under various, but constant operating conditions.
-$30 - 40~^\circ C$, $100 - 200$ bar, and $3.33-6.67 \cdot 10^{-5}$ kg/s.
-{\color{blue}The local sensitivity analysis method was applied to evaluate the model parameters' robustness by investigating the impact of infinitesimally small changes in model parameters and controls on model outputs}.
+A parameter-distributed model, consisting of a set of partial differential equations, was used to describe the governing mass transfer phenomena between solid and fluid phases under supercritical conditions using carbon dioxide as the solvent.
+The concept of quasi-one-dimensional flow was applied to reduce the number of spatial dimensions.
+The flow of carbon dioxide is assumed to be uniform across any cross-section, although the area available for the fluid phase can vary along the extractor.
+The physical properties of the solvent were estimated using the Peng-Robinson equation of state.
+Laboratory experiments were conducted under various, but constant operating conditions of $30 - 40~^\circ C$, $100 - 200$ bar and $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The local sensitivity analysis method was applied to evaluate the robustness of the model parameters by investigating the impact of infinitesimally small changes in the model parameters and controls on the model outputs.
 This study focuses on analysing the effect of pressure on the model state space and extraction yield.
@@
 
-\subfile{Sections/introduction_imp}
+	%\subfile{Sections/introduction_imp}
+	Supercritical CO$_2$ is defined as carbon dioxide that is pressurized and heated above its critical point (31.1 $^\circ C$, 74 bar).
+Depending on the operating conditions, the fluid properties such as viscosity and density can vary, which leads to multiple industrial applications of CO$_2$.
 
-\subfile{Sections/Literature_Review}
+	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993} or \citet{Sovova1994}.
+Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
+Distillation involves high temperatures that can lead to the thermal degradation of heat-sensitive compounds.
+This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction.
+Supercritical CO$_2$ is appealing due to its distinctive properties: it is inflammable, non-toxic and non-corrosive.
+Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
+
+	The applications of supercritical carbon dioxide are not limited only to an extraction process but can also be used for impregnation, as described by \citet{Weidner2018}, \citet{Machado2022} or \citet{Fathi2022}.
+Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
+The main advantage of using supercritical CO$_2$ is that, after depressurization, it desorbs from the surface and evaporates, leaving a solvent-free product.
+On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.
+
+	Another application of supercritical CO$_2$ is nanoparticle formation, as investigated by \citet{Padrela2018}, \citet{Franco2021}, \citet{SaadatiArdestani2020} or \citet{Sodeifian2022}.
+Supercritical carbon-dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating the operating conditions.
+Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nanosized particles or crystals, such as reduced use of toxic solvents.
+Moreover, the CO$_2$ is completely removed from the final product by simple depressurization.
+
+	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process.
+Chamomile is a medicinal herb widely cultivated in southern and eastern Europe — in countries such as Germany, Hungary, France and Russia.
+It can also be found outside Europe, for instance in Brazil, as discussed by \citet{Singh2011}.
+This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets.
+Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy.
+Extracts of chamomile are widely used to calm nerves and mitigate anxiety, hysteria, nightmares, insomnia and other sleep-related conditions, according to \citet{Srivastava2009}.
+\citet{Orav2010} reported that oil yields from dried chamomile samples ranged from 0.7 to 6.7 mL/kg.
+The highest yields of essential oil, between 6.1 and 6.7 mL/kg, were derived from chamomile sourced from Latvia and Ukraine.
+In comparison, chamomile from Armenia exhibited a lower oil content of 0.7 mL/kg.
+
+	The literature offers various mathematical models to describe the extraction of valuable compounds from biomass.
+Selecting a process model is case-dependent and requires analysis of each model's specific assumptions about mass transfer and thermodynamic equilibrium.
+
+	\citet{Goto1996} presented the shrinking core (SC) model, which describes a process of irreversible desorption that is followed by diffusion through the pores of a porous solid.
+When the mass transfer rate of the solute in the non-extracted inner region is significantly slower than in the outer region, where most of the solute has already been extracted or when the solute concentration exceeds its solubility in the solvent, a distinct boundary may form between the inner and outer regions.
+As extraction progresses, the core of the inner region shrinks.
+The model envisions supercritical CO$_2$ extraction as a sharp, inward-moving front, with a completely non-extracted core ahead of the front and a fully extracted shell behind it.
+
+	\citet{Sovova1994} proposed the broken-and-intact cell (BIC) model, which assumes that a portion of the solute, initially stored within plant structures and protected by cell walls, is released during the mechanical breakdown of the material.
+The solute located in the region of broken cells near the particle surface is directly exposed to the solvent, while the core of the particle contains intact cells with undamaged walls.
+This model describes three extraction phases: a fast extraction phase for accessible oil, a transient phase, and a slow phase controlled by diffusion.
+The model has been successfully applied to the extraction of grape oil (\citet{Sovova1994b}) and caraway oil (\citet{Sovova1994a}).
+
+	The supercritical fluid extraction (SFE) process can be treated similarly to heat transfer, considering solid particles as hot balls cooling down in a uniform environment.
+\citet{Bartle1990} introduced the hot ball diffusion (HBD) model, where spherical particles with a uniformly distributed solute diffuse similarly to heat diffusion.
+Unlike the BIC model, where the solute is readily available on the particle surface, the HBD model is suited for systems with small quantities of extractable materials and is not limited by solubility.
+The model is particularly relevant when internal diffusion controls mass transfer, allowing results from single particles to be extended to the entire bed under uniform conditions.
+\citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes for natural materials.
+
+	\citet{Reverchon1996} proposed a model for extraction of essential oils, which are mainly located inside the vegetable cells in organules called vacuoles.
+Only a small fraction of essential oil might be near the particle surface due to the breaking up of cells during grinding or in epidermal hairs located on the leaf surface.
+The fraction of oil freely available on the particle surface should not be significant in the case of SFE from leaves.
+Consequently, SFE of essential oil from leaves should be mainly controlled by  internal mass-transfer resistance.
+Therefore, the external mass-transfer coefficient was neglected in the development of the model of \citet{Reverchon1996}.
+The mass balances were developed with the additional hypotheses that axial dispersion can be neglected and that the solvent density and flow rate are constant along the bed.
+
+	This work builds upon the linear kinetic model suggested by \citet{Reverchon1996}, deriving fundamental governing equations to develop a comprehensive model for the chamomile oil extraction process.
+This model aims at control-oriented simplicity, assuming semi-continuous operation within a cylindrical vessel.
+The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
+Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
+Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[width=\columnwidth]{Figures/PFD.drawio.pdf}
+		\caption{Process flow diagram.}
+		\label{fig: SFE_drawing}
+	\end{figure}
+
+	%\subfile{Sections/Literature_Review}
+	This study aims to analyse the influence of changes in operating conditions on the process model described by \citet{Sliczniuk2024}.
+For that, a sensitivity analysis is applied to examine the impact of model parameters or controls on the model output.
+The results of this sensitivity analysis can be used to identify sources of uncertainty, simplify the model or detect errors by revealing unexpected relationships between inputs and outputs.
+Various sensitivity analysis methods are available, including:
+
+	\begin{itemize}
+		\item One-at-a-time method
+		\item Derivative-based local methods
+		\item Variance-based methods
+	\end{itemize}
+
+	Different supercritical extraction models have been analysed using various sensitivity analysis techniques in the literature.
+For instance, \citet{Fiori_2007} performed sensitivity calculations by varying parameters within their confidence intervals and observing the changes in model results.
+Their analysis revealed that the particle diameter and internal mass transfer coefficient significantly influence extraction during the diffusion-control regime.
+
+	\citet{Santos2000} considered the model of \citet{Sovova1994} for semi-continuous isothermal and isobaric extraction processes using carbon dioxide as a solvent.
+They conducted a parametric sensitivity analysis using a two-level factorial design, disturbing model parameters by 10\% and analysing their main effects.
+They proposed strategies for high-performance operation based on sensitivities related to superficial velocity, particle diameter, initial solute concentration in the solid phase and solute concentration in the fluid phase at the extractor inlet.
+
+	\citet{Hatami2024} performed a one-factor-at-a-time sensitivity analysis to assess the response of net present value (NPV) to variations in technical and economic variables.
+Their study consisted of two parts.
+The first part examined how net present value is influenced by changes in individual technical and economic parameters, keeping the extractor volume constant at 300 L.
+The second part investigated the effects of varying the extractor volume (from 1 to 600 L) on the project's overall profitability.
+The authors found that the raw material price, discount rate and residence time had the biggest impact on NPV (\citet{Hatami2024}).
 
@@
 
-\subfile{Sections/Model}
+	%\subfile{Sections/Model}
+	\section{Materials and methods} \label{CH: Materials and methods}
+
+	\subsection{Governing equations} \label{CH:Governing_equations_chapter}
+	The governing equations for a quasi-one-dimensional flow were derived following the work of \citet{Anderson1995}.
+A quasi-one-dimensional flow refers to a fluid flow scenario assuming that the flow properties are uniformly distributed across any cross-section.
+This simplification is typically applied when the flow channel's cross-sectional area changes, such as through irregular shapes or partial filling of an extractor.
+According to this assumption, velocity and other flow properties change solely in the flow direction.
+
+	As discussed by \citet{Anderson2023}, all flows are compressible, but some of them can be treated as incompressible since the velocities are low.
+This assumption leads to the incompressible condition: $\nabla \cdot u =0$, which is valid for constant density (strict incompressible) or varying density flow.
+The assumption allows for removing acoustic waves and large perturbations in density and/or temperature.
+In the 1-D case, the incompressibility condition becomes $\frac{du}{dz} = 0$, so the fluid velocity is constant along the $z-$ direction.
+
+	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}:
+
+	{\footnotesize
+		\begin{align}
+			\label{EQ: CompressibleEuler_1}
+			\cfrac{\partial \left( \rho_f A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v \right)}{\partial z} &= 0, \\
+			\cfrac{\partial \left( \rho_f v A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v^2 \right)}{\partial z} &= -A_f \cfrac{\partial P}{\partial z} \label{EQ: CompressibleEuler_2}, \\
+			\cfrac{\partial \left( \rho_f e A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e\right)}{\partial z} &= -P\cfrac{\left( A_f v \right)}{\partial z} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right),
+			\label{EQ: CompressibleEuler_3}
+		\end{align}  
+	}
+
+	where $\rho_f$ is the density of the fluid, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spatial direction.
+
+	\subsection{Extraction model} \label{CH: Extraction_model}
+	\subsubsection{Continuity equation} \label{CH: Continuity}
+
+	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is redefined by incorporating the function $A_f = A\phi$.
+This modification distinguishes constant and varying terms, where the varying term accounts for changes in the cross-sectional area available for the fluid.
+Equation \ref{EQ: Continuity_differential} shows the modified continuity equation:
+
+	{\footnotesize
+		\begin{equation} \label{EQ: Continuity_differential}
+			\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial z} = 0,
+		\end{equation}
+	}
+	where $A$ is the total cross-section of the extractor and $\phi$ describes porosity along the extractor.
+
+	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as
+
+	{\footnotesize
+		\begin{equation}
+			\int \frac{\partial (\rho_f v A \phi )}{\partial z} dz = F \rightarrow F=\rho_f v A\phi
+		\end{equation}
+	}
+
+	To simplify the system dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$ and $\rho_f$:
+
+	{\footnotesize
+		\begin{equation} \label{EQ:Velocity_1}
+			v = \cfrac{F}{\rho_f A\phi} 
+		\end{equation}
+	}
+
+	Similarly, superficial velocity may be introduced:
+
+	{\footnotesize
+		\begin{equation} \label{EQ:Velocity_2}
+			u = v \phi = \cfrac{F}{\rho_f A }
+		\end{equation}
+	}
+
+	The fluid density $\rho_f$ can be obtained from the Peng-Robinson equation of state if the temperature and thermodynamic pressure are known along $z$.
+Variation in fluid density may occur due to pressure or inlet temperature changes.
+In a non-isothermal case, in Equations \ref{EQ:Velocity_1} and \ref{EQ:Velocity_2}, $\rho_f$ is considered the average fluid density along the extraction column.
+
+	\subsubsection{Mass balance for the fluid phase} \label{CH: Mass_balance_fluid}
+
+	Equation \ref{Model_fluid} describes the movement of the solute in the system, which is constrained to the axial direction due to the quasi-one-dimensional assumption.
+Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to those of the solvent itself.
+It is also assumed that the thermodynamic pressure remains constant throughout the device.
+The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall.
+This leads to a uniform velocity profile across any cross-section perpendicular to the axial direction.
+Thus, the mass balance equation includes convection, diffusion and kinetic terms representing the fluid phase behaviour:
+
+	{\footnotesize
+		\begin{equation}
+			\label{Model_fluid}
+			\frac{\partial c_f}{\partial t}
+			+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial z}
+			= \frac{1-\phi}{\phi} r_e
+			+ \frac{1}{\phi} \frac{\partial}{\partial z} \left( D^M_e \frac{\partial c_f}{\partial z} \right),
+		\end{equation}
+	}
+
+	where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the axial diffusion coefficient.
+
+	\subsubsection{Mass balance for the solid phase} \label{Mass_balance_solid}
+
+	As given by Equation \ref{Model_solid}, the solid phase is considered stationary, without convection and diffusion terms in the mass balance equation.
+Therefore, the only significant term in this equation is the kinetic term of Equation \ref{Model_kinetic_basic}, which connects the solid and fluid phases.
+For simplicity, the extract is represented by a single pseudo-component:
+
+	{\footnotesize
+		\begin{equation} 
+			\label{Model_solid}
+			\cfrac{\partial c_s}{\partial t} = \underbrace{ r_e }_{\text{Kinetics}}
+	\end{equation} }
+
+	\subsubsection{Kinetic term} \label{CH: Kinetic}
+
+	As the solvent flows through the fixed bed, CO$_2$ molecules diffuse into the pores, adsorb on the inner surface and form a film due to solvent-solid matrix interactions.
+The dissolved solute diffuses into the bulk from the particle's core through the solid-fluid interface, the pore and the film.
+Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted by $c_s$, and the equilibrium concentrations at the solid-fluid interface are denoted by $c_s^*$ and $c_p^*$ for the solid and fluid phases, respectively.
+The concentration of the solutes in the fluid phase in the centre of the pore is denoted by $c_p$.
+As the solute diffuses through the pore, its concentration changes, reaching $c_{pf}$ at the opening.
+Then, the solute diffuses through the film around the particle and reaches bulk concentration $c_f$.
+The two-film theory describes the solid-fluid interface inside the pore.
+The overall mass transfer coefficient can be determined from the relationship between the solute concentration in one phase and its equilibrium concentration.
+
+	\begin{figure}[h!]
+		\centering
+		\includegraphics[trim = 45cm 0cm 60cm 20cm,clip,width=0.85\columnwidth]{Figures/SFE_PFD.drawio.png}	
+		\caption{Mass transfer mechanism.}
+		\label{fig: SFE_Mechanism}
+	\end{figure}
+
+	\citet{Bulley1984} suggest a process where the driving force for extraction is given by the difference between the concentration of the solute in the bulk, $c_f$, and in the centre of the pore, $c_p^*$.
+The concentration $c_p^*$ is in equilibrium with $c_s$ according to the equilibrium relationship.
+The rate of extraction is thus $r_e\left(c_f - c^*_p(c_s)\right)$.
+In contrast, \citet{Reverchon1996} proposes a driving force given by the difference between $c_s$ and $c_p^*$.
+As given in Equation \ref{Model_kinetic_basic}, the concentration $c_p^*$ is determined by the equilibrium relationship with $c_f$:
+
+	{\footnotesize
+		\begin{equation} \label{Model_kinetic_basic}
+			r_e = \cfrac{D_i}{\mu l^2 }\left(c_s - c_p^* \right),
+	\end{equation} }
+
+	where $\mu$ is sphericity, $l$ a characteristic dimension of particles that can be defined as $l = r/3$, $r$ is the mean particle radius, $\rho_s$ is the solid density, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is the concentration at the solid-fluid interface (which, according to the internal resistance model, is supposed to be at equilibrium with the fluid phase).
+
+	According to \citet{Bulley1984}, a linear equilibrium relationship (Equation \ref{Linear_equilibirum}) can be used to find the equilibrium concentration of the solute in the fluid phase $c_f^*$ based on the concentration of the solute in the solid phase $c_s$:
+
+	{\footnotesize
+		\begin{align} \label{Linear_equilibirum}
+			c_f^* &= k_p c_s
+	\end{align} }
+
+	The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
+\citet{Spiro2007} propose defining the mass partition coefficient $k_m$ as
+
+	{\footnotesize
+		\begin{align}
+			k_m = \cfrac{k_p \rho_s}{\rho_f}
+	\end{align} }
+
+	According to \citet{Reverchon1996}, the kinetic term becomes
+
+	{\footnotesize
+		\begin{equation}
+			\label{Model_kinetic_no_sat}
+			r_e = -\cfrac{D_i}{ \mu l^2 } \left(c_s - \cfrac{\rho_s c_f}{k_m \rho_f} \right)
+	\end{equation} }
+
+	\subsubsection{Uneven distribution of solute in the solid phase} \label{CH: Gamma_Function}
+
+	Following the idea of the broken-and-intact cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}:
+
+	{\footnotesize
+		\begin{equation}
+			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right), \label{EQ: C_sat_function}
+	\end{equation} }
+
+	where  ${\color{black}\Upsilon}$ describes the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term:
+
+	{\footnotesize
+		\begin{equation}
+			\label{Model_kinetic}
+			r_e = -\cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
+	\end{equation} }
+
+	The $\gamma$ function limits the solute's availability in the solid phase.
+Similarly to the BIC model, the solute is assumed to be contained in the cells, some of which are open because the cell walls were broken by grinding, with the rest remaining intact.
+The diffusion of the solute from a particle's core takes more time than the diffusion of the solute close to the outer surface.
+The same idea can be represented by the decaying internal diffusion coefficient, where the decreasing term is a function of the solute concentration in the solid.
+
+	An alternative interpretation of the decay function $\gamma$ involves considering the porous structure of the solid particles, where the pores are initially saturated with the solute.
+During extraction, the solute within these pores gradually dissolves into the surrounding fluid.
+Initially, the solute molecules near the pore openings dissolve and diffuse rapidly due to the short diffusion paths.
+As the extraction progresses, the dissolution front moves deeper into the pore structure, and solute from the inner regions of the pores begins to dissolve.
+The diffusion of solute molecules from the interior of the pores to the external fluid becomes progressively slower because the effective diffusion path length increases.
+This lengthening of the diffusion path enhances the mass transfer resistance, reducing the overall diffusion rate.
+
+	In an extreme case, this model could be compared with the shrinking core model presented by \citet{Goto1996}, where the particle radius decreases as the solute content in the solid phase diminishes.
+In the SC model, the reduction in particle size leads to significant changes in both the diffusion path length and the surface area available for mass transfer.
+The diminishing particle size increases the diffusion path within the remaining solid core and decreases the external surface area, both of which contribute to a slower extraction rate.
+When comparing this to the varying diffusion coefficient in our model, some conceptual similarities can be noticed.
+
+	\subsubsection{Empirical correlations}
+
+	The empirical correlations for $D_i$ and $\Upsilon$ were derived by \citet{Sliczniuk2024} and validated for temperatures of $30 - 40~^\circ C$, pressures of $100 - 200$ bar, and mass flow rates of $3.33-6.67 \cdot 10^{-5}$ kg/s.
+Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables.
+The region marked with the white dashed line represents the confidence region, where the model has been tested.
+Both correlations should be equal or greater than zero to avoid unphysical behaviour such as  reverse mass transfer.
+The multiple linear regression functions are combined with the rectifier function to ensure non-negativity.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Di.png}
+		\caption{Multiple linear regression $D_i^R = f(Re, F).$}
+		\label{fig:Correlation_Di}
+	\end{figure}
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Gamma.png}
+		\caption{Multiple linear regression $\Upsilon = f(Re, F).$}
+		\label{fig:Correlation_Gamma}
+	\end{figure}
+
+	\subsubsection{Heat balance} \label{CH: heat_balance}
+
+	The heat balance equation describes the evolution of the enthalpy in the system and is given by Equation \ref{EQ:Enthalpy_equation}:
+
+	{\footnotesize
+		\begin{equation} \label{EQ:Enthalpy_equation}
+			\cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f {\color{black}h} A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+		\end{equation}
+	}
+
+	If the value of enthalpy $h$ is known from the time evolution of the energy equation, and pressure $P$ is known from measurement, then temperature $T$ can be reconstructed based on the departure function.
+The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy or internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+The enthalpy departure function, as presented by \citet{Gmehling2019} for the Peng-Robinson equation of state,  is defined by Equation \ref{EQ:Enthalpy_PR}:
+
+	{\scriptsize
+		\begin{equation}
+			{\color{black}h}-{\color{black}h}^{id}={\color{black}R}T \left[{\color{black}T_r}({\color{black}Z}-1) -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T\right) } } \ln \left(\cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}}\right)\right],
+			\label{EQ:Enthalpy_PR}
+		\end{equation}				
+	}
+
+	where $\alpha$ is defined as $\left( 1+\kappa \left( 1 - \sqrt{T_r} \right) \right)^2$, $T_r$ is the reduced temperature, $P_r$ is the reduced pressure, $Z$ is the compressibility factor, $\kappa$ is a quadratic function of the acentric factor and $B$ is calculated as $0.07780\frac{P_r}{T_r}$.
+
+	Equation \ref{EQ:Enthalpy_PR} requires a reference state, which is assumed to be $T_{ref}=298.15$ K and $P_{ref}=1.01325$ bar.
+
+	A root finder can be used to find a temperature value which minimizes the difference between the value of enthalpy coming from the heat balance and the departure functions.
+The root-finding procedure has to be repeated at every time step to find a temperature profile along spatial direction $z$.
+
+	{\footnotesize
+		\begin{equation}
+			\min_T \left( \underbrace{h\left(t,x\right)}_{\text{Heat balance}} - \underbrace{h\left(T,P,\rho_f\left(T,P\right)\right)}_{\text{Departure function}} \right)^2
+			\label{EQ:Enthalpy_root}
+		\end{equation}
+	}
+
+	\subsubsection{Pressure term} \label{CH: Pressure}
+
+	As explained in Section \ref{CH:Governing_equations_chapter}, this low velocity region pressure is nearly constant due to the small pressure wave propagation that occurs at the speed of sound.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, {\color{blue}describing} the pressure change in the whole system.
+The pressure $P$ in the system is considered a state variable, while the pressure in the new time-step $P_{in}$ is considered a control variable.
+
+	{\footnotesize
+		\begin{equation}
+			\frac{\partial {\color{black}P}}{\partial t} \approx \frac{{\color{black}P_{in}} - {\color{black}P} }{\Delta t}
+	\end{equation}}
+
+	Such a simplified equation allows for instantaneous pressure change in the system but does not consider a gradual pressure build-up and the effects of pressure losses.
+In a real system, the dynamics of pressure change would depend on a pump and a back-pressure regulator.
+
+	\subsubsection{Extraction yield} \label{CH: Yield}
+
+	The process yield is calculated according to Equation \ref{Model_measurment_1}, as presented by \citet{Sovova1994a}.
+The measurement equation evaluates the solute's mass at the extraction unit outlet and sums it up.
+The integral form of the measurement (Equation \ref{Model_measurment_1}) can be transformed into the differential form (Equation \ref{Model_measurment_2}) and augmented with the process model.
+
+	{\footnotesize
+		\begin{align} 
+			\label{Model_measurment_1}
+			y &= \int_{t_0}^{t_f} \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} dt \\
+			\cfrac{dy}{dt} &= \qquad \cfrac{F}{\rho_f} c_f \biggr\rvert_{z=L} 
+			\label{Model_measurment_2}
+	\end{align}	}
+
+	\subsubsection{Initial and boundary conditions} 
+	It is assumed that the solvent is free of solute at the beginning of the process $c_{f0}=0$, that all the solid particles have the same initial solute content $c_{s0}$ and that the system is isothermal, hence the initial state is $h_0$.
+The fluid at the inlet is considered not to contain any solute.
+The initial and boundary conditions are defined as follows:
+
+	{\footnotesize
+		\begin{align*}
+			&c_f(t = 0, z) = 0  && c_s(t = 0, z) = c_{s0} && h(t = 0, z) = h_0 \\
+			&c_f(t,   z=0) = 0  && h(t, z=0) = h_{in}  && \frac{\partial c_f(t,z=L)}{\partial x} = 0 \\
+			&\frac{\partial h(t,z=L)}{\partial x} = 0   && c_s(t, z=\{0,L\}) = 0 && y(0) = 0 \quad P(0) = P_0 \\
+	\end{align*} }
+
+	\subsubsection{Discretization methods}
+
+	The method of lines is used to transform the process model equations into a set of ODEs denoted by $G(x;\Theta)$.
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme approximates the second-order derivative $z$ direction.
+The length of the fixed bed is divided into $N_z$, i.e.
+equally distributed points in the $z$ direction.
+The state-space model after discretization is denoted by $x$ and defined as follows:
+
+	{\footnotesize
+		\begin{align*} \label{discretization}
+			\dot{x} &= \cfrac{d x}{d t} = 
+			\begin{bmatrix}
+				\cfrac{d c_{f,1}}{d t} 	  \\
+				\vdots					  \\
+				\cfrac{d c_{f,N_z}}{d t} \\
+				\\ \hline \\
+				\cfrac{d c_{s,1}}{d t} 	  \\
+				\vdots					  \\
+				\cfrac{d c_{s,N_z}}{d t} \\
+				\\ \hline \\
+				\cfrac{d h_1}{d t} 	  \\
+				\vdots 					  \\
+				\cfrac{d h_{N_z}}{d t} \\
+				\\ \hline \\
+				\cfrac{d P}{d t} \\
+				\\ \hline \\
+				\cfrac{d y}{d t}
+			\end{bmatrix}
+			=
+			\underbrace{\begin{bmatrix}
+					G_1 \left( c_f,c_s,h; \Theta \right)\\ 
+					\vdots\\ 
+					G_{N_z} \left( c_f,c_s,h; \Theta \right)\\ 
+					\\ \hline \\ \\
+					G_{N_z+1} \left( c_f,c_s,h; \Theta \right)\\ 
+					\vdots\\
+					G_{2N_z} \left( c_f,c_s,h; \Theta \right)\\ 
+					\\ \\ \hline \\ 
+					G_{2N_z+1} \left( c_f,c_s,h; \Theta \right) \\
+					\vdots\\
+					G_{3N_z} \left( c_f,c_s,h; \Theta \right) \\ 
+					\\ \\ \hline \\
+					G_{3N_z+1} \left( c_f,c_s,h; \Theta \right) \\
+					\\ \\ \hline \\
+					G_{3N_z+2} \left( c_f,c_s,h; \Theta \right) 
+			\end{bmatrix}}_{G \left( x; \Theta \right),} 
+	\end{align*} }
+	where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.
+
+	For a derivative to be conservative, it must form a telescoping series.
+In other words, only the boundary terms should remain after adding all terms coming from the discretization over a grid, and the artificial interior points should be cancelled out.
+Discretization is applied to the conservative form of the model to ensure mass conservation.
 
 	\subsection{Local sensitivity analysis} \label{CH: Sensitivity_Analysis}
-\subfile{Sections/Sensitivity_Analysis}
+
+	Local derivative-based methods involve taking the total derivative of the state vector $x$ with respect to the parameter space $\Theta$.
+A set of derivatives, known as sensitivity equations, is integrated simultaneously with the process model.
+Sensitivity analysis shows how responsive the solution is to changes in the parameter $\Theta$.
+As discussed by \citet{Dickinson1976}, sensitivity analysis can be used to determine the influence of uncertainty on the solution of the original system.
+Another application of sensitivity analysis is to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction.
+Finally, from a control engineering point of view, sensitivity analysis allows sorting the control variables with respect to the level of effort required to change the model's output.
+
+	Following the work of \citet{Maly1996}, sensitivity equations can be defined as follows:
+
+	{\footnotesize
+		\begin{equation}
+			\label{SA_def}
+			S(x;\Theta) = \cfrac{dx}{d\Theta}
+	\end{equation} }
+
+	The new system of equations can be obtained by taking the total derivative of $S$ with respect to time $t$:
+
+	{\footnotesize
+		\begin{equation} \label{SA_dt} 
+			{\dot{S}}(x;\Theta)  = \cfrac{dS(x;\Theta)}{d t} = \cfrac{d}{d t} \left( \cfrac{dx}{d\Theta} \right) = \cfrac{d }{d\Theta} \left( \cfrac{dx}{d t} \right) = \cfrac{d G(x;\Theta)}{d\Theta} 
+	\end{equation} }
+
+	Sensitivity Equation \ref{SA_eq_full} can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}:
+
+	{\footnotesize
+		\begin{equation} \label{SA_eq_full}
+			\cfrac{d G(x;\Theta)}{d \Theta} = \underbrace{ \cfrac{\partial G(x;\Theta)}{\partial x} }_{{\bar{J}_x}(x;\Theta)} \underbrace{\cfrac{\partial x}{\partial \Theta} }_{\bar{S}(x;\Theta)} + \underbrace{ \cfrac{\partial G(x;\Theta)}{\partial \Theta} }_{{\bar{J}_\Theta}(x;\Theta)}
+	\end{equation} }
+
+	The Jacobian ${\bar{J}_x}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${\bar{J}_x}(n_x,n_x)$ is the derivative of $G_{n_x}(x;\Theta)$ with respect to the state variable $x_{n_\Theta}$:
+
+	{\footnotesize
+		\begin{align}
+			\begingroup % keep the change local
+			\setlength\arraycolsep{2pt}
+			{\bar{J}_x}(x;\Theta)=\begin{pmatrix}
+				\cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{1}}} & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{2}}} & \cdots & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {x_{N_x}}}\\
+				\cfrac{\partial {G_{2}}(x;\Theta)}{\partial {x_{1}}} & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {x_{2}}} & \cdots & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {x_{N_x}}}\\
+				\vdots & \vdots & \ddots & \vdots\\ 
+				\cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {x_{1}}} & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {x_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {x_{N_x}}}\\
+			\end{pmatrix}
+			\endgroup
+	\end{align} }
+
+	The sensitivity matrix $\bar{S}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each entry $\bar{S}(n_x,n_\Theta)$ is the derivative of state variable $x_{n_x}$ with respect to parameter $\Theta_{n_\Theta}$.
+Matrix ${\bar{J}_x}(x;\Theta)$ and $\bar{S}(x;\Theta)$ describe the indirect influence of $\Theta_{n_\Theta}$ on the state space.
+
+	{\footnotesize
+		\begin{equation}
+			\begin{split}
+				\bar{S}(x;\Theta) & = 
+				\begingroup % keep the change local
+				\setlength\arraycolsep{2pt}
+				\begin{pmatrix}
+					\cfrac{\partial {x_{1}}}{\partial {\Theta_{1}}} 	& \cfrac{\partial {x_{1}}}{d {\Theta_{2}}}     & \cdots & \cfrac{d {x_{1}}}{\partial {\Theta_{N_\Theta}}}\\
+					\cfrac{\partial {x_{2}}}{\partial {\Theta_{1}}} 	& \cfrac{\partial {x_{2}}}{d {\Theta_{2}}}     & \cdots & \cfrac{d {x_{2}}}{\partial {\Theta_{N_\Theta}}}\\
+					\vdots					 	    & \vdots 					   	  & \ddots & \vdots\\
+					\cfrac{\partial {x_{N_x}}}{\partial {\Theta_{1}}} 	& \cfrac{\partial {x_{N_x}}}{d {\Theta_{2}}}     & \cdots & \cfrac{\partial {x_{N_x}}}{d {\Theta_{N_\Theta}}}
+				\end{pmatrix} 
+				\endgroup
+			\end{split}
+	\end{equation} }
+
+	The Jacobian ${\bar{J}_\Theta}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each sub-equation ${\bar{J}_\Theta}(n_x,n_\Theta)$ is the partial derivative of process model equation $G_{n_x}$ with respect to parameter $\Theta_{n_\Theta}$.
+${\bar{J}_\Theta}(n_x,n_\Theta)$ defines the direct effect of $\Theta_{n_\Theta}$ on the state space:
+
+	{\footnotesize
+		\begin{align}
+			{\bar{J}_\Theta}(x;\Theta) & =
+			\begingroup % keep the change local
+			\setlength\arraycolsep{2pt}
+			\begin{pmatrix}
+				\cfrac{\partial {G_{1}}(x;\Theta)}{\partial {\Theta_{1}}} & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {\Theta_{2}}} & \cdots & \cfrac{\partial {G_{1}}(x;\Theta)}{\partial {\Theta_{N_\Theta}}}\\
+				\cfrac{\partial {G_{2}}(x;\Theta)}{\partial {\Theta_{1}}} & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {\Theta_{2}}} & \cdots & \cfrac{\partial {G_{2}}(x;\Theta)}{\partial {\Theta_{N_\Theta}}}\\
+				\vdots & \vdots & \ddots & \vdots\\
+				\cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {\Theta_{1}}} & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {\Theta_{2}}} & \cdots & \cfrac{\partial {G_{N_x}}(x;\Theta)}{\partial {\Theta_{N_\Theta}}}
+			\end{pmatrix}
+			\endgroup
+	\end{align}}
+
+	The augmented system containing the original set of equations $G(x;\Theta)$ and sensitivity equations is called ${\textbf{G}}\left(x;\Theta\right)$.
+The size of ${\textbf{G}}\left(x;\Theta\right)$ is equal to $N_s = N_x(N_\Theta + 1)$.
+
+	{\footnotesize
+		\begin{align}
+			{\textbf{G}}\left(x;\Theta\right) = 
+			\begin{bmatrix}
+				G(x;\Theta)\\
+				{\bar{J}_x}(x;\Theta)\bar{S}(x;\Theta) + {\bar{J}_\Theta}(x;\Theta)
+			\end{bmatrix}
+	\end{align} }
+
+	The initial conditions are described as
+
+	{\footnotesize
+		\begin{align}
+			{\textbf{G}}\left(x(t_0);\Theta\right)  &= 
+			\begin{bmatrix}
+				x(t_0),						               &
+				\cfrac{ \text{d}x(t_0) }{ d{\Theta_1} },		   &
+				\cdots,					 				   &
+				\cfrac{ dx(t_0) }{ d{\Theta_{N_\Theta}} }            
+			\end{bmatrix}^\top = \\ &=
+			\begin{bmatrix} 
+				\quad x_0,	                               &
+				\quad ~0,		                           &
+				\quad \cdots,			                   &
+				\quad 0 \quad~~
+			\end{bmatrix}^\top \nonumber
+	\end{align} }
 
@@
 
-\subfile{Sections/Results_Sensitivity}
+	%\subfile{Sections/Results_Sensitivity}
+	\section{Results} \label{CH: Results}
+	The details of the process model and parameters are provided in \citet{Sliczniuk2024}.
+The process model was validated in the following range of operating conditions: temperatures between $30 - 40 ^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
+The sensitivity analysis is performed at the midpoint of the validated range: $35 ^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+This study examines the impact of pressure change on the state space and extraction yield through local sensitivity analysis.
+The local sensitivity analysis results can be interpreted as the system's response to an infinitesimal deviation in pressure.
+
+	As discussed in Section \ref{CH:Governing_equations_chapter}, at low velocity, the fluid can be treated as incompressible, which results in the instant propagation of pressure throughout the system, enabling a single pressure value to be considered for the entire system.
+In response to a pressure change, the energy equation experiences a simultaneous deviation across the entire spatial domain.
+This pressure change impacts the fluid temperature within the computational domain, while boundary values are constrained by conditions specified at the domain's extremes.
+Dirichlet boundary conditions impose a fixed temperature value at the inlet, creating a thermal gradient that propagates through the system.
+Alternatively,  Neumann boundary conditions specify a heat flux at the extremes.
+The zero Neumann boundary conditions are applied to ensure a uniform response to the pressure change of temperatures at the inlet, outlet, and within the extractor.
+
+	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of the solute concentration in the solid phase to pressure changes.
+As discussed in Section \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, indicating that increased pressure reduces the fluid velocity.
+This results in an extended residence time, allowing for longer interaction between the solute and solvent.	Initially, the extraction process operates in the kinetic-controlled regime, where the concentration gradient is high, and solute solubility is the limiting factor.
+As noted by \citet{Sliczniuk2024}, the system is considered far from saturation, which explains the low initial system response.
+This low initial response was also observed in the sensitivity analysis by \citet{Fiori_2007}.
+The system's response becomes more pronounced as the concentration gradient decreases and the extraction shifts from the kinetic-controlled to the diffusion-controlled regime.
+In Figure \ref{fig:Sensitivty_P_CS}, all $\frac{dc_s}{dP}$ values are negative, which indicates a faster mass transfer from the solid phase, corresponding to enhanced mass transfer.
+Over time, as the amount of solute decreases, it becomes a limiting factor, reducing the effect of pressure changes on the system.
+Eventually, the sensitivities approach zero asymptotically as the solute is washed out of the bed.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
+		\caption{The effect of $P_{in}$ change on $C_s$.}
+		\label{fig:Sensitivty_P_CS}
+	\end{figure}
+
+	Figure \ref{fig:Sensitivty_P_CF} illustrates the sensitivity of solute concentration in the fluid phase to pressure changes.
+Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of fluid phase sensitivities is more apparent.
+Due to advection, the sensitivities related to the fluid phase move across the system in the direction of flow.
+Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period.
+As the process continues, the sensitivities increase, indicating faster mass transfer from the solid phase.
+The corresponding improvement in the mass transfer from the solid particles to the fluid is represented by the positive values in Figure \ref{fig:Sensitivty_P_CF}.
+When the solute in the solid phase becomes a limiting factor, the extraction rate slows, and sensitivities eventually approach zero asymptotically.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
+		\caption{The effect of $P_{in}$ change on $C_f$.}
+		\label{fig:Sensitivty_P_CF}
+	\end{figure}
+
+	Figure \ref{fig:Sensitivty_P_y} shows how sensitive the extraction yield is to pressure changes over an extended period for various pressure values.
+Initially, all sensitivity curves remain nearly flat, indicating a delayed response in the system.
+Due to the reduced fluid velocity, the solute reaches the extractor's outlet later, causing minor negative sensitivities to appear.
+Once the solute exits the extractor, the sensitivity curves rise.
+Positive yield sensitivities indicate improved process efficiency and enhanced mass transfer.
+The peak in $\frac{dy}{dP_{in}}$ represents the point of greatest deviation from the original system.
+Eventually, the sensitivities decline and converge towards zero as the concentration gradient becomes a limiting factor, reducing the impact of enhanced mass transfer.
+
+	As presented in Figure \ref{fig:Sensitivty_P_y}, higher sensitivities are observed for a low-pressure system.
+At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction, as shown by data given by \citet{Sliczniuk2024}.
+Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield.
+Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity, and therefore to higher sensitivity of the system state-space.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.1cm 0.0cm 1.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple.png}
+		\caption{The effect of $P_{in}$ change on $y(t)$.}
+		\label{fig:Sensitivty_P_y}
+	\end{figure}
 
@@
 
-Sensitivity analysis is a tool used to understand how model parameters affect its output.
+	Sensitivity analysis is a tool used to understand how the parameters of the model affect its output.
 The presented formulation involves derivative-based local sensitivity analysis of the model solution with respect to selected parameters and controls.
-This work implemented the automatic differentiation to derive the sensitivity equations.
-The local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
-In the case of dynamic systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies in time with respect to small perturbations in parameters.
+This work implemented automatic differentiation to derive the sensitivity equations.
+Local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
+In the case of dynamic systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies over time with respect to small perturbations in parameters.
 
-%The local sensitivity analysis can be performed with respect to any model parameter, but this work focuses on the effect of pressure increase.
-At selected operating conditions( $35^\circ C$ and $5\cdot 10^{-5}$ kg/s), the pressure increase enhances the mass transfer, which leads to faster mass transfer from particles and consequently to negative sensitivities in the solid phase.
-Analogously, the sensitivities in the fluid phase are characterised by positive deviations, which indicates that more solute is transported to the fluid phase.
-As a result, the extraction yield is improved and characterised by positive sensitivities.
-As the results of the local sensitivity analysis depends on the operating point, the analysis was repeated at different nominal pressures.
-It can be observed that system responses at low-pressures are stronger than at high-pressures.
-This behaviour can be explained by rapid changes of the solvent properties close to the critical point.
-
-{\color{blue}Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of pressure.
-Under the selected operating conditions, it was observed for all the cases that the pressure increment enhances mass transfer, leading to a faster mass transfer of solute from the particles.
-Consequently, the negative sensitivities can be observed in the diagram for the solid phase.
-The corresponding response in the fluid phase is characterized by positive-valued sensitivities, indicating that more amount of solute is transported into the fluid phase.
+	Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of pressure.
+Under the selected operating conditions, it was observed for all the cases that a pressure increment enhances mass transfer, leading to a faster mass transfer of solute from the particles.
+Consequently, negative sensitivities can be observed in the diagram for the solid phase.
+The corresponding response in the fluid phase is characterized by positive-valued sensitivities, indicating that a greater amount of solute is transported into the fluid phase.
 As a result, the extraction yield is improved and characterized by positive sensitivities.
 Given that the results of the local sensitivity analysis depend on the operating point, the analysis was repeated at different pressures.
-It was observed that the system responses at low pressures are stronger than those at higher pressures.
-This behaviour can be explained by the rapid changes in solvent properties occurring near the critical point of CO$_2$}.
+It was observed that the system responses at low pressures were stronger than those at higher pressures.
+This behaviour can be explained by the rapid changes in solvent properties occurring near the critical point of CO$_2$.
 
-Local sensitivity analysis results provide valuable information by identifying which parameters are influential and how these influence changes over time.
-One application of the sensitivity analysis is to spot discrepancies between model predictions and actual experimental results.
+	Local sensitivity analysis results provide valuable information by identifying which parameters are influential and how these influences change over time.
+One application of sensitivity analysis is to spot discrepancies between model predictions and actual experimental results.
 Identifying unexpected system responses prompts further investigation and refinement of the process model.
-Sensitivity analysis results can be used to design future experiments by indicating which parameters should be varied and monitored.
-Moreover, the parameters which are characterized by low sensitivity can be subject of model refinement.
+The sensitivity analysis results can be used to design future experiments by indicating which parameters should be varied and monitored.
+Moreover, the parameters which are characterized by low sensitivity can be the subject of model refinement.
 
-\section*{Acknowledgement} 
-This work was supported by: NovelBaltic, CEForestry (IBC), BIO4P (BF)
+	\section*{Acknowledgements} 
+	This work was supported by: NovelBaltic, CEForestry (IBC), BIO4P (BF).
 
@@
 	\bibliography{mybibfile}
-
-%\clearpage \appendix \label{appendix}
-%\section{Appendix} 
-%\subfile{Sections/Qubic_EOS} \label{CH: EOS}
-%\subsection{Cardano's Formula} \label{CH: Cardano}
-%\subfile{Sections/Cardano}
 

### 2025-01-11 Sections/Sensitivity_Pressure.tex
11.01

@@
 
-	{\color{blue} As discussed in Chapter \ref{CH:Governing_equations_chapter}, at the low velocity, the fluid can be treated as incompressible, which results in the instant propagation} of pressure throughout the system, enabling a single pressure value to be considered for the entire system.
+	As discussed in Chapter \ref{CH:Governing_equations_chapter}, at the low velocity, the fluid can be treated as incompressible, which results in the instant propagation of pressure throughout the system, enabling a single pressure value to be considered for the entire system.
 In response to a pressure change, the energy equation experiences a simultaneous deviation across the entire spatial domain.
@@
 The system's response becomes more pronounced as the concentration gradient decreases and the extraction shifts from the kinetic-controlled to the diffusion-controlled regime.
-{\color{blue}In Figure \ref{fig:Sensitivty_P_CS}, all $\frac{dc_s}{dP}$ values are negative, which indicates a faster mass transfer} from the solid phase, corresponding to enhanced mass transfer.
+In Figure \ref{fig:Sensitivty_P_CS}, all $\frac{dc_s}{dP}$ values are negative, which indicates a faster mass transfer from the solid phase, corresponding to enhanced mass transfer.
 Over time, as the amount of solute decreases, it becomes a limiting factor, reducing the effect of pressure changes on the system.
@@
 Compared to Figure \ref{fig:Sensitivty_P_CS}, the dynamic behaviour of fluid phase sensitivities is more apparent.
-{\color{blue}Due to advection, the sensitivities related to the fluid phase moves across the system in the direction of flow}.
+Due to advection, the sensitivities related to the fluid phase moves across the system in the direction of flow.
 Initially, the system response is low despite the pressure increase improving mass transfer, reflecting the previously discussed idle period.

### 2025-01-23 Article_Sensitivity_Analsysis-Chamomile.tex
23.01

@@
 Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nanosized particles or crystals, such as reduced use of toxic solvents.
-Moreover, the CO$_2$ is completely removed from the final product by simple depressurization.
+Moreover, the CO$_2$ is removed from the final product by simple depressurization.
 
@@
 The model is particularly relevant when internal diffusion controls mass transfer, allowing results from single particles to be extended to the entire bed under uniform conditions.
-\citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes for natural materials.
+\citet{Reverchon1993} have further elaborated on the HBD model and used it to simulate extraction processes.
 
@@
 	%\subfile{Sections/Literature_Review}
-	This study aims to analyse the influence of changes in operating conditions on the process model described by \citet{Sliczniuk2024}.
+	%This study aims to analyse the influence of changes in operating conditions on the process model described by \citet{Sliczniuk2024}.
 For that, a sensitivity analysis is applied to examine the impact of model parameters or controls on the model output.
@@
 Various sensitivity analysis methods are available, including:
+
+	{\color{blue}The primary aim of this study is to analyse the influence of changes in operating conditions on the process model developed by \citet{Sliczniuk2024}.
+Understanding how variations in parameters and control variables affect the model's behaviour is essential for improving its accuracy, robustness, and practical applicability.
+To achieve this, a comprehensive sensitivity analysis is employed, serving as a systematic approach to assess the impact of model parameters and controls on the outputs.
+
+	The results of this sensitivity analysis are valuable for multiple purposes.
+First, they help identify sources of uncertainty within the model, highlighting which parameters most significantly influence predictions.
+Second, they provide insights for potential model simplification, allowing the exclusion of non-essential parameters without compromising accuracy.
+Finally, the analysis can detect inconsistencies or errors by uncovering unexpected relationships between inputs and outputs, which may signal flaws in the model's assumptions or structure.
+
+	A range of sensitivity analysis methods can be utilized to achieve these objectives, including:}
 
@@
 
-	where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the axial diffusion coefficient.
+	where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the {\color{blue}axial dispersion coefficient}.
 
@@
 	\end{equation} }
+
+	{\color{blue}The choice between the two formulations should consider the system's properties and the underlying mass transfer assumptions.
+In systems where external mass transfer dominates, the resistance to solute transport primarily occurs at the fluid-solid interface, typically governed by the diffusion of solute across the fluid boundary layer.
+Under these conditions, the Bulley formulation is more appropriate, as it explicitly emphasizes the fluid-phase concentration ($c_f$) as the driving force for mass transfer through the term $c_f - c_p^*(c_s)$.
+Conversely, when internal mass transfer dominates, the resistance to solute transport is controlled by diffusion or adsorption processes within the solid phase.
+In such cases, the Reverchon formulation is more suitable, as it accounts for deviations in the equilibrium through the term $c_s - c_s^*(c_f)$.}
 
@@
 	As explained in Section \ref{CH:Governing_equations_chapter}, this low velocity region pressure is nearly constant due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, {\color{blue}describing} the pressure change in the whole system.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, describing the pressure change in the whole system.
 The pressure $P$ in the system is considered a state variable, while the pressure in the new time-step $P_{in}$ is considered a control variable.
@@
 		\centering
-		\includegraphics[trim = 0.1cm 0.0cm 1.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple.png}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield.png}
 		\caption{The effect of $P_{in}$ change on $y(t)$.}
 		\label{fig:Sensitivty_P_y}
+	\end{figure}
+
+	One disadvantage of using local sensitivity coefficients is that their reflect the absolute changes, which might be difficult to compare among other models or scenarios.
+The normalized local sensitivity coefficients, defined as $\tilde{S}(x;\Theta) = \frac{d G(x;\Theta)}{d\Theta} \frac{\Theta}{G(x;\Theta)}$, which can be interpreted as the percentage change in the output per percentage change in the parameter, making it a unitless.
+Although, the interpretation is straightforward it should be noted that extrapolation for large change of the parameter might leads to incorrect results.
+In the case of dynamic systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies over time with respect to small perturbations in parameters.
+If the perturbation is too large, then the definition of a derivative (or sensitivity equations) does not hold unless the system is linear.
+Consequently, the conclusions can not be scaled up to any size of parameter perturbation.
+Such a property of the local sensitivity analysis, makes it difficult to recreate in a laboratory conditions due to finite precision of machines.
+
+	{\color{blue}Figure \ref{fig:Sensitivty_P_y_norm} illustrates the time evolution of the normalized sensitivity coefficients of the extraction yield.
+Unlike the raw sensitivities shown in Figure \ref{fig:Sensitivty_P_y}, the normalized sensitivities do not start from zero.
+This is due to the absence of the exact initial time point on the logarithmic time axis.
+The pressure change impacts the system instantaneously and uniformly, leading to a rapid initial change in the normalized sensitivities.
+This behavior is analogous to a step change, where the system's response to the perturbation is immediate.
+Initially, the sensitivity curves remain flat.
+The increase in normalized sensitivity begins when the solute reaches the system's outlet and becomes detectable.
+After reaching their respective maxima, the sensitivity curves decrease as the concentration gradient driving the extraction diminishes over time.
+Ultimately, all curves approach zero, reflecting that all the solute was removed from the solid phase.}
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple_normalized.png}
+		\caption{The effect of $P_{in}$ change on $y(t)$ after normalization.}
+		\label{fig:Sensitivty_P_y_norm}
 	\end{figure}
@@
 Local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
-In the case of dynamic systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies over time with respect to small perturbations in parameters.
 
@@
 Given that the results of the local sensitivity analysis depend on the operating point, the analysis was repeated at different pressures.
+
+	{\color{blue}The normalized sensitivity coefficients provide a basis for generalizing the discussion of the results and comparing the influence of various parameters.
+The normalized sensitivity results were found to vary within the range of -0.17 to 0.6.
+The overall effect of each parameter can be evaluated by integrating the sensitivity curves.
+Similar to the analysis of yield sensitivity, the integration was performed using an extended simulation until all sensitivities approached zero.
+The cumulative integral values at pressures of 100, 125, 150, 175, and 200 bars are 31487, 8548, 4462, 2825, and 1939, respectively.
+The positive sign of these values indicates that increased pressure enhances the extraction yield under all investigated operating conditions.
+The order of magnitude of the integrals allows to identify at which operating condtions the pressure increase is the most influential.}
+
 	It was observed that the system responses at low pressures were stronger than those at higher pressures.
@@
 
+	\sout{
 	Local sensitivity analysis results provide valuable information by identifying which parameters are influential and how these influences change over time.
@@
 Moreover, the parameters which are characterized by low sensitivity can be the subject of model refinement.
+}
 

### 2025-01-25 Article_Sensitivity_Analsysis-Chamomile.tex
25.01

@@
 This study focuses on analysing the effect of pressure on the model state space and extraction yield.
+{\color{blue}It was found that the model is the most sensitive to the controls if operated close to the critical point.}
 
@@
 
-	The applications of supercritical carbon dioxide are not limited only to an extraction process but can also be used for impregnation, as described by \citet{Weidner2018}, \citet{Machado2022} or \citet{Fathi2022}.
+	The applications of supercritical carbon dioxide are not limited only to an extraction process but can also be used for impregnation, as described by \citet{Weidner2018} or \citet{Machado2022}.
 Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
@@
 On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.
+	{\color{blue}The study of \citet{Ameri2020} investigates the loading of lansoprazole into polymers using supercritical carbon dioxide and examines how various parameters, such as temperature, pressure, and time, affect the drug loading efficiency.
+The results indicate that increasing any of these parameters enhances drug loading, with temperature having the most significant impact.	The study of \citet{Fathi2022} explores the use of supercritical carbon dioxide to enhance the bioavailability of ketoconazole by impregnating it into water-soluble polymers, specifically polyvinylpyrrolidone and hydroxypropyl methylcellulose.
+Utilizing a Box-Behnken design, the researchers optimized the impregnation process by varying pressure (150–250 bar), temperature (308–328 K), and time (60–180 minutes), achieving increase in drug loadings ranging.}
 
-	Another application of supercritical CO$_2$ is nanoparticle formation, as investigated by \citet{Padrela2018}, \citet{Franco2021}, \citet{SaadatiArdestani2020} or \citet{Sodeifian2022}.
+	Another application of supercritical CO$_2$ is nanoparticle formation, as investigated by \citet{Padrela2018}, \citet{Franco2021} or \citet{Sodeifian2022}.
 Supercritical carbon-dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating the operating conditions.
@@
 Moreover, the CO$_2$ is removed from the final product by simple depressurization.
+	{\color{blue} \citet{Sodeifian2018} investigates the solubility of Letrozole, a poorly water-soluble anticancer drug, in supercritical carbon dioxide with and without menthol as a solid co-solvent.
+The addition of menthol increased Letrozole's solubility by 7.1 times compared to supercritical CO$_2$ alone.
+Using the rapid expansion of supercritical solutions with solid co-solvent method, the average particle size of Letrozole was reduced to the nanoscale.
+Temperature was found to have the most significant impact on nanoparticle size reduction, while pressure had the least effect.
+	The study of \citet{SaadatiArdestani2020} explores the preparation of phthalocyanine green nano pigment using supercritical carbon dioxide as an antisolvent.
+The researchers employed the gas antisolvent technique to achieve nano-sized particles of the pigment.
+This method offers a potential approach for producing nano pigments with enhanced properties.
+The findings contribute to the development of advanced materials in the field of pigments and coatings.
+	The study of \citet{Sodeifian2019} investigates the production of amiodarone hydrochloride nanoparticles using an ultrasonic-assisted rapid expansion of supercritical solution into a liquid solvent method.
+By optimizing parameters such as pressure, temperature, and polymeric stabilizer concentration, the researchers achieved significant particle size reduction.
+Characterization techniques confirmed the successful formation of nanoparticles with improved properties.
+	}
 
@@
 Selecting a process model is case-dependent and requires analysis of each model's specific assumptions about mass transfer and thermodynamic equilibrium.
+
+	{\color{blue}Depending on the needs one of two approaches can be considered while developing a mathematical model.
+A model, which is based on a multiple regression can be used if the relation between inputs and outputs can be simplified.
+\citet{Sodeifian2017a} investigated an influence of pressure, temperature and particle size on the extraction efficiency of oil from dracocephalum kotschyi boiss seed.
+The second order polynomial model was applied to obtain the corresponding response surface and to identify the optimum operating conditions.
+	The study of \citet{Sodeifian2017b} investigates the of essential oil from Eryngium billardieri, focusing on optimizing extraction conditions and developing a mathematical model based on the f the second order polynomial to predict the process yield.
+The researchers employed a simulated annealing algorithm to optimize parameters such as pressure, temperature, and extraction time, aiming to maximize oil efficiency.
+
+	Alternatively, a more complex model can be derived and applied to cover not only the input-output relations, but the phenomena occurring in the system.
+This approach allows for more detailed representation the system behaviour, but requires better understanding of the mass transfer and more rigorous experiments.}
 
@@
 
-	%\subfile{Sections/Literature_Review}
-	%This study aims to analyse the influence of changes in operating conditions on the process model described by \citet{Sliczniuk2024}.
-For that, a sensitivity analysis is applied to examine the impact of model parameters or controls on the model output.
-The results of this sensitivity analysis can be used to identify sources of uncertainty, simplify the model or detect errors by revealing unexpected relationships between inputs and outputs.
-Various sensitivity analysis methods are available, including:
-
 	{\color{blue}The primary aim of this study is to analyse the influence of changes in operating conditions on the process model developed by \citet{Sliczniuk2024}.
@@
 Finally, the analysis can detect inconsistencies or errors by uncovering unexpected relationships between inputs and outputs, which may signal flaws in the model's assumptions or structure.
+}
 
-	A range of sensitivity analysis methods can be utilized to achieve these objectives, including:}
+	A range of sensitivity analysis methods can be utilized to achieve these objectives, including:
 
@@
 The first part examined how net present value is influenced by changes in individual technical and economic parameters, keeping the extractor volume constant at 300 L.
-The second part investigated the effects of varying the extractor volume (from 1 to 600 L) on the project's overall profitability.
-The authors found that the raw material price, discount rate and residence time had the biggest impact on NPV (\citet{Hatami2024}).
+The second part investigated the effects of varying the extractor volume (from 1 to 600 L) on the project's profitability.
+The authors found that the raw material price, discount rate and residence time had the biggest impact on NPV.
+
+	{\color{blue}The paper of \citet{Maly1996} addresses the development of numerical methods and software tools for sensitivity analysis in differential-algebraic equation systems.
+The paper discusses the mathematical foundations of the local sensitivity analysis methods employed, providing a thorough analysis of their performance.
+The authors presented variety of problems and to prove the efficient of their method.
+
+	In his \citet{Turanyi1990} presents a comprehensive review of sensitivity analysis methods applied to spatially homogeneous, constant-parameter chemical kinetic systems.
+The work delves into various sensitivity analysis techniques, including concentration sensitivity, rate sensitivity, and feature sensitivity analysis.
+The paper explores practical applications of these methods in chemical kinetics, demonstrating their utility in understanding and predicting system behavior.
+
+	\citet{Fishtik1997} applied the local sensitivity analysis of an multiple chemical reaction system with several pure condensed phases and one ideal gas phase.
+It was shown that the system's response may be presented as a sum of contributions coming only from response equilibria defined by gas phase species.
+The effect of temperature, pressure and initial amounts of species is analyzed for gasification of coal.
+
+	\citet{Saltelli2005} provide a comprehensive review of sensitivity analysis methods applicable to chemical modeling.
+The authors discuss both local and global techniques, emphasizing the importance of global sensitivity analysis in understanding complex chemical systems.
+The manuscript highlight the role of variance-based methods, in quantifying the influence of input parameters on model outputs.
+
+	Unlike previous studies, this work focuses on derivative-based local sensitivity analysis to evaluate the robustness and predictive accuracy of a mathematical model for chamomile oil extraction under varying operational conditions.
+The analysis specifically examines the impact of operating condition changes, providing new insights into model development and optimizing extraction performance.}
 
@@
 
-	One disadvantage of using local sensitivity coefficients is that their reflect the absolute changes, which might be difficult to compare among other models or scenarios.
+	{\color{blue}One disadvantage of using local sensitivity coefficients is that their reflect the absolute changes, which might be difficult to compare among other models or scenarios.
 The normalized local sensitivity coefficients, defined as $\tilde{S}(x;\Theta) = \frac{d G(x;\Theta)}{d\Theta} \frac{\Theta}{G(x;\Theta)}$, which can be interpreted as the percentage change in the output per percentage change in the parameter, making it a unitless.
@@
 
-	{\color{blue}Figure \ref{fig:Sensitivty_P_y_norm} illustrates the time evolution of the normalized sensitivity coefficients of the extraction yield.
+	Figure \ref{fig:Sensitivty_P_y_norm} illustrates the time evolution of the normalized sensitivity coefficients of the extraction yield.
 Unlike the raw sensitivities shown in Figure \ref{fig:Sensitivty_P_y}, the normalized sensitivities do not start from zero.
@@
 This work implemented automatic differentiation to derive the sensitivity equations.
-Local sensitivity analysis techniques consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
+The results of the local sensitivity analysis and model specific and consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
 
@@
 
-	It was observed that the system responses at low pressures were stronger than those at higher pressures.
+	It can be concluded that the system responses at low pressures were stronger than those at higher pressures.
 This behaviour can be explained by the rapid changes in solvent properties occurring near the critical point of CO$_2$.
-
-	\sout{
-	Local sensitivity analysis results provide valuable information by identifying which parameters are influential and how these influences change over time.
-One application of sensitivity analysis is to spot discrepancies between model predictions and actual experimental results.
-Identifying unexpected system responses prompts further investigation and refinement of the process model.
-The sensitivity analysis results can be used to design future experiments by indicating which parameters should be varied and monitored.
-Moreover, the parameters which are characterized by low sensitivity can be the subject of model refinement.
-}
 
@@
 
-	\newpage
+	\clearpage
 

### 2025-01-25 SFE_Sensitivity_Analysis_Chamomile/main_Sensitivity_Analysis_Chamomile.m

@@ -5,6 +5,15 @@ delete(gcp('nocreate'));
 %addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
 addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
+%%
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('wpd_datasets.xlsx');
+which_dataset           = 4;
+
+SAMPLE                  = LabResults(21:34,1);
+data_org                = LabResults(21:34,which_dataset+1)';
 
 %% Load paramters
 m_total                 = 3.0;
@@ -15,8 +24,8 @@ bed                     = 0.92;                                             % Pe
 
 % Set time of the simulation
 PreparationTime         = 0;
-ExtractionTime          = 0.6;
-timeStep                = 0.0001;                                                % Minutes
+ExtractionTime          = 6e4;
+timeStep                = 0.1;                                                % Minutes
 
 simulationTime          = PreparationTime + ExtractionTime;
 
@@ -25,29 +34,6 @@ Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Se
 Time                    = [0 Time_in_sec/60];                               % Minutes
 
 N_Time                  = length(Time_in_sec);
-
-name_v = {'T_{in}', 'P'     , 'F'                                   };
-name_s = {'c_f'   , 'c_s'   , '(h\times\rho)' , 'P_{t-1}'     , 'y' };
-name_p = {'CF'    , 'CS'    , 'H'             , 'P_{in}'      , 'Y' };
-    
-My_Font = 14;
-Pressure_range          = 100:25:200;
-RES                     = nan(length(Pressure_range), N_Time+1);
-STATE                   = nan(length(Pressure_range), 152, N_Time+1);
-SENSE                   = nan(length(Pressure_range), 152, N_Time+1);
-Yield                   = nan(length(Pressure_range), N_Time+1);
-
-parfor PP = 1:length(Pressure_range)
-
-%%
[…]

### 2025-02-13 Article_Sensitivity_Analsysis-Chamomile.tex
13.02

@@
 This study focuses on analysing the effect of pressure on the model state space and extraction yield.
-{\color{blue}It was found that the model is the most sensitive to the controls if operated close to the critical point.}
+It was found that the model is the most sensitive to the controls if operated close to the critical point.
 
@@
 On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.
-	{\color{blue}The study of \citet{Ameri2020} investigates the loading of lansoprazole into polymers using supercritical carbon dioxide and examines how various parameters, such as temperature, pressure, and time, affect the drug loading efficiency.
-The results indicate that increasing any of these parameters enhances drug loading, with temperature having the most significant impact.	The study of \citet{Fathi2022} explores the use of supercritical carbon dioxide to enhance the bioavailability of ketoconazole by impregnating it into water-soluble polymers, specifically polyvinylpyrrolidone and hydroxypropyl methylcellulose.
-Utilizing a Box-Behnken design, the researchers optimized the impregnation process by varying pressure (150–250 bar), temperature (308–328 K), and time (60–180 minutes), achieving increase in drug loadings ranging.}
+	The study of \citet{Ameri2020} investigates the loading of lansoprazole into polymers using supercritical carbon dioxide and examines how various parameters, such as temperature, pressure, and time, affect the drug loading efficiency.
+The results indicate that increasing any of these parameters enhances drug loading, with temperature having the most significant impact.
+\citet{Fathi2022} explored the use of supercritical carbon dioxide to enhance the bioavailability of ketoconazole by impregnating it into water-soluble polymers, specifically polyvinylpyrrolidone and hydroxypropyl methylcellulose.
+Utilizing a Box-Behnken design, the researchers optimized the impregnation process by varying pressure, temperature, and time, achieving increase in drug loadings ranging.
 
@@
 Moreover, the CO$_2$ is removed from the final product by simple depressurization.
-	{\color{blue} \citet{Sodeifian2018} investigates the solubility of Letrozole, a poorly water-soluble anticancer drug, in supercritical carbon dioxide with and without menthol as a solid co-solvent.
+	\citet{Sodeifian2018} investigated the solubility of Letrozole, a poorly water-soluble anticancer drug, in supercritical carbon dioxide with and without menthol as a solid co-solvent.
 The addition of menthol increased Letrozole's solubility by 7.1 times compared to supercritical CO$_2$ alone.
@@
 Temperature was found to have the most significant impact on nanoparticle size reduction, while pressure had the least effect.
-	The study of \citet{SaadatiArdestani2020} explores the preparation of phthalocyanine green nano pigment using supercritical carbon dioxide as an antisolvent.
+	The study of \citet{SaadatiArdestani2020} explored the preparation of phthalocyanine green nano pigment using supercritical carbon dioxide as an antisolvent.
 The researchers employed the gas antisolvent technique to achieve nano-sized particles of the pigment.
-This method offers a potential approach for producing nano pigments with enhanced properties.
-The findings contribute to the development of advanced materials in the field of pigments and coatings.
-	The study of \citet{Sodeifian2019} investigates the production of amiodarone hydrochloride nanoparticles using an ultrasonic-assisted rapid expansion of supercritical solution into a liquid solvent method.
+	\citet{Sodeifian2019} analysed the production of amiodarone hydrochloride nanoparticles using an ultrasonic-assisted rapid expansion of supercritical solution into a liquid solvent method.
 By optimizing parameters such as pressure, temperature, and polymeric stabilizer concentration, the researchers achieved significant particle size reduction.
 Characterization techniques confirmed the successful formation of nanoparticles with improved properties.
-	}
 
@@
 
-	{\color{blue}Depending on the needs one of two approaches can be considered while developing a mathematical model.
-A model, which is based on a multiple regression can be used if the relation between inputs and outputs can be simplified.
+	Depending on the needs one of two approaches can be considered while developing a mathematical model for the extraction process.
+A model, which is based on a multiple regression can be used if the relation between inputs and outputs is the only of interests.
 \citet{Sodeifian2017a} investigated an influence of pressure, temperature and particle size on the extraction efficiency of oil from dracocephalum kotschyi boiss seed.
 The second order polynomial model was applied to obtain the corresponding response surface and to identify the optimum operating conditions.
-	The study of \citet{Sodeifian2017b} investigates the of essential oil from Eryngium billardieri, focusing on optimizing extraction conditions and developing a mathematical model based on the f the second order polynomial to predict the process yield.
+	The study of \citet{Sodeifian2017b} investigates the of essential oil from Eryngium billardieri, focusing on optimizing extraction conditions and developing a mathematical model based on the second order polynomial to predict the process yield.
 The researchers employed a simulated annealing algorithm to optimize parameters such as pressure, temperature, and extraction time, aiming to maximize oil efficiency.
 
-	Alternatively, a more complex model can be derived and applied to cover not only the input-output relations, but the phenomena occurring in the system.
-This approach allows for more detailed representation the system behaviour, but requires better understanding of the mass transfer and more rigorous experiments.}
+	Alternatively, a first principle model can be derived and applied to cover not only the input-output relations, but the phenomena occurring in the system.
+This approach allows for more detailed representation the system behaviour, but requires deeper understanding of the underlying physics and more rigorous experiments.
 
@@
 
-	{\color{blue}The primary aim of this study is to analyse the influence of changes in operating conditions on the process model developed by \citet{Sliczniuk2024}.
+	The primary aim of this study is to analyse the influence of changes in operating conditions on the process model developed by \citet{Sliczniuk2024}.
 Understanding how variations in parameters and control variables affect the model's behaviour is essential for improving its accuracy, robustness, and practical applicability.
 To achieve this, a comprehensive sensitivity analysis is employed, serving as a systematic approach to assess the impact of model parameters and controls on the outputs.
-
 The results of this sensitivity analysis are valuable for multiple purposes.
@@
 Finally, the analysis can detect inconsistencies or errors by uncovering unexpected relationships between inputs and outputs, which may signal flaws in the model's assumptions or structure.
-}
 
@@
 
-	{\color{blue}The paper of \citet{Maly1996} addresses the development of numerical methods and software tools for sensitivity analysis in differential-algebraic equation systems.
-The paper discusses the mathematical foundations of the local sensitivity analysis methods employed, providing a thorough analysis of their performance.
-The authors presented variety of problems and to prove the efficient of their method.
+	The study by \citet{Maly1996} addressed the development of numerical methods and software tools for sensitivity analysis in differential-algebraic equation systems.
+It thoroughly examines the mathematical foundations of the local sensitivity analysis methods employed, providing an in-depth analysis of their performance.
+The authors presented a variety of problems to demonstrate the efficiency and applicability of their approach.
 
-	In his \citet{Turanyi1990} presents a comprehensive review of sensitivity analysis methods applied to spatially homogeneous, constant-parameter chemical kinetic systems.
-The work delves into various sensitivity analysis techniques, including concentration sensitivity, rate sensitivity, and feature sensitivity analysis.
-The paper explores practical applications of these methods in chemical kinetics, demonstrating their utility in understanding and predicting system behavior.
+	In a his work, \citet{Turanyi1990} presented a comprehensive review of sensitivity analysis methods for spatially homogeneous, constant-parameter chemical kinetic systems.
+This study explored a range of sensitivity analysis techniques, including concentration sensitivity, rate sensitivity, and feature sensitivity analysis.
+Practical applications of these methods in chemical kinetics were highlighted, showcasing their utility in understanding and predicting system behavior.
 
-	\citet{Fishtik1997} applied the local sensitivity analysis of an multiple chemical reaction system with several pure condensed phases and one ideal gas phase.
-It was shown that the system's response may be presented as a sum of contributions coming only from response equilibria defined by gas phase species.
-The effect of temperature, pressure and initial amounts of species is analyzed for gasification of coal.
+	\citet{Fishtik1997} applied local sensitivity analysis to a complex chemical reaction system involving multiple pure condensed phases and one ideal gas phase.
+The study demonstrated that the system's response could be expressed as a sum of contributions from equilibrium states defined by gas-phase species.
+The impact of temperature, pressure, and initial species amounts was specifically analyzed in the context of coal gasification.
 
-	\citet{Saltelli2005} provide a comprehensive review of sensitivity analysis methods applicable to chemical modeling.
-The authors discuss both local and global techniques, emphasizing the importance of global sensitivity analysis in understanding complex chemical systems.
-The manuscript highlight the role of variance-based methods, in quantifying the influence of input parameters on model outputs.
+	In their comprehensive review, \citet{Saltelli2005} examined sensitivity analysis methods applicable to chemical reaction modeling.
+They discussed both local and global techniques, emphasizing the role of global sensitivity analysis in understanding complex chemical systems.
+The authors highlighted the importance of variance-based methods in quantifying the influence of input parameters on model outputs by discussing results of a few simulation analysis.
 
 	Unlike previous studies, this work focuses on derivative-based local sensitivity analysis to evaluate the robustness and predictive accuracy of a mathematical model for chamomile oil extraction under varying operational conditions.
-The analysis specifically examines the impact of operating condition changes, providing new insights into model development and optimizing extraction performance.}
+The analysis specifically investigates the effects of changes in operating conditions, offering novel insights into model development and the optimization of extraction performance.
 
@@
 
-	where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the {\color{blue}axial dispersion coefficient}.
+	where $c_f$ represents the solute concentration in the fluid phase, $r_e$ is the mass transfer kinetic term and $D^M_e$ is the axial dispersion coefficient.
 
@@
 
-	{\color{blue}The choice between the two formulations should consider the system's properties and the underlying mass transfer assumptions.
+	The choice between the two formulations should consider the system's properties and the underlying mass transfer assumptions.
 In systems where external mass transfer dominates, the resistance to solute transport primarily occurs at the fluid-solid interface, typically governed by the diffusion of solute across the fluid boundary layer.
@@
 Conversely, when internal mass transfer dominates, the resistance to solute transport is controlled by diffusion or adsorption processes within the solid phase.
-In such cases, the Reverchon formulation is more suitable, as it accounts for deviations in the equilibrium through the term $c_s - c_s^*(c_f)$.}
+In such cases, the Reverchon formulation is more suitable, as it accounts for deviations in the equilibrium through the term $c_s - c_s^*(c_f)$.
 
@@
 
-	The method of lines is used to transform the process model equations into a set of ODEs denoted by $G(x;\Theta)$.
-The backward finite difference is used to approximate the first-order derivative, while the central difference scheme approximates the second-order derivative $z$ direction.
-The length of the fixed bed is divided into $N_z$, i.e.
-equally distributed points in the $z$ direction.
-The state-space model after discretization is denoted by $x$ and defined as follows:
-
+	\begin{figure}[!h]
+		\centering
 		{\footnotesize
-		\begin{align*} \label{discretization}
+			\begin{align*}
 				\dot{x} &= \cfrac{d x}{d t} = 
@@
 						G_{3N_z+2} \left( c_f,c_s,h; \Theta \right) 
-			\end{bmatrix}}_{G \left( x; \Theta \right),} 
+				\end{bmatrix}}_{G \left( x; \Theta \right)} 
 		\end{align*} }
-	where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.
+	\caption{Discretized state-space}
+	\label{fig:discretization}
+	\end{figure}
 
+	The method of lines is used to transform the process model equations into a set of ODEs denoted by $G(x;\Theta)$.
 For a derivative to be conservative, it must form a telescoping series.
@@
 Discretization is applied to the conservative form of the model to ensure mass conservation.
+The backward finite difference is used to approximate the first-order derivative, while the central difference scheme approximates the second-order derivative $z$ direction.
+The length of the fixed bed is divided into $N_z$, i.e.
+equally distributed points in the $z$ direction.
+The state-space model after discretization is denoted by $x$ and defined as follows the Figure \ref{fig:discretization}, where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.
 
@@
 
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
+		\caption{The effect of $P_{in}$ change on $C_s$.}
+		\label{fig:Sensitivty_P_CS}
+	\end{figure}
+
 	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of the solute concentration in the solid phase to pressure changes.
@@
 		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
-		\caption{The effect of $P_{in}$ change on $C_s$.}
-		\label{fig:Sensitivty_P_CS}
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
+		\caption{The effect of $P_{in}$ change on $C_f$.}
+		\label{fig:Sensitivty_P_CF}
 	\end{figure}
@@
 
-	\begin{figure}[!ht]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
-		\caption{The effect of $P_{in}$ change on $C_f$.}
-		\label{fig:Sensitivty_P_CF}
-	\end{figure}
-
 	Figure \ref{fig:Sensitivty_P_y} shows how sensitive the extraction yield is to pressure changes over an extended period for various pressure values.
@@
 
-	As presented in Figure \ref{fig:Sensitivty_P_y}, higher sensitivities are observed for a low-pressure system.
-At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction, as shown by data given by \citet{Sliczniuk2024}.
-Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield.
-Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity, and therefore to higher sensitivity of the system state-space.
-
 	\begin{figure}[!ht]
@@
 
-	{\color{blue}One disadvantage of using local sensitivity coefficients is that their reflect the absolute changes, which might be difficult to compare among other models or scenarios.
-The normalized local sensitivity coefficients, defined as $\tilde{S}(x;\Theta) = \frac{d G(x;\Theta)}{d\Theta} \frac{\Theta}{G(x;\Theta)}$, which can be interpreted as the percentage change in the output per percentage change in the parameter, making it a unitless.
-Although, the interpretation is straightforward it should be noted that extrapolation for large change of the parameter might leads to incorrect results.
-In the case of dynamic systems, the outcome of local sensitivity analysis quantifies how the state of the system or its output varies over time with respect to small perturbations in parameters.
-If the perturbation is too large, then the definition of a derivative (or sensitivity equations) does not hold unless the system is linear.
-Consequently, the conclusions can not be scaled up to any size of parameter perturbation.
-Such a property of the local sensitivity analysis, makes it difficult to recreate in a laboratory conditions due to finite precision of machines.
+	As presented in Figure \ref{fig:Sensitivty_P_y}, higher sensitivities are observed for a low-pressure system.
+At lower pressures, the supercritical fluid has lower density and solvating power, which results in less efficient extraction, as shown by data given by \citet{Sliczniuk2024}.
+Small changes in pressure at low pressures can significantly impact the solute's solubility and, consequently, the extraction yield.
+Moreover, near the critical point, small changes in pressure can lead to significant changes in the physical properties of the supercritical fluid, such as density and viscosity, and therefore to higher sensitivity of the system state-space.
+
+	\begin{figure}[!hb]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple_normalized.png}
+		\caption{The effect of $P_{in}$ change on $y(t)$ after normalization.}
+		\label{fig:Sensitivty_P_y_norm}
+	\end{figure}
+
+	One disadvantage of using local sensitivity coefficients is that they reflect absolute changes, which can be challenging to compare across different models or scenarios.
+To address this, normalized local sensitivity coefficients (defined as: $\tilde{S}(x;\Theta) = \frac{d G(x;\Theta)}{d\Theta} \frac{\Theta}{G(x;\Theta)}$) are used.
+They can be interpreted as the percentage change in the output per percentage change in the parameter.
+Their dimensionless nature makes the invariant under rescaling of model parameters.
 
@@
 After reaching their respective maxima, the sensitivity curves decrease as the concentration gradient driving the extraction diminishes over time.
-Ultimately, all curves approach zero, reflecting that all the solute was removed from the solid phase.}
+Ultimately, all curves approach zero, reflecting that all the solute was removed from the solid phase.
 
-	\begin{figure}[!ht]
-		\centering
-		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple_normalized.png}
-		\caption{The effect of $P_{in}$ change on $y(t)$ after normalization.}
-		\label{fig:Sensitivty_P_y_norm}
-	\end{figure}
+	While this interpretation of normalized sensitivities is straightforward, it is important to note that extrapolating for large parameter changes can lead to inaccurate results.In dynamic systems, local sensitivity analysis quantifies how the system state or output varies over time in response to small parameter perturbations.
+If the perturbation is large, the derivative-based definition of sensitivity (or sensitivity equations) becomes invalid unless the system is linear.
+Consequently, the conclusions from local sensitivity analysis cannot be reliably scaled to large parameter changes.
+This limitation makes reproducing of sensitivity results in laboratory conditions challenging, given the finite precision of experimental equipment.
 
@@
 Given that the results of the local sensitivity analysis depend on the operating point, the analysis was repeated at different pressures.
-
-	{\color{blue}The normalized sensitivity coefficients provide a basis for generalizing the discussion of the results and comparing the influence of various parameters.
+The normalized sensitivity coefficients provide a basis for generalizing the discussion of the results and comparing the influence of various parameters.
 The normalized sensitivity results were found to vary within the range of -0.17 to 0.6.
 The overall effect of each parameter can be evaluated by integrating the sensitivity curves.
-Similar to the analysis of yield sensitivity, the integration was performed using an extended simulation until all sensitivities approached zero.
+Similar to the analysis of yield sensitivity, the integration was performed over extended simulation time (until all sensitivities approached zero).
 The cumulative integral values at pressures of 100, 125, 150, 175, and 200 bars are 31487, 8548, 4462, 2825, and 1939, respectively.
 The positive sign of these values indicates that increased pressure enhances the extraction yield under all investigated operating conditions.
-The order of magnitude of the integrals allows to identify at which operating condtions the pressure increase is the most influential.}
+The order of magnitude of the integrals allows to identify at which operating condtions the pressure increase is the most influential.
 

### 2025-02-13 SFE_Sensitivity_Analysis_Chamomile/Approximation_of_the_deprature_function.m

@@ -1,8 +1,8 @@
 clc, close all
 clear all
 
-addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
-%addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-windows-matlabR2016a-v3.5.1');
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
 import casadi.*
 
 Parameters_table        = readtable('Parameters.csv') ;        % Table with prameters
@@ -22,7 +22,7 @@ g = Function('g',{[T, P]},{h});
 
 %% 2) Generate a grid of (T,P) and compute H.
 Tmin = 30+273;  Tmax = 50+273;
-Pmin = 80;      Pmax = 300;
+Pmin = 74;      Pmax = 300;
 nT   = 100;     nP   = 200;
 
 Tvec = linspace(Tmin, Tmax, nT);
@@ -53,34 +53,41 @@ gof
 figure('Name','Two Surfaces','Units','normalized','Position',[0.1 0.1 0.8 0.4]);
 
 % --- (a) Left plot: original surface H=f(T,P)
-subplot(1,3,1);
-surf(HH, PP, TT-273, 'EdgeColor','none');
-xlabel('H'); ylabel('P'); zlabel('T');
-title('Surface 1: H = f(T,P)');
-view(2);
-colormap jet; colorbar
+subplot(3,1,1);
+pcolor(HH, PP, TT-273, 'EdgeColor','none');
+xlabel('H [kJ/kg]'); ylabel('P [bar]');
+title('Solution of the enthalpy departure function');
+colormap jet; hcb=colorbar;
+hcb.Title.String = '$T~[^\circ C]$';
+hcb.Title.Interpreter = 'latex';
+hcb.TickLabelInterpreter = "latex";
 axis tight; grid off
 
 % --- (b) Right plot: fitted surface T ~ g(H,P)
-subplot(1,3,2);
+subplot(3,1,2);
 
 % Evaluate the fitted polynomial
-TTplot = surfaceFit(HH, PP);
+[TTplot] = reconstruct_T_polynomial_approximation(HH, PP);
+%TTplot = surfaceFit(HH, PP);
 
-surf(HH, PP, TTplot-273, 'EdgeColor','none');
-view(2)
-xlabel('H'); ylabel('P'); zlabel('T');
[…]

### 2025-02-13 SFE_Sensitivity_Analysis_Chamomile/reconstruct_T_polynomial_approximation.m

@@ -1,0 +1,5 @@
+function [T] = reconstruct_T_polynomial_approximation(H, P)
+
+    T = 190.1 + 0.04924.*H + 2.651.*P + 0.006511.*H.^2 + 0.01881.*H.*P + -0.001048.*P.^2 + 2.098e-05.*H.^3 + 4.062e-05.*H.^2.*P + 2.552e-06.*H.*P.^2 + 2.128e-06.*P.^3;
+
+end

### 2025-03-23 Article_Sensitivity_Analsysis-Chamomile.tex
23.03

@@
 	\renewcommand{\nomentryend}{\hspace*{\fill}#1}}
-
-\usepackage{csvsimple}
 
@@
 
-	Unlike previous studies, this work focuses on derivative-based local sensitivity analysis to evaluate the robustness and predictive accuracy of a mathematical model for chamomile oil extraction under varying operational conditions.
-The analysis specifically investigates the effects of changes in operating conditions, offering novel insights into model development and the optimization of extraction performance.
+	{\color{blue}A key novelty of this work lies in its rigorous application of derivative-based local sensitivity analysis to a first-principles model of supercritical fluid extraction, specifically targeting the extraction of chamomile oil.
+While numerous studies have developed empirical or semi-empirical models for supercritical extraction, many of these either omit local sensitivity analyses altogether or provide only basic parametric comparisons (\citet{Santos2000}, \citet{Fiori_2007} or \citet{Zahedi2010}).
+In contrast, the present approach integrates a quasi-1D partial-differential-equation model with automatic differentiation of the mass and energy balances, enabling a detailed exploration of how infinitesimal changes in operating parameters propagate through the system to influence solute concentrations and overall extraction yield.
+Although this work focus on the influence of pressure, the same methodology can be analysed any other parameter of control.
+Notably, this level of detail is crucial near the critical region of CO$_2$, where small deviations in process conditions can trigger large changes in solvent properties (such as density and solubility).
+This approach thus provides a systematic and quantitative measure of the system’s sensitivity to parameter fluctuations across different extraction regimes, from kinetic- to diffusion-controlled.}
 
@@
 			\label{Model_solid}
-			\cfrac{\partial c_s}{\partial t} = \underbrace{ r_e }_{\text{Kinetics}}
+			\cfrac{\partial c_s}{\partial t} = \underbrace{-r_e}_{\text{Kinetics}}
 	\end{equation} }
@@
 			\label{Model_kinetic_no_sat}
-			r_e = -\cfrac{D_i}{ \mu l^2 } \left(c_s - \cfrac{\rho_s c_f}{k_m \rho_f} \right)
+			r_e = \cfrac{D_i}{ \mu l^2 } \left(c_s - \cfrac{\rho_s c_f}{k_m \rho_f} \right)
 	\end{equation} }
@@
 		\begin{equation}
-			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right), \label{EQ: C_sat_function}
+			D_i = D_i^R \gamma(c_s) = D_i^R \exp \left( - \Upsilon \left( 1-\cfrac{ c_s }{c_{s0}} \right) \right), \label{EQ: C_sat_function}
 	\end{equation} }
@@
 
-	As explained in Section \ref{CH:Governing_equations_chapter}, this low velocity region pressure is nearly constant due to the small pressure wave propagation that occurs at the speed of sound.
-Under such conditions, the term $\partial P/\partial t$ can be approximated by a difference equation, describing the pressure change in the whole system.
-The pressure $P$ in the system is considered a state variable, while the pressure in the new time-step $P_{in}$ is considered a control variable.
+	{\color{blue}As explained in Section \ref{CH:Governing_equations_chapter}, the pressure in the low-velocity region remains nearly constant due to the small pressure wave propagation occurring at the speed of sound.
+Under such conditions, the term $\partial P/\partial t$ can be approximated by a forward difference equation, describing the pressure change over a small time step $\Delta t$.
+The pressure $P$ in the system is treated as a state variable, while the incoming pressure at the new time-step $P_{in}$ is treated as a control:}
 
@@
 
-	Such a simplified equation allows for instantaneous pressure change in the system but does not consider a gradual pressure build-up and the effects of pressure losses.
-In a real system, the dynamics of pressure change would depend on a pump and a back-pressure regulator.
+	{\color{blue}Such a simplified equation allows for instantaneous pressure.
+In a real system, the pressure dynamics would depend on the behaviour of the pump and the back-pressure regulator, which introduce additional inertia and resistance to pressure changes, leading to pressure gradual build-up.}
 
@@
 Sensitivity analysis shows how responsive the solution is to changes in the parameter $\Theta$.
-As discussed by \citet{Dickinson1976}, sensitivity analysis can be used to determine the influence of uncertainty on the solution of the original system.
+As discussed by \citet{Dickinson1976}, sensitivity analysis can be used to evaluate the influence of uncertainty on the solution of the original system.
 Another application of sensitivity analysis is to distinguish sensitive parameters from insensitive ones, which might be helpful for model reduction.
@@
 
-	The new system of equations can be obtained by taking the total derivative of $S$ with respect to time $t$:
+	{\color{blue}The sensitivity matrix $S(x;\Theta)$ represents how the state vector $x$ changes in response to variations in the model parameters $\Theta$.
+In physical terms, this means it measures how sensitive the system is to changes in the underlying parameters that define its behavior.} The new system of equations can be obtained by taking the total derivative of $S$ with respect to time $t$:
 
@@
 
-	Sensitivity Equation \ref{SA_eq_full} can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}:
+	{\color{blue}This equation describes how the sensitivity of the system evolves over time.
+It shows that the time derivative of the sensitivity matrix depends on how the system dynamics (represented by $G(x; \Theta)$ change with respect to the parameters.} Sensitivity Equation \ref{SA_eq_full} can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}:
 
@@
 
-	The Jacobian ${\bar{J}_x}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${\bar{J}_x}(n_x,n_x)$ is the derivative of $G_{n_x}(x;\Theta)$ with respect to the state variable $x_{n_\Theta}$:
+	{\color{blue}This equation decomposes the total effect of parameter changes on the system dynamics into two parts.
+The indirect effect represented by the term involving $\bar{J}_x (x; \Theta)$ This term shows how changes in the parameters influence the system through their effect on the state variables.
+This is an indirect feedback effect where parameter changes alter the state, which in turn affects the system response.
+The direct effect given by $\bar{J}_x (x; \Theta)$ reflects the immediate sensitivity of the system to parameter variations.}
+
+	Matrix ${\bar{J}_x}(x;\Theta)$ and $\bar{S}(x;\Theta)$ describe the indirect influence of $\Theta_{n_\Theta}$ on the state space.
+The Jacobian ${\bar{J}_x}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${\bar{J}_x}(n_x,n_x)$ is the derivative of $G_{n_x}(x;\Theta)$ with respect to the state variable $x_{n_\Theta}$.
+{\color{blue}This is the Jacobian matrix with respect to the state vector, which measures how the system’s dynamics change with changes in the state itself.}
 
@@
 	The sensitivity matrix $\bar{S}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each entry $\bar{S}(n_x,n_\Theta)$ is the derivative of state variable $x_{n_x}$ with respect to parameter $\Theta_{n_\Theta}$.
-Matrix ${\bar{J}_x}(x;\Theta)$ and $\bar{S}(x;\Theta)$ describe the indirect influence of $\Theta_{n_\Theta}$ on the state space.
+{\color{blue}The sensitivity matrix $\bar{S}(x;\Theta)$ measures how the state variables respond to parameter changes.}
 
@@
 
+	{\color{blue}}
+
 	The augmented system containing the original set of equations $G(x;\Theta)$ and sensitivity equations is called ${\textbf{G}}\left(x;\Theta\right)$.
@@
 	\end{align} }
+
+	{\color{blue}The augmented system combines both the state equations and sensitivity equations into a unified system.
+This allows the simultaneous computation of both the system behavior and its sensitivity to parameter changes.}
 
@@
 
+	{\color{blue} The sensitivity starts at zero because the system initially has no variation with respect to the parameters.}
+
 	% ===================================================
@@
 The process model was validated in the following range of operating conditions: temperatures between $30 - 40 ^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
-The sensitivity analysis is performed at the midpoint of the validated range: $35 ^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
-This study examines the impact of pressure change on the state space and extraction yield through local sensitivity analysis.
-The local sensitivity analysis results can be interpreted as the system's response to an infinitesimal deviation in pressure.
+This study examines the impact of parameter change on the state space and extraction yield through local sensitivity analysis.
+The local sensitivity analysis results can be interpreted as the system's response to an infinitesimal deviation in parameters.
+{\color{blue}This work focus on two selected cases, but the same analysis can be extended to any other model parameter.
+The first case corresponds to the analysis of empirical correlations on the process model.
+The zero'th order term (denoted as $\Upsilon(0)$) of the multiple linear regression for $\Upsilon$ was selected.
+The second case corresponds to the investigation of the operating condition on the state-space.
+Particularly, on the influence of pressure variations on the model output.
+The first analysis is performed at the midpoint of the validated range: $35 ^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
+The second analysis is splitted into two sub-analysis.
+The influence of the pressure change on the state-variables (concnetration of the solute in the sold and fluid phases) are considered at the midpoint of the validated range.
+The yield analysis is conducted at the same tempature and mass flow-rate conditions but at different values of pressure (100, 125, 150, 175 and 200 bar).}
 
+	\subsection{$\Upsilon$ case}
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_gamma.png}
+		\caption{The effect of $P_{in}$ change on $C_s$}
+		\label{fig:Sensitivty_Gamma_CS}
+	\end{figure}
+
+	The $\Upsilon$ term corresponds to the curvature of decay function $\gamma$, and can be associated with uneven distribution of the solute in the solid particle.
+As the zero'th order term is not directly affect by independent variables, it physical interpretation becomes straight forward.
+The increment of the term makes the exponential decay more steep, which means that the $D_i^R$ is multiplied by a smaller number, hence it is expected to observe slower extraction rate.
+
+	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of the solute concentration in the solid phase to change into zero'th order term in the equation for $\Upsilon$.
+As discussed by \citet{Sliczniuk2024}, the system is far from the saturation point, which indicates that the concentration gradient is controlled mainly by $c_s$.
+Considering that, the extraction kinetic term act as independent on $c_f$, which explain why Figure \ref{fig:Sensitivty_P_CS} shows a uniform response in solid phase.
+The positive value of $\frac{dc_s}{d\Upsilon(0)}$ can be interpreted as an slower loss of the solute from particles and is observed when the extraction slows down.
+
+	\subsection{Pressure case}
 	As discussed in Section \ref{CH:Governing_equations_chapter}, at low velocity, the fluid can be treated as incompressible, which results in the instant propagation of pressure throughout the system, enabling a single pressure value to be considered for the entire system.
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
-		\caption{The effect of $P_{in}$ change on $C_s$.}
+		\caption{The effect of $P_{in}$ change on $C_s$}
 		\label{fig:Sensitivty_P_CS}
@@
 As discussed in Section \ref{CH: Continuity}, the velocity of a fluid is inversely proportional to its density, indicating that increased pressure reduces the fluid velocity.
-This results in an extended residence time, allowing for longer interaction between the solute and solvent.	Initially, the extraction process operates in the kinetic-controlled regime, where the concentration gradient is high, and solute solubility is the limiting factor.
+This results in an extended residence time, allowing for longer interaction between the solute and solvent.
+Initially, the extraction process operates in the kinetic-controlled regime, where the concentration gradient is high, and solute solubility is the limiting factor.
 As noted by \citet{Sliczniuk2024}, the system is considered far from saturation, which explains the low initial system response.
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
-		\caption{The effect of $P_{in}$ change on $C_f$.}
+		\caption{The effect of $P_{in}$ change on $C_f$}
 		\label{fig:Sensitivty_P_CF}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield.png}
-		\caption{The effect of $P_{in}$ change on $y(t)$.}
+		\caption{The effect of $P_{in}$ change on $y(t)$}
 		\label{fig:Sensitivty_P_y}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple_normalized.png}
-		\caption{The effect of $P_{in}$ change on $y(t)$ after normalization.}
+		\caption{The effect of $P_{in}$ change on $y(t)$ after normalization}
 		\label{fig:Sensitivty_P_y_norm}
@@
 Similar to the analysis of yield sensitivity, the integration was performed over extended simulation time (until all sensitivities approached zero).
-The cumulative integral values at pressures of 100, 125, 150, 175, and 200 bars are 31487, 8548, 4462, 2825, and 1939, respectively.
+The values of cumulative integral are presented in Table \ref{table:Cumulative_integral}.
 The positive sign of these values indicates that increased pressure enhances the extraction yield under all investigated operating conditions.
 The order of magnitude of the integrals allows to identify at which operating condtions the pressure increase is the most influential.
+
+	\begin{table}[h!]
+		\adjustbox{max width=\columnwidth}{%
+		\centering
+		\begin{tabular}{|l| c c c c c|} 
+			\hline
+			Pressure case & 100 & 125 & 150 & 175 & 200 \\ 
+			\hline
+			Initial normalized sensitivity & 0.25 & -0.08 & -0.13 & -0.15 & -0.17 \\ 
+			Max normalized sensitivity & 0.52 & 0.28 & 0.18 & 0.15 & 0.13 \\ 
+			Cumulative integral & 31487 & 8548 & 4462 & 2825 & 1939 \\ 
+			\hline
+		\end{tabular} }
+		\caption{Values of the cumulative integral of the yield sensitivity}
+		\label{table:Cumulative_integral}
+	\end{table}
+
+	{\color{blue}The findings of this work are particularly valuable for industrial-scale supercritical extraction processes, where achieving both operational efficiency and product quality can be challenging.
+The local sensitivity analysis demonstrates that even small adjustments in operating parameters can yield disproportionately large improvements in extraction rates, especially near the fluid’s critical point.
+By quantifying how parameter variations affect the model states, the high-efficiency operating setpoints can be identified.
+Moreover, linking local sensitivity analysis to numerical optimization establishes a systematic framework for industrial process design and scale-up.
+Rather than relying heavily on trial-and-error or resource-intensive pilot studies, the model-based approach can be used to pre-identify the region of interests.
+This approach reduces both the time and material costs needed to reach profitable extraction rates, moving industrial operations toward cost-effective production.}
 

### 2025-03-23 SFE_Sensitivity_Analysis_Chamomile/main_Sensitivity_Analysis_Chamomile_Di.m

@@ -1,0 +1,235 @@
+startup;
+delete(gcp('nocreate'));
+% %p = Pushbullet(pushbullet_api);
+
+%addpath('C:\Dev\casadi-3.6.3-windows64-matlab2018b');
+addpath('\\home.org.aalto.fi\sliczno1\data\Documents\casadi-3.6.3-windows64-matlab2018b');
+import casadi.*
+
+%% Load paramters
+m_total                 = 3.0;
+
+% Bed geometry
+before                  = 0.04;                                             % Precentage of length before which is empty
+bed                     = 0.92;                                             % Percentage of length occupied by fixed bed
+
+% Set time of the simulation
+PreparationTime         = 0;
+ExtractionTime          = 1.5e4;
+timeStep                = 0.1;                                                % Minutes
+
+simulationTime          = PreparationTime + ExtractionTime;
+
+timeStep_in_sec         = timeStep * 60;                                    % Seconds
+Time_in_sec             = (timeStep:timeStep:simulationTime)*60;            % Seconds
+Time                    = [0 Time_in_sec/60];                               % Minutes
+
+N_Time                  = length(Time_in_sec);
+
+%%
+name_v = {'T_{in}', 'P'     , 'F'                                   };
+name_s = {'c_f'   , 'c_s'   , '(h\times\rho)' , 'P_{t-1}'     , 'y' };
+name_p = {'CF'    , 'CS'    , 'H'             , 'P_{in}'      , 'Y' };
+
+My_Font = 17;
+num_levels = 100;
+
+Parameters_table        = readtable('Parameters.csv') ;                     % Table with prameters
+Parameters              = num2cell(Parameters_table{:,3});                  % Parameters within the model + (m_max), m_ratio, sigma
+
+LabResults              = xlsread('wpd_datasets.xlsx');
+which_dataset           = 4;
+
+SAMPLE                  = LabResults(21:34,1);
+data_org                = LabResults(21:34,which_dataset+1)';
+
+%% Specify parameters to estimate
+nstages                 = Parameters{1};
+
+nstagesbefore           = 1:floor(before*nstages);
+nstagesbed              = nstagesbefore(end)+1 : nstagesbefore(end) + floor(bed*nstages);
[…]

### 2025-03-29 Article_Sensitivity_Analsysis-Chamomile.tex
29.03

@@
 
+	One disadvantage of using local sensitivity coefficients is that they reflect absolute changes, which can be challenging to compare across different models or scenarios.
+To address this, normalized local sensitivity coefficients (defined as: $\tilde{S}(x;\Theta) = \frac{d G(x;\Theta)}{d\Theta} \frac{\Theta}{G(x;\Theta)}$) are introduced.
+They can be interpreted as the percentage change in the output per percentage change in the parameter.
+Their dimensionless nature makes the invariant under rescaling of model parameters.
+
 	% ===================================================
@@
 The local sensitivity analysis results can be interpreted as the system's response to an infinitesimal deviation in parameters.
-{\color{blue}This work focus on two selected cases, but the same analysis can be extended to any other model parameter.
+{\color{blue}This work focus on two selected cases, but the same methodology can be extended to any other model parameter.
 The first case corresponds to the analysis of empirical correlations on the process model.
-The zero'th order term (denoted as $\Upsilon(0)$) of the multiple linear regression for $\Upsilon$ was selected.
+The zero'th order term of the multiple linear regression for $\Upsilon$ (denoted as $\Upsilon(0)$) was selected.
 The second case corresponds to the investigation of the operating condition on the state-space.
@@
 The first analysis is performed at the midpoint of the validated range: $35 ^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
-The second analysis is splitted into two sub-analysis.
-The influence of the pressure change on the state-variables (concnetration of the solute in the sold and fluid phases) are considered at the midpoint of the validated range.
-The yield analysis is conducted at the same tempature and mass flow-rate conditions but at different values of pressure (100, 125, 150, 175 and 200 bar).}
+The second analysis is split into two steps.
+First, the influence of the pressure change on the state-variables (concentration of the solute in the sold and fluid phases) are considered at the midpoint of the validated range.
+Secondly, the yield analysis is conducted at the same temperature and mass flow-rate conditions but at different values of pressure (100, 125, 150, 175 and 200 bar).}
 
@@
 
+	{\color{blue}The $\Upsilon$ term describes the curvature of decay function $\gamma$, and can be associated with uneven distribution of the solute in solid particles.
+As the zero'th order term is not directly affect by independent variables (as it represents the intercept), it physical interpretation becomes straight forward.
+The increment $\Upsilon(0)$ makes the $\gamma$ steeper, which means that the $D_i^R$ is multiplied by a smaller number, hence it is expected to observe slower extraction rate.
+
 	\begin{figure}[!ht]
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_gamma.png}
-		\caption{The effect of $P_{in}$ change on $C_s$}
+		\caption{The effect of $\Upsilon(0)$ change on $c_s$}
 		\label{fig:Sensitivty_Gamma_CS}
@@
 
-	The $\Upsilon$ term corresponds to the curvature of decay function $\gamma$, and can be associated with uneven distribution of the solute in the solid particle.
-As the zero'th order term is not directly affect by independent variables, it physical interpretation becomes straight forward.
-The increment of the term makes the exponential decay more steep, which means that the $D_i^R$ is multiplied by a smaller number, hence it is expected to observe slower extraction rate.
-
-	Figure \ref{fig:Sensitivty_P_CS} illustrates the sensitivity of the solute concentration in the solid phase to change into zero'th order term in the equation for $\Upsilon$.
+	Figure \ref{fig:Sensitivty_Gamma_CS} illustrates the sensitivity of the solute concentration in the solid phase to change into zero'th order term in the equation for $\Upsilon$.
 As discussed by \citet{Sliczniuk2024}, the system is far from the saturation point, which indicates that the concentration gradient is controlled mainly by $c_s$.
-Considering that, the extraction kinetic term act as independent on $c_f$, which explain why Figure \ref{fig:Sensitivty_P_CS} shows a uniform response in solid phase.
+Consequently, the extraction kinetic term act as independent on $c_f$, which explain a uniform response in solid phase visible in Figure \ref{fig:Sensitivty_Gamma_CS}.
 The positive value of $\frac{dc_s}{d\Upsilon(0)}$ can be interpreted as an slower loss of the solute from particles and is observed when the extraction slows down.
+Due to lower reaction rate more solute stays in the particles, but as the time approach infinity the solute will be washed out from the solid matrix.
+Consequently, it is expected to observed $\frac{dc_s}{d\Upsilon(0)}$ reaching a maximum and asymptotically diminish to zero.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_gamma.png}
+		\caption{The effect of $\Upsilon(0)$ change on $c_f$}
+		\label{fig:Sensitivty_Gamma_CF}
+	\end{figure}
+
+	Figure \ref{fig:Sensitivty_Gamma_CF} illustrates the sensitivity of the solute concentration in the fluid phase with respect to change into zero'th order term in the equation for $\Upsilon$.
+As previously discussed, the extraction rate slowed down due to change of $\Upsilon(0)$ uniformly along the spatial domain.
+Consequently, the amount of delivered to the fluid phase is reduced by the same quantity along the spatial domain.
+That leads to decrease of the solute concentration $c_f$ in the fluid phase, which is characterized by negative sign of the $\frac{dc_f}{d\Upsilon(0)}$.
+The spatial distribution of $\frac{dc_f}{d\Upsilon(0)}$ in the figure is non-uniform, reflecting the effects of advection.
+Due to mass conservation, the remaining solute will reach the solid-fluid interface slower hence it is expected to observe a little positive values of $\frac{dc_f}{d\Upsilon(0)}$ in the later stage of extraction.
+Eventually it is expected to see sensitivities reaching zero asymptotically.
+
+	\begin{figure}[!ht]
+		\centering
+		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_gamma.png}
+		\caption{The effect of $\Upsilon(0)$ change on $c_f$}
+		\label{fig:Sensitivty_Gamma_Y}
+	\end{figure}
+
+	Figure \ref{fig:Sensitivty_Gamma_Y} show the normalized sensitivity curve of with respect to the yield.
+Due to slower extraction rate, the sensitivity curve is characterized by negative sign.
+The drop of the sensitivity curve can be interpreted as less solute coming out of the extractor if compared with the reference case.
+Then the sensitivity curve reach minimum, which can be also visible in Figure \ref{fig:Sensitivty_Gamma_CF}.
+Eventually, the remaining solute is released to the fluid phase and the sensitivity curve reach asymptotically zero.
+When the sensitivity function of a dynamic system approaches zero as time goes to infinity and remains at that value, it indicates that the system's long-term behavior becomes independent of the parameter in question.
+The parameter has only influence for the system's transient dynamics, it has no effect on the steady-state solution.
+This means that after the system has settled, variations in that parameter do not affect the final output.
+In terms of SFE, it means that all the solute has been removed from the system.}
 
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
-		\caption{The effect of $P_{in}$ change on $C_s$}
+		\caption{The effect of $P_{in}$ change on $c_s$}
 		\label{fig:Sensitivty_P_CS}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
-		\caption{The effect of $P_{in}$ change on $C_f$}
+		\caption{The effect of $P_{in}$ change on $c_f$}
 		\label{fig:Sensitivty_P_CF}
@@
 	\end{figure}
-
-	One disadvantage of using local sensitivity coefficients is that they reflect absolute changes, which can be challenging to compare across different models or scenarios.
-To address this, normalized local sensitivity coefficients (defined as: $\tilde{S}(x;\Theta) = \frac{d G(x;\Theta)}{d\Theta} \frac{\Theta}{G(x;\Theta)}$) are used.
-They can be interpreted as the percentage change in the output per percentage change in the parameter.
-Their dimensionless nature makes the invariant under rescaling of model parameters.
 
@@
 This work implemented automatic differentiation to derive the sensitivity equations.
-The results of the local sensitivity analysis and model specific and consider only a small region of parameter space, and the conclusions derived from such an analysis are limited to local conditions.
-
-	Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of pressure.
+The results of the local sensitivity analysis are model specific and consider only a small region of parameter space, so the conclusions derived from such an analysis are limited to local conditions.
+Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of parameters of the empirical correlation and operating conditions on the state-space.
+
+	{\color{blue}The motivation behind perform sensitivity analysis model validation and evaluation of parameters effect on the model output.
+By analysis the influence of parameters potential modelling errors and unfeasible behaviours can be identified.
+This is particularly useful technique, when introducing an empirical correlation.
+In this work, the influence of the intersect from the empirical correlation for $\Upsilon$ was tested.
+As expected, the analysis showed that increment of $\Upsilon(0)$ slows down the extraction rate, leading to negative values of $\frac{dc_s}{d\Upsilon(0)}$ and $\frac{dc_s}{d\Upsilon(0)}$, and alternating values of $\frac{dc_f}{d\Upsilon(0)}$.
+The physical interpretation of the $\Upsilon(0)$ match obtained results.
+The effect of the parameter change can be summarized by extreme and final values of the normalized sensitivity of the output (0.47 and 0, respectively).}
+
+	pressure.
 Under the selected operating conditions, it was observed for all the cases that a pressure increment enhances mass transfer, leading to a faster mass transfer of solute from the particles.

### 2025-03-30 Article_Sensitivity_Analsysis-Chamomile.tex
30.03

@@
 
-	{\color{blue}A key novelty of this work lies in its rigorous application of derivative-based local sensitivity analysis to a first-principles model of supercritical fluid extraction, specifically targeting the extraction of chamomile oil.
-While numerous studies have developed empirical or semi-empirical models for supercritical extraction, many of these either omit local sensitivity analyses altogether or provide only basic parametric comparisons (\citet{Santos2000}, \citet{Fiori_2007} or \citet{Zahedi2010}).
-In contrast, the present approach integrates a quasi-1D partial-differential-equation model with automatic differentiation of the mass and energy balances, enabling a detailed exploration of how infinitesimal changes in operating parameters propagate through the system to influence solute concentrations and overall extraction yield.
-Although this work focus on the influence of pressure, the same methodology can be analysed any other parameter of control.
+	{\color{blue}A key novelty of this work lies in its rigorous application of derivative-based local sensitivity analysis to a first-principles model of supercritical fluid extraction.
+While multiple publications available in the literature discuss application of sensitivity analysis on a supercritical extraction model, many of these either omit local sensitivity analyses and focus on basic parametric comparisons (\citet{Santos2000}, \citet{Fiori_2007} or \citet{Zahedi2010}).
+In contrast, the present approach integrates a quasi-1D partial-differential-equation model with automatic differentiation of the mass and energy balances, enabling a detailed exploration of how infinitesimal changes in parameters, which propagates propagate through the system.
+As the result, corresponding system response of the state space (with emphasis on solutes concentrations on solid and liquid phase as well as yield).
+Although this work focus on the influence of a few selected parameters, the same methodology can be extended to any other parameter.
 Notably, this level of detail is crucial near the critical region of CO$_2$, where small deviations in process conditions can trigger large changes in solvent properties (such as density and solubility).
@@
 			\label{Model_kinetic}
-			r_e = -\cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
+			r_e = \cfrac{D_i^R \gamma }{ \mu l^2 } \left( c_s  - \cfrac{\rho_s c_f }{ k_m \rho_f }  \right)
 	\end{equation} }
@@
 	\section{Results} \label{CH: Results}
-	The details of the process model and parameters are provided in \citet{Sliczniuk2024}.
-The process model was validated in the following range of operating conditions: temperatures between $30 - 40 ^\circ C$, pressures between $100 - 200$ bar, and mass flow rates between $3.33-6.67 \cdot 10^{-5}$ kg/s.
-This study examines the impact of parameter change on the state space and extraction yield through local sensitivity analysis.
-The local sensitivity analysis results can be interpreted as the system's response to an infinitesimal deviation in parameters.
-{\color{blue}This work focus on two selected cases, but the same methodology can be extended to any other model parameter.
-The first case corresponds to the analysis of empirical correlations on the process model.
-The zero'th order term of the multiple linear regression for $\Upsilon$ (denoted as $\Upsilon(0)$) was selected.
-The second case corresponds to the investigation of the operating condition on the state-space.
-Particularly, on the influence of pressure variations on the model output.
-The first analysis is performed at the midpoint of the validated range: $35 ^\circ C$, 150 bar and 5 $\cdot 10^{-5}$ kg/s.
-The second analysis is split into two steps.
-First, the influence of the pressure change on the state-variables (concentration of the solute in the sold and fluid phases) are considered at the midpoint of the validated range.
-Secondly, the yield analysis is conducted at the same temperature and mass flow-rate conditions but at different values of pressure (100, 125, 150, 175 and 200 bar).}
+	Details of the process model and its parameters can be found in \citet{Sliczniuk2024}.
+The model was validated under the following operating conditions: temperatures from $30$ to $40 ^\circ C$, pressures from $100$ to $200$ bar, and mass flow rates from $3.33$ to $6.67 \cdot 10^{-5}$ kg/s.
+In this study, the local sensitivity analysis is used to investigate how changes in model parameters affect the state space and extraction yield, where the results reflect the system’s response to infinitesimal deviations in parameter values.
+Although this work focuses on two specific cases, the methodology can be extended to any model parameter.
+The first case assesses the empirical correlations embedded in the process model, specifically the zeroth-order term $\Upsilon(0)$ in the multiple linear regression for $\Upsilon$.
+The second case examines the effect of operating conditions, particularly pressure, on the state space and model outputs.
+For the first analysis, the midpoint of the validated range ($35 ^\circ C$, $150$ bar and $5\cdot 10^{-5}$) was selected.
+The second analysis is carried out in two steps.
+First, we examine the impact of pressure changes on the state variables (solute concentrations in both solid and fluid phases) at the same midpoint conditions.
+Second, we perform a yield analysis at the same temperature and mass flow rate, but at different pressures (100, 125, 150, 175, and 200 bar).
 
@@
 
-	{\color{blue}The $\Upsilon$ term describes the curvature of decay function $\gamma$, and can be associated with uneven distribution of the solute in solid particles.
-As the zero'th order term is not directly affect by independent variables (as it represents the intercept), it physical interpretation becomes straight forward.
-The increment $\Upsilon(0)$ makes the $\gamma$ steeper, which means that the $D_i^R$ is multiplied by a smaller number, hence it is expected to observe slower extraction rate.
+	{\color{blue}The $\Upsilon$ term characterizes the curvature of the decay function $\gamma$ and can be associated with the uneven distribution of solute within solid particles.
+Because the zeroth-order term ($\Upsilon(0)$) corresponds to an intercept rather than depending on independent variables, its physical interpretation is straightforward.
+Increasing $\Upsilon(0)$ steepens $\gamma$, which means $D_i^R$ is multiplied by a smaller factor and the extraction rate consequently slows down.
 
@@
 Consequently, the extraction kinetic term act as independent on $c_f$, which explain a uniform response in solid phase visible in Figure \ref{fig:Sensitivty_Gamma_CS}.
-The positive value of $\frac{dc_s}{d\Upsilon(0)}$ can be interpreted as an slower loss of the solute from particles and is observed when the extraction slows down.
-Due to lower reaction rate more solute stays in the particles, but as the time approach infinity the solute will be washed out from the solid matrix.
+The positive value of $\frac{dc_s}{d\Upsilon(0)}$ can be interpreted as a slower loss of the solute from particles and is observed when the extraction slows down.
+Because of the lower reaction rate, more solute remains in the particles initially, however, as time approaches infinity, the solute eventually diffuses out of the solid matrix.
 Consequently, it is expected to observed $\frac{dc_s}{d\Upsilon(0)}$ reaching a maximum and asymptotically diminish to zero.
@@
 	Figure \ref{fig:Sensitivty_Gamma_CF} illustrates the sensitivity of the solute concentration in the fluid phase with respect to change into zero'th order term in the equation for $\Upsilon$.
-As previously discussed, the extraction rate slowed down due to change of $\Upsilon(0)$ uniformly along the spatial domain.
-Consequently, the amount of delivered to the fluid phase is reduced by the same quantity along the spatial domain.
-That leads to decrease of the solute concentration $c_f$ in the fluid phase, which is characterized by negative sign of the $\frac{dc_f}{d\Upsilon(0)}$.
+As previously discussed, the extraction rate slowed down due to increase of $\Upsilon(0)$ uniformly along the spatial domain.
+	Consequently, the solute delivered to the fluid phase decreases by an equal amount everywhere, causing a reduction in $c_f$, as indicated by the negative sign of  $\frac{dc_f}{d\Upsilon(0)}$.
 The spatial distribution of $\frac{dc_f}{d\Upsilon(0)}$ in the figure is non-uniform, reflecting the effects of advection.
-Due to mass conservation, the remaining solute will reach the solid-fluid interface slower hence it is expected to observe a little positive values of $\frac{dc_f}{d\Upsilon(0)}$ in the later stage of extraction.
+Due to mass conservation, the remaining solute reach the solid-fluid interface  more slowly hence it is expected to observe a little positive values of $\frac{dc_f}{d\Upsilon(0)}$ in the later stage of extraction.
 Eventually it is expected to see sensitivities reaching zero asymptotically.
@@
 
-	Figure \ref{fig:Sensitivty_Gamma_Y} show the normalized sensitivity curve of with respect to the yield.
+	Figure \ref{fig:Sensitivty_Gamma_Y}  shows the normalized sensitivity of the yield with respect to $\Upsilon(0)$.
 Due to slower extraction rate, the sensitivity curve is characterized by negative sign.
-The drop of the sensitivity curve can be interpreted as less solute coming out of the extractor if compared with the reference case.
-Then the sensitivity curve reach minimum, which can be also visible in Figure \ref{fig:Sensitivty_Gamma_CF}.
-Eventually, the remaining solute is released to the fluid phase and the sensitivity curve reach asymptotically zero.
-When the sensitivity function of a dynamic system approaches zero as time goes to infinity and remains at that value, it indicates that the system's long-term behavior becomes independent of the parameter in question.
+The  downward trend of the sensitivity curve can be interpreted as less solute coming out of the extractor if compared with the reference case.
+The curve then reaches a negative minimum (also visible in Figure \ref{fig:Sensitivty_Gamma_Y}) before the remaining solute is eventually released to the fluid phase, causing the sensitivity to approach zero asymptotically.
+When the sensitivity function of a dynamic system approaches zero as time goes to infinity and remains at that value, it indicates that the system's long-term behaviour becomes independent of the parameter.
 The parameter has only influence for the system's transient dynamics, it has no effect on the steady-state solution.
@@
 
-	{\color{blue}The motivation behind perform sensitivity analysis model validation and evaluation of parameters effect on the model output.
-By analysis the influence of parameters potential modelling errors and unfeasible behaviours can be identified.
+	{\color{blue}The motivation for performing sensitivity analysis is to validate the model and evaluate how parameter variations affect its outputs By analysis the influence of parameters, potential modelling errors and unfeasible behaviours can be identified.
 This is particularly useful technique, when introducing an empirical correlation.
-In this work, the influence of the intersect from the empirical correlation for $\Upsilon$ was tested.
-As expected, the analysis showed that increment of $\Upsilon(0)$ slows down the extraction rate, leading to negative values of $\frac{dc_s}{d\Upsilon(0)}$ and $\frac{dc_s}{d\Upsilon(0)}$, and alternating values of $\frac{dc_f}{d\Upsilon(0)}$.
-The physical interpretation of the $\Upsilon(0)$ match obtained results.
+In this work, the influence of the selected parameter from the empirical correlation for $\Upsilon$ was assessed.
+As expected, the analysis showed that increment of $\Upsilon(0)$ slows down the extraction rate, leading to negative values of $\frac{dc_s}{d\Upsilon(0)}$ and $\frac{dy}{d\Upsilon(0)}$, and alternating values of $\frac{dc_f}{d\Upsilon(0)}$.
+These findings align with the physical interpretation of $\Upsilon(0)$.
 The effect of the parameter change can be summarized by extreme and final values of the normalized sensitivity of the output (0.47 and 0, respectively).}
 
-	pressure.
-Under the selected operating conditions, it was observed for all the cases that a pressure increment enhances mass transfer, leading to a faster mass transfer of solute from the particles.
-Consequently, negative sensitivities can be observed in the diagram for the solid phase.
-The corresponding response in the fluid phase is characterized by positive-valued sensitivities, indicating that a greater amount of solute is transported into the fluid phase.
+	The second analysis was to examine influence of operating conditions on the SFE model, particularly the pressure effect.
+Given that the results of the local sensitivity analysis depend on the operating point, the analysis was conducted at different pressures.
+For all the investigated operating conditions, it was observed that the pressure increment enhanced mass transfer, leading to a faster mass transfer of solute from the particles.
+Consequently, negative sensitivities can be observed in sensitivity diagrams for the solid phase.
+The corresponding response in the fluid phase is characterized by positive-valued sensitivities, indicating that higher quantity of solute is transported into the fluid phase.
 As a result, the extraction yield is improved and characterized by positive sensitivities.
-Given that the results of the local sensitivity analysis depend on the operating point, the analysis was repeated at different pressures.
-The normalized sensitivity coefficients provide a basis for generalizing the discussion of the results and comparing the influence of various parameters.
-The normalized sensitivity results were found to vary within the range of -0.17 to 0.6.
-The overall effect of each parameter can be evaluated by integrating the sensitivity curves.
-Similar to the analysis of yield sensitivity, the integration was performed over extended simulation time (until all sensitivities approached zero).
-The values of cumulative integral are presented in Table \ref{table:Cumulative_integral}.
-The positive sign of these values indicates that increased pressure enhances the extraction yield under all investigated operating conditions.
-The order of magnitude of the integrals allows to identify at which operating condtions the pressure increase is the most influential.
+To compare the influence of various pressures, normalized sensitiviy coefficients were used, showing values between -$0.17$ and $0.6$.
+The overall effect of each parameter was assessed by integrating the yield sensitivity curves over extended simulation time (until all sensitivities approached zero).
+Table \ref{table:Cumulative_integral} presents the resulting cumulative integrals as well as initial and max values of the normalized sensitivity coefficients.
+The positive sign of the cumulative integrals confirm that increasing pressure improve the extraction yield under all investigated conditions.
+The relative magnitudes of these integrals indicate at which operating conditions are most affected by pressure variations are the most influential.
 
@@
 	{\color{blue}The findings of this work are particularly valuable for industrial-scale supercritical extraction processes, where achieving both operational efficiency and product quality can be challenging.
-The local sensitivity analysis demonstrates that even small adjustments in operating parameters can yield disproportionately large improvements in extraction rates, especially near the fluid’s critical point.
+The local sensitivity analysis demonstrates that even small adjustments in operating parameters can yield disproportionately large effects on extraction rates, especially near the fluid’s critical point.
 By quantifying how parameter variations affect the model states, the high-efficiency operating setpoints can be identified.
@@
 
-	It can be concluded that the system responses at low pressures were stronger than those at higher pressures.
-This behaviour can be explained by the rapid changes in solvent properties occurring near the critical point of CO$_2$.
-
 	\section*{Acknowledgements} 
@@
 	%\clearpage
-	%\newpage
+	\newpage
 	%\bibliographystyle{model1-num-names}

### 2025-05-21 Article_Sensitivity_Analsysis-Chamomile.tex
21.05

@@
 
-	{\color{blue}A key novelty of this work lies in its rigorous application of derivative-based local sensitivity analysis to a first-principles model of supercritical fluid extraction.
+	A key novelty of this work lies in its rigorous application of derivative-based local sensitivity analysis to a first-principles model of supercritical fluid extraction.
 While multiple publications available in the literature discuss application of sensitivity analysis on a supercritical extraction model, many of these either omit local sensitivity analyses and focus on basic parametric comparisons (\citet{Santos2000}, \citet{Fiori_2007} or \citet{Zahedi2010}).
@@
 Notably, this level of detail is crucial near the critical region of CO$_2$, where small deviations in process conditions can trigger large changes in solvent properties (such as density and solubility).
-This approach thus provides a systematic and quantitative measure of the system’s sensitivity to parameter fluctuations across different extraction regimes, from kinetic- to diffusion-controlled.}
+This approach thus provides a systematic and quantitative measure of the system’s sensitivity to parameter fluctuations across different extraction regimes, from kinetic- to diffusion-controlled.
 
@@
 
-	where  ${\color{black}\Upsilon}$ describes the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term:
+	where  $\Upsilon$ describes the curvature of the decay function. Equation \ref{Model_kinetic} describes the final form of the kinetic term:
 
@@
 		\begin{equation} \label{EQ:Enthalpy_equation}
-			\cfrac{\partial \left(\rho_f {\color{black}h} A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f {\color{black}h} A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
+			\cfrac{\partial \left(\rho_f h A_f\right)}{\partial t} = - \cfrac{\partial \left( \rho_f h A_f v \right)}{\partial z} + \cfrac{\partial \left(P A_f\right)}{\partial t} + \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right)
 		\end{equation}
@@
 		\begin{equation}
-			{\color{black}h}-{\color{black}h}^{id}={\color{black}R}T \left[{\color{black}T_r}({\color{black}Z}-1) -2.078(1+{\color{black}\kappa} ){\sqrt { {\color{black}\alpha}\left(T\right) } } \ln \left(\cfrac{{\color{black}Z}+\left( 1+\sqrt{2} \right){\color{black}B}}{{\color{black}Z}+\left( 1-\sqrt{2} \right){\color{black}B}}\right)\right],
+			h-h^{id}=RT \left[T_r(Z-1) -2.078(1+\kappa ){\sqrt { \alpha\left(T\right) } } \ln \left(\cfrac{Z+\left( 1+\sqrt{2} \right)B}{Z+\left( 1-\sqrt{2} \right)B}\right)\right]
 			\label{EQ:Enthalpy_PR}
@@
 
-	{\color{blue}As explained in Section \ref{CH:Governing_equations_chapter}, the pressure in the low-velocity region remains nearly constant due to the small pressure wave propagation occurring at the speed of sound.
+	As explained in Section \ref{CH:Governing_equations_chapter}, the pressure in the low-velocity region remains nearly constant due to the small pressure wave propagation occurring at the speed of sound.
 Under such conditions, the term $\partial P/\partial t$ can be approximated by a forward difference equation, describing the pressure change over a small time step $\Delta t$.
-The pressure $P$ in the system is treated as a state variable, while the incoming pressure at the new time-step $P_{in}$ is treated as a control:}
+The pressure $P$ in the system is treated as a state variable, while the incoming pressure at the new time-step $P_{in}$ is treated as a control:
 
@@
 		\begin{equation}
-			\frac{\partial {\color{black}P}}{\partial t} \approx \frac{{\color{black}P_{in}} - {\color{black}P} }{\Delta t}
+			\frac{\partial P}{\partial t} \approx \frac{P_{in} - P }{\Delta t}
 	\end{equation}}
 
-	{\color{blue}Such a simplified equation allows for instantaneous pressure.
-In a real system, the pressure dynamics would depend on the behaviour of the pump and the back-pressure regulator, which introduce additional inertia and resistance to pressure changes, leading to pressure gradual build-up.}
+	Such a simplified equation allows for instantaneous pressure.
+In a real system, the pressure dynamics would depend on the behaviour of the pump and the back-pressure regulator, which introduce additional inertia and resistance to pressure changes, leading to pressure gradual build-up.
 
@@
 equally distributed points in the $z$ direction.
-The state-space model after discretization is denoted by $x$ and defined as follows the Figure \ref{fig:discretization}, where ${\color{black}x} \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.
+The state-space model after discretization is denoted by $x$ and defined as follows the Figure \ref{fig:discretization}, where $x \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.
 
@@
 
-	{\color{blue}The sensitivity matrix $S(x;\Theta)$ represents how the state vector $x$ changes in response to variations in the model parameters $\Theta$.
-In physical terms, this means it measures how sensitive the system is to changes in the underlying parameters that define its behavior.} The new system of equations can be obtained by taking the total derivative of $S$ with respect to time $t$:
+	The sensitivity matrix $S(x;\Theta)$ represents how the state vector $x$ changes in response to variations in the model parameters $\Theta$.
+In physical terms, this means it measures how sensitive the system is to changes in the underlying parameters that define its behavior.
+The new system of equations can be obtained by taking the total derivative of $S$ with respect to time $t$:
 
@@
 
-	{\color{blue}This equation describes how the sensitivity of the system evolves over time.
-It shows that the time derivative of the sensitivity matrix depends on how the system dynamics (represented by $G(x; \Theta)$ change with respect to the parameters.} Sensitivity Equation \ref{SA_eq_full} can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}:
+	This equation describes how the sensitivity of the system evolves over time.
+It shows that the time derivative of the sensitivity matrix depends on how the system dynamics (represented by $G(x; \Theta)$ change with respect to the parameters.
+Sensitivity Equation \ref{SA_eq_full} can be obtained by applying the definition of the total derivative to Equation \ref{SA_dt}:
 
@@
 
-	{\color{blue}This equation decomposes the total effect of parameter changes on the system dynamics into two parts.
+	This equation decomposes the total effect of parameter changes on the system dynamics into two parts.
 The indirect effect represented by the term involving $\bar{J}_x (x; \Theta)$ This term shows how changes in the parameters influence the system through their effect on the state variables.
 This is an indirect feedback effect where parameter changes alter the state, which in turn affects the system response.
-The direct effect given by $\bar{J}_x (x; \Theta)$ reflects the immediate sensitivity of the system to parameter variations.}
+The direct effect given by $\bar{J}_x (x; \Theta)$ reflects the immediate sensitivity of the system to parameter variations.
 
@@
 The Jacobian ${\bar{J}_x}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_x$, where each equation ${\bar{J}_x}(n_x,n_x)$ is the derivative of $G_{n_x}(x;\Theta)$ with respect to the state variable $x_{n_\Theta}$.
-{\color{blue}This is the Jacobian matrix with respect to the state vector, which measures how the system’s dynamics change with changes in the state itself.}
+This is the Jacobian matrix with respect to the state vector, which measures how the system’s dynamics change with changes in the state itself.
 
@@
 	The sensitivity matrix $\bar{S}(x;\Theta)$ represents the matrix of equations of size $N_x \times N_\Theta$, where each entry $\bar{S}(n_x,n_\Theta)$ is the derivative of state variable $x_{n_x}$ with respect to parameter $\Theta_{n_\Theta}$.
-{\color{blue}The sensitivity matrix $\bar{S}(x;\Theta)$ measures how the state variables respond to parameter changes.}
+The sensitivity matrix $\bar{S}(x;\Theta)$ measures how the state variables respond to parameter changes.
 
@@
 
-	{\color{blue}}
-
 	The augmented system containing the original set of equations $G(x;\Theta)$ and sensitivity equations is called ${\textbf{G}}\left(x;\Theta\right)$.
@@
 
-	{\color{blue}The augmented system combines both the state equations and sensitivity equations into a unified system.
-This allows the simultaneous computation of both the system behavior and its sensitivity to parameter changes.}
+	The augmented system combines both the state equations and sensitivity equations into a unified system.
+This allows the simultaneous computation of both the system behavior and its sensitivity to parameter changes.
 
@@
 
-	{\color{blue} The sensitivity starts at zero because the system initially has no variation with respect to the parameters.}
+	The sensitivity starts at zero because the system initially has no variation with respect to the parameters.
 
@@
 	\section{Results} \label{CH: Results}
+
 	Details of the process model and its parameters can be found in \citet{Sliczniuk2024}.
@@
 
-	{\color{blue}The $\Upsilon$ term characterizes the curvature of the decay function $\gamma$ and can be associated with the uneven distribution of solute within solid particles.
+	The $\Upsilon$ term characterizes the curvature of the decay function $\gamma$ and can be associated with the uneven distribution of solute within solid particles.
 Because the zeroth-order term ($\Upsilon(0)$) corresponds to an intercept rather than depending on independent variables, its physical interpretation is straightforward.
@@
 This means that after the system has settled, variations in that parameter do not affect the final output.
-In terms of SFE, it means that all the solute has been removed from the system.}
+In terms of SFE, it means that all the solute has been removed from the system.
 
@@
 The results of the local sensitivity analysis are model specific and consider only a small region of parameter space, so the conclusions derived from such an analysis are limited to local conditions.
-Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses specifically on the effect of parameters of the empirical correlation and operating conditions on the state-space.
-
-	{\color{blue}The motivation for performing sensitivity analysis is to validate the model and evaluate how parameter variations affect its outputs By analysis the influence of parameters, potential modelling errors and unfeasible behaviours can be identified.
-This is particularly useful technique, when introducing an empirical correlation.
-In this work, the influence of the selected parameter from the empirical correlation for $\Upsilon$ was assessed.
-As expected, the analysis showed that increment of $\Upsilon(0)$ slows down the extraction rate, leading to negative values of $\frac{dc_s}{d\Upsilon(0)}$ and $\frac{dy}{d\Upsilon(0)}$, and alternating values of $\frac{dc_f}{d\Upsilon(0)}$.
+Although local sensitivity analysis can be performed with respect to any model parameter, this study focuses on the selected parameters of the empirical correlation and operating conditions.
+
+	The motivation for performing a sensitivity analysis is to validate the model, evaluate how parameter variations affect its outputs, and identify potential modelling errors or unfeasible behaviours.
+This work assessed the influence of the selected parameter from the empirical correlation for $\Upsilon$.
+The analysis showed that increment of $\Upsilon(0)$ slows down the extraction rate, leading to negative values of $\frac{dc_s}{d\Upsilon(0)}$ and $\frac{dy}{d\Upsilon(0)}$, and alternating values of $\frac{dc_f}{d\Upsilon(0)}$.
 These findings align with the physical interpretation of $\Upsilon(0)$.
-The effect of the parameter change can be summarized by extreme and final values of the normalized sensitivity of the output (0.47 and 0, respectively).}
+The effect of the parameter change can be summarised by extreme and final values of the normalised sensitivity of the output (0.47 and 0, respectively).
 
@@
 As a result, the extraction yield is improved and characterized by positive sensitivities.
-To compare the influence of various pressures, normalized sensitiviy coefficients were used, showing values between -$0.17$ and $0.6$.
+To compare the influence of various pressures, normalized sensitivity coefficients were used, showing values between -$0.17$ and $0.6$.
 The overall effect of each parameter was assessed by integrating the yield sensitivity curves over extended simulation time (until all sensitivities approached zero).
-Table \ref{table:Cumulative_integral} presents the resulting cumulative integrals as well as initial and max values of the normalized sensitivity coefficients.
-The positive sign of the cumulative integrals confirm that increasing pressure improve the extraction yield under all investigated conditions.
-The relative magnitudes of these integrals indicate at which operating conditions are most affected by pressure variations are the most influential.
+Table \ref{table:Cumulative_integral} presents initial, maximum and cumulative values of the integral of the normalised sensitivity coefficients.
+The cumulative integrals' positive sign confirms that increasing pressure improves the extraction yield under all investigated conditions.
+The relative magnitudes of these integrals can be used to identify the operating conditions where pressure variations are the most influential.
+Table \ref{table:Cumulative_integral} also shows that the system response change depending on the physical properties of CO$_2$ and the flow regime.
 
@@
 
-	{\color{blue}The findings of this work are particularly valuable for industrial-scale supercritical extraction processes, where achieving both operational efficiency and product quality can be challenging.
+	The findings of this work are particularly valuable for industrial-scale supercritical extraction processes, where achieving both operational efficiency and product quality can be challenging.
 The local sensitivity analysis demonstrates that even small adjustments in operating parameters can yield disproportionately large effects on extraction rates, especially near the fluid’s critical point.
@@
 Rather than relying heavily on trial-and-error or resource-intensive pilot studies, the model-based approach can be used to pre-identify the region of interests.
-This approach reduces both the time and material costs needed to reach profitable extraction rates, moving industrial operations toward cost-effective production.}
+This approach reduces both the time and material costs needed to reach profitable extraction rates, moving industrial operations toward cost-effective production.
 
@@
 	%% Loading bibliography style file
-	%\clearpage
-	\newpage
+	\clearpage
+	%\newpage
 	%\bibliographystyle{model1-num-names}
@@
 
-	\clearpage
+	%\clearpage
 

### 2025-06-07 CJCE-24-1047.R2.tex
07.06

--- 2025-05-21 Article_Sensitivity_Analsysis-Chamomile.tex
@@
 	% ===================================================
-	\title[mode=title]{Local Sensitivity Analysis of a Supercritical Extraction Model}                      
-	\shorttitle{Sensitivity Analysis}
+	\title[mode=title]{Local sensitivity analysis of a supercritical extraction model}                      
+	\shorttitle{Sensitivity analysis}
 
@@
 	\begin{keywords}
-		Supercritical extraction \sep Sensitivity analysis \sep Mathematical modelling
+		supercritical extraction \sep sensitivity analysis \sep mathematical modelling
 	\end{keywords}
@@
 
-	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993} or \citet{Sovova1994}.
+	One of the most popular applications of supercritical CO$_2$ is the extraction of essential oils, as described by many researchers, for example, by \citet{Sodeifian2017}, \citet{Reverchon1993}, or \citet{Sovova1994}.
 Traditional methods, such as distillation and organic solvent extraction, are commonly employed but have drawbacks.
@@
 This limitation has increased the popularity of alternative techniques, such as supercritical fluid extraction.
-Supercritical CO$_2$ is appealing due to its distinctive properties: it is inflammable, non-toxic and non-corrosive.
+Supercritical CO$_2$ is appealing due to its distinctive properties: it is inflammable, non-toxic, and non-corrosive.
 Supercritical fluids can exhibit both gas- and liquid-like properties, allowing for adjustable dissolving power through changes in operating conditions.
 
-	The applications of supercritical carbon dioxide are not limited only to an extraction process but can also be used for impregnation, as described by \citet{Weidner2018} or \citet{Machado2022}.
-Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
+	The applications of supercritical carbon dioxide are not limited only to an extraction process but can also be used for impregnation, as described by \citet{Weidner2018} and \citet{Machado2022} Impregnation is defined as modifying the properties of bulk substances by physically or chemically binding/adsorbing impregnates to a bulk material or surface, such as the hydrophobization of surfaces.
 The main advantage of using supercritical CO$_2$ is that, after depressurization, it desorbs from the surface and evaporates, leaving a solvent-free product.
 On the other hand, the main disadvantage of using carbon dioxide for impregnation is the low solubility of many drugs of interest.
-	The study of \citet{Ameri2020} investigates the loading of lansoprazole into polymers using supercritical carbon dioxide and examines how various parameters, such as temperature, pressure, and time, affect the drug loading efficiency.
+	The study by \citet{Ameri2020} investigates the loading of lansoprazole into polymers using supercritical carbon dioxide and examines how various parameters, such as temperature, pressure, and time, affect the drug loading efficiency.
 The results indicate that increasing any of these parameters enhances drug loading, with temperature having the most significant impact.
 \citet{Fathi2022} explored the use of supercritical carbon dioxide to enhance the bioavailability of ketoconazole by impregnating it into water-soluble polymers, specifically polyvinylpyrrolidone and hydroxypropyl methylcellulose.
-Utilizing a Box-Behnken design, the researchers optimized the impregnation process by varying pressure, temperature, and time, achieving increase in drug loadings ranging.
-
-	Another application of supercritical CO$_2$ is nanoparticle formation, as investigated by \citet{Padrela2018}, \citet{Franco2021} or \citet{Sodeifian2022}.
-Supercritical carbon-dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating the operating conditions.
+Utilizing a Box--Behnken design, the researchers optimized the impregnation process by varying pressure, temperature, and time, achieving increase in drug loadings ranging.
+
+	Another application of supercritical CO$_2$ is nanoparticle formation, as investigated by \citet{Padrela2018}, \citet{Franco2021}, and \citet{Sodeifian2022} Supercritical carbon dioxide-assisted technologies enable the production of different morphologies of different sizes, including nanoparticles and nanocrystals, by modulating the operating conditions.
 Supercritical fluid-based processes have advantages over techniques conventionally employed to produce nanosized particles or crystals, such as reduced use of toxic solvents.
@@
 The researchers employed the gas antisolvent technique to achieve nano-sized particles of the pigment.
-	\citet{Sodeifian2019} analysed the production of amiodarone hydrochloride nanoparticles using an ultrasonic-assisted rapid expansion of supercritical solution into a liquid solvent method.
+	\citet{Sodeifian2019} analyzed the production of amiodarone hydrochloride nanoparticles using an ultrasonic-assisted rapid expansion of supercritical solution into a liquid solvent method.
 By optimizing parameters such as pressure, temperature, and polymeric stabilizer concentration, the researchers achieved significant particle size reduction.
@@
 	This study investigates the extraction of essential oil from chamomile flowers (Matricaria chamomilla L.) via supercritical fluid extraction techniques and the modelling of this process.
-Chamomile is a medicinal herb widely cultivated in southern and eastern Europe — in countries such as Germany, Hungary, France and Russia.
-It can also be found outside Europe, for instance in Brazil, as discussed by \citet{Singh2011}.
-This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets.
+Chamomile is a medicinal herb widely cultivated in southern and eastern Europe---in countries such as Germany, Hungary, France and Russia.
+It can also be found outside Europe, for instance in Brazil, as discussed by \citet{Singh2011} This plant is distinguished by its hollow, bright gold cones, housing disc or tubular florets and surrounded by about fifteen white ray or ligulate florets.
 Chamomile has been used for its medicinal benefits, serving as an anti-inflammatory, antioxidant, mild astringent, and healing remedy.
@@
 
-	Depending on the needs one of two approaches can be considered while developing a mathematical model for the extraction process.
-A model, which is based on a multiple regression can be used if the relation between inputs and outputs is the only of interests.
-\citet{Sodeifian2017a} investigated an influence of pressure, temperature and particle size on the extraction efficiency of oil from dracocephalum kotschyi boiss seed.
+	Depending on the needs, one of two approaches can be considered while developing a mathematical model for the extraction process.
+A model which is based on a multiple regression can be used if the relation between inputs and outputs is the only one of interest.
+\citet{Sodeifian2017a} investigated the influence of pressure, temperature, and particle size on the extraction efficiency of oil from dracocephalum kotschyi boiss seed.
 The second order polynomial model was applied to obtain the corresponding response surface and to identify the optimum operating conditions.
@@
 
-	Alternatively, a first principle model can be derived and applied to cover not only the input-output relations, but the phenomena occurring in the system.
+	Alternatively, a first principle model can be derived and applied to cover not only the input--output relations, but the phenomena occurring in the system.
 This approach allows for more detailed representation the system behaviour, but requires deeper understanding of the underlying physics and more rigorous experiments.
@@
 The process involves a supercritical solvent being pumped through a fixed bed of finely chopped biomass to extract the solute, followed by separation of the solvent and solute in a flush drum to collect the extract.
-Parameters such as pressure ($P$), feed flow rate ($F$) and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
+Parameters such as pressure ($P$), feed flow rate ($F$), and inlet temperature ($T_{in}$) are adjustable and measurable, while the outlet temperature ($T_{out}$) and the amount of product at the outlet can only be monitored.
 Figure \ref{fig: SFE_drawing} presents a simplified process flow diagram.
@@
 
-	The primary aim of this study is to analyse the influence of changes in operating conditions on the process model developed by \citet{Sliczniuk2024}.
+	The primary aim of this study is to analyze the influence of changes in operating conditions on the process model developed by \citet{Sliczniuk2024}.
 Understanding how variations in parameters and control variables affect the model's behaviour is essential for improving its accuracy, robustness, and practical applicability.
@@
 
-	Different supercritical extraction models have been analysed using various sensitivity analysis techniques in the literature.
-For instance, \citet{Fiori_2007} performed sensitivity calculations by varying parameters within their confidence intervals and observing the changes in model results.
+	Different supercritical extraction models have been analyzed using various sensitivity analysis techniques in the literature.
+For instance, \citet{Fiori2007} performed sensitivity calculations by varying parameters within their confidence intervals and observing the changes in model results.
 Their analysis revealed that the particle diameter and internal mass transfer coefficient significantly influence extraction during the diffusion-control regime.
@@
 	\citet{Santos2000} considered the model of \citet{Sovova1994} for semi-continuous isothermal and isobaric extraction processes using carbon dioxide as a solvent.
-They conducted a parametric sensitivity analysis using a two-level factorial design, disturbing model parameters by 10\% and analysing their main effects.
-They proposed strategies for high-performance operation based on sensitivities related to superficial velocity, particle diameter, initial solute concentration in the solid phase and solute concentration in the fluid phase at the extractor inlet.
+They conducted a parametric sensitivity analysis using a two-level factorial design, disturbing model parameters by 10\% and analyzing their main effects.
+They proposed strategies for high-performance operation based on sensitivities related to superficial velocity, particle diameter, initial solute concentration in the solid phase, and solute concentration in the fluid phase at the extractor inlet.
 
@@
 
-	In a his work, \citet{Turanyi1990} presented a comprehensive review of sensitivity analysis methods for spatially homogeneous, constant-parameter chemical kinetic systems.
+	In another work, \citet{Turanyi1990} presented a comprehensive review of sensitivity analysis methods for spatially homogeneous, constant-parameter chemical kinetic systems.
 This study explored a range of sensitivity analysis techniques, including concentration sensitivity, rate sensitivity, and feature sensitivity analysis.
-Practical applications of these methods in chemical kinetics were highlighted, showcasing their utility in understanding and predicting system behavior.
+Practical applications of these methods in chemical kinetics were highlighted, showcasing their utility in understanding and predicting system behaviour.
 
@@
 
-	In their comprehensive review, \citet{Saltelli2005} examined sensitivity analysis methods applicable to chemical reaction modeling.
+	In their comprehensive review, \citet{Saltelli2005} examined sensitivity analysis methods applicable to chemical reaction modelling.
 They discussed both local and global techniques, emphasizing the role of global sensitivity analysis in understanding complex chemical systems.
@@
 	A key novelty of this work lies in its rigorous application of derivative-based local sensitivity analysis to a first-principles model of supercritical fluid extraction.
-While multiple publications available in the literature discuss application of sensitivity analysis on a supercritical extraction model, many of these either omit local sensitivity analyses and focus on basic parametric comparisons (\citet{Santos2000}, \citet{Fiori_2007} or \citet{Zahedi2010}).
+While multiple publications available in the literature discuss application of sensitivity analysis on a supercritical extraction model, many of these either omit local sensitivity analyses and focus on basic parametric comparisons (\citet{Santos2000}, \citet{Fiori_2007}, or \citet{Zahedi2010}).
 In contrast, the present approach integrates a quasi-1D partial-differential-equation model with automatic differentiation of the mass and energy balances, enabling a detailed exploration of how infinitesimal changes in parameters, which propagates propagate through the system.
@@
 
-	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1} - \ref{EQ: CompressibleEuler_3}:
+	The set of quasi-one-dimensional governing equations in Cartesian coordinates is described by Equations \ref{EQ: CompressibleEuler_1}--\ref{EQ: CompressibleEuler_3}:
 
@@
 
-	where $\rho_f$ is the density of the fluid, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time and $z$ is the spatial direction.
+	where $\rho_f$ is the density of the fluid, $A_f$ is the function which describes a change in the cross-section, $v$ is the velocity, $P$ is the total pressure, $e$ is the internal energy of the fluid, $t$ is time, and $z$ is the spatial direction.
 
@@
 
-	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as
+	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as follows:
 
@@
 
-	To simplify the system dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$ and $\rho_f$:
+	To simplify the system dynamics, it is assumed that $F$ is a control variable and affects the whole system instantaneously (due to $\nabla \cdot u = 0$), which allows finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$:
 
@@
 
-	The fluid density $\rho_f$ can be obtained from the Peng-Robinson equation of state if the temperature and thermodynamic pressure are known along $z$.
+	The fluid density $\rho_f$ can be obtained from the Peng--Robinson equation of state if the temperature and thermodynamic pressure are known along $z$.
 Variation in fluid density may occur due to pressure or inlet temperature changes.
@@
 
-	As the solvent flows through the fixed bed, CO$_2$ molecules diffuse into the pores, adsorb on the inner surface and form a film due to solvent-solid matrix interactions.
-The dissolved solute diffuses into the bulk from the particle's core through the solid-fluid interface, the pore and the film.
-Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted by $c_s$, and the equilibrium concentrations at the solid-fluid interface are denoted by $c_s^*$ and $c_p^*$ for the solid and fluid phases, respectively.
+	As the solvent flows through the fixed bed, CO$_2$ molecules diffuse into the pores, adsorb on the inner surface, and form a film due to solvent--solid matrix interactions.
+The dissolved solute diffuses into the bulk from the particle's core through the solid--fluid interface, the pore and the film.
+Figure \ref{fig: SFE_Mechanism} shows the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted by $c_s$, and the equilibrium concentrations at the solid--fluid interface are denoted by $c_s^*$ and $c_p^*$ for the solid and fluid phases, respectively.
 The concentration of the solutes in the fluid phase in the centre of the pore is denoted by $c_p$.
@@
 
-	where $\mu$ is sphericity, $l$ a characteristic dimension of particles that can be defined as $l = r/3$, $r$ is the mean particle radius, $\rho_s$ is the solid density, $D_i$ corresponds to the overall diffusion coefficient and $c_P^*$ is the concentration at the solid-fluid interface (which, according to the internal resistance model, is supposed to be at equilibrium with the fluid phase).
+	where $\mu$ is sphericity, $l$ a characteristic dimension of particles that can be defined as $l = r/3$, $r$ is the mean particle radius, $\rho_s$ is the solid density, $D_i$ corresponds to the overall diffusion coefficient, and $c_P^*$ is the concentration at the solid--fluid interface (which, according to the internal resistance model, is supposed to be at equilibrium with the fluid phase).
 
@@
 
-	The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase.
-\citet{Spiro2007} propose defining the mass partition coefficient $k_m$ as
+	The volumetric partition coefficient $k_p$ acts as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid--fluid interphase.
+\citet{Spiro2007} propose defining the mass partition coefficient $k_m$ as follows:
 
@@
 
-	According to \citet{Reverchon1996}, the kinetic term becomes
+	According to \citet{Reverchon1996}, the kinetic term becomes the following:
 
@@
 	The choice between the two formulations should consider the system's properties and the underlying mass transfer assumptions.
-In systems where external mass transfer dominates, the resistance to solute transport primarily occurs at the fluid-solid interface, typically governed by the diffusion of solute across the fluid boundary layer.
+In systems where external mass transfer dominates, the resistance to solute transport primarily occurs at the fluid--solid interface, typically governed by the diffusion of solute across the fluid boundary layer.
 Under these conditions, the Bulley formulation is more appropriate, as it explicitly emphasizes the fluid-phase concentration ($c_f$) as the driving force for mass transfer through the term $c_f - c_p^*(c_s)$.
@@
 
-	Following the idea of the broken-and-intact cell (BIC) model (\citet{Sovova2017}), the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}:
+	Following the idea of the broken-and-intact cell (BIC) model of \citet{Sovova2017}, the internal diffusion coefficient $D_i$ is considered to be a product of the reference value of $D_i^R$ and the exponential decay function $\gamma$, as given by Equation \ref{EQ: C_sat_function}:
 
@@
 
-	The empirical correlations for $D_i$ and $\Upsilon$ were derived by \citet{Sliczniuk2024} and validated for temperatures of $30 - 40~^\circ C$, pressures of $100 - 200$ bar, and mass flow rates of $3.33-6.67 \cdot 10^{-5}$ kg/s.
+	The empirical correlations for $D_i$ and $\Upsilon$ were derived by \citet{Sliczniuk2024} and validated for temperatures of $30 - 40^\circ C$, pressures of $100 - 200$ bar, and mass flow rates of $3.33-6.67 \cdot 10^{-5}$ kg/s.
 Figures \ref{fig:Correlation_Di} and \ref{fig:Correlation_Gamma} show the results of multiple linear regression applied to solutions of parameter estimation and selected independent variables.
@@
 	If the value of enthalpy $h$ is known from the time evolution of the energy equation, and pressure $P$ is known from measurement, then temperature $T$ can be reconstructed based on the departure function.
-The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy or internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
-The enthalpy departure function, as presented by \citet{Gmehling2019} for the Peng-Robinson equation of state,  is defined by Equation \ref{EQ:Enthalpy_PR}:
+The departure function is a mathematical function that characterizes the deviation of a thermodynamic property (enthalpy, entropy, or internal energy) of a real substance from that of an ideal gas at the same temperature and pressure.
+The enthalpy departure function, as presented by \citet{Gmehling2019} for the Peng--Robinson equation of state,  is defined by Equation \ref{EQ:Enthalpy_PR}:
 
@@
 
-	where $\alpha$ is defined as $\left( 1+\kappa \left( 1 - \sqrt{T_r} \right) \right)^2$, $T_r$ is the reduced temperature, $P_r$ is the reduced pressure, $Z$ is the compressibility factor, $\kappa$ is a quadratic function of the acentric factor and $B$ is calculated as $0.07780\frac{P_r}{T_r}$.
+	where $\alpha$ is defined as $\left( 1+\kappa \left( 1 - \sqrt{T_r} \right) \right)^2$, $T_r$ is the reduced temperature, $P_r$ is the reduced pressure, $Z$ is the compressibility factor, $\kappa$ is a quadratic function of the acentric factor, and $B$ is calculated as $0.07780\frac{P_r}{T_r}$.
 
@@
 The backward finite difference is used to approximate the first-order derivative, while the central difference scheme approximates the second-order derivative $z$ direction.
-The length of the fixed bed is divided into $N_z$, i.e.
-equally distributed points in the $z$ direction.
+The length of the fixed bed is divided into $N_z$, that is, equally distributed points in the $z$ direction.
 The state-space model after discretization is denoted by $x$ and defined as follows the Figure \ref{fig:discretization}, where $x \in \mathbb{R}^{N_x = 3N_z+2} $ and $\Theta \in \mathbb{R}^{N_\Theta =  N_{\theta} + N_u } $, $N_{\theta}$ is the number of parameters and $N_{u}$ is the number of control variables.
@@
 	The sensitivity matrix $S(x;\Theta)$ represents how the state vector $x$ changes in response to variations in the model parameters $\Theta$.
-In physical terms, this means it measures how sensitive the system is to changes in the underlying parameters that define its behavior.
+In physical terms, this means it measures how sensitive the system is to changes in the underlying parameters that define its behaviour.
 The new system of equations can be obtained by taking the total derivative of $S$ with respect to time $t$:
@@
 	This equation decomposes the total effect of parameter changes on the system dynamics into two parts.
-The indirect effect represented by the term involving $\bar{J}_x (x; \Theta)$ This term shows how changes in the parameters influence the system through their effect on the state variables.
+The indirect effect is represented by the term involving $\bar{J}_x (x; \Theta)$.
+This term shows how changes in the parameters influence the system through their effect on the state variables.
 This is an indirect feedback effect where parameter changes alter the state, which in turn affects the system response.
@@
 	The augmented system combines both the state equations and sensitivity equations into a unified system.
-This allows the simultaneous computation of both the system behavior and its sensitivity to parameter changes.
-
-	The initial conditions are described as
+This allows the simultaneous computation of both the system behaviour and its sensitivity to parameter changes.
+
+	The initial conditions are described as follows:
 
@@
 
-	Details of the process model and its parameters can be found in \citet{Sliczniuk2024}.
+	Details of the process model and its parameters can be found in the work of \citet{Sliczniuk2024}.
 The model was validated under the following operating conditions: temperatures from $30$ to $40 ^\circ C$, pressures from $100$ to $200$ bar, and mass flow rates from $3.33$ to $6.67 \cdot 10^{-5}$ kg/s.
@@
 The second case examines the effect of operating conditions, particularly pressure, on the state space and model outputs.
-For the first analysis, the midpoint of the validated range ($35 ^\circ C$, $150$ bar and $5\cdot 10^{-5}$) was selected.
+For the first analysis, the midpoint of the validated range ($35 ^\circ C$, $150$ bar, and $5\cdot 10^{-5}$) was selected.
 The second analysis is carried out in two steps.
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_gamma.png}
-		\caption{The effect of $\Upsilon(0)$ change on $c_s$}
+		\caption{The effect of $\Upsilon(0)$ change on $c_s$.}
 		\label{fig:Sensitivty_Gamma_CS}
@@
 
-	Figure \ref{fig:Sensitivty_Gamma_CS} illustrates the sensitivity of the solute concentration in the solid phase to change into zero'th order term in the equation for $\Upsilon$.
+	Figure \ref{fig:Sensitivty_Gamma_CS} illustrates the sensitivity of the solute concentration in the solid phase to change into zeroth order term in the equation for $\Upsilon$.
 As discussed by \citet{Sliczniuk2024}, the system is far from the saturation point, which indicates that the concentration gradient is controlled mainly by $c_s$.
-Consequently, the extraction kinetic term act as independent on $c_f$, which explain a uniform response in solid phase visible in Figure \ref{fig:Sensitivty_Gamma_CS}.
+Consequently, the extraction kinetic term acts as independent on $c_f$, which explains a uniform response in solid phase visible in Figure \ref{fig:Sensitivty_Gamma_CS}.
 The positive value of $\frac{dc_s}{d\Upsilon(0)}$ can be interpreted as a slower loss of the solute from particles and is observed when the extraction slows down.
-Because of the lower reaction rate, more solute remains in the particles initially, however, as time approaches infinity, the solute eventually diffuses out of the solid matrix.
-Consequently, it is expected to observed $\frac{dc_s}{d\Upsilon(0)}$ reaching a maximum and asymptotically diminish to zero.
+Because of the lower reaction rate, more solute remains in the particles initially; however, as time approaches infinity, the solute eventually diffuses out of the solid matrix.
+Consequently, it is expected to observ $\frac{dc_s}{d\Upsilon(0)}$ reaching a maximum and asymptotically diminish to zero.
 
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_gamma.png}
-		\caption{The effect of $\Upsilon(0)$ change on $c_f$}
+		\caption{The effect of $\Upsilon(0)$ change on $c_f$.}
 		\label{fig:Sensitivty_Gamma_CF}
@@
 
-	Figure \ref{fig:Sensitivty_Gamma_CF} illustrates the sensitivity of the solute concentration in the fluid phase with respect to change into zero'th order term in the equation for $\Upsilon$.
+	Figure \ref{fig:Sensitivty_Gamma_CF} illustrates the sensitivity of the solute concentration in the fluid phase with respect to change into zeroth order term in the equation for $\Upsilon$.
 As previously discussed, the extraction rate slowed down due to increase of $\Upsilon(0)$ uniformly along the spatial domain.
@@
 The spatial distribution of $\frac{dc_f}{d\Upsilon(0)}$ in the figure is non-uniform, reflecting the effects of advection.
-Due to mass conservation, the remaining solute reach the solid-fluid interface  more slowly hence it is expected to observe a little positive values of $\frac{dc_f}{d\Upsilon(0)}$ in the later stage of extraction.
+Due to mass conservation, the remaining solute reach the solid--fluid interface  more slowly, hence it is expected to observe a little positive values of $\frac{dc_f}{d\Upsilon(0)}$ in the later stage of extraction.
 Eventually it is expected to see sensitivities reaching zero asymptotically.
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Y_gamma.png}
-		\caption{The effect of $\Upsilon(0)$ change on $c_f$}
+		\caption{The effect of $\Upsilon(0)$ change on $c_f$.}
 		\label{fig:Sensitivty_Gamma_Y}
@@
 	Figure \ref{fig:Sensitivty_Gamma_Y}  shows the normalized sensitivity of the yield with respect to $\Upsilon(0)$.
-Due to slower extraction rate, the sensitivity curve is characterized by negative sign.
+Due to the slower extraction rate, the sensitivity curve is characterized by negative sign.
 The  downward trend of the sensitivity curve can be interpreted as less solute coming out of the extractor if compared with the reference case.
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CS_P.png}
-		\caption{The effect of $P_{in}$ change on $c_s$}
+		\caption{The effect of $P_{in}$ change on $c_s$.}
 		\label{fig:Sensitivty_P_CS}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/CF_P.png}
-		\caption{The effect of $P_{in}$ change on $c_f$}
+		\caption{The effect of $P_{in}$ change on $c_f$.}
 		\label{fig:Sensitivty_P_CF}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield.png}
-		\caption{The effect of $P_{in}$ change on $y(t)$}
+		\caption{The effect of $P_{in}$ change on $y(t)$.}
 		\label{fig:Sensitivty_P_y}
@@
 		\includegraphics[trim = 0.0cm 0.0cm 0.0cm 0.0cm,clip,width=\columnwidth]{/Results_sensitivity/Yield_Multiple_normalized.png}
-		\caption{The effect of $P_{in}$ change on $y(t)$ after normalization}
+		\caption{The effect of $P_{in}$ change on $y(t)$ after normalization.}
 		\label{fig:Sensitivty_P_y_norm}
@@
 The pressure change impacts the system instantaneously and uniformly, leading to a rapid initial change in the normalized sensitivities.
-This behavior is analogous to a step change, where the system's response to the perturbation is immediate.
+This behaviour is analogous to a step change, where the system's response to the perturbation is immediate.
 Initially, the sensitivity curves remain flat.
@@
 
-	While this interpretation of normalized sensitivities is straightforward, it is important to note that extrapolating for large parameter changes can lead to inaccurate results.In dynamic systems, local sensitivity analysis quantifies how the system state or output varies over time in response to small parameter perturbations.
+	While this interpretation of normalized sensitivities is straightforward, it is important to note that extrapolating for large parameter changes can lead to inaccurate results.
+In dynamic systems, local sensitivity analysis quantifies how the system state or output varies over time in response to small parameter perturbations.
 If the perturbation is large, the derivative-based definition of sensitivity (or sensitivity equations) becomes invalid unless the system is linear.
@@
 The overall effect of each parameter was assessed by integrating the yield sensitivity curves over extended simulation time (until all sensitivities approached zero).
-Table \ref{table:Cumulative_integral} presents initial, maximum and cumulative values of the integral of the normalised sensitivity coefficients.
+Table \ref{table:Cumulative_integral} presents initial, maximum, and cumulative values of the integral of the normalized sensitivity coefficients.
 The cumulative integrals' positive sign confirms that increasing pressure improves the extraction yield under all investigated conditions.
@@
 		\end{tabular} }
-		\caption{Values of the cumulative integral of the yield sensitivity}
+		\caption{Values of the cumulative integral of the yield sensitivity.}
 		\label{table:Cumulative_integral}
@@
 
-	\nomenclature[A]{\(P\)}{Pressure \nomunit{bar}}
-	\nomenclature[A]{\(T\)}{Temperature \nomunit{K}}
-	\nomenclature[A]{\(T_{in}\)}{Inlet temperature \nomunit{K}}
-	\nomenclature[A]{\(T_{out}\)}{Outlet temperature \nomunit{K}}
-	\nomenclature[A]{\(F\)}{Mass flow rate \nomunit{kg/s}}
-	\nomenclature[A]{\(u\)}{Superficial velocity \nomunit{m/s}}
-	\nomenclature[A]{\(v\)}{Linear velocity \nomunit{m/s}}
-	\nomenclature[A]{\(z\)}{Spatial direction \nomunit{m}}
-	\nomenclature[A]{\(e\)}{Internal energy \nomunit{J/kg}}
-	\nomenclature[A]{\(h\)}{Enthalpy \nomunit{J}}
-	\nomenclature[A]{\(t\)}{Time \nomunit{s}}
-	\nomenclature[A]{\(t_f\)}{Total extraction time \nomunit{s}}
-	\nomenclature[A]{\(t_0\)}{Initial extraction time \nomunit{s}}
-	\nomenclature[A]{\(A\)}{Total cross-section of the bed \nomunit{m$^2$}}
-	\nomenclature[A]{\(A_f\)}{Cross-section of the bed occupied by the fluid \nomunit{m$^2$}}
-	\nomenclature[A]{\(c_f\)}{Concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
-	\nomenclature[A]{\(c_{f0}\)}{Initial concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
-	\nomenclature[A]{\(c_f^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
-	\nomenclature[A]{\(c_s\)}{Concentration of solute in the solid phase \nomunit{kg/m$^3$}}
-	\nomenclature[A]{\(c_{s0}\)}{Initial concentration of solute in the solid phase \nomunit{kg/m$^3$}}
-	\nomenclature[A]{\(c_s^*\)}{Concentration of solute at the solid-fluid interface \nomunit{kg$^3$}}
-	\nomenclature[A]{\(c_p\)}{Concentration of solute in the core of a pore \nomunit{kg/m$^3$}}
-	\nomenclature[A]{\(c_{pf}\)}{Concentration of solute at the pore opening \nomunit{kg/m$^3$}}
-	\nomenclature[A]{\(D_e^M\)}{Axial diffusion coefficient \nomunit{m$^2$/s}}
-	\nomenclature[A]{\(r_e\)}{Mass transfer kinetic term \nomunit{kg/m$^3$/s}}
-	\nomenclature[A]{\(L\)}{Length of the fixed bed \nomunit{m}}
-	\nomenclature[A]{\(S\)}{Sensitivity equations}
-	\nomenclature[A]{\(\textbf{G}\)}{Augmented system}
-	\nomenclature[A]{\(\dot{S}\)}{Time derivative of the sensitivity equations}
-	\nomenclature[A]{\(\bar{S}\)}{Sensitivity matrix}
+	\nomenclature[A]{\(P\)}{pressure \nomunit{bar}}
+	\nomenclature[A]{\(T\)}{temperature \nomunit{K}}
+	\nomenclature[A]{\(T_{in}\)}{inlet temperature \nomunit{K}}
+	\nomenclature[A]{\(T_{out}\)}{outlet temperature \nomunit{K}}
+	\nomenclature[A]{\(F\)}{mass flow rate \nomunit{kg/s}}
+	\nomenclature[A]{\(u\)}{superficial velocity \nomunit{m/s}}
+	\nomenclature[A]{\(v\)}{linear velocity \nomunit{m/s}}
+	\nomenclature[A]{\(z\)}{spatial direction \nomunit{m}}
+	\nomenclature[A]{\(e\)}{internal energy \nomunit{J/kg}}
+	\nomenclature[A]{\(h\)}{enthalpy \nomunit{J}}
+	\nomenclature[A]{\(t\)}{time \nomunit{s}}
+	\nomenclature[A]{\(t_f\)}{total extraction time \nomunit{s}}
+	\nomenclature[A]{\(t_0\)}{initial extraction time \nomunit{s}}
+	\nomenclature[A]{\(A\)}{total cross-section of the bed \nomunit{m$^2$}}
+	\nomenclature[A]{\(A_f\)}{cross-section of the bed occupied by the fluid \nomunit{m$^2$}}
+	\nomenclature[A]{\(c_f\)}{concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
+	\nomenclature[A]{\(c_{f0}\)}{initial concentration of solute in the fluid phase \nomunit{kg/m$^3$}}
+	\nomenclature[A]{\(c_f^*\)}{concentration of solute at the solid-fluid interface \nomunit{kg/m$^3$}}
+	\nomenclature[A]{\(c_s\)}{concentration of solute in the solid phase \nomunit{kg/m$^3$}}
+	\nomenclature[A]{\(c_{s0}\)}{initial concentration of solute in the solid phase \nomunit{kg/m$^3$}}
+	\nomenclature[A]{\(c_s^*\)}{concentration of solute at the solid-fluid interface \nomunit{kg$^3$}}
+	\nomenclature[A]{\(c_p\)}{concentration of solute in the core of a pore \nomunit{kg/m$^3$}}
+	\nomenclature[A]{\(c_{pf}\)}{concentration of solute at the pore opening \nomunit{kg/m$^3$}}
+	\nomenclature[A]{\(D_e^M\)}{axial diffusion coefficient \nomunit{m$^2$/s}}
+	\nomenclature[A]{\(r_e\)}{mass transfer kinetic term \nomunit{kg/m$^3$/s}}
+	\nomenclature[A]{\(L\)}{length of the fixed bed \nomunit{m}}
+	\nomenclature[A]{\(S\)}{sensitivity equations}
+	\nomenclature[A]{\(\textbf{G}\)}{augmented system}
+	\nomenclature[A]{\(\dot{S}\)}{time derivative of the sensitivity equations}
+	\nomenclature[A]{\(\bar{S}\)}{sensitivity matrix}
 	\nomenclature[A]{\(\bar{J}_x\)}{Jacobian matrix with respect to the state variables}
@@
 	%\nomenclature[A]{\(\mathcal{L}\)}{Log-likelihood function}
-	\nomenclature[A]{\(l\)}{Characteristic dimension of particles \nomunit{m}}
-	\nomenclature[A]{\(D_i\)}{Internal diffusion coefficient \nomunit{m$^2$/s}}
-	\nomenclature[A]{\(D_i^R\)}{Reference value of internal diffusion coefficient \nomunit{m$^2$/s}}
-	\nomenclature[A]{\(r\)}{Particle radius \nomunit{m}}
-	\nomenclature[A]{\(k_p\)}{Volumetric partition coefficient \nomunit{-}}
-	\nomenclature[A]{\(k_m\)}{Mass partition coefficient \nomunit{-}}
-	\nomenclature[A]{\(y\)}{Extraction yield \nomunit{g}}
+	\nomenclature[A]{\(l\)}{characteristic dimension of particles \nomunit{m}}
+	\nomenclature[A]{\(D_i\)}{internal diffusion coefficient \nomunit{m$^2$/s}}
+	\nomenclature[A]{\(D_i^R\)}{reference value of internal diffusion coefficient \nomunit{m$^2$/s}}
+	\nomenclature[A]{\(r\)}{particle radius \nomunit{m}}
+	\nomenclature[A]{\(k_p\)}{volumetric partition coefficient \nomunit{-}}
+	\nomenclature[A]{\(k_m\)}{mass partition coefficient \nomunit{-}}
+	\nomenclature[A]{\(y\)}{extraction yield \nomunit{g}}
 	%\nomenclature[A]{\(Y\)}{Yield measurement \nomunit{g}}
-	\nomenclature[A]{\(x\)}{State vector}
-	\nomenclature[A]{\(G\)}{Vector of discretized differential equations}
-	\nomenclature[A]{\(p\)}{Probability distribution model \nomunit{-}}
+	\nomenclature[A]{\(x\)}{state vector}
+	\nomenclature[A]{\(G\)}{vector of discretized differential equations}
+	\nomenclature[A]{\(p\)}{probability distribution model \nomunit{-}}
 	\nomenclature[A]{\(R_e\)}{Reynolds number \nomunit{-}}
 
-	\nomenclature[B]{\(\rho_f\)}{Fluid density \nomunit{kg/m$^3$}}
-	\nomenclature[B]{\(\Phi\)}{Bed porosity \nomunit{-}}
-	\nomenclature[B]{\(\rho_s\)}{Bulk density of the solid \nomunit{kg/m$^3$}}
-	\nomenclature[B]{\(\mu\)}{Sphericity coefficient \nomunit{-}}
-	\nomenclature[B]{\(\gamma\)}{Decay function \nomunit{-}}
-	\nomenclature[B]{\(\Upsilon\)}{Decay coefficient \nomunit{-}}
-	\nomenclature[B]{\(\Theta\)}{Parameter space}
-	\nomenclature[B]{\(\theta\)}{Vector of unknown parameters}
-	\nomenclature[B]{\(\epsilon\)}{Unobservable error \nomunit{g}}
-	\nomenclature[B]{\(\sigma\)}{Standard deviation \nomunit{g}}
-
-	\nomenclature[C]{BIC}{Broke-and-Intact Cell model}
+	\nomenclature[B]{\(\rho_f\)}{fluid density \nomunit{kg/m$^3$}}
+	\nomenclature[B]{\(\Phi\)}{bed porosity \nomunit{-}}
+	\nomenclature[B]{\(\rho_s\)}{bulk density of the solid \nomunit{kg/m$^3$}}
+	\nomenclature[B]{\(\mu\)}{sphericity coefficient \nomunit{-}}
+	\nomenclature[B]{\(\gamma\)}{decay function \nomunit{-}}
+	\nomenclature[B]{\(\Upsilon\)}{decay coefficient \nomunit{-}}
+	\nomenclature[B]{\(\Theta\)}{parameter space}
+	\nomenclature[B]{\(\theta\)}{vector of unknown parameters}
+	\nomenclature[B]{\(\epsilon\)}{unobservable error \nomunit{g}}
+	\nomenclature[B]{\(\sigma\)}{standard deviation \nomunit{g}}
+
+	\nomenclature[C]{BIC}{broken-and-intact cell model}
 	%\nomenclature[C]{MLE}{Maximum Likelihood Estimation}
-	\nomenclature[C]{SFE}{Supercritical Fluid Extraction}
-	\nomenclature[C]{HBD}{Hot Ball Diffusion}
-	\nomenclature[C]{SC}{Shrinking Core}
+	\nomenclature[C]{SFE}{supercritical fluid extraction}
+	\nomenclature[C]{HBD}{hot ball diffusion}
+	\nomenclature[C]{SC}{shrinking core}
 
